\documentclass[a4paper,fleqn]{cas-sc}

\input{00_preamble/preamble.tex}

\begin{document}
% TODO: are they necessary?:
% \let\WriteBookmarks\relax
% \def\floatpagepagefraction{1}
% \def\textpagefraction{.001}
% ----

%Short title (this will be shown on the top of every page.)
\shorttitle{Variational quantum eigensolver: review and best practices}

%Short author (this will be shown as footnote on every page.)
\shortauthors{\phantom{}} % A hack to get rid of the shortauthors.
%\shortauthors{Tilly \texit{et~al.}}

% Main title of the paper
\title[mode=title]{The Variational Quantum Eigensolver: a review of methods and best practices}
% Title footnote:
% ----

% ------------------------ Authors -----------------------------
% TODO: what's the meaning of type?
% TODO: everyone's ORCIDs.
\author[1,2]{Jules Tilly}[type=editor,
                        orcid=0000-0001-5034-474X]
\cortext[cor1]{Corresponding author}
\ead{jules.tilly.18@ucl.ac.uk}
\author[2,3]{Hongxiang Chen}[
    type=editor, orcid=0000-0001-6792-7394]
\author[2,4]{Shuxiang Cao}[
    type=editor, orcid=0000-0001-7178-4250]
\author[1,2]{Dario Picozzi}[orcid=0000-0002-6517-2458]
\author[5]{Kanav Setia}[orcid=0000-0003-2032-3993]
\author[6]{Ying Li}[orcid=0000-0002-1705-2494]
\author[2,3]{Edward Grant}[orcid=0000-0003-0657-1915]
\author[2,3]{Leonard Wossnig}[orcid=0000-0002-0861-9540]
\author[7]{Ivan Rungger}[type=editor,
                        orcid=0000-0002-9222-9317]
\author[8]{George H. Booth}[orcid=0000-0003-2503-4904]
\author[1]{Jonathan Tennyson}[orcid=0000-0002-4994-5238]


\address[1]{University College London, Department of Physics and Astronomy, WC1E 6BT London, United  Kingdom}
\address[2]{Odyssey Therapeutics, WC1X 8BB London,  United  Kingdom}
\address[3]{University College London, Department of Computer Science, WC1E 6BT London, United  Kingdom}
\address[4]{University of Oxford, Department of Physics, Clarendon Laboratory, OX1 3PU, United  Kingdom}
\address[5]{qBraid, 5235, Harper Court, Chicago, IL}
\address[6]{Graduate School of China Academy of Engineering Physics, Beijing 100193, China}
\address[7]{National Physical Laboratory, TW11 0LW Teddington, United Kingdom}
\address[8]{King's College London, Department of Physics, Strand, London, WC2R 2LS, United  Kingdom}
% --------------------------------------------------------------

% ------------------- Abstract ---------------------------------
\begin{abstract}
The variational quantum eigensolver (or VQE), first developed by Peruzzo \textit{et al.} (Nature Comm.5, 4213 (2014)), has received significant attention from the research community in recent years. It uses the variational principle to compute the ground state energy of a Hamiltonian, a problem that is central to quantum chemistry and condensed matter physics. Conventional computing methods are constrained in their accuracy due to the computational limits facing exact modeling of the exponentially growing electronic wavefunction for these many-electron systems. The VQE may be used to model these complex wavefunctions in polynomial time, making it one of the most promising near-term applications for quantum computing. One important advantage is that variational algorithms have been shown to present some degree of resilience to the noise in the quantum hardware. Finding a path to navigate the relevant literature has rapidly become an overwhelming task, with many methods promising to improve different parts of the algorithm, but without clear descriptions of how the diverse parts fit together. The potential practical advantages of the algorithm are also widely discussed in the literature, but with varying conclusions. Despite strong theoretical underpinnings suggesting excellent scaling of individual VQE components, studies have pointed out that their various pre-factors could be too large to reach a quantum computing advantage over conventional methods.

This review aims at disentangling the relevant literature to provide a comprehensive overview of the progress that has been made on the different parts of the algorithm, and to discuss future areas of research that are fundamental for the VQE to deliver on its promises. All the different components of the algorithm are reviewed in detail. These include the representation of Hamiltonians and wavefunctions on a quantum computer, the optimization process to find ground state energies, the post processing mitigation of quantum errors, and suggested best practices. We identify four main areas of future research:(1) optimal measurement schemes for reduction of circuit repetitions required; (2) large scale parallelization across many quantum computers;  (3) ways to overcome the potential appearance of vanishing gradients in the optimization process for large systems, and how the number of iterations required for the optimization scales with system size; (4) the extent to which VQE suffers for quantum noise, and whether this noise can be mitigated in a tractable manner. The answers to these open research questions will determine the routes for the VQE to achieve quantum advantage as the quantum computing hardware scales up and as the noise levels are reduced.
%Overall, the VQE is undoubtedly among the most promising applications for near term quantum computing
\end{abstract}
% --------------------------------------------------------------
% Research highlights, if needed.
%\begin{highlights}
%    \item Research highlights item 1
%    \item Research highlights item 2
%    \item Research highlights item 3
%\end{highlights}

% Keywords. Each keyword is seperated by \sep
\begin{keywords}
Quantum computing \sep Variational methods \sep Noisy Intermediate Scale Quantum devices \sep Electronic structure \sep Quantum chemistry \sep Many-body physics
\end{keywords}

\maketitle
\tableofcontents 

\input{\ProjectRoot/01_Introduction.tex}
\input{\ProjectRoot/02_Overview_of_VQE.tex}
\input{\ProjectRoot/03_hamiltonian_main.tex}
\input{\ProjectRoot/04_encoding_main.tex}
\input{\ProjectRoot/05_group_main.tex}
\input{\ProjectRoot/06_ansatz_main.tex}
\input{\ProjectRoot/07_optimization_main.tex}

%NOTES on Optimization:
%
%(from VQSE paper:)
%Examples of Gradient free optimizers:
%
%Ken M Nakanishi, Keisuke Fujii, and Synge Todo, “Se-quential minimal optimization for quantum-classical hy-brid algorithms,” arXiv:1903.12166 (2019). 
%
%Robert M Parrish, Joseph T Iosue, Asier Ozaeta, and Pe-ter L McMahon, “A Jacobi diagonalization and Andersonacceleration algorithm for variational quantum algorithmparameter optimization,” arXiv:1904.03206 (2019)
%
%
%Apparently however it is shown that gradient based perform better: 
%
% Aram Harrow and John Napp, “Low-depth gradient mea-surements can improve convergence in variational hybridquantum-classical algorithms,” arXiv:1901.05374 (2019).
% 
% Jonas  M  Kübler,  Andrew  Arrasmith,  Lukasz  Cin-cio,   and Patrick J Coles, “An adaptive optimizerfor measurement-frugal variational algorithms,” arXivpreprint arXiv:1909.09083 (2019). 
% 
% Ryan Sweke, Frederik Wilde, Johannes Meyer, MariaSchuld,  Paul  K  Fährmann,  Barthélémy  Meynard-Piganeau,  and Jens Eisert, “Stochastic gradient de-scent for hybrid quantum-classical optimization,” arXivpreprint arXiv:1910.01155 (2019).
% 
% 
%Gradient can be analytical determined: 
% Kosuke Mitarai, Makoto Negoro, Masahiro Kitagawa,and Keisuke Fujii, “Quantum circuit learning,” PhysicalReview A98, 032309 (2018).
% 
% Maria Schuld, Ville Bergholm, Christian Gogolin, JoshIzaac,  and Nathan Killoran, “Evaluating analytic gra-dients on quantum hardware,” Physical Review A99,032331 (2019).

\input{\ProjectRoot/08_error-mit.tex}

\input{\ProjectRoot/09_VQE_extensions.tex}





\section{Conclusion and outlook}

The VQE is among the most promising near-term applications for quantum computers. While it is supported by strong theoretical arguments, there are still numerous open questions about the future applicability of the method. In this review, we outline the most relevant research that has been produced on the different components of the VQE, and how these are connected. To begin with, the choice of the Hamiltonian has direct implications for the number of qubits required, and for the capacity of VQE to achieve accurate results. A canonical orbital basis in second quantization has been the dominant choice in the community due to limited number of qubits required, although alternatives such as plane wave bases \cite{Babbush2018, Barkoutsos2018} and frozen natural orbitals basis \cite{Gonthier2020} have been proposed. Once the problem Hamiltonian has been constructed (and provided one decides to use second quantization), it is critical to decide on a mapping from fermionic operators to spin operators that best suits the system studied. While the Jordan-Wigner mapping \cite{Jordan1928} has been most commonly used due to its convenient implementation, low-weight mappings (in particular the ternary tree mapping \cite{Jiang2020} for molecular Hamiltonians, and the generalized superfast encoding \cite{Setia2019} for lattice models) have been shown to bring significant benefits with respect to circuit depth \cite{Tranter2015} for fermionic-based ans\"atze and resilience to the barren plateau problem \cite{Cerezo2021_BP, Uvarov2020, Uvarov2020_frustrated}. 

One of the most discussed drawbacks of VQE is the large number of measurements required to perform the optimization process \cite{Wecker2015, Elfving2020, Gonthier2020}. Some savings can be accomplished by managing the distribution of measurements, by weighting shots allocated to each operators by their respective weights in the Hamiltonian \cite{Wecker2015, Rubin2018, Arrasmith2020} or by truncating terms with significant impact on the energy \cite{mccleanTheoryVariationalHybrid2015}. However, to significantly reduce the scaling of VQE one should turn towards methods which jointly measure Hamiltonian terms. At present for molecular Hamiltonian this can most efficiently be done using a decomposed interactions method \cite{Huggins2021, Yen2021_Cartan}. For lattice models, however, because low-weight encoding are more easily achieved, a simple qubit-wise commutativity grouping scheme may the most cost effective \cite{mccleanTheoryVariationalHybrid2015, Kandala2017, Hempel2018, Rubin2018, Kokail2019, Izmaylov2019, Nam2020, Verteletskyi2020, Hamamura2020, Gokhale2019_long}. 

The core of the VQE remains the ansatz, or parametrized quantum circuit, chosen to model to the trial wavefunction. Among fixed structured ans\"atze the k-Unitary paired Generalized Coupled Cluster (k-UpCCGSD) \cite{Lee2019} and its extension \cite{Kottmann2021_1} stand out due to their ability to achieve excellent accuracy (evidenced numerous times \cite{Grimsley2019_UCC_Review, Lee2019, GreeneDiniz2020, Kottmann2021_1, Sokolov2020}), while maintaining a scaling linear in the number of qubits. For lattice models, while Unitary Coupled Cluster ans\"atze have been tested (for instance \cite{Sokolov2020}), one may prefer to use an ansatz for which the physically-motivated construction is more adapted. One such ansatz is the Hamiltonian Variational Ansatz \cite{Wecker2015, Wiersema2020}, and its extensions \cite{Babbush2018, Choquette2021}, which have been shown to be a promising methods for the study of many-body physics through VQE \cite{Wiersema2020, Babbush2018, Choquette2021}. Adaptive methods (all stemming from ADAPT-VQE \cite{Grimsley2019}), are promising avenues with demonstrated benefits \cite{Claudino2020}, but their overall cost and scaling remains unclear. 

The choice of optimizer directly impacts the ability of the VQE to converge and the overall cost of the method. Comparative studies remain sparse, and it is challenging to infer the ability of specific optimizer to navigate the complex optimization landspace of VQE \cite{Bittel2021}. However, two optimizers have received at least some level of numerical supports regarding their convergence rate and ability to avoid optimization pitfalls: the quantum natural gradient \cite{amari_natural_1998,martens_new_2020,wierichs_avoiding_2020}, and RotoSolve \cite{nakanishi_sequential_2020,ostaszewskiStructureOptimizationParameterized2021}. Finally, appropriate mitigation of quantum noise is likely required for VQE. Variational algorithms have been shown to exhibit at least some degree of ability to learn the biases created by quantum noise \cite{mccleanTheoryVariationalHybrid2015, Enrico2021EvaluatingNoiseResilience,Enrico2020NoiseInducedBreakingOfSymmetries}. However, further methods, such as symmetry verification and extrapolation based methods, despite coming at a significant computational cost, could be required to achieve the target accuracy with VQE. 

Despite numerical simulations being presented in the vast majority of papers proposing new methods, comprehensive, comparative and applied studies remain rare. This is most likely due to the rapid development of the field and the amount of different interacting components the VQE requires. Some notable exceptions (in particular \cite{Gonthier2020}) have attempted to focus on best practices to study applicability of VQE to practical electronic structure problems. Further numerical studies of these aspects can undoubtedly help guiding future research in the field. We identify four broad areas of suggested further research: (1) optimal measurement strategies to reduce the substantial number of shots required to estimate the expectation value of a Hamiltonian using a VQE ansatz; (2) the real cost and benefits of the massive parallelization potential of VQE, which is likely required for the method to ever be relevant; (3) the extent to which the method is subject to the barren plateau problem and whether current mitigation techniques are sufficient for VQE to scale, this would also involve further studying the complexity of the VQE optimization landscape, the expected convergence rate of the method and the relevance of various optimizers in avoiding local minima; and (4) the extent of the noise resilience of VQE, and the extent to which noise can be mitigated in a tractable manner. 

One interesting aspect of VQE that our review has not covered is that numerous algorithms have been inspired by it. For example, the Full Quantum Eigensolver \cite{Wei2020} (FQE) includes a quantum gradient descent to perform an optimization similar to VQE, but directly on the quantum computer to speed up convergence; the Projective Quantum Eigensolver \cite{Stair2021} optimizes energy using residuals from projection of the Schr\"odinger equation, rather than gradients. The Quantum Assisted Simulator (QAS) \cite{Bharti2020, Haug2020} and its extensions \cite{Bharti2020_IQAE} aims to avoid the barren plateau problem by replacing the usual optimization loop of VQE by a three-step process: selection of an ansatz, measurement of overlap matrices on a quantum computer, conventional computing post-processing based on the data from the second step. The Quantum Sampling Regression \cite{Rivero2020} also bypasses the VQE optimization loop and focuses on sampling the Fourier basis of the energy landscape using an ansatz to perform post-processing on a conventional computer, thereby bypassing the quantum-classical communication costs such as latency. The Variational Quantum State Eigensolver (VQSE) \cite{Cerezo2020_VQSE} adapts the VQE to cases in which one searches eigenvalues and eigenvectors of a quantum state density matrix. The Permutation VQE (PermVQE) \cite{Tkachenko2021} nests the VQE in an additional optimization loop with the objective to permute the order of the qubits at each iteration and minimize long-range correlations in ground state energy. The development of such algorithms is based on a deep knowledge of both the advantages and limitations of the VQE. The Filtering VQE \cite{Amaro2022} uses filtering operators in a VQE process to find ground states more efficiently and accurately, showing the method outperforms standard VQE and Quantum Approximate Optimization Algorithm in the case of a quadratic unconstrained binary optimization Hamiltonian \cite{Kochenberger2014}. Deep VQE \cite{Fujii2020} can be used to break down a given Hamiltonian into sub-units which can be solved separately to reduce the qubit requirements on very large systems. This methods was also extended to excited states computation by Mizuta \textit{et al.} \cite{Mizuta2021}. Meitei \textit{et al.} \cite{Meitei2021} presented a method, later optimized by Asthana \textit{et al.} \cite{Asthana2022}, to perform VQE directly at pulse level (ctrl-VQE), removing the need for a gate based ansatz. Finally, variational methods have also been used to model real and imaginary time evolution of quantum systems for ground and excited states discovery \cite{Yuan2019, Gustafson2021, Lin2021, Mansuroglu2021, McArdle2019, Nishi2021,Benedetti2021, Gomes2021}.

To assess the future worth of the VQE as an electronic structure method, one must also consider how it can be paired with other algorithms, such as those described in the paragraph above or with QPE, to help accelerate computation where needed. The algorithm is no doubt among the most promising methods for near-term applications of quantum computers. As  is the case for many emerging technologies, it faces daunting obstacles that will need to be overcome before it can be used in practical calculations, but the VQE also promises to deliver outstanding applications in fields such as drug discovery, chemical engineering, or material sciences.



\input{\ProjectRoot/acknowledgements.tex}


\appendix
\input{\ProjectRoot/appendices.tex}
% \clearpage
% \input{\ProjectRoot/10_List_of_symbols.tex}

\clearpage
% Loading bibliography style file
% https://www.elsevier.com/__data/assets/file/0007/56842/elsarticle-template.zip
% \bibliographystyle{bibstyle/elsarticle-num}  % no space btw arxiv [20]
% \bibliographystyle{bibstyle/model1-num-names}  % no link. arxiv not supported
% \bibliographystyle{bibstyle/model1a-num-names}  % no title. otherwise good.
% \bibliographystyle{bibstyle/model2-names} % has title, support arxiv, good content. sorted by author which is bad.
\bibliographystyle{bibstyle/model3-num-names} % has title. good content. arxiv does not support article type (missing journal)
% \bibliographystyle{bibstyle/model4-names} % has title, support arxiv, good content. sorted by author which is bad.
% \bibliographystyle{bibstyle/model5-names} % has title, support arxiv, good content. sorted by author which is bad.
% \bibliographystyle{bibstyle/model6-num-names} % has title. good content. arxiv does not support article type (missing journal)


% Loading bibliography database
\begin{thebibliography}{749}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\providecommand{\href}[2]{#2}
\providecommand{\path}[1]{#1}
\providecommand{\eprint}[1]{\href{http://arxiv.org/abs/#1}{\path{#1}}}
\providecommand{\DOIprefix}{doi:}
\providecommand{\ArXivprefix}{arXiv:}
\providecommand{\URLprefix}{URL: }
\providecommand{\Pubmedprefix}{pmid:}
\providecommand{\doi}[1]{\href{http://dx.doi.org/#1}{\path{#1}}}
\providecommand{\Pubmed}[1]{\href{pmid:#1}{\path{#1}}}
\providecommand{\BIBand}{and}
\providecommand{\bibinfo}[2]{#2}
\ifx\xfnm\undefined \def\xfnm[#1]{\unskip,\space#1}\fi
%Type = Article
\bibitem[{Benioff(1980)}]{Benioff1980}
\bibinfo{author}{Benioff\xfnm[ P.]}.
\newblock \bibinfo{title}{The computer as a physical system: A microscopic
  quantum mechanical hamiltonian model of computers as represented by turing
  machines}.
\newblock \bibinfo{journal}{Journal of Statistical Physics}
  \bibinfo{year}{1980};\bibinfo{volume}{22}(\bibinfo{number}{5}):\bibinfo{pages}{563--591}.
\newblock \DOIprefix\doi{10.1007/bf01011339}.
%Type = Article
\bibitem[{Feynman(1982)}]{Feynman1982}
\bibinfo{author}{Feynman\xfnm[ R.P.]}.
\newblock \bibinfo{title}{Simulating physics with computers}.
\newblock \bibinfo{journal}{International Journal of Theoretical Physics}
  \bibinfo{year}{1982};\bibinfo{volume}{21}(\bibinfo{number}{6-7}):\bibinfo{pages}{467--488}.
\newblock \DOIprefix\doi{10.1007/bf02650179}.
%Type = Article
\bibitem[{Chuang et~al.(1998)Chuang, Gershenfeld and Kubinec}]{Chuang1998}
\bibinfo{author}{Chuang\xfnm[ I.L.]}, \bibinfo{author}{Gershenfeld\xfnm[ N.]},
  \bibinfo{author}{Kubinec\xfnm[ M.]}.
\newblock \bibinfo{title}{Experimental implementation of fast quantum
  searching}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{1998};\bibinfo{volume}{80}(\bibinfo{number}{15}):\bibinfo{pages}{3408--3411}.
\newblock \DOIprefix\doi{10.1103/physrevlett.80.3408}.
%Type = Article
\bibitem[{Jones and Mosca(1999)}]{Jones1999}
\bibinfo{author}{Jones\xfnm[ J.A.]}, \bibinfo{author}{Mosca\xfnm[ M.]}.
\newblock \bibinfo{title}{Approximate quantum counting on an {NMR} ensemble
  quantum computer}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{1999};\bibinfo{volume}{83}(\bibinfo{number}{5}):\bibinfo{pages}{1050--1053}.
\newblock \DOIprefix\doi{10.1103/physrevlett.83.1050}.
%Type = Article
\bibitem[{Leung et~al.(2000)Leung, Chuang, Yamaguchi and Yamamoto}]{Leung2000}
\bibinfo{author}{Leung\xfnm[ D.W.]}, \bibinfo{author}{Chuang\xfnm[ I.L.]},
  \bibinfo{author}{Yamaguchi\xfnm[ F.]}, \bibinfo{author}{Yamamoto\xfnm[ Y.]}.
\newblock \bibinfo{title}{Efficient implementation of coupled logic gates for
  quantum computation}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2000};\bibinfo{volume}{61}(\bibinfo{number}{4}).
\newblock \DOIprefix\doi{10.1103/physreva.61.042310}.
%Type = Article
\bibitem[{Vandersypen et~al.(2001)Vandersypen, Steffen, Breyta, Yannoni,
  Sherwood and Chuang}]{Vandersypen2001}
\bibinfo{author}{Vandersypen\xfnm[ L.M.K.]}, \bibinfo{author}{Steffen\xfnm[
  M.]}, \bibinfo{author}{Breyta\xfnm[ G.]}, \bibinfo{author}{Yannoni\xfnm[
  C.S.]}, \bibinfo{author}{Sherwood\xfnm[ M.H.]}, \bibinfo{author}{Chuang\xfnm[
  I.L.]}.
\newblock \bibinfo{title}{Experimental realization of shor{\textquotesingle}s
  quantum factoring algorithm using nuclear magnetic resonance}.
\newblock \bibinfo{journal}{Nature}
  \bibinfo{year}{2001};\bibinfo{volume}{414}(\bibinfo{number}{6866}):\bibinfo{pages}{883--887}.
\newblock \DOIprefix\doi{10.1038/414883a}.
%Type = Article
\bibitem[{Häffner et~al.(2005)Häffner, Hänsel, Roos, Benhelm, Chek-al kar,
  Chwalla et~al.}]{Haffner2005}
\bibinfo{author}{Häffner\xfnm[ H.]}, \bibinfo{author}{Hänsel\xfnm[ W.]},
  \bibinfo{author}{Roos\xfnm[ C.F.]}, \bibinfo{author}{Benhelm\xfnm[ J.]},
  \bibinfo{author}{Chek-al kar\xfnm[ D.]}, \bibinfo{author}{Chwalla\xfnm[ M.]},
  et~al.
\newblock \bibinfo{title}{Scalable multiparticle entanglement of trapped ions}.
\newblock \bibinfo{journal}{Nature}
  \bibinfo{year}{2005};\bibinfo{volume}{438}(\bibinfo{number}{7068}):\bibinfo{pages}{643--646}.
\newblock \DOIprefix\doi{10.1038/nature04279}.
%Type = Article
\bibitem[{Negrevergne et~al.(2006)Negrevergne, Mahesh, Ryan, Ditty, Cyr-Racine,
  Power et~al.}]{Negrevergne2006}
\bibinfo{author}{Negrevergne\xfnm[ C.]}, \bibinfo{author}{Mahesh\xfnm[ T.S.]},
  \bibinfo{author}{Ryan\xfnm[ C.A.]}, \bibinfo{author}{Ditty\xfnm[ M.]},
  \bibinfo{author}{Cyr-Racine\xfnm[ F.]}, \bibinfo{author}{Power\xfnm[ W.]},
  et~al.
\newblock \bibinfo{title}{Benchmarking quantum control methods on a 12-qubit
  system}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2006};\bibinfo{volume}{96}(\bibinfo{number}{17}).
\newblock \DOIprefix\doi{10.1103/physrevlett.96.170501}.
%Type = Article
\bibitem[{Plantenberg et~al.(2007)Plantenberg, de~Groot, Harmans and
  Mooij}]{Plantenberg2007}
\bibinfo{author}{Plantenberg\xfnm[ J.H.]}, \bibinfo{author}{de~Groot\xfnm[
  P.C.]}, \bibinfo{author}{Harmans\xfnm[ C.J.P.M.]},
  \bibinfo{author}{Mooij\xfnm[ J.E.]}.
\newblock \bibinfo{title}{Demonstration of controlled-{NOT} quantum gates on a
  pair of superconducting quantum bits}.
\newblock \bibinfo{journal}{Nature}
  \bibinfo{year}{2007};\bibinfo{volume}{447}(\bibinfo{number}{7146}):\bibinfo{pages}{836--839}.
\newblock \DOIprefix\doi{10.1038/nature05896}.
%Type = Article
\bibitem[{Hanneke et~al.(2009)Hanneke, Home, Jost, Amini, Leibfried and
  Wineland}]{Hanneke2009}
\bibinfo{author}{Hanneke\xfnm[ D.]}, \bibinfo{author}{Home\xfnm[ J.P.]},
  \bibinfo{author}{Jost\xfnm[ J.D.]}, \bibinfo{author}{Amini\xfnm[ J.M.]},
  \bibinfo{author}{Leibfried\xfnm[ D.]}, \bibinfo{author}{Wineland\xfnm[
  D.J.]}.
\newblock \bibinfo{title}{Realization of a programmable two-qubit
  quantum~processor}.
\newblock \bibinfo{journal}{Nature Physics}
  \bibinfo{year}{2009};\bibinfo{volume}{6}(\bibinfo{number}{1}):\bibinfo{pages}{13--16}.
\newblock \DOIprefix\doi{10.1038/nphys1453}.
%Type = Article
\bibitem[{Monz et~al.(2011)Monz, Schindler, Barreiro, Chwalla, Nigg, Coish
  et~al.}]{Monz2011}
\bibinfo{author}{Monz\xfnm[ T.]}, \bibinfo{author}{Schindler\xfnm[ P.]},
  \bibinfo{author}{Barreiro\xfnm[ J.T.]}, \bibinfo{author}{Chwalla\xfnm[ M.]},
  \bibinfo{author}{Nigg\xfnm[ D.]}, \bibinfo{author}{Coish\xfnm[ W.A.]}, et~al.
\newblock \bibinfo{title}{14-qubit entanglement: Creation and coherence}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2011};\bibinfo{volume}{106}(\bibinfo{number}{13}).
\newblock \DOIprefix\doi{10.1103/physrevlett.106.130506}.
%Type = Article
\bibitem[{Devitt et~al.(2013)Devitt, Stephens, Munro and Nemoto}]{Devitt2013}
\bibinfo{author}{Devitt\xfnm[ S.J.]}, \bibinfo{author}{Stephens\xfnm[ A.M.]},
  \bibinfo{author}{Munro\xfnm[ W.J.]}, \bibinfo{author}{Nemoto\xfnm[ K.]}.
\newblock \bibinfo{title}{Requirements for fault-tolerant factoring on an
  atom-optics quantum computer}.
\newblock \bibinfo{journal}{Nature Communications}
  \bibinfo{year}{2013};\bibinfo{volume}{4}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1038/ncomms3524}.
%Type = Article
\bibitem[{Devitt(2016)}]{Devitt2016}
\bibinfo{author}{Devitt\xfnm[ S.J.]}.
\newblock \bibinfo{title}{Performing quantum computing experiments in the
  cloud}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2016};\bibinfo{volume}{94}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physreva.94.032329}.
%Type = Article
\bibitem[{Monz et~al.(2016)Monz, Nigg, Martinez, Brandl, Schindler, Rines
  et~al.}]{Monz2016}
\bibinfo{author}{Monz\xfnm[ T.]}, \bibinfo{author}{Nigg\xfnm[ D.]},
  \bibinfo{author}{Martinez\xfnm[ E.A.]}, \bibinfo{author}{Brandl\xfnm[ M.F.]},
  \bibinfo{author}{Schindler\xfnm[ P.]}, \bibinfo{author}{Rines\xfnm[ R.]},
  et~al.
\newblock \bibinfo{title}{Realization of a scalable shor algorithm}.
\newblock \bibinfo{journal}{Science}
  \bibinfo{year}{2016};\bibinfo{volume}{351}(\bibinfo{number}{6277}):\bibinfo{pages}{1068--1070}.
\newblock \DOIprefix\doi{10.1126/science.aad9480}.
%Type = Article
\bibitem[{Jurcevic et~al.(2021)Jurcevic, Javadi-Abhari, Bishop, Lauer, Bogorin,
  Brink et~al.}]{Jurcevic2021}
\bibinfo{author}{Jurcevic\xfnm[ P.]}, \bibinfo{author}{Javadi-Abhari\xfnm[
  A.]}, \bibinfo{author}{Bishop\xfnm[ L.S.]}, \bibinfo{author}{Lauer\xfnm[
  I.]}, \bibinfo{author}{Bogorin\xfnm[ D.F.]}, \bibinfo{author}{Brink\xfnm[
  M.]}, et~al.
\newblock \bibinfo{title}{Demonstration of quantum volume 64 on a
  superconducting quantum computing system}.
\newblock \bibinfo{journal}{Quantum Science and Technology}
  \bibinfo{year}{2021};\bibinfo{volume}{6}(\bibinfo{number}{2}):\bibinfo{pages}{025020}.
\newblock \DOIprefix\doi{10.1088/2058-9565/abe519}.
%Type = Article
\bibitem[{Pino et~al.(2021)Pino, Dreiling, Figgatt, Gaebler, Moses, Allman
  et~al.}]{Pino2021}
\bibinfo{author}{Pino\xfnm[ J.M.]}, \bibinfo{author}{Dreiling\xfnm[ J.M.]},
  \bibinfo{author}{Figgatt\xfnm[ C.]}, \bibinfo{author}{Gaebler\xfnm[ J.P.]},
  \bibinfo{author}{Moses\xfnm[ S.A.]}, \bibinfo{author}{Allman\xfnm[ M.S.]},
  et~al.
\newblock \bibinfo{title}{Demonstration of the trapped-ion quantum {CCD}
  computer architecture}.
\newblock \bibinfo{journal}{Nature}
  \bibinfo{year}{2021};\bibinfo{volume}{592}(\bibinfo{number}{7853}):\bibinfo{pages}{209--213}.
\newblock \DOIprefix\doi{10.1038/s41586-021-03318-4}.
%Type = Article
\bibitem[{Ebadi et~al.(2021)Ebadi, Wang, Levine, Keesling, Semeghini, Omran
  et~al.}]{Ebadi2021}
\bibinfo{author}{Ebadi\xfnm[ S.]}, \bibinfo{author}{Wang\xfnm[ T.T.]},
  \bibinfo{author}{Levine\xfnm[ H.]}, \bibinfo{author}{Keesling\xfnm[ A.]},
  \bibinfo{author}{Semeghini\xfnm[ G.]}, \bibinfo{author}{Omran\xfnm[ A.]},
  et~al.
\newblock \bibinfo{title}{Quantum phases of matter on a 256-atom programmable
  quantum simulator}.
\newblock \bibinfo{journal}{Nature}
  \bibinfo{year}{2021};\bibinfo{volume}{595}(\bibinfo{number}{7866}):\bibinfo{pages}{227--232}.
\newblock \DOIprefix\doi{10.1038/s41586-021-03582-4}.
%Type = Article
\bibitem[{Preskill(2018)}]{preskillQuantumComputingNISQ2018}
\bibinfo{author}{Preskill\xfnm[ J.]}.
\newblock \bibinfo{title}{Quantum computing in the {NISQ} era and beyond}.
\newblock \bibinfo{journal}{Quantum}
  \bibinfo{year}{2018};\bibinfo{volume}{2}:\bibinfo{pages}{79}.
\newblock \DOIprefix\doi{10.22331/q-2018-08-06-79}.
%Type = Article
\bibitem[{Brooks(2019)}]{Brooks2019}
\bibinfo{author}{Brooks\xfnm[ M.]}.
\newblock \bibinfo{title}{Beyond quantum supremacy: the hunt for useful quantum
  computers}.
\newblock \bibinfo{journal}{Nature}
  \bibinfo{year}{2019};\bibinfo{volume}{574}(\bibinfo{number}{7776}):\bibinfo{pages}{19--21}.
\newblock \DOIprefix\doi{10.1038/d41586-019-02936-3}.
%Type = Article
\bibitem[{Arute et~al.(2019)Arute, Arya, Babbush, Bacon, Bardin, Barends
  et~al.}]{Arute2019}
\bibinfo{author}{Arute\xfnm[ F.]}, \bibinfo{author}{Arya\xfnm[ K.]},
  \bibinfo{author}{Babbush\xfnm[ R.]}, \bibinfo{author}{Bacon\xfnm[ D.]},
  \bibinfo{author}{Bardin\xfnm[ J.C.]}, \bibinfo{author}{Barends\xfnm[ R.]},
  et~al.
\newblock \bibinfo{title}{Quantum supremacy using a programmable
  superconducting processor}.
\newblock \bibinfo{journal}{Nature}
  \bibinfo{year}{2019};\bibinfo{volume}{574}(\bibinfo{number}{7779}):\bibinfo{pages}{505--510}.
\newblock \DOIprefix\doi{10.1038/s41586-019-1666-5}.
%Type = Article
\bibitem[{Zhong et~al.(2020)Zhong, Wang, Deng, Chen, Peng, Luo
  et~al.}]{Zhong2020}
\bibinfo{author}{Zhong\xfnm[ H.S.]}, \bibinfo{author}{Wang\xfnm[ H.]},
  \bibinfo{author}{Deng\xfnm[ Y.H.]}, \bibinfo{author}{Chen\xfnm[ M.C.]},
  \bibinfo{author}{Peng\xfnm[ L.C.]}, \bibinfo{author}{Luo\xfnm[ Y.H.]}, et~al.
\newblock \bibinfo{title}{Quantum computational advantage using photons}.
\newblock \bibinfo{journal}{Science}
  \bibinfo{year}{2020};\bibinfo{volume}{370}(\bibinfo{number}{6523}):\bibinfo{pages}{1460--1463}.
\newblock \DOIprefix\doi{10.1126/science.abe8770}.
%Type = Misc
\bibitem[{Wu et~al.(2021{\natexlab{a}})Wu, Bao, Cao, Chen, Chen, Chen
  et~al.}]{Wu2021}
\bibinfo{author}{Wu\xfnm[ Y.]}, \bibinfo{author}{Bao\xfnm[ W.S.]},
  \bibinfo{author}{Cao\xfnm[ S.]}, \bibinfo{author}{Chen\xfnm[ F.]},
  \bibinfo{author}{Chen\xfnm[ M.C.]}, \bibinfo{author}{Chen\xfnm[ X.]}, et~al.
\newblock \bibinfo{title}{Strong quantum computational advantage using a
  superconducting quantum processor}.
\newblock \bibinfo{year}{2021}{\natexlab{a}}.
\newblock \href{http://arxiv.org/abs/2106.14734v1}{\tt arXiv:2106.14734v1}.
%Type = Article
\bibitem[{Madsen et~al.(2022)Madsen, Laudenbach, Askarani, Rortais, Vincent,
  Bulmer et~al.}]{Madsen2022}
\bibinfo{author}{Madsen\xfnm[ L.S.]}, \bibinfo{author}{Laudenbach\xfnm[ F.]},
  \bibinfo{author}{Askarani\xfnm[ M.F.]}, \bibinfo{author}{Rortais\xfnm[ F.]},
  \bibinfo{author}{Vincent\xfnm[ T.]}, \bibinfo{author}{Bulmer\xfnm[ J.F.F.]},
  et~al.
\newblock \bibinfo{title}{Quantum computational advantage with a programmable
  photonic processor}.
\newblock \bibinfo{journal}{Nature}
  \bibinfo{year}{2022};\bibinfo{volume}{606}(\bibinfo{number}{7912}):\bibinfo{pages}{75--81}.
\newblock \URLprefix \url{https://doi.org/10.1038/s41586-022-04725-x}.
  \DOIprefix\doi{10.1038/s41586-022-04725-x}.
%Type = Inproceedings
\bibitem[{Shor(1994)}]{shorAlgorithmsQuantumComputation}
\bibinfo{author}{Shor\xfnm[ P.]}.
\newblock \bibinfo{title}{Algorithms for quantum computation: discrete
  logarithms and factoring}.
\newblock In: \bibinfo{booktitle}{Proceedings 35th {{Annual Symposium}} on
  {{Foundations}} of {{Computer Science}}}. \bibinfo{publisher}{{IEEE} Comput.
  Soc. Press}.
\newblock ISBN \bibinfo{isbn}{0-8186-6580-7}; \bibinfo{year}{1994}, p.
  \bibinfo{pages}{124--134}.
\newblock \DOIprefix\doi{10.1109/sfcs.1994.365700}.
%Type = Article
\bibitem[{Lu et~al.(2007)Lu, Browne, Yang and Pan}]{ChaoYang2007}
\bibinfo{author}{Lu\xfnm[ C.Y.]}, \bibinfo{author}{Browne\xfnm[ D.E.]},
  \bibinfo{author}{Yang\xfnm[ T.]}, \bibinfo{author}{Pan\xfnm[ J.W.]}.
\newblock \bibinfo{title}{Demonstration of a compiled version of shor's quantum
  factoring algorithm using photonic qubits}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2007};\bibinfo{volume}{99}(\bibinfo{number}{25}).
\newblock \DOIprefix\doi{10.1103/physrevlett.99.250504}.
%Type = Article
\bibitem[{Lanyon et~al.(2007)Lanyon, Weinhold, Langford, Barbieri, James,
  Gilchrist et~al.}]{Lanyon2007}
\bibinfo{author}{Lanyon\xfnm[ B.P.]}, \bibinfo{author}{Weinhold\xfnm[ T.J.]},
  \bibinfo{author}{Langford\xfnm[ N.K.]}, \bibinfo{author}{Barbieri\xfnm[ M.]},
  \bibinfo{author}{James\xfnm[ D.F.V.]}, \bibinfo{author}{Gilchrist\xfnm[ A.]},
  et~al.
\newblock \bibinfo{title}{Experimental demonstration of a compiled version of
  shor's algorithm with quantum entanglement}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2007};\bibinfo{volume}{99}(\bibinfo{number}{25}).
\newblock \DOIprefix\doi{10.1103/physrevlett.99.250505}.
%Type = Article
\bibitem[{Lucero et~al.(2012)Lucero, Barends, Chen, Kelly, Mariantoni, Megrant
  et~al.}]{Lucero2012}
\bibinfo{author}{Lucero\xfnm[ E.]}, \bibinfo{author}{Barends\xfnm[ R.]},
  \bibinfo{author}{Chen\xfnm[ Y.]}, \bibinfo{author}{Kelly\xfnm[ J.]},
  \bibinfo{author}{Mariantoni\xfnm[ M.]}, \bibinfo{author}{Megrant\xfnm[ A.]},
  et~al.
\newblock \bibinfo{title}{Computing prime factors with a josephson phase qubit
  quantum processor}.
\newblock \bibinfo{journal}{Nature Physics}
  \bibinfo{year}{2012};\bibinfo{volume}{8}(\bibinfo{number}{10}):\bibinfo{pages}{719--723}.
\newblock \DOIprefix\doi{10.1038/nphys2385}.
%Type = Article
\bibitem[{Mart{\'{\i}}n-L{\'{o}}pez et~al.(2012)Mart{\'{\i}}n-L{\'{o}}pez,
  Laing, Lawson, Alvarez, Zhou and O{\textquotesingle}Brien}]{MartinLopez2012}
\bibinfo{author}{Mart{\'{\i}}n-L{\'{o}}pez\xfnm[ E.]},
  \bibinfo{author}{Laing\xfnm[ A.]}, \bibinfo{author}{Lawson\xfnm[ T.]},
  \bibinfo{author}{Alvarez\xfnm[ R.]}, \bibinfo{author}{Zhou\xfnm[ X.Q.]},
  \bibinfo{author}{O{\textquotesingle}Brien\xfnm[ J.L.]}.
\newblock \bibinfo{title}{Experimental realization of shor{\textquotesingle}s
  quantum factoring algorithm using qubit recycling}.
\newblock \bibinfo{journal}{Nature Photonics}
  \bibinfo{year}{2012};\bibinfo{volume}{6}(\bibinfo{number}{11}):\bibinfo{pages}{773--776}.
\newblock \DOIprefix\doi{10.1038/nphoton.2012.259}.
%Type = Article
\bibitem[{Markov and Saeedi(2013)}]{Markov2013}
\bibinfo{author}{Markov\xfnm[ I.L.]}, \bibinfo{author}{Saeedi\xfnm[ M.]}.
\newblock \bibinfo{title}{Faster quantum number factoring via circuit
  synthesis}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2013};\bibinfo{volume}{87}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1103/physreva.87.012310}.
%Type = Article
\bibitem[{Amico et~al.(2019)Amico, Saleem and Kumph}]{Amico2019}
\bibinfo{author}{Amico\xfnm[ M.]}, \bibinfo{author}{Saleem\xfnm[ Z.H.]},
  \bibinfo{author}{Kumph\xfnm[ M.]}.
\newblock \bibinfo{title}{Experimental study of shor{\textquotesingle}s
  factoring algorithm using the {IBM} q experience}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2019};\bibinfo{volume}{100}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1103/physreva.100.012305}.
%Type = Inproceedings
\bibitem[{Grover(1996)}]{groverFastQuantumMechanical1996}
\bibinfo{author}{Grover\xfnm[ L.K.]}.
\newblock \bibinfo{title}{A fast quantum mechanical algorithm for database
  search}.
\newblock In: \bibinfo{booktitle}{Proceedings of the Twenty-Eighth Annual ACM
  Symposium on Theory of Computing}. STOC '96; \bibinfo{address}{New York, NY,
  USA}: \bibinfo{publisher}{Association for Computing Machinery}.
\newblock ISBN \bibinfo{isbn}{0897917855}; \bibinfo{year}{1996}, p.
  \bibinfo{pages}{212–219}.
\newblock \DOIprefix\doi{10.1145/237814.237866}.
%Type = Article
\bibitem[{Bennett et~al.(1997)Bennett, Bernstein, Brassard and
  Vazirani}]{Bennett1997}
\bibinfo{author}{Bennett\xfnm[ C.H.]}, \bibinfo{author}{Bernstein\xfnm[ E.]},
  \bibinfo{author}{Brassard\xfnm[ G.]}, \bibinfo{author}{Vazirani\xfnm[ U.]}.
\newblock \bibinfo{title}{Strengths and weaknesses of quantum computing}.
\newblock \bibinfo{journal}{SIAM Journal on Computing}
  \bibinfo{year}{1997};\bibinfo{volume}{26}(\bibinfo{number}{5}):\bibinfo{pages}{1510--1523}.
\newblock \DOIprefix\doi{10.1137/s0097539796300933}.
%Type = Article
\bibitem[{Cerf et~al.(2000)Cerf, Grover and Williams}]{Cerf2000}
\bibinfo{author}{Cerf\xfnm[ N.J.]}, \bibinfo{author}{Grover\xfnm[ L.K.]},
  \bibinfo{author}{Williams\xfnm[ C.P.]}.
\newblock \bibinfo{title}{Nested quantum search and {NP}-hard problems}.
\newblock \bibinfo{journal}{Applicable Algebra in Engineering, Communication
  and Computing}
  \bibinfo{year}{2000};\bibinfo{volume}{10}(\bibinfo{number}{4-5}):\bibinfo{pages}{311--338}.
\newblock \DOIprefix\doi{10.1007/s002000050134}.
%Type = Article
\bibitem[{Ambainis(2004)}]{Ambainis2004}
\bibinfo{author}{Ambainis\xfnm[ A.]}.
\newblock \bibinfo{title}{Quantum search algorithms}.
\newblock \bibinfo{journal}{ACM SIGACT News}
  \bibinfo{year}{2004};\bibinfo{volume}{35}(\bibinfo{number}{2}):\bibinfo{pages}{22--35}.
\newblock \DOIprefix\doi{10.1145/992287.992296}.
%Type = Article
\bibitem[{Ambainis(2007)}]{Ambainis2007}
\bibinfo{author}{Ambainis\xfnm[ A.]}.
\newblock \bibinfo{title}{Quantum walk algorithm for element distinctness}.
\newblock \bibinfo{journal}{SIAM Journal on Computing}
  \bibinfo{year}{2007};\bibinfo{volume}{37}(\bibinfo{number}{1}):\bibinfo{pages}{210--239}.
\newblock \DOIprefix\doi{10.1137/s0097539705447311}.
%Type = Incollection
\bibitem[{Bernstein(2010)}]{Bernstein2010}
\bibinfo{author}{Bernstein\xfnm[ D.J.]}.
\newblock \bibinfo{title}{Grover vs.~{McEliece}}.
\newblock In: \bibinfo{booktitle}{Lecture Notes in Computer Science}; vol.
  \bibinfo{volume}{6061}. \bibinfo{publisher}{Springer Berlin Heidelberg};
  \bibinfo{year}{2010}, p. \bibinfo{pages}{73--80}.
\newblock \DOIprefix\doi{10.1007/978-3-642-12929-2_6}.
%Type = Article
\bibitem[{Peruzzo et~al.(2014)Peruzzo, McClean, Shadbolt, Yung, Zhou, Love
  et~al.}]{Peruzzo2014}
\bibinfo{author}{Peruzzo\xfnm[ A.]}, \bibinfo{author}{McClean\xfnm[ J.]},
  \bibinfo{author}{Shadbolt\xfnm[ P.]}, \bibinfo{author}{Yung\xfnm[ M.H.]},
  \bibinfo{author}{Zhou\xfnm[ X.Q.]}, \bibinfo{author}{Love\xfnm[ P.J.]},
  et~al.
\newblock \bibinfo{title}{A variational eigenvalue solver on a photonic quantum
  processor}.
\newblock \bibinfo{journal}{Nature Communications}
  \bibinfo{year}{2014};\bibinfo{volume}{5}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1038/ncomms5213}.
%Type = Article
\bibitem[{McClean et~al.(2016)McClean, Romero, Babbush and
  Aspuru-Guzik}]{mccleanTheoryVariationalHybrid2015}
\bibinfo{author}{McClean\xfnm[ J.R.]}, \bibinfo{author}{Romero\xfnm[ J.]},
  \bibinfo{author}{Babbush\xfnm[ R.]}, \bibinfo{author}{Aspuru-Guzik\xfnm[
  A.]}.
\newblock \bibinfo{title}{The theory of variational hybrid quantum-classical
  algorithms}.
\newblock \bibinfo{journal}{New Journal of Physics}
  \bibinfo{year}{2016};\bibinfo{volume}{18}(\bibinfo{number}{2}):\bibinfo{pages}{023023}.
\newblock \DOIprefix\doi{10.1088/1367-2630/18/2/023023}.
%Type = Article
\bibitem[{Deglmann et~al.(2014)Deglmann, Schäfer and Lennartz}]{Deglmann2014}
\bibinfo{author}{Deglmann\xfnm[ P.]}, \bibinfo{author}{Schäfer\xfnm[ A.]},
  \bibinfo{author}{Lennartz\xfnm[ C.]}.
\newblock \bibinfo{title}{Application of quantum calculations in the chemical
  industry-an overview}.
\newblock \bibinfo{journal}{International Journal of Quantum Chemistry}
  \bibinfo{year}{2014};\bibinfo{volume}{115}(\bibinfo{number}{3}):\bibinfo{pages}{107--136}.
\newblock \DOIprefix\doi{10.1002/qua.24811}.
%Type = Article
\bibitem[{Williams-Noonan et~al.(2017)Williams-Noonan, Yuriev and
  Chalmers}]{WilliamsNoonan2017}
\bibinfo{author}{Williams-Noonan\xfnm[ B.J.]}, \bibinfo{author}{Yuriev\xfnm[
  E.]}, \bibinfo{author}{Chalmers\xfnm[ D.K.]}.
\newblock \bibinfo{title}{Free energy methods in drug design: Prospects of
  {\textquotedblleft}alchemical perturbation{\textquotedblright} in medicinal
  chemistry}.
\newblock \bibinfo{journal}{Journal of Medicinal Chemistry}
  \bibinfo{year}{2017};\bibinfo{volume}{61}(\bibinfo{number}{3}):\bibinfo{pages}{638--649}.
\newblock \DOIprefix\doi{10.1021/acs.jmedchem.7b00681}.
%Type = Book
\bibitem[{Heifetz(2020)}]{Heifetz2020}
\bibinfo{editor}{Heifetz\xfnm[ A.]}, editor.
\newblock \bibinfo{title}{Quantum Mechanics in Drug Discovery}.
\newblock \bibinfo{publisher}{Springer {US}}; \bibinfo{year}{2020}.
\newblock ISBN \bibinfo{isbn}{9781071602829}.
\newblock \DOIprefix\doi{10.1007/978-1-0716-0282-9}.
%Type = Book
\bibitem[{Continentino(2021)}]{Continentino2021}
\bibinfo{author}{Continentino\xfnm[ M.A.]}.
\newblock \bibinfo{title}{Key Methods and Concepts in Condensed Matter
  Physics}.
\newblock \bibinfo{publisher}{{IOP} Publishing}; \bibinfo{year}{2021}.
\newblock ISBN \bibinfo{isbn}{9780750333955}.
\newblock \DOIprefix\doi{10.1088/978-0-7503-3395-5}.
%Type = Article
\bibitem[{der Ven et~al.(2020)der Ven, Deng, Banerjee and Ong}]{VanderVen2020}
\bibinfo{author}{der Ven\xfnm[ A.V.]}, \bibinfo{author}{Deng\xfnm[ Z.]},
  \bibinfo{author}{Banerjee\xfnm[ S.]}, \bibinfo{author}{Ong\xfnm[ S.P.]}.
\newblock \bibinfo{title}{Rechargeable alkali-ion battery materials: Theory and
  computation}.
\newblock \bibinfo{journal}{Chemical Reviews}
  \bibinfo{year}{2020};\bibinfo{volume}{120}(\bibinfo{number}{14}):\bibinfo{pages}{6977--7019}.
\newblock \DOIprefix\doi{10.1021/acs.chemrev.9b00601}.
%Type = Article
\bibitem[{Cao et~al.(2018)Cao, Romero and Aspuru-Guzik}]{Cao2018_DD}
\bibinfo{author}{Cao\xfnm[ Y.]}, \bibinfo{author}{Romero\xfnm[ J.]},
  \bibinfo{author}{Aspuru-Guzik\xfnm[ A.]}.
\newblock \bibinfo{title}{Potential of quantum computing for drug discovery}.
\newblock \bibinfo{journal}{IBM Journal of Research and Development}
  \bibinfo{year}{2018};\bibinfo{volume}{62}(\bibinfo{number}{6}):\bibinfo{pages}{6:1--6:20}.
\newblock \DOIprefix\doi{10.1147/jrd.2018.2888987}.
%Type = Misc
\bibitem[{Blunt et~al.(2022)Blunt, Camps, Crawford, Izsák, Leontica, Mirani
  et~al.}]{Blunt2022}
\bibinfo{author}{Blunt\xfnm[ N.S.]}, \bibinfo{author}{Camps\xfnm[ J.]},
  \bibinfo{author}{Crawford\xfnm[ O.]}, \bibinfo{author}{Izsák\xfnm[ R.]},
  \bibinfo{author}{Leontica\xfnm[ S.]}, \bibinfo{author}{Mirani\xfnm[ A.]},
  et~al.
\newblock \bibinfo{title}{A perspective on the current state-of-the-art of
  quantum computing for drug discovery applications}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2206.00551}.
  \DOIprefix\doi{10.48550/ARXIV.2206.00551}.
%Type = Article
\bibitem[{Lordi and Nichol(2021)}]{Lordi2021}
\bibinfo{author}{Lordi\xfnm[ V.]}, \bibinfo{author}{Nichol\xfnm[ J.M.]}.
\newblock \bibinfo{title}{Advances and opportunities in materials science for
  scalable quantum computing}.
\newblock \bibinfo{journal}{MRS Bulletin}
  \bibinfo{year}{2021};\bibinfo{volume}{46}(\bibinfo{number}{7}):\bibinfo{pages}{589--595}.
\newblock \DOIprefix\doi{10.1557/s43577-021-00133-0}.
%Type = Article
\bibitem[{Cao et~al.(2019)Cao, Romero, Olson, Degroote, Johnson,
  Kieferov{\'{a}} et~al.}]{Cao2019_QC}
\bibinfo{author}{Cao\xfnm[ Y.]}, \bibinfo{author}{Romero\xfnm[ J.]},
  \bibinfo{author}{Olson\xfnm[ J.P.]}, \bibinfo{author}{Degroote\xfnm[ M.]},
  \bibinfo{author}{Johnson\xfnm[ P.D.]}, \bibinfo{author}{Kieferov{\'{a}}\xfnm[
  M.]}, et~al.
\newblock \bibinfo{title}{Quantum chemistry in the age of quantum computing}.
\newblock \bibinfo{journal}{Chemical Reviews}
  \bibinfo{year}{2019};\bibinfo{volume}{119}(\bibinfo{number}{19}):\bibinfo{pages}{10856--10915}.
\newblock \DOIprefix\doi{10.1021/acs.chemrev.8b00803}.
%Type = Article
\bibitem[{Zhou et~al.(2020)Zhou, Stoudenmire and Waintal}]{Zhou2020}
\bibinfo{author}{Zhou\xfnm[ Y.]}, \bibinfo{author}{Stoudenmire\xfnm[ E.M.]},
  \bibinfo{author}{Waintal\xfnm[ X.]}.
\newblock \bibinfo{title}{What limits the simulation of quantum computers?}
\newblock \bibinfo{journal}{Physical Review X}
  \bibinfo{year}{2020};\bibinfo{volume}{10}(\bibinfo{number}{4}).
\newblock \DOIprefix\doi{10.1103/physrevx.10.041038}.
%Type = Article
\bibitem[{Boixo et~al.(2018)Boixo, Isakov, Smelyanskiy, Babbush, Ding, Jiang
  et~al.}]{Boixo2018}
\bibinfo{author}{Boixo\xfnm[ S.]}, \bibinfo{author}{Isakov\xfnm[ S.V.]},
  \bibinfo{author}{Smelyanskiy\xfnm[ V.N.]}, \bibinfo{author}{Babbush\xfnm[
  R.]}, \bibinfo{author}{Ding\xfnm[ N.]}, \bibinfo{author}{Jiang\xfnm[ Z.]},
  et~al.
\newblock \bibinfo{title}{Characterizing quantum supremacy in near-term
  devices}.
\newblock \bibinfo{journal}{Nature Physics}
  \bibinfo{year}{2018};\bibinfo{volume}{14}(\bibinfo{number}{6}):\bibinfo{pages}{595--600}.
\newblock \DOIprefix\doi{10.1038/s41567-018-0124-x}.
%Type = Article
\bibitem[{McCaskey et~al.(2019)McCaskey, Parks, Jakowski, Moore, Morris, Humble
  et~al.}]{mccaskeyQuantumChemistryBenchmark2019}
\bibinfo{author}{McCaskey\xfnm[ A.J.]}, \bibinfo{author}{Parks\xfnm[ Z.P.]},
  \bibinfo{author}{Jakowski\xfnm[ J.]}, \bibinfo{author}{Moore\xfnm[ S.V.]},
  \bibinfo{author}{Morris\xfnm[ T.D.]}, \bibinfo{author}{Humble\xfnm[ T.S.]},
  et~al.
\newblock \bibinfo{title}{Quantum chemistry as a benchmark for near-term
  quantum computers}.
\newblock \bibinfo{journal}{npj Quantum Information}
  \bibinfo{year}{2019};\bibinfo{volume}{5}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1038/s41534-019-0209-0}.
%Type = Book
\bibitem[{Silverman(2008)}]{Silverman2008}
\bibinfo{author}{Silverman\xfnm[ M.]}.
\newblock \bibinfo{title}{Quantum superposition : counterintuitive consequences
  of coherence, entanglement, and interference}.
\newblock \bibinfo{address}{Berlin}: \bibinfo{publisher}{Springer};
  \bibinfo{year}{2008}.
\newblock ISBN \bibinfo{isbn}{3540718834}.
%Type = Article
\bibitem[{Ballentine(2008)}]{Ballentine2008}
\bibinfo{author}{Ballentine\xfnm[ L.E.]}.
\newblock \bibinfo{title}{Quantum superposition: Counterintuitive consequences
  of coherence, entanglement and {InterferenceQuantum} superposition:
  Counterintuitive consequences of coherence, entanglement and
  {InterferenceMark} p.silverman. 378 pp. springer, berlin, 2008. price:
  {\textdollar}89.95 {ISBN} 978-3-540-71883-3.}
\newblock \bibinfo{journal}{American Journal of Physics}
  \bibinfo{year}{2008};\bibinfo{volume}{76}(\bibinfo{number}{11}):\bibinfo{pages}{1078--1079}.
\newblock \DOIprefix\doi{10.1119/1.2973810}.
%Type = Book
\bibitem[{Helgaker et~al.(2000)Helgaker, J{\o}rgensen and Olsen}]{Helgaker2000}
\bibinfo{author}{Helgaker\xfnm[ T.]}, \bibinfo{author}{J{\o}rgensen\xfnm[ P.]},
  \bibinfo{author}{Olsen\xfnm[ J.]}.
\newblock \bibinfo{title}{Molecular Electronic-Structure Theory}.
\newblock \bibinfo{publisher}{John Wiley {\&} Sons, Ltd}; \bibinfo{year}{2000}.
\newblock ISBN \bibinfo{isbn}{9781118531471}.
\newblock \DOIprefix\doi{10.1002/9781119019572}.
%Type = Article
\bibitem[{Kratzer and Neugebauer(2019)}]{Kratzer2019}
\bibinfo{author}{Kratzer\xfnm[ P.]}, \bibinfo{author}{Neugebauer\xfnm[ J.]}.
\newblock \bibinfo{title}{The basics of electronic structure theory for
  periodic systems}.
\newblock \bibinfo{journal}{Frontiers in Chemistry}
  \bibinfo{year}{2019};\bibinfo{volume}{7}.
\newblock \DOIprefix\doi{10.3389/fchem.2019.00106}.
%Type = Article
\bibitem[{Li et~al.(2020)Li, Govind, Isborn, DePrince and Lopata}]{Li2020_EST}
\bibinfo{author}{Li\xfnm[ X.]}, \bibinfo{author}{Govind\xfnm[ N.]},
  \bibinfo{author}{Isborn\xfnm[ C.]}, \bibinfo{author}{DePrince\xfnm[ A.E.]},
  \bibinfo{author}{Lopata\xfnm[ K.]}.
\newblock \bibinfo{title}{Real-time time-dependent electronic structure
  theory}.
\newblock \bibinfo{journal}{Chemical Reviews}
  \bibinfo{year}{2020};\bibinfo{volume}{120}(\bibinfo{number}{18}):\bibinfo{pages}{9951--9993}.
\newblock \DOIprefix\doi{10.1021/acs.chemrev.0c00223}.
%Type = Inproceedings
\bibitem[{Miceli and McGuigan(2019)}]{Miceli2019}
\bibinfo{author}{Miceli\xfnm[ R.]}, \bibinfo{author}{McGuigan\xfnm[ M.]}.
\newblock \bibinfo{title}{Effective matrix model for nuclear physics on a
  quantum computer}.
\newblock In: \bibinfo{booktitle}{2019 New York Scientific Data Summit
  (NYSDS)}. \bibinfo{year}{2019}, p. \bibinfo{pages}{1--4}.
\newblock \DOIprefix\doi{10.1109/NYSDS.2019.8909693}.
%Type = Article
\bibitem[{Matteo et~al.(2021)Matteo, McCoy, Gysbers, Miyagi, Woloshyn and
  Navr{\'{a}}til}]{DiMatteo2021}
\bibinfo{author}{Matteo\xfnm[ O.D.]}, \bibinfo{author}{McCoy\xfnm[ A.]},
  \bibinfo{author}{Gysbers\xfnm[ P.]}, \bibinfo{author}{Miyagi\xfnm[ T.]},
  \bibinfo{author}{Woloshyn\xfnm[ R.M.]}, \bibinfo{author}{Navr{\'{a}}til\xfnm[
  P.]}.
\newblock \bibinfo{title}{Improving hamiltonian encodings with the gray code}.
\newblock \bibinfo{journal}{Phys Rev A}
  \bibinfo{year}{2021};\bibinfo{volume}{103}(\bibinfo{number}{4}).
\newblock \DOIprefix\doi{10.1103/physreva.103.042405}.
%Type = Misc
\bibitem[{Kiss et~al.(2022)Kiss, Grossi, Lougovski, Sanchez, Vallecorsa and
  Papenbrock}]{Kiss2022}
\bibinfo{author}{Kiss\xfnm[ O.]}, \bibinfo{author}{Grossi\xfnm[ M.]},
  \bibinfo{author}{Lougovski\xfnm[ P.]}, \bibinfo{author}{Sanchez\xfnm[ F.]},
  \bibinfo{author}{Vallecorsa\xfnm[ S.]}, \bibinfo{author}{Papenbrock\xfnm[
  T.]}.
\newblock \bibinfo{title}{Quantum computing of the $^6$li nucleus via ordered
  unitary coupled cluster}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2205.00864}.
  \DOIprefix\doi{10.48550/ARXIV.2205.00864}.
%Type = Misc
\bibitem[{Romero et~al.(2022)Romero, Engel, Tang and Economou}]{Romero2022}
\bibinfo{author}{Romero\xfnm[ A.M.]}, \bibinfo{author}{Engel\xfnm[ J.]},
  \bibinfo{author}{Tang\xfnm[ H.L.]}, \bibinfo{author}{Economou\xfnm[ S.E.]}.
\newblock \bibinfo{title}{Solving nuclear structure problems with the adaptive
  variational quantum algorithm}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2203.01619}.
  \DOIprefix\doi{10.48550/ARXIV.2203.01619}.
%Type = Article
\bibitem[{Ba{\~{n}}uls et~al.(2020)Ba{\~{n}}uls, Blatt, Catani, Celi, Cirac,
  Dalmonte et~al.}]{Bauls2020}
\bibinfo{author}{Ba{\~{n}}uls\xfnm[ M.C.]}, \bibinfo{author}{Blatt\xfnm[ R.]},
  \bibinfo{author}{Catani\xfnm[ J.]}, \bibinfo{author}{Celi\xfnm[ A.]},
  \bibinfo{author}{Cirac\xfnm[ J.I.]}, \bibinfo{author}{Dalmonte\xfnm[ M.]},
  et~al.
\newblock \bibinfo{title}{Simulating lattice gauge theories within quantum
  technologies}.
\newblock \bibinfo{journal}{The European Physical Journal D}
  \bibinfo{year}{2020};\bibinfo{volume}{74}(\bibinfo{number}{8}).
\newblock \URLprefix \url{https://doi.org/10.1140/epjd/e2020-100571-8}.
  \DOIprefix\doi{10.1140/epjd/e2020-100571-8}.
%Type = Article
\bibitem[{Bass and Zohar(2021)}]{Bass2021}
\bibinfo{author}{Bass\xfnm[ S.D.]}, \bibinfo{author}{Zohar\xfnm[ E.]}.
\newblock \bibinfo{title}{Quantum technologies in particle physics}.
\newblock \bibinfo{journal}{Philosophical Transactions of the Royal Society A:
  Mathematical, Physical and Engineering Sciences}
  \bibinfo{year}{2021};\bibinfo{volume}{380}(\bibinfo{number}{2216}).
\newblock \URLprefix \url{https://doi.org/10.1098/rsta.2021.0072}.
  \DOIprefix\doi{10.1098/rsta.2021.0072}.
%Type = Misc
\bibitem[{Bauer et~al.(2022)Bauer, Davoudi, Balantekin, Bhattacharya, Carena,
  de~Jong et~al.}]{Bauer2022}
\bibinfo{author}{Bauer\xfnm[ C.W.]}, \bibinfo{author}{Davoudi\xfnm[ Z.]},
  \bibinfo{author}{Balantekin\xfnm[ A.B.]}, \bibinfo{author}{Bhattacharya\xfnm[
  T.]}, \bibinfo{author}{Carena\xfnm[ M.]}, \bibinfo{author}{de~Jong\xfnm[
  W.A.]}, et~al.
\newblock \bibinfo{title}{Quantum simulation for high energy physics}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2204.03381}.
  \DOIprefix\doi{10.48550/ARXIV.2204.03381}.
%Type = Article
\bibitem[{McArdle et~al.(2019{\natexlab{a}})McArdle, Mayorov, Shan, Benjamin
  and Yuan}]{McArdle2019_vibra}
\bibinfo{author}{McArdle\xfnm[ S.]}, \bibinfo{author}{Mayorov\xfnm[ A.]},
  \bibinfo{author}{Shan\xfnm[ X.]}, \bibinfo{author}{Benjamin\xfnm[ S.]},
  \bibinfo{author}{Yuan\xfnm[ X.]}.
\newblock \bibinfo{title}{Digital quantum simulation of molecular vibrations}.
\newblock \bibinfo{journal}{Chemical Science}
  \bibinfo{year}{2019}{\natexlab{a}};\bibinfo{volume}{10}(\bibinfo{number}{22}):\bibinfo{pages}{5725--5735}.
\newblock \URLprefix \url{https://doi.org/10.1039/c9sc01313j}.
  \DOIprefix\doi{10.1039/c9sc01313j}.
%Type = Article
\bibitem[{Sawaya and Huh(2019)}]{Sawaya2019}
\bibinfo{author}{Sawaya\xfnm[ N.P.D.]}, \bibinfo{author}{Huh\xfnm[ J.]}.
\newblock \bibinfo{title}{Quantum algorithm for calculating molecular vibronic
  spectra}.
\newblock \bibinfo{journal}{The Journal of Physical Chemistry Letters}
  \bibinfo{year}{2019};\bibinfo{volume}{10}(\bibinfo{number}{13}):\bibinfo{pages}{3586--3591}.
\newblock \URLprefix \url{https://doi.org/10.1021/acs.jpclett.9b01117}.
  \DOIprefix\doi{10.1021/acs.jpclett.9b01117}.
%Type = Article
\bibitem[{Ollitrault et~al.(2020{\natexlab{a}})Ollitrault, Baiardi, Reiher and
  Tavernelli}]{Ollitrault2020_vibrational}
\bibinfo{author}{Ollitrault\xfnm[ P.J.]}, \bibinfo{author}{Baiardi\xfnm[ A.]},
  \bibinfo{author}{Reiher\xfnm[ M.]}, \bibinfo{author}{Tavernelli\xfnm[ I.]}.
\newblock \bibinfo{title}{Hardware efficient quantum algorithms for vibrational
  structure calculations}.
\newblock \bibinfo{journal}{Chemical Science}
  \bibinfo{year}{2020}{\natexlab{a}};\bibinfo{volume}{11}(\bibinfo{number}{26}):\bibinfo{pages}{6842--6855}.
\newblock \URLprefix \url{https://doi.org/10.1039/d0sc01908a}.
  \DOIprefix\doi{10.1039/d0sc01908a}.
%Type = Article
\bibitem[{Jahangiri et~al.(2020)Jahangiri, Arrazola, Quesada and
  Delgado}]{Jahangiri2020}
\bibinfo{author}{Jahangiri\xfnm[ S.]}, \bibinfo{author}{Arrazola\xfnm[ J.M.]},
  \bibinfo{author}{Quesada\xfnm[ N.]}, \bibinfo{author}{Delgado\xfnm[ A.]}.
\newblock \bibinfo{title}{Quantum algorithm for simulating molecular
  vibrational excitations}.
\newblock \bibinfo{journal}{Physical Chemistry Chemical Physics}
  \bibinfo{year}{2020};\bibinfo{volume}{22}(\bibinfo{number}{44}):\bibinfo{pages}{25528--25537}.
\newblock \URLprefix \url{https://doi.org/10.1039/d0cp03593a}.
  \DOIprefix\doi{10.1039/d0cp03593a}.
%Type = Article
\bibitem[{L\"{o}tstedt et~al.(2021)L\"{o}tstedt, Yamanouchi, Tsuchiya and
  Tachikawa}]{Ltstedt2021}
\bibinfo{author}{L\"{o}tstedt\xfnm[ E.]}, \bibinfo{author}{Yamanouchi\xfnm[
  K.]}, \bibinfo{author}{Tsuchiya\xfnm[ T.]}, \bibinfo{author}{Tachikawa\xfnm[
  Y.]}.
\newblock \bibinfo{title}{Calculation of vibrational eigenenergies on a quantum
  computer: Application to the fermi resonance in $\mathrm{CO}_2$}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2021};\bibinfo{volume}{103}(\bibinfo{number}{6}).
\newblock \URLprefix \url{https://doi.org/10.1103/physreva.103.062609}.
  \DOIprefix\doi{10.1103/physreva.103.062609}.
%Type = Article
\bibitem[{Sawaya et~al.(2021)Sawaya, Paesani and Tabor}]{Sawaya2021}
\bibinfo{author}{Sawaya\xfnm[ N.P.D.]}, \bibinfo{author}{Paesani\xfnm[ F.]},
  \bibinfo{author}{Tabor\xfnm[ D.P.]}.
\newblock \bibinfo{title}{Near- and long-term quantum algorithmic approaches
  for vibrational spectroscopy}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2021};\bibinfo{volume}{104}(\bibinfo{number}{6}).
\newblock \URLprefix \url{https://doi.org/10.1103/physreva.104.062419}.
  \DOIprefix\doi{10.1103/physreva.104.062419}.
%Type = Article
\bibitem[{Mitarai et~al.(2020)Mitarai, Nakagawa and Mizukami}]{Mitarai2020}
\bibinfo{author}{Mitarai\xfnm[ K.]}, \bibinfo{author}{Nakagawa\xfnm[ Y.O.]},
  \bibinfo{author}{Mizukami\xfnm[ W.]}.
\newblock \bibinfo{title}{Theory of analytical energy derivatives for the
  variational quantum eigensolver}.
\newblock \bibinfo{journal}{Physical Review Research}
  \bibinfo{year}{2020};\bibinfo{volume}{2}(\bibinfo{number}{1}).
\newblock \URLprefix \url{https://doi.org/10.1103/physrevresearch.2.013129}.
  \DOIprefix\doi{10.1103/physrevresearch.2.013129}.
%Type = Article
\bibitem[{Omiya et~al.(2022)Omiya, Nakagawa, Koh, Mizukami, Gao and
  Kobayashi}]{Omiya2022}
\bibinfo{author}{Omiya\xfnm[ K.]}, \bibinfo{author}{Nakagawa\xfnm[ Y.O.]},
  \bibinfo{author}{Koh\xfnm[ S.]}, \bibinfo{author}{Mizukami\xfnm[ W.]},
  \bibinfo{author}{Gao\xfnm[ Q.]}, \bibinfo{author}{Kobayashi\xfnm[ T.]}.
\newblock \bibinfo{title}{Analytical energy gradient for state-averaged
  orbital-optimized variational quantum eigensolvers and its application to a
  photochemical reaction}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2022};\bibinfo{volume}{18}(\bibinfo{number}{2}):\bibinfo{pages}{741--748}.
\newblock \URLprefix \url{https://doi.org/10.1021/acs.jctc.1c00877}.
  \DOIprefix\doi{10.1021/acs.jctc.1c00877}.
%Type = Article
\bibitem[{Liu et~al.(2020)Liu, Wan, Li and Yang}]{Liu2020}
\bibinfo{author}{Liu\xfnm[ J.]}, \bibinfo{author}{Wan\xfnm[ L.]},
  \bibinfo{author}{Li\xfnm[ Z.]}, \bibinfo{author}{Yang\xfnm[ J.]}.
\newblock \bibinfo{title}{Simulating periodic systems on a quantum computer
  using molecular orbitals}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2020};\bibinfo{volume}{16}(\bibinfo{number}{11}):\bibinfo{pages}{6904--6914}.
\newblock \URLprefix \url{https://doi.org/10.1021/acs.jctc.0c00881}.
  \DOIprefix\doi{10.1021/acs.jctc.0c00881}.
%Type = Article
\bibitem[{Yoshioka et~al.(2022)Yoshioka, Sato, Nakagawa, ya~Ohnishi and
  Mizukami}]{Yoshioka2022}
\bibinfo{author}{Yoshioka\xfnm[ N.]}, \bibinfo{author}{Sato\xfnm[ T.]},
  \bibinfo{author}{Nakagawa\xfnm[ Y.O.]}, \bibinfo{author}{ya~Ohnishi\xfnm[
  Y.]}, \bibinfo{author}{Mizukami\xfnm[ W.]}.
\newblock \bibinfo{title}{Variational quantum simulation for periodic
  materials}.
\newblock \bibinfo{journal}{Physical Review Research}
  \bibinfo{year}{2022};\bibinfo{volume}{4}(\bibinfo{number}{1}).
\newblock \URLprefix \url{https://doi.org/10.1103/physrevresearch.4.013052}.
  \DOIprefix\doi{10.1103/physrevresearch.4.013052}.
%Type = Misc
\bibitem[{Manrique et~al.(2020)Manrique, Khan, Yamamoto, Wichitwechkarn and
  Ramo}]{Manrique2020}
\bibinfo{author}{Manrique\xfnm[ D.Z.]}, \bibinfo{author}{Khan\xfnm[ I.T.]},
  \bibinfo{author}{Yamamoto\xfnm[ K.]}, \bibinfo{author}{Wichitwechkarn\xfnm[
  V.]}, \bibinfo{author}{Ramo\xfnm[ D.M.]}.
\newblock \bibinfo{title}{Momentum-space unitary coupled cluster and
  translational quantum subspace expansion for periodic systems on quantum
  computers}.
\newblock \bibinfo{year}{2020}.
\newblock \URLprefix \url{https://arxiv.org/abs/2008.08694}.
  \DOIprefix\doi{10.48550/ARXIV.2008.08694}.
%Type = Article
\bibitem[{Lubasch et~al.(2020)Lubasch, Joo, Moinier, Kiffner and
  Jaksch}]{Lubasch2020}
\bibinfo{author}{Lubasch\xfnm[ M.]}, \bibinfo{author}{Joo\xfnm[ J.]},
  \bibinfo{author}{Moinier\xfnm[ P.]}, \bibinfo{author}{Kiffner\xfnm[ M.]},
  \bibinfo{author}{Jaksch\xfnm[ D.]}.
\newblock \bibinfo{title}{Variational quantum algorithms for nonlinear
  problems}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2020};\bibinfo{volume}{101}(\bibinfo{number}{1}).
\newblock \URLprefix \url{https://doi.org/10.1103/physreva.101.010301}.
  \DOIprefix\doi{10.1103/physreva.101.010301}.
%Type = Misc
\bibitem[{Joseph et~al.(2022)Joseph, White, Chandra and McGuigan}]{Joseph2022}
\bibinfo{author}{Joseph\xfnm[ A.]}, \bibinfo{author}{White\xfnm[ T.]},
  \bibinfo{author}{Chandra\xfnm[ V.]}, \bibinfo{author}{McGuigan\xfnm[ M.]}.
\newblock \bibinfo{title}{Quantum computing of schwarzschild-de sitter black
  holes and kantowski-sachs cosmology}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2202.09906}.
  \DOIprefix\doi{10.48550/ARXIV.2202.09906}.
%Type = Book
\bibitem[{Nielsen and Chuang(2009)}]{nielsenQuantumComputationQuantum2010}
\bibinfo{author}{Nielsen\xfnm[ M.A.]}, \bibinfo{author}{Chuang\xfnm[ I.L.]}.
\newblock \bibinfo{title}{Quantum Computation and Quantum Information}.
\newblock \bibinfo{address}{{Cambridge}}: \bibinfo{publisher}{Cambridge
  University Press}; \bibinfo{year}{2009}.
\newblock ISBN \bibinfo{isbn}{9780511976667}.
\newblock \DOIprefix\doi{10.1017/cbo9780511976667}.
%Type = Article
\bibitem[{Rayleigh(1870)}]{Rayleigh1870}
\bibinfo{author}{Rayleigh\xfnm[ J.W.]}.
\newblock \bibinfo{title}{In finding the correction for the open end of an
  organ-pipe}.
\newblock \bibinfo{journal}{Phil Trans}
  \bibinfo{year}{1870};\bibinfo{volume}{161}(\bibinfo{number}{77}).
%Type = Article
\bibitem[{Ritz(1908)}]{Ritz1908}
\bibinfo{author}{Ritz\xfnm[ W.]}.
\newblock \bibinfo{title}{{\"{U}}ber eine neue methode zur l{\"{o}}sung
  gewisser variationsprobleme der mathematischen physik}.
\newblock \bibinfo{journal}{J reine angew Math}
  \bibinfo{year}{1908};\bibinfo{volume}{135}:\bibinfo{pages}{1--61}.
%Type = Incollection
\bibitem[{Arfken and Weber(1985)}]{Arfken1985}
\bibinfo{author}{Arfken\xfnm[ G.B.]}, \bibinfo{author}{Weber\xfnm[ H.J.]}.
\newblock \bibinfo{title}{Rayleigh-ritz variational technique}.
\newblock In: \bibinfo{booktitle}{Mathematical Methods for Physicists, 3rd ed}.
  \bibinfo{publisher}{Orlando, FL: Academic Press}.
\newblock ISBN \bibinfo{isbn}{9781483277820}; \bibinfo{year}{1985}, p.
  \bibinfo{pages}{957--961}.
%Type = Article
\bibitem[{Lee et~al.(2018{\natexlab{a}})Lee, Huggins, Head-Gordon and
  Whaley}]{Lee2019}
\bibinfo{author}{Lee\xfnm[ J.]}, \bibinfo{author}{Huggins\xfnm[ W.J.]},
  \bibinfo{author}{Head-Gordon\xfnm[ M.]}, \bibinfo{author}{Whaley\xfnm[
  K.B.]}.
\newblock \bibinfo{title}{Generalized unitary coupled cluster wave functions
  for quantum computation}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2018}{\natexlab{a}};\bibinfo{volume}{15}(\bibinfo{number}{1}):\bibinfo{pages}{311--324}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.8b01004}.
%Type = Book
\bibitem[{Szabo and Ostlund(1996)}]{Szabo1996}
\bibinfo{author}{Szabo\xfnm[ A.]}, \bibinfo{author}{Ostlund\xfnm[ N.]}.
\newblock \bibinfo{title}{Modern Quantum Chemistry: Introduction to Advanced
  Electronic Structure Theory}.
\newblock Dover Books on Chemistry; \bibinfo{publisher}{Dover Publications};
  \bibinfo{year}{1996}.
\newblock ISBN \bibinfo{isbn}{9780486691862}.
%Type = Article
\bibitem[{Wecker et~al.(2015{\natexlab{a}})Wecker, Hastings and
  Troyer}]{Wecker2015}
\bibinfo{author}{Wecker\xfnm[ D.]}, \bibinfo{author}{Hastings\xfnm[ M.B.]},
  \bibinfo{author}{Troyer\xfnm[ M.]}.
\newblock \bibinfo{title}{Progress towards practical quantum variational
  algorithms}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2015}{\natexlab{a}};\bibinfo{volume}{92}(\bibinfo{number}{4}):\bibinfo{pages}{042303}.
\newblock \DOIprefix\doi{10.1103/physreva.92.042303}.
%Type = Misc
\bibitem[{Elfving et~al.(2020)Elfving, Broer, Webber, Gavartin, Halls, Lorton
  et~al.}]{Elfving2020}
\bibinfo{author}{Elfving\xfnm[ V.E.]}, \bibinfo{author}{Broer\xfnm[ B.W.]},
  \bibinfo{author}{Webber\xfnm[ M.]}, \bibinfo{author}{Gavartin\xfnm[ J.]},
  \bibinfo{author}{Halls\xfnm[ M.D.]}, \bibinfo{author}{Lorton\xfnm[ K.P.]},
  et~al.
\newblock \bibinfo{title}{How will quantum computers provide an industrially
  relevant computational advantage in quantum chemistry?}
\newblock \bibinfo{year}{2020}.
\newblock \href{http://arxiv.org/abs/2009.12472v1}{\tt arXiv:2009.12472v1}.
%Type = Article
\bibitem[{K{\"u}hn et~al.(2019)K{\"u}hn, Zanker, Deglmann, Marthaler and
  Wei{\ss}}]{Kuhn2019}
\bibinfo{author}{K{\"u}hn\xfnm[ M.]}, \bibinfo{author}{Zanker\xfnm[ S.]},
  \bibinfo{author}{Deglmann\xfnm[ P.]}, \bibinfo{author}{Marthaler\xfnm[ M.]},
  \bibinfo{author}{Wei{\ss}\xfnm[ H.]}.
\newblock \bibinfo{title}{Accuracy and resource estimations for quantum
  chemistry on a near-term quantum computer}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2019};\bibinfo{volume}{15}(\bibinfo{number}{9}):\bibinfo{pages}{4764--4780}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.9b00236}.
%Type = Misc
\bibitem[{Gonthier et~al.(2020)Gonthier, Radin, Buda, Doskocil, Abuan and
  Romero}]{Gonthier2020}
\bibinfo{author}{Gonthier\xfnm[ J.F.]}, \bibinfo{author}{Radin\xfnm[ M.D.]},
  \bibinfo{author}{Buda\xfnm[ C.]}, \bibinfo{author}{Doskocil\xfnm[ E.J.]},
  \bibinfo{author}{Abuan\xfnm[ C.M.]}, \bibinfo{author}{Romero\xfnm[ J.]}.
\newblock \bibinfo{title}{Identifying challenges towards practical quantum
  advantage through resource estimation: the measurement roadblock in the
  variational quantum eigensolver}.
\newblock \bibinfo{year}{2020}.
\newblock \href{http://arxiv.org/abs/2012.04001v1}{\tt arXiv:2012.04001v1}.
%Type = Article
\bibitem[{McClean et~al.(2018)McClean, Boixo, Smelyanskiy, Babbush and
  Neven}]{McClean2018}
\bibinfo{author}{McClean\xfnm[ J.R.]}, \bibinfo{author}{Boixo\xfnm[ S.]},
  \bibinfo{author}{Smelyanskiy\xfnm[ V.N.]}, \bibinfo{author}{Babbush\xfnm[
  R.]}, \bibinfo{author}{Neven\xfnm[ H.]}.
\newblock \bibinfo{title}{Barren plateaus in quantum neural network training
  landscapes}.
\newblock \bibinfo{journal}{Nature Communications}
  \bibinfo{year}{2018};\bibinfo{volume}{9}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1038/s41467-018-07090-4}.
%Type = Article
\bibitem[{Cerezo et~al.(2021{\natexlab{a}})Cerezo, Sone, Volkoff, Cincio and
  Coles}]{Cerezo2021_BP}
\bibinfo{author}{Cerezo\xfnm[ M.]}, \bibinfo{author}{Sone\xfnm[ A.]},
  \bibinfo{author}{Volkoff\xfnm[ T.]}, \bibinfo{author}{Cincio\xfnm[ L.]},
  \bibinfo{author}{Coles\xfnm[ P.J.]}.
\newblock \bibinfo{title}{Cost function dependent barren plateaus in shallow
  parametrized quantum circuits}.
\newblock \bibinfo{journal}{Nature Communications}
  \bibinfo{year}{2021}{\natexlab{a}};\bibinfo{volume}{12}(\bibinfo{number}{1}):\bibinfo{pages}{1791}.
\newblock \DOIprefix\doi{10.1038/s41467-021-21728-w}.
%Type = Article
\bibitem[{Holmes et~al.(2016{\natexlab{a}})Holmes, Changlani and
  Umrigar}]{Holmes2016}
\bibinfo{author}{Holmes\xfnm[ A.A.]}, \bibinfo{author}{Changlani\xfnm[ H.J.]},
  \bibinfo{author}{Umrigar\xfnm[ C.J.]}.
\newblock \bibinfo{title}{Efficient heat-bath sampling in fock space}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2016}{\natexlab{a}};\bibinfo{volume}{12}(\bibinfo{number}{4}):\bibinfo{pages}{1561--1571}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.5b01170}.
%Type = Misc
\bibitem[{Marrero et~al.(2020)Marrero, Kieferová and Wiebe}]{OrtizMarrero2020}
\bibinfo{author}{Marrero\xfnm[ C.O.]}, \bibinfo{author}{Kieferová\xfnm[ M.]},
  \bibinfo{author}{Wiebe\xfnm[ N.]}.
\newblock \bibinfo{title}{Entanglement induced barren plateaus}.
\newblock \bibinfo{year}{2020}.
\newblock \href{http://arxiv.org/abs/2010.15968v2}{\tt arXiv:2010.15968v2}.
%Type = Article
\bibitem[{Patti et~al.(2021{\natexlab{a}})Patti, Najafi, Gao and
  Yelin}]{Patti2021}
\bibinfo{author}{Patti\xfnm[ T.L.]}, \bibinfo{author}{Najafi\xfnm[ K.]},
  \bibinfo{author}{Gao\xfnm[ X.]}, \bibinfo{author}{Yelin\xfnm[ S.F.]}.
\newblock \bibinfo{title}{Entanglement devised barren plateau mitigation}.
\newblock \bibinfo{journal}{Physical Review Research}
  \bibinfo{year}{2021}{\natexlab{a}};\bibinfo{volume}{3}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physrevresearch.3.033090}.
%Type = Article
\bibitem[{Uvarov and Biamonte(2021)}]{Uvarov2020}
\bibinfo{author}{Uvarov\xfnm[ A.V.]}, \bibinfo{author}{Biamonte\xfnm[ J.D.]}.
\newblock \bibinfo{title}{On barren plateaus and cost function locality in
  variational quantum algorithms}.
\newblock \bibinfo{journal}{Journal of Physics A: Mathematical and Theoretical}
  \bibinfo{year}{2021};\bibinfo{volume}{54}(\bibinfo{number}{24}):\bibinfo{pages}{245301}.
\newblock \DOIprefix\doi{10.1088/1751-8121/abfac7}.
  \href{http://arxiv.org/abs/2011.10530v1}{\tt arXiv:2011.10530v1};
  \bibinfo{note}{journal of Physics A: Mathematical and Theoretical 54 (24),
  245301 (2021)}.
%Type = Misc
\bibitem[{Sharma et~al.(2020)Sharma, Cerezo, Cincio and Coles}]{Sharma2020}
\bibinfo{author}{Sharma\xfnm[ K.]}, \bibinfo{author}{Cerezo\xfnm[ M.]},
  \bibinfo{author}{Cincio\xfnm[ L.]}, \bibinfo{author}{Coles\xfnm[ P.J.]}.
\newblock \bibinfo{title}{Trainability of dissipative perceptron-based quantum
  neural networks}.
\newblock \bibinfo{year}{2020}.
\newblock \href{http://arxiv.org/abs/2005.12458v1}{\tt arXiv:2005.12458v1}.
%Type = Article
\bibitem[{Bittel and Kliesch(2021)}]{Bittel2021}
\bibinfo{author}{Bittel\xfnm[ L.]}, \bibinfo{author}{Kliesch\xfnm[ M.]}.
\newblock \bibinfo{title}{Training variational quantum algorithms is
  {NP}-hard}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2021};\bibinfo{volume}{127}(\bibinfo{number}{12}).
\newblock \DOIprefix\doi{10.1103/physrevlett.127.120502}.
  \href{http://arxiv.org/abs/2101.07267v1}{\tt arXiv:2101.07267v1};
  \bibinfo{note}{phys. Rev. Lett. 127, 120502 (2021)}.
%Type = Article
\bibitem[{Fontana et~al.(2021)Fontana, Fitzpatrick, Ramo, Duncan and
  Rungger}]{Enrico2021EvaluatingNoiseResilience}
\bibinfo{author}{Fontana\xfnm[ E.]}, \bibinfo{author}{Fitzpatrick\xfnm[ N.]},
  \bibinfo{author}{Ramo\xfnm[ D.M.]}, \bibinfo{author}{Duncan\xfnm[ R.]},
  \bibinfo{author}{Rungger\xfnm[ I.]}.
\newblock \bibinfo{title}{Evaluating the noise resilience of variational
  quantum algorithms}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2021};\bibinfo{volume}{104}(\bibinfo{number}{2}).
\newblock \DOIprefix\doi{10.1103/physreva.104.022403}.
%Type = Misc
\bibitem[{Fontana et~al.(2020)Fontana, Cerezo, Arrasmith, Rungger and
  Coles}]{Enrico2020NoiseInducedBreakingOfSymmetries}
\bibinfo{author}{Fontana\xfnm[ E.]}, \bibinfo{author}{Cerezo\xfnm[ M.]},
  \bibinfo{author}{Arrasmith\xfnm[ A.]}, \bibinfo{author}{Rungger\xfnm[ I.]},
  \bibinfo{author}{Coles\xfnm[ P.J.]}.
\newblock \bibinfo{title}{Optimizing parametrized quantum circuits via
  noise-induced breaking of symmetries}.
\newblock \bibinfo{year}{2020}.
\newblock \href{http://arxiv.org/abs/2011.08763}{\tt arXiv:2011.08763}.
%Type = Misc
\bibitem[{Takagi et~al.(2021)Takagi, Endo, Minagawa and
  Gu}]{RyujiFundamentalLimits2021}
\bibinfo{author}{Takagi\xfnm[ R.]}, \bibinfo{author}{Endo\xfnm[ S.]},
  \bibinfo{author}{Minagawa\xfnm[ S.]}, \bibinfo{author}{Gu\xfnm[ M.]}.
\newblock \bibinfo{title}{Fundamental limits of quantum error mitigation}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2109.04457v2}{\tt arXiv:2109.04457v2}.
%Type = Misc
\bibitem[{Whitfield et~al.(2022)Whitfield, Yan, Wang, Heath and
  Harrison}]{Whitfield2022}
\bibinfo{author}{Whitfield\xfnm[ J.D.]}, \bibinfo{author}{Yan\xfnm[ J.]},
  \bibinfo{author}{Wang\xfnm[ W.]}, \bibinfo{author}{Heath\xfnm[ J.T.]},
  \bibinfo{author}{Harrison\xfnm[ B.]}.
\newblock \bibinfo{title}{Quantum computing 2022}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2201.09877}.
  \DOIprefix\doi{10.48550/ARXIV.2201.09877}.
%Type = Article
\bibitem[{McArdle et~al.(2020)McArdle, Endo, Aspuru-Guzik, Benjamin and
  Yuan}]{mcardleQuantumComputationalChemistry2018}
\bibinfo{author}{McArdle\xfnm[ S.]}, \bibinfo{author}{Endo\xfnm[ S.]},
  \bibinfo{author}{Aspuru-Guzik\xfnm[ A.]}, \bibinfo{author}{Benjamin\xfnm[
  S.C.]}, \bibinfo{author}{Yuan\xfnm[ X.]}.
\newblock \bibinfo{title}{Quantum computational chemistry}.
\newblock \bibinfo{journal}{Reviews of Modern Physics}
  \bibinfo{year}{2020};\bibinfo{volume}{92}(\bibinfo{number}{1}):\bibinfo{pages}{15003--15003}.
\newblock \DOIprefix\doi{10.1103/revmodphys.92.015003}.
%Type = Article
\bibitem[{Bauer et~al.(2020)Bauer, Bravyi, Motta and
  Chan}]{bauerQuantumAlgorithmsQuantum2020}
\bibinfo{author}{Bauer\xfnm[ B.]}, \bibinfo{author}{Bravyi\xfnm[ S.]},
  \bibinfo{author}{Motta\xfnm[ M.]}, \bibinfo{author}{Chan\xfnm[ G.K.L.]}.
\newblock \bibinfo{title}{Quantum algorithms for quantum chemistry and quantum
  materials science}.
\newblock \bibinfo{journal}{Chemical Reviews}
  \bibinfo{year}{2020};\bibinfo{volume}{120}(\bibinfo{number}{22}):\bibinfo{pages}{12685--12717}.
\newblock \DOIprefix\doi{10.1021/acs.chemrev.9b00829}.
%Type = Misc
\bibitem[{Motta and Rice(2021)}]{Motta2021_review}
\bibinfo{author}{Motta\xfnm[ M.]}, \bibinfo{author}{Rice\xfnm[ J.]}.
\newblock \bibinfo{title}{Emerging quantum computing algorithms for quantum
  chemistry}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2109.02873v1}{\tt arXiv:2109.02873v1}.
%Type = Article
\bibitem[{Cerezo et~al.(2021{\natexlab{b}})Cerezo, Arrasmith, Babbush,
  Benjamin, Endo, Fujii et~al.}]{cerezoVariationalQuantumAlgorithms2020}
\bibinfo{author}{Cerezo\xfnm[ M.]}, \bibinfo{author}{Arrasmith\xfnm[ A.]},
  \bibinfo{author}{Babbush\xfnm[ R.]}, \bibinfo{author}{Benjamin\xfnm[ S.C.]},
  \bibinfo{author}{Endo\xfnm[ S.]}, \bibinfo{author}{Fujii\xfnm[ K.]}, et~al.
\newblock \bibinfo{title}{Variational quantum algorithms}.
\newblock \bibinfo{journal}{Nature Reviews Physics}
  \bibinfo{year}{2021}{\natexlab{b}};\bibinfo{volume}{3}(\bibinfo{number}{9}):\bibinfo{pages}{625--644}.
\newblock \DOIprefix\doi{10.1038/s42254-021-00348-9}.
%Type = Misc
\bibitem[{Bharti et~al.(2021)Bharti, Cervera-Lierta, Kyaw, Haug, Alperin-Lea,
  Anand et~al.}]{Bharti2021_review}
\bibinfo{author}{Bharti\xfnm[ K.]}, \bibinfo{author}{Cervera-Lierta\xfnm[ A.]},
  \bibinfo{author}{Kyaw\xfnm[ T.H.]}, \bibinfo{author}{Haug\xfnm[ T.]},
  \bibinfo{author}{Alperin-Lea\xfnm[ S.]}, \bibinfo{author}{Anand\xfnm[ A.]},
  et~al.
\newblock \bibinfo{title}{Noisy intermediate-scale quantum (nisq) algorithms}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2101.08448v2}{\tt arXiv:2101.08448v2}.
%Type = Misc
\bibitem[{Fedorov et~al.(2021)Fedorov, Peng, Govind and Alexeev}]{Fedorov2021}
\bibinfo{author}{Fedorov\xfnm[ D.A.]}, \bibinfo{author}{Peng\xfnm[ B.]},
  \bibinfo{author}{Govind\xfnm[ N.]}, \bibinfo{author}{Alexeev\xfnm[ Y.]}.
\newblock \bibinfo{title}{Vqe method: A short survey and recent developments}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2103.08505v1}{\tt arXiv:2103.08505v1}.
%Type = Misc
\bibitem[{Anand et~al.(2021)Anand, Schleich, Alperin-Lea, Jensen, Sim,
  Díaz-Tinoco et~al.}]{Anand2021_review}
\bibinfo{author}{Anand\xfnm[ A.]}, \bibinfo{author}{Schleich\xfnm[ P.]},
  \bibinfo{author}{Alperin-Lea\xfnm[ S.]}, \bibinfo{author}{Jensen\xfnm[
  P.W.K.]}, \bibinfo{author}{Sim\xfnm[ S.]},
  \bibinfo{author}{Díaz-Tinoco\xfnm[ M.]}, et~al.
\newblock \bibinfo{title}{A quantum computing view on unitary coupled cluster
  theory}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2109.15176v1}{\tt arXiv:2109.15176v1}.
%Type = Article
\bibitem[{Parr(1990)}]{Parr1990}
\bibinfo{author}{Parr\xfnm[ R.G.]}.
\newblock \bibinfo{title}{On the genesis of a theory}.
\newblock \bibinfo{journal}{International Journal of Quantum Chemistry}
  \bibinfo{year}{1990};\bibinfo{volume}{37}(\bibinfo{number}{4}):\bibinfo{pages}{327--347}.
\newblock \DOIprefix\doi{10.1002/qua.560370407}.
%Type = Article
\bibitem[{Friesner(2005)}]{Friesner2005}
\bibinfo{author}{Friesner\xfnm[ R.A.]}.
\newblock \bibinfo{title}{Ab initio quantum chemistry: Methodology and
  applications}.
\newblock \bibinfo{journal}{PNAS}
  \bibinfo{year}{2005};\bibinfo{volume}{102}(\bibinfo{number}{19}):\bibinfo{pages}{6648--6653}.
\newblock \DOIprefix\doi{10.1073/pnas.0408036102}.
%Type = Book
\bibitem[{Jensen(2017)}]{Jensen2017}
\bibinfo{author}{Jensen\xfnm[ F.]}.
\newblock \bibinfo{title}{Introduction to computational chemistry}.
\newblock \bibinfo{address}{Chichester, UK Hoboken, NJ}:
  \bibinfo{publisher}{Wiley}; \bibinfo{year}{2017}.
\newblock ISBN \bibinfo{isbn}{978-1-118-82595-2}.
%Type = Book
\bibitem[{Nemoshkalenko(1998)}]{nemoshkalenko1998computational}
\bibinfo{author}{Nemoshkalenko\xfnm[ V.]}.
\newblock \bibinfo{title}{Computational Methods in Solid State Physics}.
\newblock \bibinfo{address}{Amsterdam}: \bibinfo{publisher}{Gordon and Breach
  Science Publishers}; \bibinfo{year}{1998}.
\newblock ISBN \bibinfo{isbn}{9789056990947}.
%Type = Book
\bibitem[{Martin(2004)}]{Martin2004}
\bibinfo{author}{Martin\xfnm[ R.M.]}.
\newblock \bibinfo{title}{Electronic Structure}.
\newblock \bibinfo{publisher}{Cambridge University Press};
  \bibinfo{year}{2004}.
\newblock \DOIprefix\doi{10.1017/cbo9780511805769}.
%Type = Book
\bibitem[{Marder(2010)}]{Marder2010}
\bibinfo{author}{Marder\xfnm[ M.P.]}.
\newblock \bibinfo{title}{Condensed Matter Physics}.
\newblock \bibinfo{publisher}{John Wiley {\&} Sons, Inc.};
  \bibinfo{year}{2010}.
\newblock \DOIprefix\doi{10.1002/9780470949955}.
%Type = Book
\bibitem[{Clark and Ristig(1997)}]{Clark1997}
\bibinfo{editor}{Clark\xfnm[ J.W.]}, \bibinfo{editor}{Ristig\xfnm[ M.L.]},
  editors.
\newblock \bibinfo{title}{Theory of Spin Lattices and Lattice Gauge Models}.
\newblock \bibinfo{publisher}{Springer Berlin Heidelberg};
  \bibinfo{year}{1997}.
\newblock \DOIprefix\doi{10.1007/bfb0104298}.
%Type = Article
\bibitem[{Pauli(1925)}]{Pauli1925}
\bibinfo{author}{Pauli\xfnm[ W.]}.
\newblock \bibinfo{title}{{\"{U}}ber den zusammenhang des abschlusses der
  elektronengruppen im atom mit der komplexstruktur der spektren}.
\newblock \bibinfo{journal}{Zeitschrift f{\"u}r Physik}
  \bibinfo{year}{1925};\bibinfo{volume}{31}(\bibinfo{number}{1}):\bibinfo{pages}{765--783}.
\newblock \DOIprefix\doi{10.1007/bf02980631}.
%Type = Book
\bibitem[{Griffiths and Griffiths(2005)}]{griffiths2005introduction}
\bibinfo{author}{Griffiths\xfnm[ D.]}, \bibinfo{author}{Griffiths\xfnm[ P.]}.
\newblock \bibinfo{title}{Introduction to Quantum Mechanics}.
\newblock Pearson International Edition; \bibinfo{publisher}{{Pearson Prentice
  Hall}}; \bibinfo{year}{2005}.
\newblock ISBN \bibinfo{isbn}{978-0-13-111892-8}.
\newblock \URLprefix \url{https://books.google.co.uk/books?id=-BsvAQAAIAAJ}.
%Type = Article
\bibitem[{Jordan and Wigner(1928)}]{Jordan1928}
\bibinfo{author}{Jordan\xfnm[ P.]}, \bibinfo{author}{Wigner\xfnm[ E.]}.
\newblock \bibinfo{title}{{\"U}ber das paulische {\"a}quivalenzverbot}.
\newblock \bibinfo{journal}{Zeitschrift f{\"u}r Physik}
  \bibinfo{year}{1928};\bibinfo{volume}{47}(\bibinfo{number}{9}):\bibinfo{pages}{631--651}.
\newblock \DOIprefix\doi{10.1007/BF01331938}.
%Type = Article
\bibitem[{Rubin et~al.(2018)Rubin, Babbush and McClean}]{Rubin2018}
\bibinfo{author}{Rubin\xfnm[ N.C.]}, \bibinfo{author}{Babbush\xfnm[ R.]},
  \bibinfo{author}{McClean\xfnm[ J.]}.
\newblock \bibinfo{title}{Application of fermionic marginal constraints to
  hybrid quantum algorithms}.
\newblock \bibinfo{journal}{New Journal of Physics}
  \bibinfo{year}{2018};\bibinfo{volume}{20}(\bibinfo{number}{5}):\bibinfo{pages}{053020}.
\newblock \DOIprefix\doi{10.1088/1367-2630/aab919}.
%Type = Misc
\bibitem[{Arrasmith et~al.(2020{\natexlab{a}})Arrasmith, Cincio, Somma and
  Coles}]{Arrasmith2020}
\bibinfo{author}{Arrasmith\xfnm[ A.]}, \bibinfo{author}{Cincio\xfnm[ L.]},
  \bibinfo{author}{Somma\xfnm[ R.D.]}, \bibinfo{author}{Coles\xfnm[ P.J.]}.
\newblock \bibinfo{title}{Operator sampling for shot-frugal optimization in
  variational algorithms}.
\newblock \bibinfo{year}{2020}{\natexlab{a}}.
\newblock \href{http://arxiv.org/abs/2004.06252v1}{\tt arXiv:2004.06252v1}.
%Type = Misc
\bibitem[{Gokhale et~al.(2019)Gokhale, Angiuli, Ding, Gui, Tomesh, Suchara
  et~al.}]{Gokhale2019_long}
\bibinfo{author}{Gokhale\xfnm[ P.]}, \bibinfo{author}{Angiuli\xfnm[ O.]},
  \bibinfo{author}{Ding\xfnm[ Y.]}, \bibinfo{author}{Gui\xfnm[ K.]},
  \bibinfo{author}{Tomesh\xfnm[ T.]}, \bibinfo{author}{Suchara\xfnm[ M.]},
  et~al.
\newblock \bibinfo{title}{Minimizing state preparations in variational quantum
  eigensolver by partitioning into commuting families}.
\newblock \bibinfo{year}{2019}.
\newblock \href{http://arxiv.org/abs/1907.13623v1}{\tt arXiv:1907.13623v1}.
%Type = Article
\bibitem[{Hamamura and Imamichi(2020)}]{Hamamura2020}
\bibinfo{author}{Hamamura\xfnm[ I.]}, \bibinfo{author}{Imamichi\xfnm[ T.]}.
\newblock \bibinfo{title}{Efficient evaluation of quantum observables using
  entangled measurements}.
\newblock \bibinfo{journal}{npj Quantum Information}
  \bibinfo{year}{2020};\bibinfo{volume}{6}(\bibinfo{number}{1}):\bibinfo{pages}{56}.
\newblock \DOIprefix\doi{10.1038/s41534-020-0284-2}.
%Type = Article
\bibitem[{Huggins et~al.(2021)Huggins, McClean, Rubin, Jiang, Wiebe, Whaley
  et~al.}]{Huggins2021}
\bibinfo{author}{Huggins\xfnm[ W.J.]}, \bibinfo{author}{McClean\xfnm[ J.R.]},
  \bibinfo{author}{Rubin\xfnm[ N.C.]}, \bibinfo{author}{Jiang\xfnm[ Z.]},
  \bibinfo{author}{Wiebe\xfnm[ N.]}, \bibinfo{author}{Whaley\xfnm[ K.B.]},
  et~al.
\newblock \bibinfo{title}{Efficient and noise resilient measurements for
  quantum chemistry on near-term quantum computers}.
\newblock \bibinfo{journal}{npj Quantum Information}
  \bibinfo{year}{2021};\bibinfo{volume}{7}(\bibinfo{number}{1}):\bibinfo{pages}{23}.
\newblock \DOIprefix\doi{10.1038/s41534-020-00341-7}.
%Type = Article
\bibitem[{Torlai et~al.(2020)Torlai, Mazzola, Carleo and
  Mezzacapo}]{Torlai2020}
\bibinfo{author}{Torlai\xfnm[ G.]}, \bibinfo{author}{Mazzola\xfnm[ G.]},
  \bibinfo{author}{Carleo\xfnm[ G.]}, \bibinfo{author}{Mezzacapo\xfnm[ A.]}.
\newblock \bibinfo{title}{Precise measurement of quantum observables with
  neural-network estimators}.
\newblock \bibinfo{journal}{Physical Review Research}
  \bibinfo{year}{2020};\bibinfo{volume}{2}(\bibinfo{number}{2}):\bibinfo{pages}{022060(R)}.
\newblock \DOIprefix\doi{10.1103/physrevresearch.2.022060}.
%Type = Article
\bibitem[{Huang et~al.(2020)Huang, Kueng and Preskill}]{Huang2020}
\bibinfo{author}{Huang\xfnm[ H.Y.]}, \bibinfo{author}{Kueng\xfnm[ R.]},
  \bibinfo{author}{Preskill\xfnm[ J.]}.
\newblock \bibinfo{title}{Predicting many properties of a quantum system from
  very few measurements}.
\newblock \bibinfo{journal}{Nature Physics}
  \bibinfo{year}{2020};\bibinfo{volume}{16}(\bibinfo{number}{10}):\bibinfo{pages}{1050--1057}.
\newblock \DOIprefix\doi{10.1038/s41567-020-0932-7}.
%Type = Misc
\bibitem[{Holmes et~al.(2021)Holmes, Sharma, Cerezo and Coles}]{Holmes2021}
\bibinfo{author}{Holmes\xfnm[ Z.]}, \bibinfo{author}{Sharma\xfnm[ K.]},
  \bibinfo{author}{Cerezo\xfnm[ M.]}, \bibinfo{author}{Coles\xfnm[ P.J.]}.
\newblock \bibinfo{title}{Connecting ansatz expressibility to gradient
  magnitudes and barren plateaus}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2101.02138v1}{\tt arXiv:2101.02138v1}.
%Type = Article
\bibitem[{Nakaji and Yamamoto(2021)}]{Nakaji2021}
\bibinfo{author}{Nakaji\xfnm[ K.]}, \bibinfo{author}{Yamamoto\xfnm[ N.]}.
\newblock \bibinfo{title}{Expressibility of the alternating layered ansatz for
  quantum computation}.
\newblock \bibinfo{journal}{Quantum}
  \bibinfo{year}{2021};\bibinfo{volume}{5}:\bibinfo{pages}{434}.
\newblock \DOIprefix\doi{10.22331/q-2021-04-19-434}.
%Type = Misc
\bibitem[{Crooks(2019)}]{crooks_gradients_2019}
\bibinfo{author}{Crooks\xfnm[ G.E.]}.
\newblock \bibinfo{title}{Gradients of parameterized quantum gates using the
  parameter-shift rule and gate decomposition}.
\newblock \bibinfo{year}{2019}.
\newblock \href{http://arxiv.org/abs/1905.13311v1}{\tt arXiv:1905.13311v1}.
%Type = Misc
\bibitem[{Izmaylov et~al.(2021)Izmaylov, Lang and Yen}]{izmaylov_analytic_2021}
\bibinfo{author}{Izmaylov\xfnm[ A.F.]}, \bibinfo{author}{Lang\xfnm[ R.A.]},
  \bibinfo{author}{Yen\xfnm[ T.C.]}.
\newblock \bibinfo{title}{Analytic gradients in variational quantum algorithms:
  Algebraic extensions of the parameter-shift rule to general unitary
  transformations}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2107.08131v2}{\tt arXiv:2107.08131v2}.
%Type = Misc
\bibitem[{Haug et~al.(2021)Haug, Bharti and Kim}]{haug_capacity_2021}
\bibinfo{author}{Haug\xfnm[ T.]}, \bibinfo{author}{Bharti\xfnm[ K.]},
  \bibinfo{author}{Kim\xfnm[ M.S.]}.
\newblock \bibinfo{title}{Capacity and quantum geometry of parametrized quantum
  circuits}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2102.01659v2}{\tt arXiv:2102.01659v2}.
%Type = Misc
\bibitem[{Haug and Kim(2021)}]{haug_optimal_2021}
\bibinfo{author}{Haug\xfnm[ T.]}, \bibinfo{author}{Kim\xfnm[ M.S.]}.
\newblock \bibinfo{title}{Optimal training of variational quantum algorithms
  without barren plateaus}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2104.14543v3}{\tt arXiv:2104.14543v3}.
%Type = Article
\bibitem[{Nakanishi et~al.(2020)Nakanishi, Fujii and
  Todo}]{nakanishi_sequential_2020}
\bibinfo{author}{Nakanishi\xfnm[ K.M.]}, \bibinfo{author}{Fujii\xfnm[ K.]},
  \bibinfo{author}{Todo\xfnm[ S.]}.
\newblock \bibinfo{title}{Sequential minimal optimization for quantum-classical
  hybrid algorithms}.
\newblock \bibinfo{journal}{Physical Review Research}
  \bibinfo{year}{2020};\bibinfo{volume}{2}(\bibinfo{number}{4}).
\newblock \DOIprefix\doi{10.1103/physrevresearch.2.043158}.
%Type = Article
\bibitem[{Ostaszewski et~al.(2021)Ostaszewski, Grant and
  Benedetti}]{ostaszewskiStructureOptimizationParameterized2021}
\bibinfo{author}{Ostaszewski\xfnm[ M.]}, \bibinfo{author}{Grant\xfnm[ E.]},
  \bibinfo{author}{Benedetti\xfnm[ M.]}.
\newblock \bibinfo{title}{Structure optimization for parameterized quantum
  circuits}.
\newblock \bibinfo{journal}{Quantum}
  \bibinfo{year}{2021};\bibinfo{volume}{5}:\bibinfo{pages}{391}.
\newblock \DOIprefix\doi{10.22331/q-2021-01-28-391}.
  \href{http://arxiv.org/abs/1905.09692}{\tt arXiv:1905.09692}.
%Type = Misc
\bibitem[{Koczor and Benjamin(2019)}]{koczor_quantum_2020}
\bibinfo{author}{Koczor\xfnm[ B.]}, \bibinfo{author}{Benjamin\xfnm[ S.C.]}.
\newblock \bibinfo{title}{Quantum natural gradient generalised to non-unitary
  circuits}.
\newblock \bibinfo{year}{2019}.
\newblock \href{http://arxiv.org/abs/1912.08660v4}{\tt arXiv:1912.08660v4}.
%Type = Article
\bibitem[{Hartree(1928)}]{Hartree1928}
\bibinfo{author}{Hartree\xfnm[ D.R.]}.
\newblock \bibinfo{title}{The wave mechanics of an atom with a non-coulomb
  central field. part {II}. some results and discussion}.
\newblock \bibinfo{journal}{Math Proc Camb Philos Soc}
  \bibinfo{year}{1928};\bibinfo{volume}{24}(\bibinfo{number}{1}):\bibinfo{pages}{111--132}.
\newblock \DOIprefix\doi{10.1017/s0305004100011920}.
%Type = Article
\bibitem[{Slater(1928)}]{Slater1928}
\bibinfo{author}{Slater\xfnm[ J.C.]}.
\newblock \bibinfo{title}{The self consistent field and the structure of
  atoms}.
\newblock \bibinfo{journal}{PhysRev}
  \bibinfo{year}{1928};\bibinfo{volume}{32}(\bibinfo{number}{3}):\bibinfo{pages}{339--348}.
\newblock \DOIprefix\doi{10.1103/physrev.32.339}.
%Type = Article
\bibitem[{Gaunt(1928)}]{Gaunt1928}
\bibinfo{author}{Gaunt\xfnm[ J.A.]}.
\newblock \bibinfo{title}{A theory of hartree{\textquotesingle}s atomic
  fields}.
\newblock \bibinfo{journal}{Math Proc Camb Philos Soc}
  \bibinfo{year}{1928};\bibinfo{volume}{24}(\bibinfo{number}{2}):\bibinfo{pages}{328--342}.
\newblock \DOIprefix\doi{10.1017/s0305004100015851}.
%Type = Article
\bibitem[{Hartree(1935)}]{Hartree1935}
\bibinfo{author}{Hartree\xfnm[ D.R.]}.
\newblock \bibinfo{title}{Self-consistent field, with exchange, for beryllium}.
\newblock \bibinfo{journal}{Proc Royal Soc Lond A 1}
  \bibinfo{year}{1935};\bibinfo{volume}{150}(\bibinfo{number}{869}):\bibinfo{pages}{9--33}.
\newblock \DOIprefix\doi{10.1098/rspa.1935.0085}.
%Type = Article
\bibitem[{Grant et~al.(2019)Grant, Wossnig, Ostaszewski and
  Benedetti}]{Grant2019}
\bibinfo{author}{Grant\xfnm[ E.]}, \bibinfo{author}{Wossnig\xfnm[ L.]},
  \bibinfo{author}{Ostaszewski\xfnm[ M.]}, \bibinfo{author}{Benedetti\xfnm[
  M.]}.
\newblock \bibinfo{title}{An initialization strategy for addressing barren
  plateaus in parametrized quantum circuits}.
\newblock \bibinfo{journal}{Quantum}
  \bibinfo{year}{2019};\bibinfo{volume}{3}:\bibinfo{pages}{214}.
\newblock \DOIprefix\doi{10.22331/q-2019-12-09-214}.
%Type = Misc
\bibitem[{Farhi et~al.(2014)Farhi, Goldstone and Gutmann}]{Farhi2014}
\bibinfo{author}{Farhi\xfnm[ E.]}, \bibinfo{author}{Goldstone\xfnm[ J.]},
  \bibinfo{author}{Gutmann\xfnm[ S.]}.
\newblock \bibinfo{title}{A quantum approximate optimization algorithm}.
\newblock \bibinfo{year}{2014}.
\newblock \href{http://arxiv.org/abs/1411.4028v1}{\tt arXiv:1411.4028v1}.
%Type = Misc
\bibitem[{Bravo-Prieto et~al.(2019)Bravo-Prieto, LaRose, Cerezo, Subasi, Cincio
  and Coles}]{BravoPrieto2019}
\bibinfo{author}{Bravo-Prieto\xfnm[ C.]}, \bibinfo{author}{LaRose\xfnm[ R.]},
  \bibinfo{author}{Cerezo\xfnm[ M.]}, \bibinfo{author}{Subasi\xfnm[ Y.]},
  \bibinfo{author}{Cincio\xfnm[ L.]}, \bibinfo{author}{Coles\xfnm[ P.J.]}.
\newblock \bibinfo{title}{Variational quantum linear solver}.
\newblock \bibinfo{year}{2019}.
\newblock \URLprefix \url{https://arxiv.org/abs/1909.05820}.
  \DOIprefix\doi{10.48550/ARXIV.1909.05820}.
%Type = Article
\bibitem[{Pellow-Jarman et~al.(2021)Pellow-Jarman, Sinayskiy, Pillay and
  Petruccione}]{Pellow-Jarman2021}
\bibinfo{author}{Pellow-Jarman\xfnm[ A.]}, \bibinfo{author}{Sinayskiy\xfnm[
  I.]}, \bibinfo{author}{Pillay\xfnm[ A.]}, \bibinfo{author}{Petruccione\xfnm[
  F.]}.
\newblock \bibinfo{title}{A comparison of various classical optimizers for a
  variational quantum linear solver}.
\newblock \bibinfo{journal}{Quantum Information Processing}
  \bibinfo{year}{2021};\bibinfo{volume}{20}(\bibinfo{number}{6}):\bibinfo{pages}{202}.
\newblock \DOIprefix\doi{10.1007/s11128-021-03140-x}.
%Type = Misc
\bibitem[{Kwak et~al.(2021)Kwak, Yun, Jung and Kim}]{Kwak2021}
\bibinfo{author}{Kwak\xfnm[ Y.]}, \bibinfo{author}{Yun\xfnm[ W.J.]},
  \bibinfo{author}{Jung\xfnm[ S.]}, \bibinfo{author}{Kim\xfnm[ J.]}.
\newblock \bibinfo{title}{Quantum neural networks: Concepts, applications, and
  challenges}.
\newblock \bibinfo{year}{2021}.
\newblock \URLprefix \url{https://arxiv.org/abs/2108.01468}.
  \DOIprefix\doi{10.48550/ARXIV.2108.01468}.
%Type = Misc
\bibitem[{García et~al.(2022)García, Cruz-Benito and
  García-Peñalvo}]{Garcia2022}
\bibinfo{author}{García\xfnm[ D.P.]}, \bibinfo{author}{Cruz-Benito\xfnm[ J.]},
  \bibinfo{author}{García-Peñalvo\xfnm[ F.J.]}.
\newblock \bibinfo{title}{Systematic literature review: Quantum machine
  learning and its applications}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2201.04093}.
  \DOIprefix\doi{10.48550/ARXIV.2201.04093}.
%Type = Article
\bibitem[{Abbas et~al.(2021)Abbas, Sutter, Zoufal, Lucchi, Figalli and
  Woerner}]{Abbas2021}
\bibinfo{author}{Abbas\xfnm[ A.]}, \bibinfo{author}{Sutter\xfnm[ D.]},
  \bibinfo{author}{Zoufal\xfnm[ C.]}, \bibinfo{author}{Lucchi\xfnm[ A.]},
  \bibinfo{author}{Figalli\xfnm[ A.]}, \bibinfo{author}{Woerner\xfnm[ S.]}.
\newblock \bibinfo{title}{The power of quantum neural networks}.
\newblock \bibinfo{journal}{Nature Computational Science}
  \bibinfo{year}{2021};\bibinfo{volume}{1}(\bibinfo{number}{6}):\bibinfo{pages}{403--409}.
\newblock \URLprefix \url{https://doi.org/10.1038/s43588-021-00084-1}.
  \DOIprefix\doi{10.1038/s43588-021-00084-1}.
%Type = Article
\bibitem[{Schuld and Killoran(2019)}]{Schuld2019}
\bibinfo{author}{Schuld\xfnm[ M.]}, \bibinfo{author}{Killoran\xfnm[ N.]}.
\newblock \bibinfo{title}{Quantum machine learning in feature hilbert spaces}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2019};\bibinfo{volume}{122}(\bibinfo{number}{4}).
\newblock \URLprefix \url{https://doi.org/10.1103/physrevlett.122.040504}.
  \DOIprefix\doi{10.1103/physrevlett.122.040504}.
%Type = Article
\bibitem[{Huang et~al.(2021{\natexlab{a}})Huang, Broughton, Mohseni, Babbush,
  Boixo, Neven et~al.}]{Huang2021_powerofdata}
\bibinfo{author}{Huang\xfnm[ H.Y.]}, \bibinfo{author}{Broughton\xfnm[ M.]},
  \bibinfo{author}{Mohseni\xfnm[ M.]}, \bibinfo{author}{Babbush\xfnm[ R.]},
  \bibinfo{author}{Boixo\xfnm[ S.]}, \bibinfo{author}{Neven\xfnm[ H.]}, et~al.
\newblock \bibinfo{title}{Power of data in quantum machine learning}.
\newblock \bibinfo{journal}{Nature Communications}
  \bibinfo{year}{2021}{\natexlab{a}};\bibinfo{volume}{12}(\bibinfo{number}{1}).
\newblock \URLprefix \url{https://doi.org/10.1038/s41467-021-22539-9}.
  \DOIprefix\doi{10.1038/s41467-021-22539-9}.
%Type = Misc
\bibitem[{Preskill(2012)}]{Preskill2013}
\bibinfo{author}{Preskill\xfnm[ J.]}.
\newblock \bibinfo{title}{Quantum computing and the entanglement frontier}.
\newblock \bibinfo{year}{2012}.
\newblock \href{http://arxiv.org/abs/1203.5813v3}{\tt arXiv:1203.5813v3}.
%Type = Misc
\bibitem[{Pednault et~al.(2019)Pednault, Gunnels, Nannicini, Horesh and
  Wisnieff}]{Pednault2021}
\bibinfo{author}{Pednault\xfnm[ E.]}, \bibinfo{author}{Gunnels\xfnm[ J.A.]},
  \bibinfo{author}{Nannicini\xfnm[ G.]}, \bibinfo{author}{Horesh\xfnm[ L.]},
  \bibinfo{author}{Wisnieff\xfnm[ R.]}.
\newblock \bibinfo{title}{Leveraging secondary storage to simulate deep
  54-qubit sycamore circuits}.
\newblock \bibinfo{year}{2019}.
\newblock \href{http://arxiv.org/abs/1910.09534v2}{\tt arXiv:1910.09534v2}.
%Type = Article
\bibitem[{Liu et~al.(2021{\natexlab{a}})Liu, Liu, Li, Fu, Yang, Song
  et~al.}]{Liu2021}
\bibinfo{author}{Liu\xfnm[ Y.A.]}, \bibinfo{author}{Liu\xfnm[ X.L.]},
  \bibinfo{author}{Li\xfnm[ F.N.]}, \bibinfo{author}{Fu\xfnm[ H.]},
  \bibinfo{author}{Yang\xfnm[ Y.]}, \bibinfo{author}{Song\xfnm[ J.]}, et~al.
\newblock \bibinfo{title}{Closing the “quantum supremacy” gap}.
\newblock \bibinfo{journal}{Proceedings of the International Conference for
  High Performance Computing, Networking, Storage and Analysis}
  \bibinfo{year}{2021}{\natexlab{a}};\DOIprefix\doi{10.1145/3458817.3487399}.
%Type = Misc
\bibitem[{Jaschke and Montangero(2022)}]{Jaschke2022}
\bibinfo{author}{Jaschke\xfnm[ D.]}, \bibinfo{author}{Montangero\xfnm[ S.]}.
\newblock \bibinfo{title}{Is quantum computing green? an estimate for an
  energy-efficiency quantum advantage}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2205.12092}.
  \DOIprefix\doi{10.48550/ARXIV.2205.12092}.
%Type = Article
\bibitem[{Barkoutsos et~al.(2018)Barkoutsos, Gonthier, Sokolov, Moll, Salis,
  Fuhrer et~al.}]{Barkoutsos2018}
\bibinfo{author}{Barkoutsos\xfnm[ P.K.]}, \bibinfo{author}{Gonthier\xfnm[
  J.F.]}, \bibinfo{author}{Sokolov\xfnm[ I.]}, \bibinfo{author}{Moll\xfnm[
  N.]}, \bibinfo{author}{Salis\xfnm[ G.]}, \bibinfo{author}{Fuhrer\xfnm[ A.]},
  et~al.
\newblock \bibinfo{title}{Quantum algorithms for electronic structure
  calculations: Particle-hole hamiltonian and optimized wave-function
  expansions}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2018};\bibinfo{volume}{98}(\bibinfo{number}{2}):\bibinfo{pages}{022322}.
\newblock \DOIprefix\doi{10.1103/physreva.98.022322}.
%Type = Article
\bibitem[{O'Malley et~al.(2016)O'Malley, Babbush, Kivlichan, Romero, McClean,
  Barends et~al.}]{OMalley2016}
\bibinfo{author}{O'Malley\xfnm[ P.]}, \bibinfo{author}{Babbush\xfnm[ R.]},
  \bibinfo{author}{Kivlichan\xfnm[ I.]}, \bibinfo{author}{Romero\xfnm[ J.]},
  \bibinfo{author}{McClean\xfnm[ J.]}, \bibinfo{author}{Barends\xfnm[ R.]},
  et~al.
\newblock \bibinfo{title}{Scalable quantum simulation of molecular energies}.
\newblock \bibinfo{journal}{Physical Review X}
  \bibinfo{year}{2016};\bibinfo{volume}{6}(\bibinfo{number}{3}):\bibinfo{pages}{031007}.
\newblock \DOIprefix\doi{10.1103/physrevx.6.031007}.
%Type = Article
\bibitem[{Wiersema et~al.(2020)Wiersema, Zhou, de~Sereville, Carrasquilla, Kim
  and Yuen}]{Wiersema2020}
\bibinfo{author}{Wiersema\xfnm[ R.]}, \bibinfo{author}{Zhou\xfnm[ C.]},
  \bibinfo{author}{de~Sereville\xfnm[ Y.]}, \bibinfo{author}{Carrasquilla\xfnm[
  J.F.]}, \bibinfo{author}{Kim\xfnm[ Y.B.]}, \bibinfo{author}{Yuen\xfnm[ H.]}.
\newblock \bibinfo{title}{Exploring entanglement and optimization within the
  hamiltonian variational ansatz}.
\newblock \bibinfo{journal}{PRX Quantum}
  \bibinfo{year}{2020};\bibinfo{volume}{1}(\bibinfo{number}{2}).
\newblock \DOIprefix\doi{10.1103/prxquantum.1.020319}.
%Type = Misc
\bibitem[{Malone et~al.(2021)Malone, Parrish, Welden, Fox, Degroote, Kyoseva
  et~al.}]{Malone2021}
\bibinfo{author}{Malone\xfnm[ F.D.]}, \bibinfo{author}{Parrish\xfnm[ R.M.]},
  \bibinfo{author}{Welden\xfnm[ A.R.]}, \bibinfo{author}{Fox\xfnm[ T.]},
  \bibinfo{author}{Degroote\xfnm[ M.]}, \bibinfo{author}{Kyoseva\xfnm[ E.]},
  et~al.
\newblock \bibinfo{title}{Towards the simulation of large scale protein-ligand
  interactions on nisq-era quantum computers}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2110.01589v1}{\tt arXiv:2110.01589v1}.
%Type = Misc
\bibitem[{Kirsopp et~al.(2021)Kirsopp, Paola, Manrique, Krompiec, Greene-Diniz,
  Guba et~al.}]{Kirsopp2021}
\bibinfo{author}{Kirsopp\xfnm[ J.J.M.]}, \bibinfo{author}{Paola\xfnm[ C.D.]},
  \bibinfo{author}{Manrique\xfnm[ D.Z.]}, \bibinfo{author}{Krompiec\xfnm[ M.]},
  \bibinfo{author}{Greene-Diniz\xfnm[ G.]}, \bibinfo{author}{Guba\xfnm[ W.]},
  et~al.
\newblock \bibinfo{title}{Quantum computational quantification of
  protein-ligand interactions}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2110.08163v1}{\tt arXiv:2110.08163v1}.
%Type = Misc
\bibitem[{Anschuetz and Kiani(2022)}]{Anschuetz2022}
\bibinfo{author}{Anschuetz\xfnm[ E.R.]}, \bibinfo{author}{Kiani\xfnm[ B.T.]}.
\newblock \bibinfo{title}{Beyond barren plateaus: Quantum variational
  algorithms are swamped with traps}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2205.05786}.
  \DOIprefix\doi{10.48550/ARXIV.2205.05786}.
%Type = Article
\bibitem[{Krentel(1988)}]{Krentel1988}
\bibinfo{author}{Krentel\xfnm[ M.W.]}.
\newblock \bibinfo{title}{The complexity of optimization problems}.
\newblock \bibinfo{journal}{Journal of Computer and System Sciences}
  \bibinfo{year}{1988};\bibinfo{volume}{36}(\bibinfo{number}{3}):\bibinfo{pages}{490--509}.
\newblock \DOIprefix\doi{10.1016/0022-0000(88)90039-6}.
%Type = Misc
\bibitem[{Barron and Wood(2020)}]{Barron2020}
\bibinfo{author}{Barron\xfnm[ G.S.]}, \bibinfo{author}{Wood\xfnm[ C.J.]}.
\newblock \bibinfo{title}{Measurement error mitigation for variational quantum
  algorithms}.
\newblock \bibinfo{year}{2020}.
\newblock \href{http://arxiv.org/abs/2010.08520v1}{\tt arXiv:2010.08520v1}.
%Type = Article
\bibitem[{Sagastizabal et~al.(2019)Sagastizabal, Bonet-Monroig, Singh, Rol,
  Bultink, Fu et~al.}]{Sagastizabal2019}
\bibinfo{author}{Sagastizabal\xfnm[ R.]}, \bibinfo{author}{Bonet-Monroig\xfnm[
  X.]}, \bibinfo{author}{Singh\xfnm[ M.]}, \bibinfo{author}{Rol\xfnm[ M.A.]},
  \bibinfo{author}{Bultink\xfnm[ C.C.]}, \bibinfo{author}{Fu\xfnm[ X.]}, et~al.
\newblock \bibinfo{title}{Experimental error mitigation via symmetry
  verification in a variational quantum eigensolver}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2019};\bibinfo{volume}{100}(\bibinfo{number}{1}):\bibinfo{pages}{010302(R)}.
\newblock \DOIprefix\doi{10.1103/physreva.100.010302}.
%Type = Article
\bibitem[{Nam et~al.(2020)Nam, Chen, Pisenti, Wright, Delaney, Maslov
  et~al.}]{Nam2020}
\bibinfo{author}{Nam\xfnm[ Y.]}, \bibinfo{author}{Chen\xfnm[ J.S.]},
  \bibinfo{author}{Pisenti\xfnm[ N.C.]}, \bibinfo{author}{Wright\xfnm[ K.]},
  \bibinfo{author}{Delaney\xfnm[ C.]}, \bibinfo{author}{Maslov\xfnm[ D.]},
  et~al.
\newblock \bibinfo{title}{Ground-state energy estimation of the water molecule
  on a trapped-ion quantum computer}.
\newblock \bibinfo{journal}{npj Quantum Information}
  \bibinfo{year}{2020};\bibinfo{volume}{6}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1038/s41534-020-0259-3}.
%Type = Article
\bibitem[{and Frank~Arute et~al.(2020)and Frank~Arute, Arya, Babbush, Bacon,
  Bardin, Barends et~al.}]{Arute2020}
\bibinfo{author}{and Frank~Arute\xfnm[]}, \bibinfo{author}{Arya\xfnm[ K.]},
  \bibinfo{author}{Babbush\xfnm[ R.]}, \bibinfo{author}{Bacon\xfnm[ D.]},
  \bibinfo{author}{Bardin\xfnm[ J.C.]}, \bibinfo{author}{Barends\xfnm[ R.]},
  et~al.
\newblock \bibinfo{title}{Hartree-fock on a superconducting qubit quantum
  computer}.
\newblock \bibinfo{journal}{Science}
  \bibinfo{year}{2020};\bibinfo{volume}{369}(\bibinfo{number}{6507}):\bibinfo{pages}{1084--1089}.
\newblock \DOIprefix\doi{10.1126/science.abb9811}.
%Type = Article
\bibitem[{Tilly et~al.(2021)Tilly, Sriluckshmy, Patel, Fontana, Rungger, Grant
  et~al.}]{Tilly2021}
\bibinfo{author}{Tilly\xfnm[ J.]}, \bibinfo{author}{Sriluckshmy\xfnm[ P.V.]},
  \bibinfo{author}{Patel\xfnm[ A.]}, \bibinfo{author}{Fontana\xfnm[ E.]},
  \bibinfo{author}{Rungger\xfnm[ I.]}, \bibinfo{author}{Grant\xfnm[ E.]},
  et~al.
\newblock \bibinfo{title}{Reduced density matrix sampling: Self-consistent
  embedding and multiscale electronic structure on current generation quantum
  computers}.
\newblock \bibinfo{journal}{Physical Review Research}
  \bibinfo{year}{2021};\bibinfo{volume}{3}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physrevresearch.3.033230}.
  \href{http://arxiv.org/abs/2104.05531v1}{\tt arXiv:2104.05531v1};
  \bibinfo{note}{phys. Rev. Research 3, 033230 (2021)}.
%Type = Article
\bibitem[{Benfenati et~al.(2021)Benfenati, Mazzola, Capecci, Barkoutsos,
  Ollitrault, Tavernelli et~al.}]{Benfenati2021}
\bibinfo{author}{Benfenati\xfnm[ F.]}, \bibinfo{author}{Mazzola\xfnm[ G.]},
  \bibinfo{author}{Capecci\xfnm[ C.]}, \bibinfo{author}{Barkoutsos\xfnm[
  P.K.]}, \bibinfo{author}{Ollitrault\xfnm[ P.J.]},
  \bibinfo{author}{Tavernelli\xfnm[ I.]}, et~al.
\newblock \bibinfo{title}{Improved accuracy on noisy devices by nonunitary
  variational quantum eigensolver for chemistry applications}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2021};\bibinfo{volume}{17}(\bibinfo{number}{7}):\bibinfo{pages}{3946--3954}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.1c00091}.
%Type = Article
\bibitem[{Evangelista et~al.(2019)Evangelista, Chan and
  Scuseria}]{Evangelista2019}
\bibinfo{author}{Evangelista\xfnm[ F.A.]}, \bibinfo{author}{Chan\xfnm[
  G.K.L.]}, \bibinfo{author}{Scuseria\xfnm[ G.E.]}.
\newblock \bibinfo{title}{Exact parameterization of fermionic wave functions
  via unitary coupled cluster theory}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2019};\bibinfo{volume}{151}(\bibinfo{number}{24}):\bibinfo{pages}{244112}.
\newblock \DOIprefix\doi{10.1063/1.5133059}.
%Type = Article
\bibitem[{Hohenberg and Kohn(1964)}]{Hohenberg1964}
\bibinfo{author}{Hohenberg\xfnm[ P.]}, \bibinfo{author}{Kohn\xfnm[ W.]}.
\newblock \bibinfo{title}{Inhomogeneous electron gas}.
\newblock \bibinfo{journal}{Physical Review}
  \bibinfo{year}{1964};\bibinfo{volume}{136}(\bibinfo{number}{3B}):\bibinfo{pages}{B864--B871}.
\newblock \DOIprefix\doi{10.1103/physrev.136.b864}.
%Type = Article
\bibitem[{Levy(1979)}]{Levy1979}
\bibinfo{author}{Levy\xfnm[ M.]}.
\newblock \bibinfo{title}{Universal variational functionals of electron
  densities, first-order density matrices, and natural spin-orbitals and
  solution of the v-representability problem}.
\newblock \bibinfo{journal}{Proceedings of the National Academy of Sciences}
  \bibinfo{year}{1979};\bibinfo{volume}{76}(\bibinfo{number}{12}):\bibinfo{pages}{6062--6065}.
\newblock \DOIprefix\doi{10.1073/pnas.76.12.6062}.
%Type = Article
\bibitem[{Vignale and Rasolt(1987)}]{Vignale1987}
\bibinfo{author}{Vignale\xfnm[ G.]}, \bibinfo{author}{Rasolt\xfnm[ M.]}.
\newblock \bibinfo{title}{Density-functional theory in strong magnetic fields}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{1987};\bibinfo{volume}{59}(\bibinfo{number}{20}):\bibinfo{pages}{2360--2363}.
\newblock \DOIprefix\doi{10.1103/physrevlett.59.2360}.
%Type = Article
\bibitem[{Kohn and Sham(1965)}]{Kohn1965}
\bibinfo{author}{Kohn\xfnm[ W.]}, \bibinfo{author}{Sham\xfnm[ L.J.]}.
\newblock \bibinfo{title}{Self-consistent equations including exchange and
  correlation effects}.
\newblock \bibinfo{journal}{Physical Review}
  \bibinfo{year}{1965};\bibinfo{volume}{140}(\bibinfo{number}{4A}):\bibinfo{pages}{A1133--A1138}.
\newblock \DOIprefix\doi{10.1103/physrev.140.a1133}.
%Type = Book
\bibitem[{Parr and Weitao(1995)}]{Parr1995}
\bibinfo{author}{Parr\xfnm[ R.G.]}, \bibinfo{author}{Weitao\xfnm[ Y.]}.
\newblock \bibinfo{title}{Density-Functional Theory of Atoms and Molecules}.
\newblock \bibinfo{publisher}{Oxford University Press}; \bibinfo{year}{1995}.
\newblock ISBN \bibinfo{isbn}{9780197560709}.
\newblock \DOIprefix\doi{10.1093/oso/9780195092769.001.0001}.
%Type = Article
\bibitem[{Bagayoko(2014)}]{Bagayoko2014}
\bibinfo{author}{Bagayoko\xfnm[ D.]}.
\newblock \bibinfo{title}{Understanding density functional theory ({DFT}) and
  completing it in practice}.
\newblock \bibinfo{journal}{AIP Advances}
  \bibinfo{year}{2014};\bibinfo{volume}{4}(\bibinfo{number}{12}):\bibinfo{pages}{127104}.
\newblock \DOIprefix\doi{10.1063/1.4903408}.
%Type = Article
\bibitem[{Eriksen et~al.(2020)Eriksen, Anderson, Deustua, Ghanem, Hait,
  Hoffmann et~al.}]{Eriksen2020}
\bibinfo{author}{Eriksen\xfnm[ J.J.]}, \bibinfo{author}{Anderson\xfnm[ T.A.]},
  \bibinfo{author}{Deustua\xfnm[ J.E.]}, \bibinfo{author}{Ghanem\xfnm[ K.]},
  \bibinfo{author}{Hait\xfnm[ D.]}, \bibinfo{author}{Hoffmann\xfnm[ M.R.]},
  et~al.
\newblock \bibinfo{title}{The ground state electronic energy of benzene}.
\newblock \bibinfo{journal}{The Journal of Physical Chemistry Letters}
  \bibinfo{year}{2020};\bibinfo{volume}{11}(\bibinfo{number}{20}):\bibinfo{pages}{8922--8929}.
\newblock \DOIprefix\doi{10.1021/acs.jpclett.0c02621}.
%Type = Article
\bibitem[{Williams et~al.(2020)Williams, Yao, Li, Chen, Shi, Motta
  et~al.}]{Williams2020}
\bibinfo{author}{Williams\xfnm[ K.T.]}, \bibinfo{author}{Yao\xfnm[ Y.]},
  \bibinfo{author}{Li\xfnm[ J.]}, \bibinfo{author}{Chen\xfnm[ L.]},
  \bibinfo{author}{Shi\xfnm[ H.]}, \bibinfo{author}{Motta\xfnm[ M.]}, et~al.
\newblock \bibinfo{title}{Direct comparison of many-body methods for realistic
  electronic hamiltonians}.
\newblock \bibinfo{journal}{Physical Review X}
  \bibinfo{year}{2020};\bibinfo{volume}{10}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1103/physrevx.10.011041}.
%Type = Article
\bibitem[{Babbush et~al.(2019)Babbush, Berry, McClean and Neven}]{Babbush2019}
\bibinfo{author}{Babbush\xfnm[ R.]}, \bibinfo{author}{Berry\xfnm[ D.W.]},
  \bibinfo{author}{McClean\xfnm[ J.R.]}, \bibinfo{author}{Neven\xfnm[ H.]}.
\newblock \bibinfo{title}{Quantum simulation of chemistry with sublinear
  scaling in basis size}.
\newblock \bibinfo{journal}{npj Quantum Information}
  \bibinfo{year}{2019};\bibinfo{volume}{5}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1038/s41534-019-0199-y}.
%Type = Incollection
\bibitem[{Sherrill and Schaefer(1999)}]{DavidSherrill1999}
\bibinfo{author}{Sherrill\xfnm[ C.D.]}, \bibinfo{author}{Schaefer\xfnm[ H.F.]}.
\newblock \bibinfo{title}{The configuration interaction method: Advances in
  highly correlated approaches}.
\newblock In: \bibinfo{booktitle}{Advances in Quantum Chemistry}.
  \bibinfo{publisher}{Elsevier}; \bibinfo{year}{1999}, p.
  \bibinfo{pages}{143--269}.
\newblock \DOIprefix\doi{10.1016/s0065-3276(08)60532-8}.
%Type = Article
\bibitem[{Vogiatzis et~al.(2017)Vogiatzis, Ma, Olsen, Gagliardi and
  de~Jong}]{Vogiatzis2017}
\bibinfo{author}{Vogiatzis\xfnm[ K.D.]}, \bibinfo{author}{Ma\xfnm[ D.]},
  \bibinfo{author}{Olsen\xfnm[ J.]}, \bibinfo{author}{Gagliardi\xfnm[ L.]},
  \bibinfo{author}{de~Jong\xfnm[ W.A.]}.
\newblock \bibinfo{title}{Pushing configuration-interaction to the limit:
  Towards massively parallel mcscf calculations}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2017};\bibinfo{volume}{147}(\bibinfo{number}{18}):\bibinfo{pages}{184111}.
\newblock \DOIprefix\doi{10.1063/1.4989858}.
  \href{http://arxiv.org/abs/https://doi.org/10.1063/1.4989858}{\tt
  arXiv:https://doi.org/10.1063/1.4989858}.
%Type = Article
\bibitem[{Ross(1952)}]{Ross1952}
\bibinfo{author}{Ross\xfnm[ I.G.]}.
\newblock \bibinfo{title}{Calculations of the energy levels of acetylene by the
  method of antisymmetric molecular orbitals, including $\sigma$-$\pi$
  interaction}.
\newblock \bibinfo{journal}{Transactions of the Faraday Society}
  \bibinfo{year}{1952};\bibinfo{volume}{48}:\bibinfo{pages}{973}.
\newblock \DOIprefix\doi{10.1039/tf9524800973}.
%Type = Book
\bibitem[{Foresman(1996)}]{Foresman1996}
\bibinfo{author}{Foresman\xfnm[ J.]}.
\newblock \bibinfo{title}{Exploring chemistry with electronic structure
  methods}.
\newblock \bibinfo{address}{Pittsburgh, PA}: \bibinfo{publisher}{Gaussian,
  Inc}; \bibinfo{year}{1996}.
\newblock ISBN \bibinfo{isbn}{978-0963676931}.
%Type = Article
\bibitem[{White(1992)}]{White1992}
\bibinfo{author}{White\xfnm[ S.R.]}.
\newblock \bibinfo{title}{Density matrix formulation for quantum
  renormalization groups}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{1992};\bibinfo{volume}{69}(\bibinfo{number}{19}):\bibinfo{pages}{2863--2866}.
\newblock \DOIprefix\doi{10.1103/physrevlett.69.2863}.
%Type = Article
\bibitem[{Sharma and Chan(2012)}]{Sharma2012}
\bibinfo{author}{Sharma\xfnm[ S.]}, \bibinfo{author}{Chan\xfnm[ G.K.L.]}.
\newblock \bibinfo{title}{Spin-adapted density matrix renormalization group
  algorithms for quantum chemistry}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2012};\bibinfo{volume}{136}(\bibinfo{number}{12}):\bibinfo{pages}{124121}.
\newblock \DOIprefix\doi{10.1063/1.3695642}.
%Type = Article
\bibitem[{Tubman et~al.(2016)Tubman, Lee, Takeshita, Head-Gordon and
  Whaley}]{Tubman2016}
\bibinfo{author}{Tubman\xfnm[ N.M.]}, \bibinfo{author}{Lee\xfnm[ J.]},
  \bibinfo{author}{Takeshita\xfnm[ T.Y.]}, \bibinfo{author}{Head-Gordon\xfnm[
  M.]}, \bibinfo{author}{Whaley\xfnm[ K.B.]}.
\newblock \bibinfo{title}{A deterministic alternative to the full configuration
  interaction quantum monte carlo method}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2016};\bibinfo{volume}{145}(\bibinfo{number}{4}):\bibinfo{pages}{044112}.
\newblock \DOIprefix\doi{10.1063/1.4955109}.
%Type = Article
\bibitem[{Booth and Alavi(2010)}]{Booth2010}
\bibinfo{author}{Booth\xfnm[ G.H.]}, \bibinfo{author}{Alavi\xfnm[ A.]}.
\newblock \bibinfo{title}{Approaching chemical accuracy using full
  configuration-interaction quantum monte carlo: A study of ionization
  potentials}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2010};\bibinfo{volume}{132}(\bibinfo{number}{17}):\bibinfo{pages}{174104}.
\newblock \DOIprefix\doi{10.1063/1.3407895}.
%Type = Article
\bibitem[{Thomas et~al.(2015)Thomas, Booth and Alavi}]{Thomas2015}
\bibinfo{author}{Thomas\xfnm[ R.E.]}, \bibinfo{author}{Booth\xfnm[ G.H.]},
  \bibinfo{author}{Alavi\xfnm[ A.]}.
\newblock \bibinfo{title}{{AccurateAb}~{InitioCalculation} of ionization
  potentials of the first-row transition metals with the
  configuration-interaction quantum monte~carlo technique}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2015};\bibinfo{volume}{114}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physrevlett.114.033001}.
%Type = Article
\bibitem[{Li et~al.(2018)Li, Otten, Holmes, Sharma and Umrigar}]{Li2018}
\bibinfo{author}{Li\xfnm[ J.]}, \bibinfo{author}{Otten\xfnm[ M.]},
  \bibinfo{author}{Holmes\xfnm[ A.A.]}, \bibinfo{author}{Sharma\xfnm[ S.]},
  \bibinfo{author}{Umrigar\xfnm[ C.J.]}.
\newblock \bibinfo{title}{Fast semistochastic heat-bath configuration
  interaction}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2018};\bibinfo{volume}{149}(\bibinfo{number}{21}):\bibinfo{pages}{214110}.
\newblock \DOIprefix\doi{10.1063/1.5055390}.
%Type = Article
\bibitem[{Peterson et~al.(2012)Peterson, Feller and Dixon}]{Peterson2012}
\bibinfo{author}{Peterson\xfnm[ K.A.]}, \bibinfo{author}{Feller\xfnm[ D.]},
  \bibinfo{author}{Dixon\xfnm[ D.A.]}.
\newblock \bibinfo{title}{Chemical accuracy in ab initio thermochemistry and
  spectroscopy: current strategies and future challenges}.
\newblock \bibinfo{journal}{Theoretical Chemistry Accounts}
  \bibinfo{year}{2012};\bibinfo{volume}{131}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1007/s00214-011-1079-5}.
%Type = Article
\bibitem[{Tubman et~al.(2020)Tubman, Freeman, Levine, Hait, Head-Gordon and
  Whaley}]{Tubman2020}
\bibinfo{author}{Tubman\xfnm[ N.M.]}, \bibinfo{author}{Freeman\xfnm[ C.D.]},
  \bibinfo{author}{Levine\xfnm[ D.S.]}, \bibinfo{author}{Hait\xfnm[ D.]},
  \bibinfo{author}{Head-Gordon\xfnm[ M.]}, \bibinfo{author}{Whaley\xfnm[
  K.B.]}.
\newblock \bibinfo{title}{Modern approaches to exact diagonalization and
  selected configuration interaction with the adaptive sampling {CI} method}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2020};\bibinfo{volume}{16}(\bibinfo{number}{4}):\bibinfo{pages}{2139--2159}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.8b00536}.
%Type = Article
\bibitem[{Hait et~al.(2019)Hait, Tubman, Levine, Whaley and
  Head-Gordon}]{Hait2019}
\bibinfo{author}{Hait\xfnm[ D.]}, \bibinfo{author}{Tubman\xfnm[ N.M.]},
  \bibinfo{author}{Levine\xfnm[ D.S.]}, \bibinfo{author}{Whaley\xfnm[ K.B.]},
  \bibinfo{author}{Head-Gordon\xfnm[ M.]}.
\newblock \bibinfo{title}{What levels of coupled cluster theory are appropriate
  for transition metal systems? a study using near-exact quantum chemical
  values for 3d transition metal binary compounds}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2019};\bibinfo{volume}{15}(\bibinfo{number}{10}):\bibinfo{pages}{5370--5385}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.9b00674}.
%Type = Article
\bibitem[{Levine et~al.(2020)Levine, Hait, Tubman, Lehtola, Whaley and
  Head-Gordon}]{Levine2020}
\bibinfo{author}{Levine\xfnm[ D.S.]}, \bibinfo{author}{Hait\xfnm[ D.]},
  \bibinfo{author}{Tubman\xfnm[ N.M.]}, \bibinfo{author}{Lehtola\xfnm[ S.]},
  \bibinfo{author}{Whaley\xfnm[ K.B.]}, \bibinfo{author}{Head-Gordon\xfnm[
  M.]}.
\newblock \bibinfo{title}{{CASSCF} with extremely large active spaces using the
  adaptive sampling configuration interaction method}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2020};\bibinfo{volume}{16}(\bibinfo{number}{4}):\bibinfo{pages}{2340--2354}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.9b01255}.
%Type = Article
\bibitem[{Petruzielo et~al.(2012)Petruzielo, Holmes, Changlani, Nightingale and
  Umrigar}]{Petruzielo2012}
\bibinfo{author}{Petruzielo\xfnm[ F.R.]}, \bibinfo{author}{Holmes\xfnm[ A.A.]},
  \bibinfo{author}{Changlani\xfnm[ H.J.]}, \bibinfo{author}{Nightingale\xfnm[
  M.P.]}, \bibinfo{author}{Umrigar\xfnm[ C.J.]}.
\newblock \bibinfo{title}{Semistochastic projector monte~carlo method}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2012};\bibinfo{volume}{109}(\bibinfo{number}{23}).
\newblock \DOIprefix\doi{10.1103/physrevlett.109.230201}.
%Type = Article
\bibitem[{Holmes et~al.(2016{\natexlab{b}})Holmes, Tubman and
  Umrigar}]{Holmes2016_2}
\bibinfo{author}{Holmes\xfnm[ A.A.]}, \bibinfo{author}{Tubman\xfnm[ N.M.]},
  \bibinfo{author}{Umrigar\xfnm[ C.J.]}.
\newblock \bibinfo{title}{Heat-bath configuration interaction: An efficient
  selected configuration interaction algorithm inspired by heat-bath sampling}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2016}{\natexlab{b}};\bibinfo{volume}{12}(\bibinfo{number}{8}):\bibinfo{pages}{3674--3680}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.6b00407}.
%Type = Article
\bibitem[{Sharma et~al.(2017)Sharma, Holmes, Jeanmairet, Alavi and
  Umrigar}]{Sharma2017}
\bibinfo{author}{Sharma\xfnm[ S.]}, \bibinfo{author}{Holmes\xfnm[ A.A.]},
  \bibinfo{author}{Jeanmairet\xfnm[ G.]}, \bibinfo{author}{Alavi\xfnm[ A.]},
  \bibinfo{author}{Umrigar\xfnm[ C.J.]}.
\newblock \bibinfo{title}{Semistochastic heat-bath configuration interaction
  method: Selected configuration interaction with semistochastic perturbation
  theory}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2017};\bibinfo{volume}{13}(\bibinfo{number}{4}):\bibinfo{pages}{1595--1604}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.6b01028}.
%Type = Article
\bibitem[{Smith et~al.(2017)Smith, Mussard, Holmes and Sharma}]{Smith2017}
\bibinfo{author}{Smith\xfnm[ J.E.T.]}, \bibinfo{author}{Mussard\xfnm[ B.]},
  \bibinfo{author}{Holmes\xfnm[ A.A.]}, \bibinfo{author}{Sharma\xfnm[ S.]}.
\newblock \bibinfo{title}{Cheap and near exact {CASSCF} with large active
  spaces}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2017};\bibinfo{volume}{13}(\bibinfo{number}{11}):\bibinfo{pages}{5468--5478}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.7b00900}.
%Type = Article
\bibitem[{Holmes et~al.(2017)Holmes, Umrigar and Sharma}]{Holmes2017}
\bibinfo{author}{Holmes\xfnm[ A.A.]}, \bibinfo{author}{Umrigar\xfnm[ C.J.]},
  \bibinfo{author}{Sharma\xfnm[ S.]}.
\newblock \bibinfo{title}{Excited states using semistochastic heat-bath
  configuration interaction}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2017};\bibinfo{volume}{147}(\bibinfo{number}{16}):\bibinfo{pages}{164111}.
\newblock \DOIprefix\doi{10.1063/1.4998614}.
%Type = Article
\bibitem[{Cleland et~al.(2012)Cleland, Booth, Overy and Alavi}]{Cleland2012}
\bibinfo{author}{Cleland\xfnm[ D.]}, \bibinfo{author}{Booth\xfnm[ G.H.]},
  \bibinfo{author}{Overy\xfnm[ C.]}, \bibinfo{author}{Alavi\xfnm[ A.]}.
\newblock \bibinfo{title}{Taming the first-row diatomics: A full configuration
  interaction quantum monte carlo study}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2012};\bibinfo{volume}{8}(\bibinfo{number}{11}):\bibinfo{pages}{4138--4152}.
\newblock \DOIprefix\doi{10.1021/ct300504f}.
%Type = Article
\bibitem[{Anderson and Booth(2020)}]{Anderson2020}
\bibinfo{author}{Anderson\xfnm[ R.J.]}, \bibinfo{author}{Booth\xfnm[ G.H.]}.
\newblock \bibinfo{title}{Four-component full configuration interaction quantum
  monte carlo for relativistic correlated electron problems}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2020};\bibinfo{volume}{153}(\bibinfo{number}{18}):\bibinfo{pages}{184103}.
\newblock \DOIprefix\doi{10.1063/5.0029863}.
%Type = Article
\bibitem[{Booth et~al.(2011)Booth, Cleland, Thom and Alavi}]{Booth2011}
\bibinfo{author}{Booth\xfnm[ G.H.]}, \bibinfo{author}{Cleland\xfnm[ D.]},
  \bibinfo{author}{Thom\xfnm[ A.J.W.]}, \bibinfo{author}{Alavi\xfnm[ A.]}.
\newblock \bibinfo{title}{Breaking the carbon dimer: The challenges of multiple
  bond dissociation with full configuration interaction quantum monte carlo
  methods}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2011};\bibinfo{volume}{135}(\bibinfo{number}{8}):\bibinfo{pages}{084104}.
\newblock \DOIprefix\doi{10.1063/1.3624383}.
%Type = Article
\bibitem[{Blunt et~al.(2019)Blunt, Thom and Scott}]{Blunt2019}
\bibinfo{author}{Blunt\xfnm[ N.S.]}, \bibinfo{author}{Thom\xfnm[ A.J.W.]},
  \bibinfo{author}{Scott\xfnm[ C.J.C.]}.
\newblock \bibinfo{title}{Preconditioning and perturbative estimators in full
  configuration interaction quantum monte carlo}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2019};\bibinfo{volume}{15}(\bibinfo{number}{6}):\bibinfo{pages}{3537--3551}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.9b00049}.
%Type = Article
\bibitem[{White(1993)}]{White1993}
\bibinfo{author}{White\xfnm[ S.R.]}.
\newblock \bibinfo{title}{Density-matrix algorithms for quantum renormalization
  groups}.
\newblock \bibinfo{journal}{Physical Review B}
  \bibinfo{year}{1993};\bibinfo{volume}{48}(\bibinfo{number}{14}):\bibinfo{pages}{10345--10356}.
\newblock \DOIprefix\doi{10.1103/physrevb.48.10345}.
%Type = Article
\bibitem[{White and Martin(1999)}]{White1999}
\bibinfo{author}{White\xfnm[ S.R.]}, \bibinfo{author}{Martin\xfnm[ R.L.]}.
\newblock \bibinfo{title}{Ab initio quantum chemistry using the density matrix
  renormalization group}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{1999};\bibinfo{volume}{110}(\bibinfo{number}{9}):\bibinfo{pages}{4127--4130}.
\newblock \DOIprefix\doi{10.1063/1.478295}.
%Type = Article
\bibitem[{Mitrushenkov et~al.(2001)Mitrushenkov, Fano, Ortolani, Linguerri and
  Palmieri}]{Mitrushenkov2001}
\bibinfo{author}{Mitrushenkov\xfnm[ A.O.]}, \bibinfo{author}{Fano\xfnm[ G.]},
  \bibinfo{author}{Ortolani\xfnm[ F.]}, \bibinfo{author}{Linguerri\xfnm[ R.]},
  \bibinfo{author}{Palmieri\xfnm[ P.]}.
\newblock \bibinfo{title}{Quantum chemistry using the density matrix
  renormalization group}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2001};\bibinfo{volume}{115}(\bibinfo{number}{15}):\bibinfo{pages}{6815--6821}.
\newblock \DOIprefix\doi{10.1063/1.1389475}.
%Type = Article
\bibitem[{Legeza et~al.(2003)Legeza, R\"oder and Hess}]{Legeza2003}
\bibinfo{author}{Legeza\xfnm[ O.]}, \bibinfo{author}{R\"oder\xfnm[ J.]},
  \bibinfo{author}{Hess\xfnm[ B.A.]}.
\newblock \bibinfo{title}{Controlling the accuracy of the density-matrix
  renormalization-group method: The dynamical block state selection approach}.
\newblock \bibinfo{journal}{Phys Rev B}
  \bibinfo{year}{2003};\bibinfo{volume}{67}:\bibinfo{pages}{125114}.
\newblock \DOIprefix\doi{10.1103/PhysRevB.67.125114}.
%Type = Article
\bibitem[{Chan and Head-Gordon(2002)}]{Chan2002}
\bibinfo{author}{Chan\xfnm[ G.K.L.]}, \bibinfo{author}{Head-Gordon\xfnm[ M.]}.
\newblock \bibinfo{title}{Highly correlated calculations with a polynomial cost
  algorithm: A study of the density matrix renormalization group}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2002};\bibinfo{volume}{116}(\bibinfo{number}{11}):\bibinfo{pages}{4462--4476}.
\newblock \DOIprefix\doi{10.1063/1.1449459}.
%Type = Article
\bibitem[{Chan and Sharma(2011)}]{Chan2011}
\bibinfo{author}{Chan\xfnm[ G.K.L.]}, \bibinfo{author}{Sharma\xfnm[ S.]}.
\newblock \bibinfo{title}{The density matrix renormalization group in quantum
  chemistry}.
\newblock \bibinfo{journal}{Annual Review of Physical Chemistry}
  \bibinfo{year}{2011};\bibinfo{volume}{62}(\bibinfo{number}{1}):\bibinfo{pages}{465--481}.
\newblock \DOIprefix\doi{10.1146/annurev-physchem-032210-103338}.
%Type = Article
\bibitem[{Olivares-Amaya et~al.(2015)Olivares-Amaya, Hu, Nakatani, Sharma, Yang
  and Chan}]{OlivaresAmaya2015}
\bibinfo{author}{Olivares-Amaya\xfnm[ R.]}, \bibinfo{author}{Hu\xfnm[ W.]},
  \bibinfo{author}{Nakatani\xfnm[ N.]}, \bibinfo{author}{Sharma\xfnm[ S.]},
  \bibinfo{author}{Yang\xfnm[ J.]}, \bibinfo{author}{Chan\xfnm[ G.K.L.]}.
\newblock \bibinfo{title}{Theab-initiodensity matrix renormalization group in
  practice}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2015};\bibinfo{volume}{142}(\bibinfo{number}{3}):\bibinfo{pages}{034102}.
\newblock \DOIprefix\doi{10.1063/1.4905329}.
%Type = Article
\bibitem[{Wouters and Neck(2014)}]{Wouters2014}
\bibinfo{author}{Wouters\xfnm[ S.]}, \bibinfo{author}{Neck\xfnm[ D.V.]}.
\newblock \bibinfo{title}{The density matrix renormalization group for ab
  initio quantum chemistry}.
\newblock \bibinfo{journal}{The European Physical Journal D}
  \bibinfo{year}{2014};\bibinfo{volume}{68}(\bibinfo{number}{9}).
\newblock \DOIprefix\doi{10.1140/epjd/e2014-50500-1}.
%Type = Article
\bibitem[{Yanai et~al.(2014)Yanai, Kurashige, Mizukami, Chalupsk{\'{y}}, Lan
  and Saitow}]{Yanai2014}
\bibinfo{author}{Yanai\xfnm[ T.]}, \bibinfo{author}{Kurashige\xfnm[ Y.]},
  \bibinfo{author}{Mizukami\xfnm[ W.]}, \bibinfo{author}{Chalupsk{\'{y}}\xfnm[
  J.]}, \bibinfo{author}{Lan\xfnm[ T.N.]}, \bibinfo{author}{Saitow\xfnm[ M.]}.
\newblock \bibinfo{title}{Density matrix renormalization group forab
  {initioCalculations} and associated dynamic correlation methods: A review of
  theory and applications}.
\newblock \bibinfo{journal}{International Journal of Quantum Chemistry}
  \bibinfo{year}{2014};\bibinfo{volume}{115}(\bibinfo{number}{5}):\bibinfo{pages}{283--299}.
\newblock \DOIprefix\doi{10.1002/qua.24808}.
%Type = Article
\bibitem[{Knecht et~al.(2016)Knecht, Hedeg{\aa}rd, Keller, Kovyrshin, Ma, Muolo
  et~al.}]{Knecht2016}
\bibinfo{author}{Knecht\xfnm[ S.]}, \bibinfo{author}{Hedeg{\aa}rd\xfnm[ E.D.]},
  \bibinfo{author}{Keller\xfnm[ S.]}, \bibinfo{author}{Kovyrshin\xfnm[ A.]},
  \bibinfo{author}{Ma\xfnm[ Y.]}, \bibinfo{author}{Muolo\xfnm[ A.]}, et~al.
\newblock \bibinfo{title}{New approaches for \textit{ab initio} calculations of
  molecules with strong electron correlation}.
\newblock \bibinfo{journal}{CHIMIA International Journal for Chemistry}
  \bibinfo{year}{2016};\bibinfo{volume}{70}(\bibinfo{number}{4}):\bibinfo{pages}{244--251}.
\newblock \DOIprefix\doi{10.2533/chimia.2016.244}.
%Type = Misc
\bibitem[{Biamonte and Bergholm(2017)}]{Biamonte2017}
\bibinfo{author}{Biamonte\xfnm[ J.]}, \bibinfo{author}{Bergholm\xfnm[ V.]}.
\newblock \bibinfo{title}{Tensor networks in a nutshell}.
\newblock \bibinfo{year}{2017}.
\newblock \URLprefix \url{https://arxiv.org/abs/1708.00006}.
  \DOIprefix\doi{10.48550/ARXIV.1708.00006}.
%Type = Article
\bibitem[{Or{\'{u}}s(2019)}]{Ors2019}
\bibinfo{author}{Or{\'{u}}s\xfnm[ R.]}.
\newblock \bibinfo{title}{Tensor networks for complex quantum systems}.
\newblock \bibinfo{journal}{Nature Reviews Physics}
  \bibinfo{year}{2019};\bibinfo{volume}{1}(\bibinfo{number}{9}):\bibinfo{pages}{538--550}.
\newblock \URLprefix \url{https://doi.org/10.1038/s42254-019-0086-7}.
  \DOIprefix\doi{10.1038/s42254-019-0086-7}.
%Type = Misc
\bibitem[{Schneider et~al.(2021)Schneider, Ostmeyer, Jansen, Luu and
  Urbach}]{Schneider2021}
\bibinfo{author}{Schneider\xfnm[ M.]}, \bibinfo{author}{Ostmeyer\xfnm[ J.]},
  \bibinfo{author}{Jansen\xfnm[ K.]}, \bibinfo{author}{Luu\xfnm[ T.]},
  \bibinfo{author}{Urbach\xfnm[ C.]}.
\newblock \bibinfo{title}{The hubbard model with fermionic tensor networks}.
\newblock \bibinfo{year}{2021}.
\newblock \URLprefix \url{https://arxiv.org/abs/2110.15340}.
  \DOIprefix\doi{10.48550/ARXIV.2110.15340}.
%Type = Article
\bibitem[{Kaneko and Danshita(2022)}]{Kaneko2022}
\bibinfo{author}{Kaneko\xfnm[ R.]}, \bibinfo{author}{Danshita\xfnm[ I.]}.
\newblock \bibinfo{title}{Tensor-network study of correlation-spreading
  dynamics in the two-dimensional bose-hubbard model}.
\newblock \bibinfo{journal}{Communications Physics}
  \bibinfo{year}{2022};\bibinfo{volume}{5}(\bibinfo{number}{1}).
\newblock \URLprefix \url{https://doi.org/10.1038/s42005-022-00848-9}.
  \DOIprefix\doi{10.1038/s42005-022-00848-9}.
%Type = Incollection
\bibitem[{Toulouse et~al.(2016)Toulouse, Assaraf and Umrigar}]{TOULOUSE2016285}
\bibinfo{author}{Toulouse\xfnm[ J.]}, \bibinfo{author}{Assaraf\xfnm[ R.]},
  \bibinfo{author}{Umrigar\xfnm[ C.J.]}.
\newblock \bibinfo{title}{Chapter fifteen - introduction to the variational and
  diffusion monte carlo methods}.
\newblock In: \bibinfo{editor}{Hoggan\xfnm[ P.E.]},
  \bibinfo{editor}{Ozdogan\xfnm[ T.]}, editors. \bibinfo{booktitle}{Electron
  Correlation in Molecules -- ab initio Beyond Gaussian Quantum Chemistry};
  vol.~\bibinfo{volume}{73} of \emph{\bibinfo{series}{Advances in Quantum
  Chemistry}}. \bibinfo{publisher}{Academic Press}; \bibinfo{year}{2016}, p.
  \bibinfo{pages}{285--314}.
\newblock \DOIprefix\doi{https://doi.org/10.1016/bs.aiq.2015.07.003}.
%Type = Article
\bibitem[{Needs et~al.(2020)Needs, Towler, Drummond, L{\'o}pez~R{\'\i}os and
  Trail}]{Needs2020}
\bibinfo{author}{Needs\xfnm[ R.J.]}, \bibinfo{author}{Towler\xfnm[ M.D.]},
  \bibinfo{author}{Drummond\xfnm[ N.D.]},
  \bibinfo{author}{L{\'o}pez~R{\'\i}os\xfnm[ P.]}, \bibinfo{author}{Trail\xfnm[
  J.R.]}.
\newblock \bibinfo{title}{Variational and diffusion quantum monte carlo
  calculations with the casino code}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2020};\bibinfo{volume}{152}(\bibinfo{number}{15}):\bibinfo{pages}{154106}.
\newblock \DOIprefix\doi{10.1063/1.5144288}.
  \href{http://arxiv.org/abs/https://doi.org/10.1063/1.5144288}{\tt
  arXiv:https://doi.org/10.1063/1.5144288}.
%Type = Article
\bibitem[{Pfau et~al.(2020)Pfau, Spencer, Matthews and Foulkes}]{Pfau2020}
\bibinfo{author}{Pfau\xfnm[ D.]}, \bibinfo{author}{Spencer\xfnm[ J.S.]},
  \bibinfo{author}{Matthews\xfnm[ A.G.D.G.]}, \bibinfo{author}{Foulkes\xfnm[
  W.M.C.]}.
\newblock \bibinfo{title}{Ab initio solution of the many-electron schrödinger
  equation with deep neural networks}.
\newblock \bibinfo{journal}{Physical Review Research}
  \bibinfo{year}{2020};\bibinfo{volume}{2}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physrevresearch.2.033429}.
%Type = Article
\bibitem[{Eriksen et~al.(2016{\natexlab{a}})Eriksen, Matthews, J{\o}rgensen and
  Gauss}]{Eriksen2016_I}
\bibinfo{author}{Eriksen\xfnm[ J.J.]}, \bibinfo{author}{Matthews\xfnm[ D.A.]},
  \bibinfo{author}{J{\o}rgensen\xfnm[ P.]}, \bibinfo{author}{Gauss\xfnm[ J.]}.
\newblock \bibinfo{title}{Assessment of the accuracy of coupled cluster
  perturbation theory for open-shell systems. i. triples expansions}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2016}{\natexlab{a}};\bibinfo{volume}{144}(\bibinfo{number}{19}):\bibinfo{pages}{194102}.
\newblock \DOIprefix\doi{10.1063/1.4948780}.
%Type = Article
\bibitem[{Eriksen et~al.(2016{\natexlab{b}})Eriksen, Matthews, J{\o}rgensen and
  Gauss}]{Eriksen2016_II}
\bibinfo{author}{Eriksen\xfnm[ J.J.]}, \bibinfo{author}{Matthews\xfnm[ D.A.]},
  \bibinfo{author}{J{\o}rgensen\xfnm[ P.]}, \bibinfo{author}{Gauss\xfnm[ J.]}.
\newblock \bibinfo{title}{Assessment of the accuracy of coupled cluster
  perturbation theory for open-shell systems. {II}. quadruples expansions}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2016}{\natexlab{b}};\bibinfo{volume}{144}(\bibinfo{number}{19}):\bibinfo{pages}{194103}.
\newblock \DOIprefix\doi{10.1063/1.4948781}.
%Type = Article
\bibitem[{Zhang and Gr\"{u}neis(2019)}]{Ying2019}
\bibinfo{author}{Zhang\xfnm[ I.Y.]}, \bibinfo{author}{Gr\"{u}neis\xfnm[ A.]}.
\newblock \bibinfo{title}{Coupled cluster theory in materials science}.
\newblock \bibinfo{journal}{Frontiers in Materials}
  \bibinfo{year}{2019};\bibinfo{volume}{6}.
\newblock \DOIprefix\doi{10.3389/fmats.2019.00123}.
%Type = Article
\bibitem[{Bartlett and Musia{\l}(2007)}]{Bartlett2007}
\bibinfo{author}{Bartlett\xfnm[ R.J.]}, \bibinfo{author}{Musia{\l}\xfnm[ M.]}.
\newblock \bibinfo{title}{Coupled-cluster theory in quantum chemistry}.
\newblock \bibinfo{journal}{Reviews of Modern Physics}
  \bibinfo{year}{2007};\bibinfo{volume}{79}(\bibinfo{number}{1}):\bibinfo{pages}{291--352}.
\newblock \DOIprefix\doi{10.1103/revmodphys.79.291}.
%Type = Article
\bibitem[{Wang et~al.(2020{\natexlab{a}})Wang, Duan, Xu, Zou and
  Li}]{Wang2020_BCCC}
\bibinfo{author}{Wang\xfnm[ Q.]}, \bibinfo{author}{Duan\xfnm[ M.]},
  \bibinfo{author}{Xu\xfnm[ E.]}, \bibinfo{author}{Zou\xfnm[ J.]},
  \bibinfo{author}{Li\xfnm[ S.]}.
\newblock \bibinfo{title}{Describing strong correlation with block-correlated
  coupled cluster theory}.
\newblock \bibinfo{journal}{The Journal of Physical Chemistry Letters}
  \bibinfo{year}{2020}{\natexlab{a}};\bibinfo{volume}{11}(\bibinfo{number}{18}):\bibinfo{pages}{7536--7543}.
\newblock \DOIprefix\doi{10.1021/acs.jpclett.0c02117}.
%Type = Article
\bibitem[{Lyakh et~al.(2011)Lyakh, Musia{\l}, Lotrich and Bartlett}]{Lyakh2011}
\bibinfo{author}{Lyakh\xfnm[ D.I.]}, \bibinfo{author}{Musia{\l}\xfnm[ M.]},
  \bibinfo{author}{Lotrich\xfnm[ V.F.]}, \bibinfo{author}{Bartlett\xfnm[
  R.J.]}.
\newblock \bibinfo{title}{Multireference nature of chemistry: The
  coupled-cluster view}.
\newblock \bibinfo{journal}{Chemical Reviews}
  \bibinfo{year}{2011};\bibinfo{volume}{112}(\bibinfo{number}{1}):\bibinfo{pages}{182--243}.
\newblock \DOIprefix\doi{10.1021/cr2001417}.
%Type = Article
\bibitem[{Grimsley et~al.(2019{\natexlab{a}})Grimsley, Economou, Barnes and
  Mayhall}]{Grimsley2019}
\bibinfo{author}{Grimsley\xfnm[ H.R.]}, \bibinfo{author}{Economou\xfnm[ S.E.]},
  \bibinfo{author}{Barnes\xfnm[ E.]}, \bibinfo{author}{Mayhall\xfnm[ N.J.]}.
\newblock \bibinfo{title}{An adaptive variational algorithm for exact molecular
  simulations on a quantum computer}.
\newblock \bibinfo{journal}{Nature Communications}
  \bibinfo{year}{2019}{\natexlab{a}};\bibinfo{volume}{10}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1038/s41467-019-10988-2}.
%Type = Article
\bibitem[{Gard et~al.(2020)Gard, Zhu, Barron, Mayhall, Economou and
  Barnes}]{Gard2020}
\bibinfo{author}{Gard\xfnm[ B.T.]}, \bibinfo{author}{Zhu\xfnm[ L.]},
  \bibinfo{author}{Barron\xfnm[ G.S.]}, \bibinfo{author}{Mayhall\xfnm[ N.J.]},
  \bibinfo{author}{Economou\xfnm[ S.E.]}, \bibinfo{author}{Barnes\xfnm[ E.]}.
\newblock \bibinfo{title}{Efficient symmetry-preserving state preparation
  circuits for the variational quantum eigensolver algorithm}.
\newblock \bibinfo{journal}{npj Quantum Information}
  \bibinfo{year}{2020};\bibinfo{volume}{6}(\bibinfo{number}{1}):\bibinfo{pages}{10}.
\newblock \DOIprefix\doi{10.1038/s41534-019-0240-1}.
%Type = Article
\bibitem[{Grimsley et~al.(2019{\natexlab{b}})Grimsley, Claudino, Economou,
  Barnes and Mayhall}]{Grimsley2019_UCC_Review}
\bibinfo{author}{Grimsley\xfnm[ H.R.]}, \bibinfo{author}{Claudino\xfnm[ D.]},
  \bibinfo{author}{Economou\xfnm[ S.E.]}, \bibinfo{author}{Barnes\xfnm[ E.]},
  \bibinfo{author}{Mayhall\xfnm[ N.J.]}.
\newblock \bibinfo{title}{Is the trotterized {UCCSD} ansatz chemically
  well-defined?}
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2019}{\natexlab{b}};\bibinfo{volume}{16}(\bibinfo{number}{1}):\bibinfo{pages}{1--6}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.9b01083}.
%Type = Article
\bibitem[{Carleo and Troyer(2017)}]{Carleo2017}
\bibinfo{author}{Carleo\xfnm[ G.]}, \bibinfo{author}{Troyer\xfnm[ M.]}.
\newblock \bibinfo{title}{Solving the quantum many-body problem with artificial
  neural networks}.
\newblock \bibinfo{journal}{Science}
  \bibinfo{year}{2017};\bibinfo{volume}{355}(\bibinfo{number}{6325}):\bibinfo{pages}{602--606}.
\newblock \DOIprefix\doi{10.1126/science.aag2302}.
%Type = Article
\bibitem[{Nomura et~al.(2017)Nomura, Darmawan, Yamaji and Imada}]{Nomura2017}
\bibinfo{author}{Nomura\xfnm[ Y.]}, \bibinfo{author}{Darmawan\xfnm[ A.S.]},
  \bibinfo{author}{Yamaji\xfnm[ Y.]}, \bibinfo{author}{Imada\xfnm[ M.]}.
\newblock \bibinfo{title}{Restricted boltzmann machine learning for solving
  strongly correlated quantum systems}.
\newblock \bibinfo{journal}{Physical Review B}
  \bibinfo{year}{2017};\bibinfo{volume}{96}(\bibinfo{number}{20}).
\newblock \DOIprefix\doi{10.1103/physrevb.96.205152}.
%Type = Article
\bibitem[{Choo et~al.(2018)Choo, Carleo, Regnault and Neupert}]{Choo2018}
\bibinfo{author}{Choo\xfnm[ K.]}, \bibinfo{author}{Carleo\xfnm[ G.]},
  \bibinfo{author}{Regnault\xfnm[ N.]}, \bibinfo{author}{Neupert\xfnm[ T.]}.
\newblock \bibinfo{title}{Symmetries and many-body excitations with
  neural-network quantum states}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2018};\bibinfo{volume}{121}(\bibinfo{number}{16}).
\newblock \DOIprefix\doi{10.1103/physrevlett.121.167204}.
%Type = Article
\bibitem[{Glielmo et~al.(2020)Glielmo, Rath, Cs{\'{a}}nyi, Vita and
  Booth}]{Glielmo2020}
\bibinfo{author}{Glielmo\xfnm[ A.]}, \bibinfo{author}{Rath\xfnm[ Y.]},
  \bibinfo{author}{Cs{\'{a}}nyi\xfnm[ G.]}, \bibinfo{author}{Vita\xfnm[ A.D.]},
  \bibinfo{author}{Booth\xfnm[ G.H.]}.
\newblock \bibinfo{title}{Gaussian process states: A data-driven representation
  of quantum many-body physics}.
\newblock \bibinfo{journal}{Physical Review X}
  \bibinfo{year}{2020};\bibinfo{volume}{10}(\bibinfo{number}{4}).
\newblock \DOIprefix\doi{10.1103/physrevx.10.041026}.
%Type = Article
\bibitem[{Luo and Clark(2019)}]{Luo2019}
\bibinfo{author}{Luo\xfnm[ D.]}, \bibinfo{author}{Clark\xfnm[ B.K.]}.
\newblock \bibinfo{title}{Backflow transformations via neural networks for
  quantum many-body wave functions}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2019};\bibinfo{volume}{122}(\bibinfo{number}{22}).
\newblock \DOIprefix\doi{10.1103/physrevlett.122.226401}.
%Type = Article
\bibitem[{Choo et~al.(2020)Choo, Mezzacapo and Carleo}]{Choo2020}
\bibinfo{author}{Choo\xfnm[ K.]}, \bibinfo{author}{Mezzacapo\xfnm[ A.]},
  \bibinfo{author}{Carleo\xfnm[ G.]}.
\newblock \bibinfo{title}{Fermionic neural-network states for ab-initio
  electronic structure}.
\newblock \bibinfo{journal}{Nature Communications}
  \bibinfo{year}{2020};\bibinfo{volume}{11}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1038/s41467-020-15724-9}.
%Type = Article
\bibitem[{Hermann et~al.(2020)Hermann, Schätzle and No{\'{e}}}]{Hermann2020}
\bibinfo{author}{Hermann\xfnm[ J.]}, \bibinfo{author}{Schätzle\xfnm[ Z.]},
  \bibinfo{author}{No{\'{e}}\xfnm[ F.]}.
\newblock \bibinfo{title}{Deep-neural-network solution of the electronic
  schrödinger equation}.
\newblock \bibinfo{journal}{Nature Chemistry}
  \bibinfo{year}{2020};\bibinfo{volume}{12}(\bibinfo{number}{10}):\bibinfo{pages}{891--897}.
\newblock \DOIprefix\doi{10.1038/s41557-020-0544-y}.
%Type = Misc
\bibitem[{Kitaev(1995)}]{Kitaev1995}
\bibinfo{author}{Kitaev\xfnm[ A.Y.]}.
\newblock \bibinfo{title}{Quantum measurements and the abelian stabilizer
  problem}.
\newblock \bibinfo{year}{1995}.
\newblock \href{http://arxiv.org/abs/quant-ph/9511026v1}{\tt
  arXiv:quant-ph/9511026v1}.
%Type = Article
\bibitem[{Abrams and Lloyd(1997)}]{Abrams1997}
\bibinfo{author}{Abrams\xfnm[ D.S.]}, \bibinfo{author}{Lloyd\xfnm[ S.]}.
\newblock \bibinfo{title}{Simulation of many-body fermi systems on a universal
  quantum computer}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{1997};\bibinfo{volume}{79}(\bibinfo{number}{13}):\bibinfo{pages}{2586--2589}.
\newblock \DOIprefix\doi{10.1103/physrevlett.79.2586}.
%Type = Article
\bibitem[{Abrams and Lloyd(1999)}]{abramsQuantumAlgorithmProviding1998}
\bibinfo{author}{Abrams\xfnm[ D.S.]}, \bibinfo{author}{Lloyd\xfnm[ S.]}.
\newblock \bibinfo{title}{Quantum algorithm providing exponential speed
  increase for finding eigenvalues and eigenvectors}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{1999};\bibinfo{volume}{83}(\bibinfo{number}{24}):\bibinfo{pages}{5162--5165}.
\newblock \DOIprefix\doi{10.1103/physrevlett.83.5162}.
%Type = Article
\bibitem[{Cleve et~al.(1998)Cleve, Ekert, Macchiavello and Mosca}]{Cleve1998}
\bibinfo{author}{Cleve\xfnm[ R.]}, \bibinfo{author}{Ekert\xfnm[ A.]},
  \bibinfo{author}{Macchiavello\xfnm[ C.]}, \bibinfo{author}{Mosca\xfnm[ M.]}.
\newblock \bibinfo{title}{Quantum algorithms revisited}.
\newblock \bibinfo{journal}{Proceedings of the Royal Society of London Series
  A: Mathematical, Physical and Engineering Sciences}
  \bibinfo{year}{1998};\bibinfo{volume}{454}(\bibinfo{number}{1969}):\bibinfo{pages}{339--354}.
\newblock \DOIprefix\doi{10.1098/rspa.1998.0164}.
%Type = Article
\bibitem[{Aspuru-Guzik et~al.(2005)Aspuru-Guzik, Dutoi, Love and
  Head-Gordon}]{AspuruGuzik2005}
\bibinfo{author}{Aspuru-Guzik\xfnm[ A.]}, \bibinfo{author}{Dutoi\xfnm[ A.D.]},
  \bibinfo{author}{Love\xfnm[ P.J.]}, \bibinfo{author}{Head-Gordon\xfnm[ M.]}.
\newblock \bibinfo{title}{Simulated quantum computation of molecular energies}.
\newblock \bibinfo{journal}{Science}
  \bibinfo{year}{2005};\bibinfo{volume}{309}(\bibinfo{number}{5741}):\bibinfo{pages}{1704--1707}.
\newblock \DOIprefix\doi{10.1126/science.1113479}.
%Type = Article
\bibitem[{McClean et~al.(2014)McClean, Babbush, Love and
  Aspuru-Guzik}]{McClean2014}
\bibinfo{author}{McClean\xfnm[ J.R.]}, \bibinfo{author}{Babbush\xfnm[ R.]},
  \bibinfo{author}{Love\xfnm[ P.J.]}, \bibinfo{author}{Aspuru-Guzik\xfnm[ A.]}.
\newblock \bibinfo{title}{Exploiting locality in quantum computation for
  quantum chemistry}.
\newblock \bibinfo{journal}{The Journal of Physical Chemistry Letters}
  \bibinfo{year}{2014};\bibinfo{volume}{5}(\bibinfo{number}{24}):\bibinfo{pages}{4368--4380}.
\newblock \DOIprefix\doi{10.1021/jz501649m}.
%Type = Article
\bibitem[{Reiher et~al.(2017)Reiher, Wiebe, Svore, Wecker and
  Troyer}]{reiherElucidatingReactionMechanisms2017}
\bibinfo{author}{Reiher\xfnm[ M.]}, \bibinfo{author}{Wiebe\xfnm[ N.]},
  \bibinfo{author}{Svore\xfnm[ K.M.]}, \bibinfo{author}{Wecker\xfnm[ D.]},
  \bibinfo{author}{Troyer\xfnm[ M.]}.
\newblock \bibinfo{title}{Elucidating reaction mechanisms on quantum
  computers}.
\newblock \bibinfo{journal}{Proceedings of the National Academy of Sciences}
  \bibinfo{year}{2017};\bibinfo{volume}{114}(\bibinfo{number}{29}):\bibinfo{pages}{7555--7560}.
\newblock \DOIprefix\doi{10.1073/pnas.1619152114}.
%Type = Article
\bibitem[{Childs et~al.(2018)Childs, Maslov, Nam, Ross and Su}]{Childs2018}
\bibinfo{author}{Childs\xfnm[ A.M.]}, \bibinfo{author}{Maslov\xfnm[ D.]},
  \bibinfo{author}{Nam\xfnm[ Y.]}, \bibinfo{author}{Ross\xfnm[ N.J.]},
  \bibinfo{author}{Su\xfnm[ Y.]}.
\newblock \bibinfo{title}{Toward the first quantum simulation with quantum
  speedup}.
\newblock \bibinfo{journal}{Proceedings of the National Academy of Sciences}
  \bibinfo{year}{2018};\bibinfo{volume}{115}(\bibinfo{number}{38}):\bibinfo{pages}{9456--9461}.
\newblock \DOIprefix\doi{10.1073/pnas.1801723115}.
%Type = Article
\bibitem[{Babbush et~al.(2018{\natexlab{a}})Babbush, Wiebe, McClean, McClain,
  Neven and Chan}]{Babbush2018}
\bibinfo{author}{Babbush\xfnm[ R.]}, \bibinfo{author}{Wiebe\xfnm[ N.]},
  \bibinfo{author}{McClean\xfnm[ J.]}, \bibinfo{author}{McClain\xfnm[ J.]},
  \bibinfo{author}{Neven\xfnm[ H.]}, \bibinfo{author}{Chan\xfnm[ G.K.L.]}.
\newblock \bibinfo{title}{Low-depth quantum simulation of materials}.
\newblock \bibinfo{journal}{Physical Review X}
  \bibinfo{year}{2018}{\natexlab{a}};\bibinfo{volume}{8}(\bibinfo{number}{1}):\bibinfo{pages}{011044}.
\newblock \DOIprefix\doi{10.1103/physrevx.8.011044}.
%Type = Misc
\bibitem[{Tubman et~al.(2018)Tubman, Mejuto-Zaera, Epstein, Hait, Levine,
  Huggins et~al.}]{tubman2018postponing}
\bibinfo{author}{Tubman\xfnm[ N.M.]}, \bibinfo{author}{Mejuto-Zaera\xfnm[ C.]},
  \bibinfo{author}{Epstein\xfnm[ J.M.]}, \bibinfo{author}{Hait\xfnm[ D.]},
  \bibinfo{author}{Levine\xfnm[ D.S.]}, \bibinfo{author}{Huggins\xfnm[ W.]},
  et~al.
\newblock \bibinfo{title}{Postponing the orthogonality catastrophe: efficient
  state preparation for electronic structure simulations on quantum devices}.
\newblock \bibinfo{year}{2018}.
\newblock \href{http://arxiv.org/abs/1809.05523}{\tt arXiv:1809.05523}.
%Type = Article
\bibitem[{Sugisaki et~al.(2018)Sugisaki, Nakazawa, Toyota, Sato, Shiomi and
  Takui}]{Sugisaki2018}
\bibinfo{author}{Sugisaki\xfnm[ K.]}, \bibinfo{author}{Nakazawa\xfnm[ S.]},
  \bibinfo{author}{Toyota\xfnm[ K.]}, \bibinfo{author}{Sato\xfnm[ K.]},
  \bibinfo{author}{Shiomi\xfnm[ D.]}, \bibinfo{author}{Takui\xfnm[ T.]}.
\newblock \bibinfo{title}{Quantum chemistry on quantum computers: A method for
  preparation of multiconfigurational wave functions on quantum computers
  without performing post-hartree{\textendash}fock calculations}.
\newblock \bibinfo{journal}{ACS Cent Sci}
  \bibinfo{year}{2018};\bibinfo{volume}{5}(\bibinfo{number}{1}):\bibinfo{pages}{167--175}.
\newblock \DOIprefix\doi{10.1021/acscentsci.8b00788}.
%Type = Article
\bibitem[{Sugisaki et~al.(2019)Sugisaki, Yamamoto, Nakazawa, Toyota, Sato,
  Shiomi et~al.}]{Sugisaki2019}
\bibinfo{author}{Sugisaki\xfnm[ K.]}, \bibinfo{author}{Yamamoto\xfnm[ S.]},
  \bibinfo{author}{Nakazawa\xfnm[ S.]}, \bibinfo{author}{Toyota\xfnm[ K.]},
  \bibinfo{author}{Sato\xfnm[ K.]}, \bibinfo{author}{Shiomi\xfnm[ D.]}, et~al.
\newblock \bibinfo{title}{Open shell electronic state calculations on quantum
  computers: A quantum circuit for the preparation of configuration state
  functions based on serber construction}.
\newblock \bibinfo{journal}{Chem Phys Letts}
  \bibinfo{year}{2019};\bibinfo{volume}{737}:\bibinfo{pages}{100002}.
\newblock \DOIprefix\doi{10.1016/j.cpletx.2018.100002}.
%Type = Article
\bibitem[{Motta et~al.(2019)Motta, Sun, Tan, O'Rourke, Ye, Minnich
  et~al.}]{Motta2019}
\bibinfo{author}{Motta\xfnm[ M.]}, \bibinfo{author}{Sun\xfnm[ C.]},
  \bibinfo{author}{Tan\xfnm[ A.T.K.]}, \bibinfo{author}{O'Rourke\xfnm[ M.J.]},
  \bibinfo{author}{Ye\xfnm[ E.]}, \bibinfo{author}{Minnich\xfnm[ A.J.]}, et~al.
\newblock \bibinfo{title}{Determining eigenstates and thermal states on a
  quantum computer using quantum imaginary time evolution}.
\newblock \bibinfo{journal}{Nature Phys}
  \bibinfo{year}{2019};\bibinfo{volume}{16}(\bibinfo{number}{2}):\bibinfo{pages}{205--210}.
\newblock \DOIprefix\doi{10.1038/s41567-019-0704-4}.
%Type = Article
\bibitem[{Murta and Fern{\'{a}}ndez-Rossier(2021)}]{Murta2021}
\bibinfo{author}{Murta\xfnm[ B.]},
  \bibinfo{author}{Fern{\'{a}}ndez-Rossier\xfnm[ J.]}.
\newblock \bibinfo{title}{Gutzwiller wave function on a digital quantum
  computer}.
\newblock \bibinfo{journal}{Phys Rev B}
  \bibinfo{year}{2021};\bibinfo{volume}{103}(\bibinfo{number}{24}).
\newblock \DOIprefix\doi{10.1103/physrevb.103.l241113}.
%Type = Article
\bibitem[{Albash and Lidar(2018)}]{Albash2018}
\bibinfo{author}{Albash\xfnm[ T.]}, \bibinfo{author}{Lidar\xfnm[ D.A.]}.
\newblock \bibinfo{title}{Adiabatic quantum computation}.
\newblock \bibinfo{journal}{Rev Mod Phys}
  \bibinfo{year}{2018};\bibinfo{volume}{90}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1103/revmodphys.90.015002}.
%Type = Article
\bibitem[{Matsuura et~al.(2020)Matsuura, Yamazaki, Senicourt, Huntington and
  Zaribafiyan}]{Matsuura2020}
\bibinfo{author}{Matsuura\xfnm[ S.]}, \bibinfo{author}{Yamazaki\xfnm[ T.]},
  \bibinfo{author}{Senicourt\xfnm[ V.]}, \bibinfo{author}{Huntington\xfnm[
  L.]}, \bibinfo{author}{Zaribafiyan\xfnm[ A.]}.
\newblock \bibinfo{title}{Vanqver: the variational and adiabatically navigated
  quantum eigensolver}.
\newblock \bibinfo{journal}{New Journal of Physics}
  \bibinfo{year}{2020};\bibinfo{volume}{22}(\bibinfo{number}{5}):\bibinfo{pages}{053023}.
\newblock \DOIprefix\doi{10.1088/1367-2630/ab8080}.
%Type = Article
\bibitem[{Du et~al.(2010)Du, Xu, Peng, Wang, Wu and Lu}]{Du2010}
\bibinfo{author}{Du\xfnm[ J.]}, \bibinfo{author}{Xu\xfnm[ N.]},
  \bibinfo{author}{Peng\xfnm[ X.]}, \bibinfo{author}{Wang\xfnm[ P.]},
  \bibinfo{author}{Wu\xfnm[ S.]}, \bibinfo{author}{Lu\xfnm[ D.]}.
\newblock \bibinfo{title}{{NMR} implementation of a molecular hydrogen quantum
  simulation with adiabatic state preparation}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2010};\bibinfo{volume}{104}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physrevlett.104.030502}.
%Type = Article
\bibitem[{Lanyon et~al.(2010)Lanyon, Whitfield, Gillett, Goggin, Almeida,
  Kassal et~al.}]{Lanyon2010}
\bibinfo{author}{Lanyon\xfnm[ B.P.]}, \bibinfo{author}{Whitfield\xfnm[ J.D.]},
  \bibinfo{author}{Gillett\xfnm[ G.G.]}, \bibinfo{author}{Goggin\xfnm[ M.E.]},
  \bibinfo{author}{Almeida\xfnm[ M.P.]}, \bibinfo{author}{Kassal\xfnm[ I.]},
  et~al.
\newblock \bibinfo{title}{Towards quantum chemistry on a quantum computer}.
\newblock \bibinfo{journal}{Nature Chemistry}
  \bibinfo{year}{2010};\bibinfo{volume}{2}(\bibinfo{number}{2}):\bibinfo{pages}{106--111}.
\newblock \DOIprefix\doi{10.1038/nchem.483}.
%Type = Article
\bibitem[{Li et~al.(2011)Li, Yung, Chen, Lu, Whitfield, Peng et~al.}]{Li2011}
\bibinfo{author}{Li\xfnm[ Z.]}, \bibinfo{author}{Yung\xfnm[ M.H.]},
  \bibinfo{author}{Chen\xfnm[ H.]}, \bibinfo{author}{Lu\xfnm[ D.]},
  \bibinfo{author}{Whitfield\xfnm[ J.D.]}, \bibinfo{author}{Peng\xfnm[ X.]},
  et~al.
\newblock \bibinfo{title}{Solving quantum ground-state problems with nuclear
  magnetic resonance}.
\newblock \bibinfo{journal}{Scientific Reports}
  \bibinfo{year}{2011};\bibinfo{volume}{1}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1038/srep00088}.
%Type = Article
\bibitem[{Wang et~al.(2015)Wang, Dolde, Biamonte, Babbush, Bergholm, Yang
  et~al.}]{Wang2015}
\bibinfo{author}{Wang\xfnm[ Y.]}, \bibinfo{author}{Dolde\xfnm[ F.]},
  \bibinfo{author}{Biamonte\xfnm[ J.]}, \bibinfo{author}{Babbush\xfnm[ R.]},
  \bibinfo{author}{Bergholm\xfnm[ V.]}, \bibinfo{author}{Yang\xfnm[ S.]},
  et~al.
\newblock \bibinfo{title}{Quantum simulation of helium hydride cation in a
  solid-state spin register}.
\newblock \bibinfo{journal}{ACS Nano}
  \bibinfo{year}{2015};\bibinfo{volume}{9}(\bibinfo{number}{8}):\bibinfo{pages}{7769--7774}.
\newblock \DOIprefix\doi{10.1021/acsnano.5b01651}.
%Type = Article
\bibitem[{Paesani et~al.(2017)Paesani, Gentile, Santagati, Wang, Wiebe, Tew
  et~al.}]{Paesani2017}
\bibinfo{author}{Paesani\xfnm[ S.]}, \bibinfo{author}{Gentile\xfnm[ A.]},
  \bibinfo{author}{Santagati\xfnm[ R.]}, \bibinfo{author}{Wang\xfnm[ J.]},
  \bibinfo{author}{Wiebe\xfnm[ N.]}, \bibinfo{author}{Tew\xfnm[ D.]}, et~al.
\newblock \bibinfo{title}{Experimental bayesian quantum phase estimation on a
  silicon photonic chip}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2017};\bibinfo{volume}{118}(\bibinfo{number}{10}).
\newblock \DOIprefix\doi{10.1103/physrevlett.118.100503}.
%Type = Article
\bibitem[{Santagati et~al.(2018)Santagati, Wang, Gentile, Paesani, Wiebe,
  McClean et~al.}]{Santagati2018}
\bibinfo{author}{Santagati\xfnm[ R.]}, \bibinfo{author}{Wang\xfnm[ J.]},
  \bibinfo{author}{Gentile\xfnm[ A.A.]}, \bibinfo{author}{Paesani\xfnm[ S.]},
  \bibinfo{author}{Wiebe\xfnm[ N.]}, \bibinfo{author}{McClean\xfnm[ J.R.]},
  et~al.
\newblock \bibinfo{title}{Witnessing eigenstates for quantum simulation of
  hamiltonian spectra}.
\newblock \bibinfo{journal}{Science Advances}
  \bibinfo{year}{2018};\bibinfo{volume}{4}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1126/sciadv.aap9646}.
%Type = Article
\bibitem[{Beinert et~al.(1997)Beinert, Holm and M\"unck}]{Beinert1997}
\bibinfo{author}{Beinert\xfnm[ H.]}, \bibinfo{author}{Holm\xfnm[ R.H.]},
  \bibinfo{author}{M\"unck\xfnm[ E.]}.
\newblock \bibinfo{title}{Iron-sulfur clusters: Nature{\textquotesingle}s
  modular, multipurpose structures}.
\newblock \bibinfo{journal}{Science}
  \bibinfo{year}{1997};\bibinfo{volume}{277}(\bibinfo{number}{5326}):\bibinfo{pages}{653--659}.
\newblock \DOIprefix\doi{10.1126/science.277.5326.653}.
%Type = Article
\bibitem[{Low and Chuang(2019)}]{Low2019}
\bibinfo{author}{Low\xfnm[ G.H.]}, \bibinfo{author}{Chuang\xfnm[ I.L.]}.
\newblock \bibinfo{title}{Hamiltonian simulation by qubitization}.
\newblock \bibinfo{journal}{Quantum}
  \bibinfo{year}{2019};\bibinfo{volume}{3}:\bibinfo{pages}{163}.
\newblock \DOIprefix\doi{10.22331/q-2019-07-12-163}.
%Type = Article
\bibitem[{Li et~al.(2019)Li, Li, Dattani, Umrigar and Chan}]{Li2019}
\bibinfo{author}{Li\xfnm[ Z.]}, \bibinfo{author}{Li\xfnm[ J.]},
  \bibinfo{author}{Dattani\xfnm[ N.S.]}, \bibinfo{author}{Umrigar\xfnm[ C.J.]},
  \bibinfo{author}{Chan\xfnm[ G.K.L.]}.
\newblock \bibinfo{title}{The electronic complexity of the ground-state of the
  {FeMo} cofactor of nitrogenase as relevant to quantum simulations}.
\newblock \bibinfo{journal}{J Chem Phys}
  \bibinfo{year}{2019};\bibinfo{volume}{150}(\bibinfo{number}{2}):\bibinfo{pages}{024302}.
\newblock \DOIprefix\doi{10.1063/1.5063376}.
%Type = Article
\bibitem[{Lee et~al.(2021)Lee, Berry, Gidney, Huggins, McClean, Wiebe
  et~al.}]{Lee2021}
\bibinfo{author}{Lee\xfnm[ J.]}, \bibinfo{author}{Berry\xfnm[ D.W.]},
  \bibinfo{author}{Gidney\xfnm[ C.]}, \bibinfo{author}{Huggins\xfnm[ W.J.]},
  \bibinfo{author}{McClean\xfnm[ J.R.]}, \bibinfo{author}{Wiebe\xfnm[ N.]},
  et~al.
\newblock \bibinfo{title}{Even more efficient quantum computations of chemistry
  through tensor hypercontraction}.
\newblock \bibinfo{journal}{PRX Quantum}
  \bibinfo{year}{2021};\bibinfo{volume}{2}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/prxquantum.2.030305}.
%Type = Article
\bibitem[{Babbush et~al.(2018{\natexlab{b}})Babbush, Gidney, Berry, Wiebe,
  McClean, Paler et~al.}]{Babbush2018_Ham_Sim}
\bibinfo{author}{Babbush\xfnm[ R.]}, \bibinfo{author}{Gidney\xfnm[ C.]},
  \bibinfo{author}{Berry\xfnm[ D.W.]}, \bibinfo{author}{Wiebe\xfnm[ N.]},
  \bibinfo{author}{McClean\xfnm[ J.]}, \bibinfo{author}{Paler\xfnm[ A.]},
  et~al.
\newblock \bibinfo{title}{Encoding electronic spectra in quantum circuits with
  linear t complexity}.
\newblock \bibinfo{journal}{Phys Rev X}
  \bibinfo{year}{2018}{\natexlab{b}};\bibinfo{volume}{8}(\bibinfo{number}{4}).
\newblock \DOIprefix\doi{10.1103/physrevx.8.041015}.
%Type = Article
\bibitem[{Kivlichan et~al.(2020)Kivlichan, Gidney, Berry, Wiebe, McClean, Sun
  et~al.}]{Kivlichan2020}
\bibinfo{author}{Kivlichan\xfnm[ I.D.]}, \bibinfo{author}{Gidney\xfnm[ C.]},
  \bibinfo{author}{Berry\xfnm[ D.W.]}, \bibinfo{author}{Wiebe\xfnm[ N.]},
  \bibinfo{author}{McClean\xfnm[ J.]}, \bibinfo{author}{Sun\xfnm[ W.]}, et~al.
\newblock \bibinfo{title}{Improved fault-tolerant quantum simulation of
  condensed-phase correlated electrons via trotterization}.
\newblock \bibinfo{journal}{Quantum}
  \bibinfo{year}{2020};\bibinfo{volume}{4}:\bibinfo{pages}{296}.
\newblock \DOIprefix\doi{10.22331/q-2020-07-16-296}.
%Type = Article
\bibitem[{Wang et~al.(2019)Wang, Higgott and Brierley}]{Wang2019}
\bibinfo{author}{Wang\xfnm[ D.]}, \bibinfo{author}{Higgott\xfnm[ O.]},
  \bibinfo{author}{Brierley\xfnm[ S.]}.
\newblock \bibinfo{title}{Accelerated variational quantum eigensolver}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2019};\bibinfo{volume}{122}(\bibinfo{number}{14}).
\newblock \DOIprefix\doi{10.1103/physrevlett.122.140504}.
%Type = Article
\bibitem[{Jiang et~al.(2020)Jiang, Kalev, Mruczkiewicz and Neven}]{Jiang2020}
\bibinfo{author}{Jiang\xfnm[ Z.]}, \bibinfo{author}{Kalev\xfnm[ A.]},
  \bibinfo{author}{Mruczkiewicz\xfnm[ W.]}, \bibinfo{author}{Neven\xfnm[ H.]}.
\newblock \bibinfo{title}{Optimal fermion-to-qubit mapping via ternary trees
  with applications to reduced quantum states learning}.
\newblock \bibinfo{journal}{Quantum}
  \bibinfo{year}{2020};\bibinfo{volume}{4}:\bibinfo{pages}{276}.
\newblock \DOIprefix\doi{10.22331/q-2020-06-04-276}.
%Type = Article
\bibitem[{Setia et~al.(2019)Setia, Bravyi, Mezzacapo and Whitfield}]{Setia2019}
\bibinfo{author}{Setia\xfnm[ K.]}, \bibinfo{author}{Bravyi\xfnm[ S.]},
  \bibinfo{author}{Mezzacapo\xfnm[ A.]}, \bibinfo{author}{Whitfield\xfnm[
  J.D.]}.
\newblock \bibinfo{title}{Superfast encodings for fermionic quantum
  simulation}.
\newblock \bibinfo{journal}{Physical Review Research}
  \bibinfo{year}{2019};\bibinfo{volume}{1}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physrevresearch.1.033033}.
%Type = Article
\bibitem[{Uvarov et~al.(2020)Uvarov, Biamonte and
  Yudin}]{Uvarov2020_frustrated}
\bibinfo{author}{Uvarov\xfnm[ A.]}, \bibinfo{author}{Biamonte\xfnm[ J.D.]},
  \bibinfo{author}{Yudin\xfnm[ D.]}.
\newblock \bibinfo{title}{Variational quantum eigensolver for frustrated
  quantum systems}.
\newblock \bibinfo{journal}{Phys Rev B}
  \bibinfo{year}{2020};\bibinfo{volume}{102}(\bibinfo{number}{7}).
\newblock \DOIprefix\doi{10.1103/physrevb.102.075104}.
%Type = Article
\bibitem[{Sawaya et~al.(2016)Sawaya, Smelyanskiy, McClean and
  Aspuru-Guzik}]{Sawaya2016}
\bibinfo{author}{Sawaya\xfnm[ N.P.D.]}, \bibinfo{author}{Smelyanskiy\xfnm[
  M.]}, \bibinfo{author}{McClean\xfnm[ J.R.]},
  \bibinfo{author}{Aspuru-Guzik\xfnm[ A.]}.
\newblock \bibinfo{title}{Error sensitivity to environmental noise in quantum
  circuits for chemical state preparation}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2016};\bibinfo{volume}{12}(\bibinfo{number}{7}):\bibinfo{pages}{3097--3108}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.6b00220}.
%Type = Article
\bibitem[{Derby et~al.(2021)Derby, Klassen, Bausch and Cubitt}]{Derby2021}
\bibinfo{author}{Derby\xfnm[ C.]}, \bibinfo{author}{Klassen\xfnm[ J.]},
  \bibinfo{author}{Bausch\xfnm[ J.]}, \bibinfo{author}{Cubitt\xfnm[ T.]}.
\newblock \bibinfo{title}{Compact fermion to qubit mappings}.
\newblock \bibinfo{journal}{Physical Review B}
  \bibinfo{year}{2021};\bibinfo{volume}{104}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physrevb.104.035118}.
%Type = Misc
\bibitem[{Derby and Klassen(2021)}]{Derby2021_part2}
\bibinfo{author}{Derby\xfnm[ C.]}, \bibinfo{author}{Klassen\xfnm[ J.]}.
\newblock \bibinfo{title}{A compact fermion to qubit mapping part 2:
  Alternative lattice geometries}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2101.10735v1}{\tt arXiv:2101.10735v1}.
%Type = Misc
\bibitem[{Yen and Izmaylov(2021)}]{Yen2021_Cartan}
\bibinfo{author}{Yen\xfnm[ T.C.]}, \bibinfo{author}{Izmaylov\xfnm[ A.F.]}.
\newblock \bibinfo{title}{Cartan sub-algebra approach to efficient measurements
  of quantum observables}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2007.01234}{\tt arXiv:2007.01234}.
%Type = Article
\bibitem[{Kandala et~al.(2017)Kandala, Mezzacapo, Temme, Takita, Brink, Chow
  et~al.}]{Kandala2017}
\bibinfo{author}{Kandala\xfnm[ A.]}, \bibinfo{author}{Mezzacapo\xfnm[ A.]},
  \bibinfo{author}{Temme\xfnm[ K.]}, \bibinfo{author}{Takita\xfnm[ M.]},
  \bibinfo{author}{Brink\xfnm[ M.]}, \bibinfo{author}{Chow\xfnm[ J.M.]}, et~al.
\newblock \bibinfo{title}{Hardware-efficient variational quantum eigensolver
  for small molecules and quantum magnets}.
\newblock \bibinfo{journal}{Nature}
  \bibinfo{year}{2017};\bibinfo{volume}{549}(\bibinfo{number}{7671}):\bibinfo{pages}{242--246}.
\newblock \DOIprefix\doi{10.1038/nature23879}.
%Type = Article
\bibitem[{Hempel et~al.(2018)Hempel, Maier, Romero, McClean, Monz, Shen
  et~al.}]{Hempel2018}
\bibinfo{author}{Hempel\xfnm[ C.]}, \bibinfo{author}{Maier\xfnm[ C.]},
  \bibinfo{author}{Romero\xfnm[ J.]}, \bibinfo{author}{McClean\xfnm[ J.]},
  \bibinfo{author}{Monz\xfnm[ T.]}, \bibinfo{author}{Shen\xfnm[ H.]}, et~al.
\newblock \bibinfo{title}{Quantum chemistry calculations on a trapped-ion
  quantum simulator}.
\newblock \bibinfo{journal}{Physical Review X}
  \bibinfo{year}{2018};\bibinfo{volume}{8}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physrevx.8.031022}.
%Type = Article
\bibitem[{Kokail et~al.(2019)Kokail, Maier, van Bijnen, Brydges, Joshi,
  Jurcevic et~al.}]{Kokail2019}
\bibinfo{author}{Kokail\xfnm[ C.]}, \bibinfo{author}{Maier\xfnm[ C.]},
  \bibinfo{author}{van Bijnen\xfnm[ R.]}, \bibinfo{author}{Brydges\xfnm[ T.]},
  \bibinfo{author}{Joshi\xfnm[ M.K.]}, \bibinfo{author}{Jurcevic\xfnm[ P.]},
  et~al.
\newblock \bibinfo{title}{Self-verifying variational quantum simulation of
  lattice models}.
\newblock \bibinfo{journal}{Nature}
  \bibinfo{year}{2019};\bibinfo{volume}{569}(\bibinfo{number}{7756}):\bibinfo{pages}{355--360}.
\newblock \DOIprefix\doi{10.1038/s41586-019-1177-4}.
%Type = Article
\bibitem[{Izmaylov et~al.(2019{\natexlab{a}})Izmaylov, Yen and
  Ryabinkin}]{Izmaylov2019}
\bibinfo{author}{Izmaylov\xfnm[ A.F.]}, \bibinfo{author}{Yen\xfnm[ T.C.]},
  \bibinfo{author}{Ryabinkin\xfnm[ I.G.]}.
\newblock \bibinfo{title}{Revising the measurement process in the variational
  quantum eigensolver: is it possible to reduce the number of separately
  measured operators?}
\newblock \bibinfo{journal}{Chemical Science}
  \bibinfo{year}{2019}{\natexlab{a}};\bibinfo{volume}{10}(\bibinfo{number}{13}):\bibinfo{pages}{3746--3755}.
\newblock \DOIprefix\doi{10.1039/c8sc05592k}.
%Type = Article
\bibitem[{Verteletskyi et~al.(2020)Verteletskyi, Yen and
  Izmaylov}]{Verteletskyi2020}
\bibinfo{author}{Verteletskyi\xfnm[ V.]}, \bibinfo{author}{Yen\xfnm[ T.C.]},
  \bibinfo{author}{Izmaylov\xfnm[ A.F.]}.
\newblock \bibinfo{title}{Measurement optimization in the variational quantum
  eigensolver using a minimum clique cover}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2020};\bibinfo{volume}{152}(\bibinfo{number}{12}):\bibinfo{pages}{124114}.
\newblock \DOIprefix\doi{10.1063/1.5141458}.
%Type = Misc
\bibitem[{O'Brien et~al.(2021{\natexlab{a}})O'Brien, Streif, Rubin, Santagati,
  Su, Huggins et~al.}]{OBrien2021}
\bibinfo{author}{O'Brien\xfnm[ T.E.]}, \bibinfo{author}{Streif\xfnm[ M.]},
  \bibinfo{author}{Rubin\xfnm[ N.C.]}, \bibinfo{author}{Santagati\xfnm[ R.]},
  \bibinfo{author}{Su\xfnm[ Y.]}, \bibinfo{author}{Huggins\xfnm[ W.J.]}, et~al.
\newblock \bibinfo{title}{Efficient quantum computation of molecular forces and
  other energy gradients}.
\newblock \bibinfo{year}{2021}{\natexlab{a}}.
\newblock \URLprefix \url{https://arxiv.org/abs/2111.12437}.
  \DOIprefix\doi{10.48550/ARXIV.2111.12437}.
%Type = Misc
\bibitem[{Yordanov et~al.(2020{\natexlab{a}})Yordanov, Armaos, Barnes and
  Arvidsson-Shukur}]{Yordanov2020_IQEB}
\bibinfo{author}{Yordanov\xfnm[ Y.S.]}, \bibinfo{author}{Armaos\xfnm[ V.]},
  \bibinfo{author}{Barnes\xfnm[ C.H.W.]},
  \bibinfo{author}{Arvidsson-Shukur\xfnm[ D.R.M.]}.
\newblock \bibinfo{title}{Iterative qubit-excitation based variational quantum
  eigensolver}.
\newblock \bibinfo{year}{2020}{\natexlab{a}}.
\newblock \href{http://arxiv.org/abs/2011.10540v1}{\tt arXiv:2011.10540v1}.
%Type = Article
\bibitem[{Tang et~al.(2021)Tang, Shkolnikov, Barron, Grimsley, Mayhall, Barnes
  et~al.}]{Tang2021}
\bibinfo{author}{Tang\xfnm[ H.L.]}, \bibinfo{author}{Shkolnikov\xfnm[ V.]},
  \bibinfo{author}{Barron\xfnm[ G.S.]}, \bibinfo{author}{Grimsley\xfnm[ H.R.]},
  \bibinfo{author}{Mayhall\xfnm[ N.J.]}, \bibinfo{author}{Barnes\xfnm[ E.]},
  et~al.
\newblock \bibinfo{title}{Qubit-{ADAPT}-{VQE}: An adaptive algorithm for
  constructing hardware-efficient ansätze on a quantum processor}.
\newblock \bibinfo{journal}{PRX Quantum}
  \bibinfo{year}{2021};\bibinfo{volume}{2}(\bibinfo{number}{2}):\bibinfo{pages}{020310}.
\newblock \DOIprefix\doi{10.1103/prxquantum.2.020310}.
%Type = Misc
\bibitem[{Vidal and Theis(2018{\natexlab{a}})}]{Vidal2018}
\bibinfo{author}{Vidal\xfnm[ J.G.]}, \bibinfo{author}{Theis\xfnm[ D.O.]}.
\newblock \bibinfo{title}{Calculus on parameterized quantum circuits}.
\newblock \bibinfo{year}{2018}{\natexlab{a}}.
\newblock \URLprefix \url{https://arxiv.org/abs/1812.06323}.
  \DOIprefix\doi{10.48550/ARXIV.1812.06323}.
%Type = Misc
\bibitem[{Watanabe et~al.(2021)Watanabe, Raymond, Ohnishi, Kaminishi and
  Sugawara}]{Watanabe2021WatanabeOptimizingSelection}
\bibinfo{author}{Watanabe\xfnm[ H.C.]}, \bibinfo{author}{Raymond\xfnm[ R.]},
  \bibinfo{author}{Ohnishi\xfnm[ Y.y.]}, \bibinfo{author}{Kaminishi\xfnm[ E.]},
  \bibinfo{author}{Sugawara\xfnm[ M.]}.
\newblock \bibinfo{title}{Optimizing parameterized quantum circuits with
  free-axis selection}.
\newblock \bibinfo{year}{2021}.
\newblock \URLprefix \url{https://arxiv.org/abs/2104.14875}.
  \DOIprefix\doi{10.48550/ARXIV.2104.14875}.
%Type = Misc
\bibitem[{Wada et~al.(2021)Wada, Raymond, Ohnishi, Kaminishi, Sugawara,
  Yamamoto et~al.}]{Wada2021SimulatingCircuits}
\bibinfo{author}{Wada\xfnm[ K.]}, \bibinfo{author}{Raymond\xfnm[ R.]},
  \bibinfo{author}{Ohnishi\xfnm[ Y.y.]}, \bibinfo{author}{Kaminishi\xfnm[ E.]},
  \bibinfo{author}{Sugawara\xfnm[ M.]}, \bibinfo{author}{Yamamoto\xfnm[ N.]},
  et~al.
\newblock \bibinfo{title}{Simulating time evolution with fully optimized
  single-qubit gates on parameterized quantum circuits}.
\newblock \bibinfo{year}{2021}.
\newblock \URLprefix \url{https://arxiv.org/abs/2111.05538}.
  \DOIprefix\doi{10.48550/ARXIV.2111.05538}.
%Type = Article
\bibitem[{McArdle et~al.(2019{\natexlab{b}})McArdle, Yuan and
  Benjamin}]{mcardleErrorMitigatedDigitalQuantum2019}
\bibinfo{author}{McArdle\xfnm[ S.]}, \bibinfo{author}{Yuan\xfnm[ X.]},
  \bibinfo{author}{Benjamin\xfnm[ S.]}.
\newblock \bibinfo{title}{Error-mitigated digital quantum simulation}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2019}{\natexlab{b}};\bibinfo{volume}{122}(\bibinfo{number}{18}):\bibinfo{pages}{1--17}.
\newblock \DOIprefix\doi{10.1103/physrevlett.122.180501}.
%Type = Article
\bibitem[{Bonet-Monroig et~al.(2018)Bonet-Monroig, Sagastizabal, Singh and
  O{\textquotesingle}Brien}]{bonet-monroigLowcostErrorMitigation2018}
\bibinfo{author}{Bonet-Monroig\xfnm[ X.]}, \bibinfo{author}{Sagastizabal\xfnm[
  R.]}, \bibinfo{author}{Singh\xfnm[ M.]},
  \bibinfo{author}{O{\textquotesingle}Brien\xfnm[ T.E.]}.
\newblock \bibinfo{title}{Low-cost error mitigation by symmetry verification}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2018};\bibinfo{volume}{98}(\bibinfo{number}{6}):\bibinfo{pages}{062339}.
\newblock \DOIprefix\doi{10.1103/physreva.98.062339}.
%Type = Article
\bibitem[{Temme et~al.(2017)Temme, Bravyi and
  Gambetta}]{temmeErrorMitigationShortDepth2017}
\bibinfo{author}{Temme\xfnm[ K.]}, \bibinfo{author}{Bravyi\xfnm[ S.]},
  \bibinfo{author}{Gambetta\xfnm[ J.M.]}.
\newblock \bibinfo{title}{Error mitigation for short-depth quantum circuits}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2017};\bibinfo{volume}{119}(\bibinfo{number}{18}):\bibinfo{pages}{1--15}.
\newblock \DOIprefix\doi{10.1103/physrevlett.119.180509}.
%Type = Article
\bibitem[{Li and Benjamin(2017)}]{liEfficientVariationalQuantum2017}
\bibinfo{author}{Li\xfnm[ Y.]}, \bibinfo{author}{Benjamin\xfnm[ S.C.]}.
\newblock \bibinfo{title}{Efficient variational quantum simulator incorporating
  active error minimization}.
\newblock \bibinfo{journal}{Physical Review X}
  \bibinfo{year}{2017};\bibinfo{volume}{7}(\bibinfo{number}{2}):\bibinfo{pages}{021050--021050}.
\newblock \DOIprefix\doi{10.1103/physrevx.7.021050}.
%Type = Article
\bibitem[{Berry et~al.(2018)Berry, Kieferov{\'{a}}, Scherer, Sanders, Low,
  Wiebe et~al.}]{Berry2018}
\bibinfo{author}{Berry\xfnm[ D.W.]}, \bibinfo{author}{Kieferov{\'{a}}\xfnm[
  M.]}, \bibinfo{author}{Scherer\xfnm[ A.]}, \bibinfo{author}{Sanders\xfnm[
  Y.R.]}, \bibinfo{author}{Low\xfnm[ G.H.]}, \bibinfo{author}{Wiebe\xfnm[ N.]},
  et~al.
\newblock \bibinfo{title}{Improved techniques for preparing eigenstates of
  fermionic hamiltonians}.
\newblock \bibinfo{journal}{npj Quantum Information}
  \bibinfo{year}{2018};\bibinfo{volume}{4}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1038/s41534-018-0071-5}.
%Type = Article
\bibitem[{Seeley et~al.(2012)Seeley, Richard and Love}]{Seeley2012}
\bibinfo{author}{Seeley\xfnm[ J.T.]}, \bibinfo{author}{Richard\xfnm[ M.J.]},
  \bibinfo{author}{Love\xfnm[ P.J.]}.
\newblock \bibinfo{title}{The {B}ravyi-{K}itaev transformation for quantum
  computation of electronic structure}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2012};\bibinfo{volume}{137}(\bibinfo{number}{22}):\bibinfo{pages}{224109}.
\newblock \DOIprefix\doi{10.1063/1.4768229}.
%Type = Article
\bibitem[{Bravyi and Kitaev(2002)}]{Bravyi2002}
\bibinfo{author}{Bravyi\xfnm[ S.B.]}, \bibinfo{author}{Kitaev\xfnm[ A.Y.]}.
\newblock \bibinfo{title}{Fermionic quantum computation}.
\newblock \bibinfo{journal}{Annals of Physics}
  \bibinfo{year}{2002};\bibinfo{volume}{298}(\bibinfo{number}{1}):\bibinfo{pages}{210--226}.
\newblock \DOIprefix\doi{10.1006/aphy.2002.6254}.
%Type = Article
\bibitem[{Tranter et~al.(2015)Tranter, Sofia, Seeley, Kaicher, McClean, Babbush
  et~al.}]{Tranter2015}
\bibinfo{author}{Tranter\xfnm[ A.]}, \bibinfo{author}{Sofia\xfnm[ S.]},
  \bibinfo{author}{Seeley\xfnm[ J.]}, \bibinfo{author}{Kaicher\xfnm[ M.]},
  \bibinfo{author}{McClean\xfnm[ J.]}, \bibinfo{author}{Babbush\xfnm[ R.]},
  et~al.
\newblock \bibinfo{title}{The bravyi-kitaev transformation: Properties and
  applications}.
\newblock \bibinfo{journal}{International Journal of Quantum Chemistry}
  \bibinfo{year}{2015};\bibinfo{volume}{115}(\bibinfo{number}{19}):\bibinfo{pages}{1431--1441}.
\newblock \DOIprefix\doi{10.1002/qua.24969}.
%Type = Misc
\bibitem[{Bravyi et~al.(2017)Bravyi, Gambetta, Mezzacapo and
  Temme}]{bravyi_tapering_2017}
\bibinfo{author}{Bravyi\xfnm[ S.]}, \bibinfo{author}{Gambetta\xfnm[ J.M.]},
  \bibinfo{author}{Mezzacapo\xfnm[ A.]}, \bibinfo{author}{Temme\xfnm[ K.]}.
\newblock \bibinfo{title}{Tapering off qubits to simulate fermionic
  hamiltonians}.
\newblock \bibinfo{year}{2017}.
\newblock \href{http://arxiv.org/abs/1701.08213v1}{\tt arXiv:1701.08213v1}.
%Type = Article
\bibitem[{Setia et~al.(2020)Setia, Chen, Rice, Mezzacapo, Pistoia and
  Whitfield}]{Setia2020}
\bibinfo{author}{Setia\xfnm[ K.]}, \bibinfo{author}{Chen\xfnm[ R.]},
  \bibinfo{author}{Rice\xfnm[ J.E.]}, \bibinfo{author}{Mezzacapo\xfnm[ A.]},
  \bibinfo{author}{Pistoia\xfnm[ M.]}, \bibinfo{author}{Whitfield\xfnm[ J.D.]}.
\newblock \bibinfo{title}{Reducing qubit requirements for quantum simulations
  using molecular point group symmetries}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2020};\bibinfo{volume}{16}(\bibinfo{number}{10}):\bibinfo{pages}{6091--6097}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.0c00113}.
%Type = Article
\bibitem[{Kirby et~al.(2021)Kirby, Tranter and Love}]{Kirby2021_CSVQE}
\bibinfo{author}{Kirby\xfnm[ W.M.]}, \bibinfo{author}{Tranter\xfnm[ A.]},
  \bibinfo{author}{Love\xfnm[ P.J.]}.
\newblock \bibinfo{title}{Contextual subspace variational quantum eigensolver}.
\newblock \bibinfo{journal}{Quantum}
  \bibinfo{year}{2021};\bibinfo{volume}{5}:\bibinfo{pages}{456}.
\newblock \DOIprefix\doi{10.22331/q-2021-05-14-456}.
%Type = Misc
\bibitem[{Gokhale and Chong(2019)}]{Gokhale2019_short}
\bibinfo{author}{Gokhale\xfnm[ P.]}, \bibinfo{author}{Chong\xfnm[ F.T.]}.
\newblock \bibinfo{title}{{$O(N^3)$} measurement cost for variational quantum
  eigensolver on molecular hamiltonians}.
\newblock \bibinfo{year}{2019}.
\newblock \href{http://arxiv.org/abs/1908.11857v1}{\tt arXiv:1908.11857v1}.
%Type = Article
\bibitem[{Crawford et~al.(2021)Crawford, van Straaten, Wang, Parks, Campbell
  and Brierley}]{Crawford2021}
\bibinfo{author}{Crawford\xfnm[ O.]}, \bibinfo{author}{van Straaten\xfnm[ B.]},
  \bibinfo{author}{Wang\xfnm[ D.]}, \bibinfo{author}{Parks\xfnm[ T.]},
  \bibinfo{author}{Campbell\xfnm[ E.]}, \bibinfo{author}{Brierley\xfnm[ S.]}.
\newblock \bibinfo{title}{Efficient quantum measurement of pauli operators in
  the presence of finite sampling error}.
\newblock \bibinfo{journal}{Quantum}
  \bibinfo{year}{2021};\bibinfo{volume}{5}:\bibinfo{pages}{385}.
\newblock \DOIprefix\doi{10.22331/q-2021-01-20-385}.
%Type = Article
\bibitem[{Ryabinkin et~al.(2020)Ryabinkin, Lang, Genin and
  Izmaylov}]{Ryabinkin2020}
\bibinfo{author}{Ryabinkin\xfnm[ I.G.]}, \bibinfo{author}{Lang\xfnm[ R.A.]},
  \bibinfo{author}{Genin\xfnm[ S.N.]}, \bibinfo{author}{Izmaylov\xfnm[ A.F.]}.
\newblock \bibinfo{title}{Iterative qubit coupled cluster approach with
  efficient screening of generators}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2020};\bibinfo{volume}{16}(\bibinfo{number}{2}):\bibinfo{pages}{1055--1063}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.9b01084}.
%Type = Misc
\bibitem[{Zhang et~al.(2020{\natexlab{a}})Zhang, Hsieh, Liu and
  Tao}]{Zhang2020}
\bibinfo{author}{Zhang\xfnm[ K.]}, \bibinfo{author}{Hsieh\xfnm[ M.H.]},
  \bibinfo{author}{Liu\xfnm[ L.]}, \bibinfo{author}{Tao\xfnm[ D.]}.
\newblock \bibinfo{title}{Toward trainability of quantum neural networks}.
\newblock \bibinfo{year}{2020}{\natexlab{a}}.
\newblock \href{http://arxiv.org/abs/2011.06258v2}{\tt arXiv:2011.06258v2}.
%Type = Article
\bibitem[{Claudino et~al.(2020)Claudino, Wright, McCaskey and
  Humble}]{Claudino2020}
\bibinfo{author}{Claudino\xfnm[ D.]}, \bibinfo{author}{Wright\xfnm[ J.]},
  \bibinfo{author}{McCaskey\xfnm[ A.J.]}, \bibinfo{author}{Humble\xfnm[ T.S.]}.
\newblock \bibinfo{title}{Benchmarking adaptive variational quantum
  eigensolvers}.
\newblock \bibinfo{journal}{Frontiers in Chemistry}
  \bibinfo{year}{2020};\bibinfo{volume}{8}.
\newblock \DOIprefix\doi{10.3389/fchem.2020.606863}.
%Type = Article
\bibitem[{Stokes et~al.(2020)Stokes, Izaac, Killoran and
  Carleo}]{stokes_quantum_2020}
\bibinfo{author}{Stokes\xfnm[ J.]}, \bibinfo{author}{Izaac\xfnm[ J.]},
  \bibinfo{author}{Killoran\xfnm[ N.]}, \bibinfo{author}{Carleo\xfnm[ G.]}.
\newblock \bibinfo{title}{Quantum natural gradient}.
\newblock \bibinfo{journal}{Quantum}
  \bibinfo{year}{2020};\bibinfo{volume}{4}:\bibinfo{pages}{269}.
\newblock \DOIprefix\doi{10.22331/q-2020-05-25-269}; \bibinfo{note}{arXiv:
  1909.02108}.
%Type = Article
\bibitem[{McArdle et~al.(2019{\natexlab{c}})McArdle, Jones, Endo, Li, Benjamin
  and Yuan}]{McArdle2019}
\bibinfo{author}{McArdle\xfnm[ S.]}, \bibinfo{author}{Jones\xfnm[ T.]},
  \bibinfo{author}{Endo\xfnm[ S.]}, \bibinfo{author}{Li\xfnm[ Y.]},
  \bibinfo{author}{Benjamin\xfnm[ S.C.]}, \bibinfo{author}{Yuan\xfnm[ X.]}.
\newblock \bibinfo{title}{Variational ansatz-based quantum simulation of
  imaginary time evolution}.
\newblock \bibinfo{journal}{npj Quantum Information}
  \bibinfo{year}{2019}{\natexlab{c}};\bibinfo{volume}{5}(\bibinfo{number}{1}):\bibinfo{pages}{75}.
\newblock \DOIprefix\doi{10.1038/s41534-019-0187-2}; \bibinfo{note}{arXiv:
  1804.03023}.
%Type = Article
\bibitem[{K\"{o}ppl and Werner(2016)}]{Koppl2016}
\bibinfo{author}{K\"{o}ppl\xfnm[ C.]}, \bibinfo{author}{Werner\xfnm[ H.J.]}.
\newblock \bibinfo{title}{Parallel and low-order scaling implementation of
  hartree{\textendash}fock exchange using local density fitting}.
\newblock \bibinfo{journal}{J Chem Theory Comput}
  \bibinfo{year}{2016};\bibinfo{volume}{12}(\bibinfo{number}{7}):\bibinfo{pages}{3122--3134}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.6b00251}.
%Type = Article
\bibitem[{Havl{\'{\i}}{\v{c}}ek et~al.(2017)Havl{\'{\i}}{\v{c}}ek, Troyer and
  Whitfield}]{Havlek2017}
\bibinfo{author}{Havl{\'{\i}}{\v{c}}ek\xfnm[ V.]},
  \bibinfo{author}{Troyer\xfnm[ M.]}, \bibinfo{author}{Whitfield\xfnm[ J.D.]}.
\newblock \bibinfo{title}{Operator locality in the quantum simulation of
  fermionic models}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2017};\bibinfo{volume}{95}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physreva.95.032332}.
%Type = Article
\bibitem[{Sokolov et~al.(2020)Sokolov, Barkoutsos, Ollitrault, Greenberg, Rice,
  Pistoia et~al.}]{Sokolov2020}
\bibinfo{author}{Sokolov\xfnm[ I.O.]}, \bibinfo{author}{Barkoutsos\xfnm[
  P.K.]}, \bibinfo{author}{Ollitrault\xfnm[ P.J.]},
  \bibinfo{author}{Greenberg\xfnm[ D.]}, \bibinfo{author}{Rice\xfnm[ J.]},
  \bibinfo{author}{Pistoia\xfnm[ M.]}, et~al.
\newblock \bibinfo{title}{Quantum orbital-optimized unitary coupled cluster
  methods in the strongly correlated regime: Can quantum algorithms outperform
  their classical equivalents?}
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2020};\bibinfo{volume}{152}(\bibinfo{number}{12}):\bibinfo{pages}{124107}.
\newblock \DOIprefix\doi{10.1063/1.5141835}.
%Type = Article
\bibitem[{Setia and Whitfield(2018)}]{Setia2018}
\bibinfo{author}{Setia\xfnm[ K.]}, \bibinfo{author}{Whitfield\xfnm[ J.D.]}.
\newblock \bibinfo{title}{Bravyi-kitaev superfast simulation of electronic
  structure on a quantum computer}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2018};\bibinfo{volume}{148}(\bibinfo{number}{16}):\bibinfo{pages}{164104}.
\newblock \DOIprefix\doi{10.1063/1.5019371}.
%Type = Misc
\bibitem[{Vogt et~al.(2020)Vogt, Zanker, Reiner, Eckl, Marusczyk and
  Marthaler}]{Vogt2020}
\bibinfo{author}{Vogt\xfnm[ N.]}, \bibinfo{author}{Zanker\xfnm[ S.]},
  \bibinfo{author}{Reiner\xfnm[ J.M.]}, \bibinfo{author}{Eckl\xfnm[ T.]},
  \bibinfo{author}{Marusczyk\xfnm[ A.]}, \bibinfo{author}{Marthaler\xfnm[ M.]}.
\newblock \bibinfo{title}{Preparing symmetry broken ground states with
  variational quantum algorithms}.
\newblock \bibinfo{year}{2020}.
\newblock \href{http://arxiv.org/abs/2007.01582v2}{\tt arXiv:2007.01582v2}.
%Type = Article
\bibitem[{Choquette et~al.(2021)Choquette, Paolo, Barkoutsos,
  S{\'{e}}n{\'{e}}chal, Tavernelli and Blais}]{Choquette2021}
\bibinfo{author}{Choquette\xfnm[ A.]}, \bibinfo{author}{Paolo\xfnm[ A.D.]},
  \bibinfo{author}{Barkoutsos\xfnm[ P.K.]},
  \bibinfo{author}{S{\'{e}}n{\'{e}}chal\xfnm[ D.]},
  \bibinfo{author}{Tavernelli\xfnm[ I.]}, \bibinfo{author}{Blais\xfnm[ A.]}.
\newblock \bibinfo{title}{Quantum-optimal-control-inspired ansatz for
  variational quantum algorithms}.
\newblock \bibinfo{journal}{Physical Review Research}
  \bibinfo{year}{2021};\bibinfo{volume}{3}(\bibinfo{number}{2}).
\newblock \DOIprefix\doi{10.1103/physrevresearch.3.023092}.
%Type = Article
\bibitem[{Fan and Wu(1970)}]{Fan1970}
\bibinfo{author}{Fan\xfnm[ C.]}, \bibinfo{author}{Wu\xfnm[ F.Y.]}.
\newblock \bibinfo{title}{General lattice model of phase transitions}.
\newblock \bibinfo{journal}{Phys Rev B}
  \bibinfo{year}{1970};\bibinfo{volume}{2}(\bibinfo{number}{3}):\bibinfo{pages}{723--733}.
\newblock \DOIprefix\doi{10.1103/physrevb.2.723}.
%Type = Book
\bibitem[{Marro and Dickman(1999)}]{Marro1999}
\bibinfo{author}{Marro\xfnm[ J.]}, \bibinfo{author}{Dickman\xfnm[ R.]}.
\newblock \bibinfo{title}{Nonequilibrium Phase Transitions in Lattice Models}.
\newblock \bibinfo{publisher}{Cambridge University Press};
  \bibinfo{year}{1999}.
\newblock \DOIprefix\doi{10.1017/cbo9780511524288}.
%Type = Article
\bibitem[{Stanislavchuk et~al.(2015)Stanislavchuk, Litvinchuk, Hu, Jeon, Ji,
  Cheong et~al.}]{Stanislavchuk2015}
\bibinfo{author}{Stanislavchuk\xfnm[ T.N.]}, \bibinfo{author}{Litvinchuk\xfnm[
  A.P.]}, \bibinfo{author}{Hu\xfnm[ R.]}, \bibinfo{author}{Jeon\xfnm[ Y.H.]},
  \bibinfo{author}{Ji\xfnm[ S.D.]}, \bibinfo{author}{Cheong\xfnm[ S.W.]},
  et~al.
\newblock \bibinfo{title}{Optical properties, lattice dynamics, and structural
  phase transition in hexagonal2h-{BaMnO}3single crystals}.
\newblock \bibinfo{journal}{Phys Rev B}
  \bibinfo{year}{2015};\bibinfo{volume}{92}(\bibinfo{number}{13}).
\newblock \DOIprefix\doi{10.1103/physrevb.92.134308}.
%Type = Article
\bibitem[{Choi et~al.(2019)Choi, Dar and Pappu}]{Choi2019}
\bibinfo{author}{Choi\xfnm[ J.M.]}, \bibinfo{author}{Dar\xfnm[ F.]},
  \bibinfo{author}{Pappu\xfnm[ R.V.]}.
\newblock \bibinfo{title}{{LASSI}: A lattice model for simulating phase
  transitions of multivalent proteins}.
\newblock \bibinfo{journal}{PLoS Comput Biol}
  \bibinfo{year}{2019};\bibinfo{volume}{15}(\bibinfo{number}{10}):\bibinfo{pages}{e1007028}.
\newblock \DOIprefix\doi{10.1371/journal.pcbi.1007028}.
%Type = Article
\bibitem[{Li et~al.(2013)Li, Wang, Wang, Gao, Geng, Li et~al.}]{Li2013}
\bibinfo{author}{Li\xfnm[ Y.N.]}, \bibinfo{author}{Wang\xfnm[ S.]},
  \bibinfo{author}{Wang\xfnm[ T.]}, \bibinfo{author}{Gao\xfnm[ R.]},
  \bibinfo{author}{Geng\xfnm[ C.Y.]}, \bibinfo{author}{Li\xfnm[ Y.W.]}, et~al.
\newblock \bibinfo{title}{Energies and spin states of fes$^{0/-}$,
  fes$_2^{0/-}$, fe$_2$s$_2^{0/-}$, fe$_3$s$_4 ^{0/-}$, and fe$_4$s$_4 ^{0/-}$
  clusters}.
\newblock \bibinfo{journal}{ChemPhysChem}
  \bibinfo{year}{2013};\bibinfo{volume}{14}(\bibinfo{number}{6}):\bibinfo{pages}{1182--1189}.
\newblock \URLprefix \url{https://doi.org/10.1002/cphc.201201043}.
  \DOIprefix\doi{10.1002/cphc.201201043}.
%Type = Article
\bibitem[{Kjaergaard et~al.(2020)Kjaergaard, Schwartz, Braumüller, Krantz,
  Wang, Gustavsson et~al.}]{Kjaergaard2020}
\bibinfo{author}{Kjaergaard\xfnm[ M.]}, \bibinfo{author}{Schwartz\xfnm[ M.E.]},
  \bibinfo{author}{Braumüller\xfnm[ J.]}, \bibinfo{author}{Krantz\xfnm[ P.]},
  \bibinfo{author}{Wang\xfnm[ J.I.J.]}, \bibinfo{author}{Gustavsson\xfnm[ S.]},
  et~al.
\newblock \bibinfo{title}{Superconducting qubits: Current state of play}.
\newblock \bibinfo{journal}{Annual Review of Condensed Matter Physics}
  \bibinfo{year}{2020};\bibinfo{volume}{11}(\bibinfo{number}{1}):\bibinfo{pages}{369--395}.
\newblock \DOIprefix\doi{10.1146/annurev-conmatphys-031119-050605}.
%Type = Article
\bibitem[{Stenger et~al.(2022)Stenger, Gunlycke and Hellberg}]{Stenger2022}
\bibinfo{author}{Stenger\xfnm[ J.P.T.]}, \bibinfo{author}{Gunlycke\xfnm[ D.]},
  \bibinfo{author}{Hellberg\xfnm[ C.S.]}.
\newblock \bibinfo{title}{Expanding variational quantum eigensolvers to larger
  systems by dividing the calculations between classical and quantum hardware}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2022};\bibinfo{volume}{105}(\bibinfo{number}{2}).
\newblock \URLprefix \url{https://doi.org/10.1103/physreva.105.022438}.
  \DOIprefix\doi{10.1103/physreva.105.022438}.
%Type = Misc
\bibitem[{Okada et~al.(2022)Okada, Osaki, Mitarai and Fujii}]{Okada2022}
\bibinfo{author}{Okada\xfnm[ K.N.]}, \bibinfo{author}{Osaki\xfnm[ K.]},
  \bibinfo{author}{Mitarai\xfnm[ K.]}, \bibinfo{author}{Fujii\xfnm[ K.]}.
\newblock \bibinfo{title}{Identification of topological phases using
  classically-optimized variational quantum eigensolver}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2202.02909}.
  \DOIprefix\doi{10.48550/ARXIV.2202.02909}.
%Type = Misc
\bibitem[{Zhang et~al.(2021{\natexlab{a}})Zhang, Cincio, Negre, Czarnik, Coles,
  Anisimov et~al.}]{Zhang2021}
\bibinfo{author}{Zhang\xfnm[ Y.]}, \bibinfo{author}{Cincio\xfnm[ L.]},
  \bibinfo{author}{Negre\xfnm[ C.F.A.]}, \bibinfo{author}{Czarnik\xfnm[ P.]},
  \bibinfo{author}{Coles\xfnm[ P.]}, \bibinfo{author}{Anisimov\xfnm[ P.M.]},
  et~al.
\newblock \bibinfo{title}{Variational quantum eigensolver with reduced circuit
  complexity}.
\newblock \bibinfo{year}{2021}{\natexlab{a}}.
\newblock \href{http://arxiv.org/abs/2106.07619v1}{\tt arXiv:2106.07619v1}.
%Type = Article
\bibitem[{Hehre et~al.(1969)Hehre, Stewart and Pople}]{Hehre1969}
\bibinfo{author}{Hehre\xfnm[ W.J.]}, \bibinfo{author}{Stewart\xfnm[ R.F.]},
  \bibinfo{author}{Pople\xfnm[ J.A.]}.
\newblock \bibinfo{title}{Self-consistent molecular-orbital methods. i. use of
  gaussian expansions of slater-type atomic orbitals}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{1969};\bibinfo{volume}{51}(\bibinfo{number}{6}):\bibinfo{pages}{2657--2664}.
\newblock \DOIprefix\doi{10.1063/1.1672392}.
%Type = Article
\bibitem[{Stewart(1970)}]{Stewart1970}
\bibinfo{author}{Stewart\xfnm[ R.F.]}.
\newblock \bibinfo{title}{Small gaussian expansions of slater-type orbitals}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{1970};\bibinfo{volume}{52}(\bibinfo{number}{1}):\bibinfo{pages}{431--438}.
\newblock \DOIprefix\doi{10.1063/1.1672702}.
%Type = Article
\bibitem[{Dunning(1989)}]{Dunning1989}
\bibinfo{author}{Dunning\xfnm[ T.H.]}.
\newblock \bibinfo{title}{Gaussian basis sets for use in correlated molecular
  calculations. i. the atoms boron through neon and hydrogen}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{1989};\bibinfo{volume}{90}(\bibinfo{number}{2}):\bibinfo{pages}{1007--1023}.
\newblock \DOIprefix\doi{10.1063/1.456153}.
%Type = Article
\bibitem[{Varandas(2000)}]{Varandas2000}
\bibinfo{author}{Varandas\xfnm[ A.J.C.]}.
\newblock \bibinfo{title}{Basis-set extrapolation of the correlation energy}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2000};\bibinfo{volume}{113}(\bibinfo{number}{20}):\bibinfo{pages}{8880--8887}.
\newblock \URLprefix \url{https://doi.org/10.1063/1.1319644}.
  \DOIprefix\doi{10.1063/1.1319644}.
  \href{http://arxiv.org/abs/https://doi.org/10.1063/1.1319644}{\tt
  arXiv:https://doi.org/10.1063/1.1319644}.
%Type = Article
\bibitem[{Kottmann et~al.(2021{\natexlab{a}})Kottmann, Schleich, Tamayo-Mendoza
  and Aspuru-Guzik}]{Kottmann2021_1}
\bibinfo{author}{Kottmann\xfnm[ J.S.]}, \bibinfo{author}{Schleich\xfnm[ P.]},
  \bibinfo{author}{Tamayo-Mendoza\xfnm[ T.]},
  \bibinfo{author}{Aspuru-Guzik\xfnm[ A.]}.
\newblock \bibinfo{title}{Reducing qubit requirements while maintaining
  numerical precision for the variational quantum eigensolver: A basis-set-free
  approach}.
\newblock \bibinfo{journal}{The Journal of Physical Chemistry Letters}
  \bibinfo{year}{2021}{\natexlab{a}};\bibinfo{volume}{12}(\bibinfo{number}{1}):\bibinfo{pages}{663--673}.
\newblock \DOIprefix\doi{10.1021/acs.jpclett.0c03410}.
%Type = Misc
\bibitem[{Wiesner(1996)}]{Wiesner1996}
\bibinfo{author}{Wiesner\xfnm[ S.]}.
\newblock \bibinfo{title}{Simulations of many-body quantum systems by a quantum
  computer}.
\newblock \bibinfo{year}{1996}.
\newblock \href{http://arxiv.org/abs/quant-ph/9603028v1}{\tt
  arXiv:quant-ph/9603028v1}.
%Type = Article
\bibitem[{Zalka(1998)}]{Zalka1998}
\bibinfo{author}{Zalka\xfnm[ C.]}.
\newblock \bibinfo{title}{Simulating quantum systems on a quantum computer}.
\newblock \bibinfo{journal}{Proceedings of the Royal Society of London Series
  A: Mathematical, Physical and Engineering Sciences}
  \bibinfo{year}{1998};\bibinfo{volume}{454}(\bibinfo{number}{1969}):\bibinfo{pages}{313--322}.
\newblock \DOIprefix\doi{10.1098/rspa.1998.0162}.
%Type = Article
\bibitem[{Lidar and Wang(1999)}]{Lidar1999}
\bibinfo{author}{Lidar\xfnm[ D.A.]}, \bibinfo{author}{Wang\xfnm[ H.]}.
\newblock \bibinfo{title}{Calculating the thermal rate constant with
  exponential speedup on a quantum computer}.
\newblock \bibinfo{journal}{Physical Review E}
  \bibinfo{year}{1999};\bibinfo{volume}{59}(\bibinfo{number}{2}):\bibinfo{pages}{2429--2438}.
\newblock \DOIprefix\doi{10.1103/physreve.59.2429}.
%Type = Article
\bibitem[{Kassal et~al.(2008)Kassal, Jordan, Love, Mohseni and
  Aspuru-Guzik}]{Kassal2008}
\bibinfo{author}{Kassal\xfnm[ I.]}, \bibinfo{author}{Jordan\xfnm[ S.P.]},
  \bibinfo{author}{Love\xfnm[ P.J.]}, \bibinfo{author}{Mohseni\xfnm[ M.]},
  \bibinfo{author}{Aspuru-Guzik\xfnm[ A.]}.
\newblock \bibinfo{title}{Polynomial-time quantum algorithm for the simulation
  of chemical dynamics}.
\newblock \bibinfo{journal}{Proceedings of the National Academy of Sciences}
  \bibinfo{year}{2008};\bibinfo{volume}{105}(\bibinfo{number}{48}):\bibinfo{pages}{18681--18686}.
\newblock \DOIprefix\doi{10.1073/pnas.0808245105}.
%Type = Article
\bibitem[{Ward et~al.(2009)Ward, Kassal and Aspuru-Guzik}]{Ward2009}
\bibinfo{author}{Ward\xfnm[ N.J.]}, \bibinfo{author}{Kassal\xfnm[ I.]},
  \bibinfo{author}{Aspuru-Guzik\xfnm[ A.]}.
\newblock \bibinfo{title}{Preparation of many-body states for quantum
  simulation}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2009};\bibinfo{volume}{130}(\bibinfo{number}{19}):\bibinfo{pages}{194105}.
\newblock \DOIprefix\doi{10.1063/1.3115177}.
%Type = Article
\bibitem[{Jones et~al.(2012)Jones, Whitfield, McMahon, Yung, Meter,
  Aspuru-Guzik et~al.}]{Jones2012}
\bibinfo{author}{Jones\xfnm[ N.C.]}, \bibinfo{author}{Whitfield\xfnm[ J.D.]},
  \bibinfo{author}{McMahon\xfnm[ P.L.]}, \bibinfo{author}{Yung\xfnm[ M.H.]},
  \bibinfo{author}{Meter\xfnm[ R.V.]}, \bibinfo{author}{Aspuru-Guzik\xfnm[
  A.]}, et~al.
\newblock \bibinfo{title}{Faster quantum chemistry simulation on fault-tolerant
  quantum computers}.
\newblock \bibinfo{journal}{New Journal of Physics}
  \bibinfo{year}{2012};\bibinfo{volume}{14}(\bibinfo{number}{11}):\bibinfo{pages}{115023}.
\newblock \DOIprefix\doi{10.1088/1367-2630/14/11/115023}.
%Type = Article
\bibitem[{Kivlichan et~al.(2017)Kivlichan, Wiebe, Babbush and
  Aspuru-Guzik}]{Kivlichan2017}
\bibinfo{author}{Kivlichan\xfnm[ I.D.]}, \bibinfo{author}{Wiebe\xfnm[ N.]},
  \bibinfo{author}{Babbush\xfnm[ R.]}, \bibinfo{author}{Aspuru-Guzik\xfnm[
  A.]}.
\newblock \bibinfo{title}{Bounding the costs of quantum simulation of many-body
  physics in real space}.
\newblock \bibinfo{journal}{Journal of Physics A: Mathematical and Theoretical}
  \bibinfo{year}{2017};\bibinfo{volume}{50}(\bibinfo{number}{30}):\bibinfo{pages}{305301}.
\newblock \DOIprefix\doi{10.1088/1751-8121/aa77b8}.
%Type = Article
\bibitem[{Verma et~al.(2021)Verma, Huntington, Coons, Kawashima, Yamazaki and
  Zaribafiyan}]{Verma2021}
\bibinfo{author}{Verma\xfnm[ P.]}, \bibinfo{author}{Huntington\xfnm[ L.]},
  \bibinfo{author}{Coons\xfnm[ M.P.]}, \bibinfo{author}{Kawashima\xfnm[ Y.]},
  \bibinfo{author}{Yamazaki\xfnm[ T.]}, \bibinfo{author}{Zaribafiyan\xfnm[
  A.]}.
\newblock \bibinfo{title}{Scaling up electronic structure calculations on
  quantum computers: The frozen natural orbital based method of increments}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2021};\bibinfo{volume}{155}(\bibinfo{number}{3}):\bibinfo{pages}{034110}.
\newblock \URLprefix \url{https://doi.org/10.1063/5.0054647}.
  \DOIprefix\doi{10.1063/5.0054647}.
%Type = Article
\bibitem[{Mochizuki et~al.(2019)Mochizuki, Okuwaki, Kato and
  Minato}]{Mochizuki2019}
\bibinfo{author}{Mochizuki\xfnm[ Y.]}, \bibinfo{author}{Okuwaki\xfnm[ K.]},
  \bibinfo{author}{Kato\xfnm[ T.]}, \bibinfo{author}{Minato\xfnm[ Y.]}.
\newblock \bibinfo{title}{Reduction of orbital space for molecular orbital
  calculations with quantum computation simulator for educations}.
\newblock \bibinfo{journal}{ChemRxiv} \bibinfo{year}{2019};\URLprefix
  \url{https://doi.org/10.26434/chemrxiv.9863810.v1}.
  \DOIprefix\doi{10.26434/chemrxiv.9863810.v1}.
%Type = Article
\bibitem[{Lloyd(1996)}]{Lloyd1996}
\bibinfo{author}{Lloyd\xfnm[ S.]}.
\newblock \bibinfo{title}{Universal quantum simulators}.
\newblock \bibinfo{journal}{Science}
  \bibinfo{year}{1996};\bibinfo{volume}{273}(\bibinfo{number}{5278}):\bibinfo{pages}{1073--1078}.
\newblock \DOIprefix\doi{10.1126/science.273.5278.1073}.
%Type = Article
\bibitem[{Boghosian and Taylor(1998)}]{Boghosian1998}
\bibinfo{author}{Boghosian\xfnm[ B.M.]}, \bibinfo{author}{Taylor\xfnm[ W.]}.
\newblock \bibinfo{title}{Simulating quantum mechanics on a quantum computer}.
\newblock \bibinfo{journal}{Physica D: Nonlinear Phenomena}
  \bibinfo{year}{1998};\bibinfo{volume}{120}(\bibinfo{number}{1-2}):\bibinfo{pages}{30--42}.
\newblock \DOIprefix\doi{10.1016/s0167-2789(98)00042-6}.
%Type = Misc
\bibitem[{Su et~al.(2021)Su, Berry, Wiebe, Rubin and Babbush}]{Su2021}
\bibinfo{author}{Su\xfnm[ Y.]}, \bibinfo{author}{Berry\xfnm[ D.W.]},
  \bibinfo{author}{Wiebe\xfnm[ N.]}, \bibinfo{author}{Rubin\xfnm[ N.]},
  \bibinfo{author}{Babbush\xfnm[ R.]}.
\newblock \bibinfo{title}{Fault-tolerant quantum simulations of chemistry in
  first quantization}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2105.12767v3}{\tt arXiv:2105.12767v3}.
%Type = Article
\bibitem[{Slater(1929)}]{Slater1929}
\bibinfo{author}{Slater\xfnm[ J.C.]}.
\newblock \bibinfo{title}{The theory of complex spectra}.
\newblock \bibinfo{journal}{Physical Review}
  \bibinfo{year}{1929};\bibinfo{volume}{34}(\bibinfo{number}{10}):\bibinfo{pages}{1293--1322}.
\newblock \DOIprefix\doi{10.1103/physrev.34.1293}.
%Type = Article
\bibitem[{Condon(1930)}]{Condon1930}
\bibinfo{author}{Condon\xfnm[ E.U.]}.
\newblock \bibinfo{title}{The theory of complex spectra}.
\newblock \bibinfo{journal}{Physical Review}
  \bibinfo{year}{1930};\bibinfo{volume}{36}(\bibinfo{number}{7}):\bibinfo{pages}{1121--1133}.
\newblock \DOIprefix\doi{10.1103/physrev.36.1121}.
%Type = Article
\bibitem[{Moll et~al.(2018)Moll, Barkoutsos, Bishop, Chow, Cross, Egger
  et~al.}]{Moll2018}
\bibinfo{author}{Moll\xfnm[ N.]}, \bibinfo{author}{Barkoutsos\xfnm[ P.]},
  \bibinfo{author}{Bishop\xfnm[ L.S.]}, \bibinfo{author}{Chow\xfnm[ J.M.]},
  \bibinfo{author}{Cross\xfnm[ A.]}, \bibinfo{author}{Egger\xfnm[ D.J.]},
  et~al.
\newblock \bibinfo{title}{Quantum optimization using variational algorithms on
  near-term quantum devices}.
\newblock \bibinfo{journal}{Quantum Science and Technology}
  \bibinfo{year}{2018};\bibinfo{volume}{3}(\bibinfo{number}{3}):\bibinfo{pages}{030503}.
\newblock \DOIprefix\doi{10.1088/2058-9565/aab822}.
%Type = Book
\bibitem[{Harrison(2004)}]{Harrison2004}
\bibinfo{author}{Harrison\xfnm[ W.A.]}.
\newblock \bibinfo{title}{Elementary Electronic Structure}.
\newblock \bibinfo{publisher}{{WSPC}}; \bibinfo{year}{2004}.
\newblock \DOIprefix\doi{10.1142/5432}.
%Type = Article
\bibitem[{Vojta(2003)}]{Vojta2003}
\bibinfo{author}{Vojta\xfnm[ M.]}.
\newblock \bibinfo{title}{Quantum phase transitions}.
\newblock \bibinfo{journal}{Reports on Progress in Physics}
  \bibinfo{year}{2003};\bibinfo{volume}{66}(\bibinfo{number}{12}):\bibinfo{pages}{2069--2110}.
\newblock \DOIprefix\doi{10.1088/0034-4885/66/12/r01}.
%Type = Book
\bibitem[{Sachdev(2009)}]{Sachdev2009}
\bibinfo{author}{Sachdev\xfnm[ S.]}.
\newblock \bibinfo{title}{Quantum Phase Transitions}.
\newblock \bibinfo{publisher}{Cambridge University Press};
  \bibinfo{year}{2009}.
\newblock \DOIprefix\doi{10.1017/cbo9780511973765}.
%Type = Book
\bibitem[{Simon(2013)}]{Simon2013}
\bibinfo{author}{Simon\xfnm[ S.]}.
\newblock \bibinfo{title}{The Oxford Solid State Basics}.
\newblock \bibinfo{address}{Oxford}: \bibinfo{publisher}{Oxford University
  Press}; \bibinfo{year}{2013}.
\newblock ISBN \bibinfo{isbn}{9780199680771}.
%Type = Article
\bibitem[{Bauer et~al.(2016)Bauer, Wecker, Millis, Hastings and
  Troyer}]{Bauer2016}
\bibinfo{author}{Bauer\xfnm[ B.]}, \bibinfo{author}{Wecker\xfnm[ D.]},
  \bibinfo{author}{Millis\xfnm[ A.J.]}, \bibinfo{author}{Hastings\xfnm[ M.B.]},
  \bibinfo{author}{Troyer\xfnm[ M.]}.
\newblock \bibinfo{title}{Hybrid quantum-classical approach to correlated
  materials}.
\newblock \bibinfo{journal}{Phys Rev X}
  \bibinfo{year}{2016};\bibinfo{volume}{6}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physrevx.6.031045}.
%Type = Misc
\bibitem[{Bosse and Montanaro(2021)}]{bosse2021probing}
\bibinfo{author}{Bosse\xfnm[ J.L.]}, \bibinfo{author}{Montanaro\xfnm[ A.]}.
\newblock \bibinfo{title}{Probing ground state properties of the kagome
  antiferromagnetic heisenberg model using the variational quantum
  eigensolver}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2108.08086}{\tt arXiv:2108.08086}.
%Type = Misc
\bibitem[{Kattemölle and van Wezel(2021)}]{kattemolle2021variational}
\bibinfo{author}{Kattemölle\xfnm[ J.]}, \bibinfo{author}{van Wezel\xfnm[ J.]}.
\newblock \bibinfo{title}{Variational quantum eigensolver for the heisenberg
  antiferromagnet on the kagome lattice}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2108.02175}{\tt arXiv:2108.02175}.
%Type = Inbook
\bibitem[{Pesonen and Halonen(2003)}]{03PeHa}
\bibinfo{author}{Pesonen\xfnm[ J.]}, \bibinfo{author}{Halonen\xfnm[ L.]}.
\newblock \bibinfo{title}{Recent Advances in the Theory of Vibration–Rotation
  Hamiltonians}; chap.~\bibinfo{chapter}{4}.
\newblock \bibinfo{publisher}{John Wiley \& Sons, Ltd}.
\newblock ISBN \bibinfo{isbn}{9780471428022}; \bibinfo{year}{2003}, p.
  \bibinfo{pages}{269--349}.
\newblock \DOIprefix\doi{10.1002/0471428027.ch4}.
%Type = Article
\bibitem[{McClain et~al.(2017)McClain, Sun, Chan and Berkelbach}]{McClain2017}
\bibinfo{author}{McClain\xfnm[ J.]}, \bibinfo{author}{Sun\xfnm[ Q.]},
  \bibinfo{author}{Chan\xfnm[ G.K.L.]}, \bibinfo{author}{Berkelbach\xfnm[
  T.C.]}.
\newblock \bibinfo{title}{Gaussian-based coupled-cluster theory for the
  ground-state and band structure of solids}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2017};\bibinfo{volume}{13}(\bibinfo{number}{3}):\bibinfo{pages}{1209--1218}.
\newblock \URLprefix \url{https://doi.org/10.1021/acs.jctc.7b00049}.
  \DOIprefix\doi{10.1021/acs.jctc.7b00049}.
%Type = Article
\bibitem[{Moll et~al.(2016)Moll, Fuhrer, Staar and Tavernelli}]{Moll2016}
\bibinfo{author}{Moll\xfnm[ N.]}, \bibinfo{author}{Fuhrer\xfnm[ A.]},
  \bibinfo{author}{Staar\xfnm[ P.]}, \bibinfo{author}{Tavernelli\xfnm[ I.]}.
\newblock \bibinfo{title}{Optimizing qubit resources for quantum chemistry
  simulations in second quantization on a quantum computer}.
\newblock \bibinfo{journal}{Journal of Physics A: Mathematical and Theoretical}
  \bibinfo{year}{2016};\bibinfo{volume}{49}(\bibinfo{number}{29}):\bibinfo{pages}{295301}.
\newblock \DOIprefix\doi{10.1088/1751-8113/49/29/295301}.
%Type = Article
\bibitem[{Steudtner and Wehner(2018)}]{Steudtner2018}
\bibinfo{author}{Steudtner\xfnm[ M.]}, \bibinfo{author}{Wehner\xfnm[ S.]}.
\newblock \bibinfo{title}{Fermion-to-qubit mappings with varying resource
  requirements for quantum simulation}.
\newblock \bibinfo{journal}{New Journal of Physics}
  \bibinfo{year}{2018};\bibinfo{volume}{20}(\bibinfo{number}{6}):\bibinfo{pages}{063010}.
\newblock \DOIprefix\doi{10.1088/1367-2630/aac54f}.
%Type = Article
\bibitem[{Clinton et~al.(2021)Clinton, Bausch and Cubitt}]{Clinton2020}
\bibinfo{author}{Clinton\xfnm[ L.]}, \bibinfo{author}{Bausch\xfnm[ J.]},
  \bibinfo{author}{Cubitt\xfnm[ T.]}.
\newblock \bibinfo{title}{Hamiltonian simulation algorithms for near-term
  quantum hardware}.
\newblock \bibinfo{journal}{Nature Communications}
  \bibinfo{year}{2021};\bibinfo{volume}{12}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1038/s41467-021-25196-0}.
  \href{http://arxiv.org/abs/2003.06886v3}{\tt arXiv:2003.06886v3};
  \bibinfo{note}{nat Commun 12, 4989 (2021)}.
%Type = Article
\bibitem[{Cade et~al.(2020)Cade, Mineh, Montanaro and Stanisic}]{Cade2020}
\bibinfo{author}{Cade\xfnm[ C.]}, \bibinfo{author}{Mineh\xfnm[ L.]},
  \bibinfo{author}{Montanaro\xfnm[ A.]}, \bibinfo{author}{Stanisic\xfnm[ S.]}.
\newblock \bibinfo{title}{Strategies for solving the fermi-hubbard model on
  near-term quantum computers}.
\newblock \bibinfo{journal}{Physical Review B}
  \bibinfo{year}{2020};\bibinfo{volume}{102}(\bibinfo{number}{23}).
\newblock \DOIprefix\doi{10.1103/physrevb.102.235122}.
%Type = Article
\bibitem[{Tranter et~al.(2018)Tranter, Love, Mintert and Coveney}]{Tranter2018}
\bibinfo{author}{Tranter\xfnm[ A.]}, \bibinfo{author}{Love\xfnm[ P.J.]},
  \bibinfo{author}{Mintert\xfnm[ F.]}, \bibinfo{author}{Coveney\xfnm[ P.V.]}.
\newblock \bibinfo{title}{A comparison of the bravyi{\textendash}kitaev and
  jordan{\textendash}wigner transformations for the quantum simulation of
  quantum chemistry}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2018};\bibinfo{volume}{14}(\bibinfo{number}{11}):\bibinfo{pages}{5617--5630}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.8b00450}.
%Type = Article
\bibitem[{Ortiz et~al.(2001)Ortiz, Gubernatis, Knill and Laflamme}]{Ortiz2001}
\bibinfo{author}{Ortiz\xfnm[ G.]}, \bibinfo{author}{Gubernatis\xfnm[ J.E.]},
  \bibinfo{author}{Knill\xfnm[ E.]}, \bibinfo{author}{Laflamme\xfnm[ R.]}.
\newblock \bibinfo{title}{Quantum algorithms for fermionic simulations}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2001};\bibinfo{volume}{64}(\bibinfo{number}{2}).
\newblock \DOIprefix\doi{10.1103/physreva.64.022319}.
%Type = Article
\bibitem[{Somma et~al.(2002)Somma, Ortiz, Gubernatis, Knill and
  Laflamme}]{Somma2002}
\bibinfo{author}{Somma\xfnm[ R.]}, \bibinfo{author}{Ortiz\xfnm[ G.]},
  \bibinfo{author}{Gubernatis\xfnm[ J.E.]}, \bibinfo{author}{Knill\xfnm[ E.]},
  \bibinfo{author}{Laflamme\xfnm[ R.]}.
\newblock \bibinfo{title}{Simulating physical phenomena by quantum networks}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2002};\bibinfo{volume}{65}(\bibinfo{number}{4}).
\newblock \DOIprefix\doi{10.1103/physreva.65.042323}.
%Type = Article
\bibitem[{Somma et~al.(2003)Somma, Ortiz, Knill and Gubernatis}]{Somma2003}
\bibinfo{author}{Somma\xfnm[ R.]}, \bibinfo{author}{Ortiz\xfnm[ G.]},
  \bibinfo{author}{Knill\xfnm[ E.]}, \bibinfo{author}{Gubernatis\xfnm[ J.]}.
\newblock \bibinfo{title}{Quantum simulations of physics problems}.
\newblock \bibinfo{journal}{International Journal of Quantum Information}
  \bibinfo{year}{2003};\bibinfo{volume}{01}(\bibinfo{number}{02}):\bibinfo{pages}{189--206}.
\newblock \DOIprefix\doi{10.1142/s0219749903000140}.
%Type = Article
\bibitem[{Yordanov et~al.(2021)Yordanov, Armaos, Barnes and
  Arvidsson-Shukur}]{Yordanov2021}
\bibinfo{author}{Yordanov\xfnm[ Y.S.]}, \bibinfo{author}{Armaos\xfnm[ V.]},
  \bibinfo{author}{Barnes\xfnm[ C.H.W.]},
  \bibinfo{author}{Arvidsson-Shukur\xfnm[ D.R.M.]}.
\newblock \bibinfo{title}{Qubit-excitation-based adaptive variational quantum
  eigensolver}.
\newblock \bibinfo{journal}{Communications Physics}
  \bibinfo{year}{2021};\bibinfo{volume}{4}(\bibinfo{number}{1}).
\newblock \URLprefix \url{https://doi.org/10.1038/s42005-021-00730-0}.
  \DOIprefix\doi{10.1038/s42005-021-00730-0}.
%Type = Misc
\bibitem[{Consiglio et~al.(2021)Consiglio, Chetcuti, Bravo-Prieto,
  Ramos-Calderer, Minguzzi, Latorre et~al.}]{Consiglio2021}
\bibinfo{author}{Consiglio\xfnm[ M.]}, \bibinfo{author}{Chetcuti\xfnm[ W.J.]},
  \bibinfo{author}{Bravo-Prieto\xfnm[ C.]},
  \bibinfo{author}{Ramos-Calderer\xfnm[ S.]}, \bibinfo{author}{Minguzzi\xfnm[
  A.]}, \bibinfo{author}{Latorre\xfnm[ J.I.]}, et~al.
\newblock \bibinfo{title}{Variational quantum eigensolver for su($n$)
  fermions}.
\newblock \bibinfo{year}{2021}.
\newblock \URLprefix \url{https://arxiv.org/abs/2106.15552}.
  \DOIprefix\doi{10.48550/ARXIV.2106.15552}.
%Type = Misc
\bibitem[{Vlasov(2019)}]{Vlasov2019}
\bibinfo{author}{Vlasov\xfnm[ A.Y.]}.
\newblock \bibinfo{title}{Clifford algebras, spin groups and qubit trees}.
\newblock \bibinfo{year}{2019}.
\newblock \href{http://arxiv.org/abs/1904.09912v5}{\tt arXiv:1904.09912v5}.
%Type = Article
\bibitem[{Majorana(1937)}]{Majorana1937}
\bibinfo{author}{Majorana\xfnm[ E.]}.
\newblock \bibinfo{title}{Teoria simmetrica dell'elettrone e del positrone}.
\newblock \bibinfo{journal}{Il Nuovo Cimento}
  \bibinfo{year}{1937};\bibinfo{volume}{14}(\bibinfo{number}{4}):\bibinfo{pages}{171--184}.
\newblock \DOIprefix\doi{10.1007/bf02961314}.
%Type = Incollection
\bibitem[{Majorana and Maiani(2006)}]{Majorana2006}
\bibinfo{author}{Majorana\xfnm[ E.]}, \bibinfo{author}{Maiani\xfnm[ L.]}.
\newblock \bibinfo{title}{A symmetric theory of electrons and positrons}.
\newblock In: \bibinfo{booktitle}{Ettore Majorana Scientific Papers}.
  \bibinfo{publisher}{Springer Berlin Heidelberg}; \bibinfo{year}{2006}, p.
  \bibinfo{pages}{201--233}.
\newblock \DOIprefix\doi{10.1007/978-3-540-48095-2_10}.
%Type = Article
\bibitem[{Kayser(2009)}]{Kayser2009}
\bibinfo{author}{Kayser\xfnm[ B.]}.
\newblock \bibinfo{title}{Are neutrinos their own antiparticles?}
\newblock \bibinfo{journal}{Journal of Physics: Conference Series}
  \bibinfo{year}{2009};\bibinfo{volume}{173}:\bibinfo{pages}{012013}.
\newblock \DOIprefix\doi{10.1088/1742-6596/173/1/012013}.
%Type = Article
\bibitem[{Balantekin et~al.(2019)Balantekin, de~Gouv{\^{e}}a and
  Kayser}]{Baha2019}
\bibinfo{author}{Balantekin\xfnm[ A.B.]},
  \bibinfo{author}{de~Gouv{\^{e}}a\xfnm[ A.]}, \bibinfo{author}{Kayser\xfnm[
  B.]}.
\newblock \bibinfo{title}{Addressing the majorana vs. dirac question with
  neutrino decays}.
\newblock \bibinfo{journal}{Physics Letters B}
  \bibinfo{year}{2019};\bibinfo{volume}{789}:\bibinfo{pages}{488--495}.
\newblock \DOIprefix\doi{10.1016/j.physletb.2018.11.068}.
%Type = Article
\bibitem[{Hirsch et~al.(2018)Hirsch, Srivastava and Valle}]{Hirsch2018}
\bibinfo{author}{Hirsch\xfnm[ M.]}, \bibinfo{author}{Srivastava\xfnm[ R.]},
  \bibinfo{author}{Valle\xfnm[ J.W.]}.
\newblock \bibinfo{title}{Can one ever prove that neutrinos are dirac
  particles?}
\newblock \bibinfo{journal}{Physics Letters B}
  \bibinfo{year}{2018};\bibinfo{volume}{781}:\bibinfo{pages}{302--305}.
\newblock \DOIprefix\doi{10.1016/j.physletb.2018.03.073}.
%Type = Misc
\bibitem[{Bilenky(2020)}]{Bilenky2020}
\bibinfo{author}{Bilenky\xfnm[ S.]}.
\newblock \bibinfo{title}{Neutrinos: Majorana or dirac?}
\newblock \bibinfo{year}{2020}.
\newblock \href{http://arxiv.org/abs/2008.02110}{\tt arXiv:2008.02110}.
%Type = Article
\bibitem[{Wilczek(2009)}]{Wilczek2009}
\bibinfo{author}{Wilczek\xfnm[ F.]}.
\newblock \bibinfo{title}{Majorana returns}.
\newblock \bibinfo{journal}{Nature Phys}
  \bibinfo{year}{2009};\bibinfo{volume}{5}(\bibinfo{number}{9}):\bibinfo{pages}{614--618}.
\newblock \DOIprefix\doi{10.1038/nphys1380}.
%Type = Article
\bibitem[{Verstraete and Cirac(2005)}]{Verstraete2005}
\bibinfo{author}{Verstraete\xfnm[ F.]}, \bibinfo{author}{Cirac\xfnm[ J.I.]}.
\newblock \bibinfo{title}{Mapping local hamiltonians of fermions to local
  hamiltonians of spins}.
\newblock \bibinfo{journal}{Journal of Statistical Mechanics: Theory and
  Experiment}
  \bibinfo{year}{2005};\bibinfo{volume}{2005}(\bibinfo{number}{09}):\bibinfo{pages}{P09012--P09012}.
\newblock \DOIprefix\doi{10.1088/1742-5468/2005/09/p09012}.
%Type = Article
\bibitem[{Ball(2005)}]{Ball2005}
\bibinfo{author}{Ball\xfnm[ R.C.]}.
\newblock \bibinfo{title}{Fermions without fermion fields}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2005};\bibinfo{volume}{95}(\bibinfo{number}{17}).
\newblock \DOIprefix\doi{10.1103/physrevlett.95.176407}.
%Type = Article
\bibitem[{Levin and Wen(2003)}]{Levin2003}
\bibinfo{author}{Levin\xfnm[ M.]}, \bibinfo{author}{Wen\xfnm[ X.G.]}.
\newblock \bibinfo{title}{Fermions, strings, and gauge fields in lattice spin
  models}.
\newblock \bibinfo{journal}{Physical Review B}
  \bibinfo{year}{2003};\bibinfo{volume}{67}(\bibinfo{number}{24}).
\newblock \DOIprefix\doi{10.1103/physrevb.67.245316}.
%Type = Article
\bibitem[{Wen(2003)}]{Wen2003}
\bibinfo{author}{Wen\xfnm[ X.G.]}.
\newblock \bibinfo{title}{Quantum order from string-net condensations and the
  origin of light and massless fermions}.
\newblock \bibinfo{journal}{Physical Review D}
  \bibinfo{year}{2003};\bibinfo{volume}{68}(\bibinfo{number}{6}).
\newblock \DOIprefix\doi{10.1103/physrevd.68.065003}.
%Type = Article
\bibitem[{Whitfield et~al.(2016)Whitfield, Havl{\'{\i}}{\v{c}}ek and
  Troyer}]{Whitfield2016}
\bibinfo{author}{Whitfield\xfnm[ J.D.]},
  \bibinfo{author}{Havl{\'{\i}}{\v{c}}ek\xfnm[ V.]},
  \bibinfo{author}{Troyer\xfnm[ M.]}.
\newblock \bibinfo{title}{Local spin operators for fermion simulations}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2016};\bibinfo{volume}{94}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physreva.94.030301}.
%Type = Article
\bibitem[{Steudtner and Wehner(2019)}]{Steudtner2019}
\bibinfo{author}{Steudtner\xfnm[ M.]}, \bibinfo{author}{Wehner\xfnm[ S.]}.
\newblock \bibinfo{title}{Quantum codes for quantum simulation of fermions on a
  square lattice of qubits}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2019};\bibinfo{volume}{99}(\bibinfo{number}{2}).
\newblock \DOIprefix\doi{10.1103/physreva.99.022308}.
%Type = Article
\bibitem[{Jiang et~al.(2019)Jiang, McClean, Babbush and Neven}]{Jiang2019}
\bibinfo{author}{Jiang\xfnm[ Z.]}, \bibinfo{author}{McClean\xfnm[ J.]},
  \bibinfo{author}{Babbush\xfnm[ R.]}, \bibinfo{author}{Neven\xfnm[ H.]}.
\newblock \bibinfo{title}{Majorana loop stabilizer codes for error mitigation
  in fermionic quantum simulations}.
\newblock \bibinfo{journal}{Physical Review Applied}
  \bibinfo{year}{2019};\bibinfo{volume}{12}(\bibinfo{number}{6}).
\newblock \DOIprefix\doi{10.1103/physrevapplied.12.064041}.
%Type = Misc
\bibitem[{Chien and Whitfield(2020)}]{Chien2020}
\bibinfo{author}{Chien\xfnm[ R.W.]}, \bibinfo{author}{Whitfield\xfnm[ J.D.]}.
\newblock \bibinfo{title}{Custom fermionic codes for quantum simulation}.
\newblock \bibinfo{year}{2020}.
\newblock \href{http://arxiv.org/abs/2009.11860v1}{\tt arXiv:2009.11860v1}.
%Type = Misc
\bibitem[{Bausch et~al.(2020)Bausch, Cubitt, Derby and Klassen}]{Bausch2020}
\bibinfo{author}{Bausch\xfnm[ J.]}, \bibinfo{author}{Cubitt\xfnm[ T.]},
  \bibinfo{author}{Derby\xfnm[ C.]}, \bibinfo{author}{Klassen\xfnm[ J.]}.
\newblock \bibinfo{title}{Mitigating errors in local fermionic encodings}.
\newblock \bibinfo{year}{2020}.
\newblock \href{http://arxiv.org/abs/2003.07125v2}{\tt arXiv:2003.07125v2}.
%Type = Article
\bibitem[{Chien et~al.(2019)Chien, Xue, Hardikar, Setia and
  Whitfield}]{Chien2019}
\bibinfo{author}{Chien\xfnm[ R.W.]}, \bibinfo{author}{Xue\xfnm[ S.]},
  \bibinfo{author}{Hardikar\xfnm[ T.S.]}, \bibinfo{author}{Setia\xfnm[ K.]},
  \bibinfo{author}{Whitfield\xfnm[ J.D.]}.
\newblock \bibinfo{title}{Analysis of superfast encoding performance for
  electronic structure simulations}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2019};\bibinfo{volume}{100}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physreva.100.032337}.
%Type = Book
\bibitem[{Messiah(2014)}]{messiah2014quantum}
\bibinfo{author}{Messiah\xfnm[ A.]}.
\newblock \bibinfo{title}{Quantum Mechanics}.
\newblock \bibinfo{address}{City}: \bibinfo{publisher}{Dover Publications};
  \bibinfo{year}{2014}.
\newblock ISBN \bibinfo{isbn}{9780486784557}.
%Type = Book
\bibitem[{Cotton(1990)}]{cotton1990chemical}
\bibinfo{author}{Cotton\xfnm[ F.]}.
\newblock \bibinfo{title}{Chemical applications of group theory}.
\newblock \bibinfo{address}{New York}: \bibinfo{publisher}{Wiley};
  \bibinfo{year}{1990}.
\newblock ISBN \bibinfo{isbn}{978-0-471-51094-9}.
%Type = Article
\bibitem[{Zhang et~al.(2021{\natexlab{b}})Zhang, Gomes, Berthusen, Orth, Wang,
  Ho et~al.}]{Zhang2021_shallow}
\bibinfo{author}{Zhang\xfnm[ F.]}, \bibinfo{author}{Gomes\xfnm[ N.]},
  \bibinfo{author}{Berthusen\xfnm[ N.F.]}, \bibinfo{author}{Orth\xfnm[ P.P.]},
  \bibinfo{author}{Wang\xfnm[ C.Z.]}, \bibinfo{author}{Ho\xfnm[ K.M.]}, et~al.
\newblock \bibinfo{title}{Shallow-circuit variational quantum eigensolver based
  on symmetry-inspired hilbert space partitioning for quantum chemical
  calculations}.
\newblock \bibinfo{journal}{Physical Review Research}
  \bibinfo{year}{2021}{\natexlab{b}};\bibinfo{volume}{3}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1103/physrevresearch.3.013039}.
%Type = Article
\bibitem[{Raussendorf(2013)}]{Raussendorf2013}
\bibinfo{author}{Raussendorf\xfnm[ R.]}.
\newblock \bibinfo{title}{Contextuality in measurement-based quantum
  computation}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2013};\bibinfo{volume}{88}(\bibinfo{number}{2}).
\newblock \DOIprefix\doi{10.1103/physreva.88.022322}.
%Type = Article
\bibitem[{Howard et~al.(2014)Howard, Wallman, Veitch and Emerson}]{Howard2014}
\bibinfo{author}{Howard\xfnm[ M.]}, \bibinfo{author}{Wallman\xfnm[ J.]},
  \bibinfo{author}{Veitch\xfnm[ V.]}, \bibinfo{author}{Emerson\xfnm[ J.]}.
\newblock \bibinfo{title}{Contextuality supplies the `magic' for quantum
  computation}.
\newblock \bibinfo{journal}{Nature}
  \bibinfo{year}{2014};\bibinfo{volume}{510}(\bibinfo{number}{7505}):\bibinfo{pages}{351--355}.
\newblock \DOIprefix\doi{10.1038/nature13460}.
%Type = Article
\bibitem[{Cabello et~al.(2014)Cabello, Severini and Winter}]{Cabello2014}
\bibinfo{author}{Cabello\xfnm[ A.]}, \bibinfo{author}{Severini\xfnm[ S.]},
  \bibinfo{author}{Winter\xfnm[ A.]}.
\newblock \bibinfo{title}{Graph-theoretic approach to quantum correlations}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2014};\bibinfo{volume}{112}(\bibinfo{number}{4}).
\newblock \DOIprefix\doi{10.1103/physrevlett.112.040401}.
%Type = Article
\bibitem[{Cabello et~al.(2015)Cabello, Kleinmann and Budroni}]{Cabello2015}
\bibinfo{author}{Cabello\xfnm[ A.]}, \bibinfo{author}{Kleinmann\xfnm[ M.]},
  \bibinfo{author}{Budroni\xfnm[ C.]}.
\newblock \bibinfo{title}{Necessary and sufficient condition for quantum
  state-independent contextuality}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2015};\bibinfo{volume}{114}(\bibinfo{number}{25}).
\newblock \DOIprefix\doi{10.1103/physrevlett.114.250402}.
%Type = Article
\bibitem[{Ramanathan and Horodecki(2014)}]{Ramanathan2014}
\bibinfo{author}{Ramanathan\xfnm[ R.]}, \bibinfo{author}{Horodecki\xfnm[ P.]}.
\newblock \bibinfo{title}{Necessary and sufficient condition for
  state-independent contextual measurement scenarios}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2014};\bibinfo{volume}{112}(\bibinfo{number}{4}).
\newblock \DOIprefix\doi{10.1103/physrevlett.112.040404}.
%Type = Article
\bibitem[{Kirby and Love(2019)}]{Kirby2019}
\bibinfo{author}{Kirby\xfnm[ W.M.]}, \bibinfo{author}{Love\xfnm[ P.J.]}.
\newblock \bibinfo{title}{Contextuality test of the nonclassicality of
  variational quantum eigensolvers}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2019};\bibinfo{volume}{123}(\bibinfo{number}{20}).
\newblock \DOIprefix\doi{10.1103/physrevlett.123.200501}.
%Type = Article
\bibitem[{Kirby and Love(2020)}]{Kirby2020_classical_sim}
\bibinfo{author}{Kirby\xfnm[ W.M.]}, \bibinfo{author}{Love\xfnm[ P.J.]}.
\newblock \bibinfo{title}{Classical simulation of noncontextual pauli
  hamiltonians}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2020};\bibinfo{volume}{102}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physreva.102.032418}.
%Type = Book
\bibitem[{Dekking(2005)}]{Dekking2005}
\bibinfo{author}{Dekking\xfnm[ M.]}.
\newblock \bibinfo{title}{A modern introduction to probability and statistics :
  understanding why and how}.
\newblock \bibinfo{address}{London}: \bibinfo{publisher}{Springer};
  \bibinfo{year}{2005}.
\newblock ISBN \bibinfo{isbn}{978-1-84628-168-6}.
%Type = Article
\bibitem[{K{\"{u}}bler et~al.(2020)K{\"{u}}bler, Arrasmith, Cincio and
  Coles}]{Kubler2020adaptiveoptimizer}
\bibinfo{author}{K{\"{u}}bler\xfnm[ J.M.]}, \bibinfo{author}{Arrasmith\xfnm[
  A.]}, \bibinfo{author}{Cincio\xfnm[ L.]}, \bibinfo{author}{Coles\xfnm[
  P.J.]}.
\newblock \bibinfo{title}{An {A}daptive {O}ptimizer for {M}easurement-{F}rugal
  {V}ariational {A}lgorithms}.
\newblock \bibinfo{journal}{{Quantum}}
  \bibinfo{year}{2020};\bibinfo{volume}{4}:\bibinfo{pages}{263}.
\newblock \DOIprefix\doi{10.22331/q-2020-05-11-263}.
%Type = Article
\bibitem[{Yen et~al.(2020)Yen, Verteletskyi and Izmaylov}]{Yen2020}
\bibinfo{author}{Yen\xfnm[ T.C.]}, \bibinfo{author}{Verteletskyi\xfnm[ V.]},
  \bibinfo{author}{Izmaylov\xfnm[ A.F.]}.
\newblock \bibinfo{title}{Measuring all compatible operators in one series of
  single-qubit measurements using unitary transformations}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2020};\bibinfo{volume}{16}(\bibinfo{number}{4}):\bibinfo{pages}{2400--2409}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.0c00008}.
%Type = Article
\bibitem[{Izmaylov et~al.(2019{\natexlab{b}})Izmaylov, Yen, Lang and
  Verteletskyi}]{Izmaylov2020a}
\bibinfo{author}{Izmaylov\xfnm[ A.F.]}, \bibinfo{author}{Yen\xfnm[ T.C.]},
  \bibinfo{author}{Lang\xfnm[ R.A.]}, \bibinfo{author}{Verteletskyi\xfnm[ V.]}.
\newblock \bibinfo{title}{Unitary partitioning approach to the measurement
  problem in the variational quantum eigensolver method}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2019}{\natexlab{b}};\bibinfo{volume}{16}(\bibinfo{number}{1}):\bibinfo{pages}{190--195}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.9b00791}.
%Type = Incollection
\bibitem[{D'Ariano et~al.(2003)D'Ariano, Paris and Sacchi}]{MauroDAriano2003}
\bibinfo{author}{D'Ariano\xfnm[ G.M.]}, \bibinfo{author}{Paris\xfnm[ M.G.]},
  \bibinfo{author}{Sacchi\xfnm[ M.F.]}.
\newblock \bibinfo{title}{Quantum tomography}.
\newblock In: \bibinfo{booktitle}{Advances in Imaging and Electron Physics}.
  \bibinfo{publisher}{Elsevier}; \bibinfo{year}{2003}, p.
  \bibinfo{pages}{205--308}.
\newblock \DOIprefix\doi{10.1016/s1076-5670(03)80065-4}.
%Type = Article
\bibitem[{Cramer et~al.(2010)Cramer, Plenio, Flammia, Somma, Gross, Bartlett
  et~al.}]{Cramer2010}
\bibinfo{author}{Cramer\xfnm[ M.]}, \bibinfo{author}{Plenio\xfnm[ M.B.]},
  \bibinfo{author}{Flammia\xfnm[ S.T.]}, \bibinfo{author}{Somma\xfnm[ R.]},
  \bibinfo{author}{Gross\xfnm[ D.]}, \bibinfo{author}{Bartlett\xfnm[ S.D.]},
  et~al.
\newblock \bibinfo{title}{Efficient quantum state tomography}.
\newblock \bibinfo{journal}{Nature Communications}
  \bibinfo{year}{2010};\bibinfo{volume}{1}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1038/ncomms1147}.
%Type = Article
\bibitem[{Christandl and Renner(2012)}]{Christandl2012}
\bibinfo{author}{Christandl\xfnm[ M.]}, \bibinfo{author}{Renner\xfnm[ R.]}.
\newblock \bibinfo{title}{Reliable quantum state tomography}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2012};\bibinfo{volume}{109}(\bibinfo{number}{12}).
\newblock \DOIprefix\doi{10.1103/physrevlett.109.120403}.
%Type = Article
\bibitem[{Bisio et~al.(2009)Bisio, Chiribella, D{\textquotesingle}Ariano,
  Facchini and Perinotti}]{Bisio2009}
\bibinfo{author}{Bisio\xfnm[ A.]}, \bibinfo{author}{Chiribella\xfnm[ G.]},
  \bibinfo{author}{D{\textquotesingle}Ariano\xfnm[ G.]},
  \bibinfo{author}{Facchini\xfnm[ S.]}, \bibinfo{author}{Perinotti\xfnm[ P.]}.
\newblock \bibinfo{title}{Optimal quantum tomography}.
\newblock \bibinfo{journal}{IEEE Journal of Selected Topics in Quantum
  Electronics}
  \bibinfo{year}{2009};\bibinfo{volume}{15}(\bibinfo{number}{6}):\bibinfo{pages}{1646--1660}.
\newblock \DOIprefix\doi{10.1109/jstqe.2009.2029243}.
%Type = Inproceedings
\bibitem[{O{\textquotesingle}Donnell and Wright(2016)}]{ODonnell2016}
\bibinfo{author}{O{\textquotesingle}Donnell\xfnm[ R.]},
  \bibinfo{author}{Wright\xfnm[ J.]}.
\newblock \bibinfo{title}{Efficient quantum tomography}.
\newblock In: \bibinfo{booktitle}{Proceedings of the forty-eighth annual {ACM}
  symposium on Theory of Computing}. \bibinfo{publisher}{{ACM}};
  \bibinfo{year}{2016}, p. \bibinfo{pages}{899--912}.
\newblock \DOIprefix\doi{10.1145/2897518.2897544}.
%Type = Inproceedings
\bibitem[{O{\textquotesingle}Donnell and Wright(2017)}]{ODonnell2017}
\bibinfo{author}{O{\textquotesingle}Donnell\xfnm[ R.]},
  \bibinfo{author}{Wright\xfnm[ J.]}.
\newblock \bibinfo{title}{Efficient quantum tomography {II}}.
\newblock In: \bibinfo{booktitle}{Proceedings of the 49th Annual {ACM} {SIGACT}
  Symposium on Theory of Computing}. \bibinfo{publisher}{{ACM}};
  \bibinfo{year}{2017}, p. \bibinfo{pages}{962--974}.
\newblock \DOIprefix\doi{10.1145/3055399.3055454}.
%Type = Article
\bibitem[{Haah et~al.(2017)Haah, Harrow, Ji, Wu and Yu}]{Haah2017}
\bibinfo{author}{Haah\xfnm[ J.]}, \bibinfo{author}{Harrow\xfnm[ A.W.]},
  \bibinfo{author}{Ji\xfnm[ Z.]}, \bibinfo{author}{Wu\xfnm[ X.]},
  \bibinfo{author}{Yu\xfnm[ N.]}.
\newblock \bibinfo{title}{Sample-optimal tomography of quantum states}.
\newblock \bibinfo{journal}{IEEE Transactions on Information Theory}
  \bibinfo{year}{2017};:\bibinfo{pages}{1--1}\DOIprefix\doi{10.1109/tit.2017.2719044}.
%Type = Book
\bibitem[{Hall(2015)}]{Hall2015}
\bibinfo{author}{Hall\xfnm[ B.C.]}.
\newblock \bibinfo{title}{Lie Groups, Lie Algebras, and Representations}.
\newblock \bibinfo{publisher}{Springer International Publishing};
  \bibinfo{year}{2015}.
\newblock \DOIprefix\doi{10.1007/978-3-319-13467-3}.
%Type = Article
\bibitem[{Cotler and Wilczek(2020)}]{Cotler2020}
\bibinfo{author}{Cotler\xfnm[ J.]}, \bibinfo{author}{Wilczek\xfnm[ F.]}.
\newblock \bibinfo{title}{Quantum overlapping tomography}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2020};\bibinfo{volume}{124}(\bibinfo{number}{10}):\bibinfo{pages}{100401}.
\newblock \DOIprefix\doi{10.1103/physrevlett.124.100401}.
%Type = Misc
\bibitem[{Evans et~al.(2019)Evans, Harper and Flammia}]{Evans2019}
\bibinfo{author}{Evans\xfnm[ T.J.]}, \bibinfo{author}{Harper\xfnm[ R.]},
  \bibinfo{author}{Flammia\xfnm[ S.T.]}.
\newblock \bibinfo{title}{Scalable bayesian hamiltonian learning}.
\newblock \bibinfo{year}{2019}.
\newblock \href{http://arxiv.org/abs/1912.07636v1}{\tt arXiv:1912.07636v1}.
%Type = Misc
\bibitem[{Aaronson(2017)}]{Aaronson2019}
\bibinfo{author}{Aaronson\xfnm[ S.]}.
\newblock \bibinfo{title}{Shadow tomography of quantum states}.
\newblock \bibinfo{year}{2017}.
\newblock \href{http://arxiv.org/abs/1711.01053v2}{\tt arXiv:1711.01053v2}.
%Type = Inproceedings
\bibitem[{Aaronson and Rothblum(2019)}]{Aaronson2019_prooceed}
\bibinfo{author}{Aaronson\xfnm[ S.]}, \bibinfo{author}{Rothblum\xfnm[ G.N.]}.
\newblock \bibinfo{title}{Gentle measurement of quantum states and differential
  privacy}.
\newblock In: \bibinfo{booktitle}{Proceedings of the 51st Annual ACM SIGACT
  Symposium on Theory of Computing}. STOC 2019; \bibinfo{address}{New York, NY,
  USA}: \bibinfo{publisher}{Association for Computing Machinery}.
\newblock ISBN \bibinfo{isbn}{9781450367059}; \bibinfo{year}{2019}, p.
  \bibinfo{pages}{322--333}.
\newblock \DOIprefix\doi{10.1145/3313276.3316378}.
%Type = Article
\bibitem[{Jerrum et~al.(1986)Jerrum, Valiant and Vazirani}]{Jerrum1986}
\bibinfo{author}{Jerrum\xfnm[ M.R.]}, \bibinfo{author}{Valiant\xfnm[ L.G.]},
  \bibinfo{author}{Vazirani\xfnm[ V.V.]}.
\newblock \bibinfo{title}{Random generation of combinatorial structures from a
  uniform distribution}.
\newblock \bibinfo{journal}{Theoretical Computer Science}
  \bibinfo{year}{1986};\bibinfo{volume}{43}:\bibinfo{pages}{169--188}.
\newblock \DOIprefix\doi{10.1016/0304-3975(86)90174-x}.
%Type = Book
\bibitem[{Blair(1985)}]{Nemirovsky1983}
\bibinfo{author}{Blair\xfnm[ C.]}.
\newblock \bibinfo{title}{Problem Complexity and Method Efficiency in
  Optimization (A. S. Nemirovsky and D. B. Yudin)}; vol.~\bibinfo{volume}{27}.
\newblock \bibinfo{publisher}{Society for Industrial {\&} Applied Mathematics
  ({SIAM})}; \bibinfo{year}{1985}.
\newblock \DOIprefix\doi{10.1137/1027074}.
%Type = Misc
\bibitem[{Hadfield et~al.(2020)Hadfield, Bravyi, Raymond and
  Mezzacapo}]{Hadfield2020}
\bibinfo{author}{Hadfield\xfnm[ C.]}, \bibinfo{author}{Bravyi\xfnm[ S.]},
  \bibinfo{author}{Raymond\xfnm[ R.]}, \bibinfo{author}{Mezzacapo\xfnm[ A.]}.
\newblock \bibinfo{title}{Measurements of quantum hamiltonians with
  locally-biased classical shadows}.
\newblock \bibinfo{year}{2020}.
\newblock \href{http://arxiv.org/abs/2006.15788v1}{\tt arXiv:2006.15788v1}.
%Type = Article
\bibitem[{Huang et~al.(2021{\natexlab{b}})Huang, Kueng and
  Preskill}]{Huang2021}
\bibinfo{author}{Huang\xfnm[ H.Y.]}, \bibinfo{author}{Kueng\xfnm[ R.]},
  \bibinfo{author}{Preskill\xfnm[ J.]}.
\newblock \bibinfo{title}{Efficient estimation of pauli observables by
  derandomization}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2021}{\natexlab{b}};\bibinfo{volume}{127}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physrevlett.127.030503}.
  \href{http://arxiv.org/abs/2103.07510v1}{\tt arXiv:2103.07510v1};
  \bibinfo{note}{phys. Rev. Lett. 127, 030503 (2021)}.
%Type = Misc
\bibitem[{Acharya et~al.(2021)Acharya, Saha and
  Sengupta}]{acharya2021informationally}
\bibinfo{author}{Acharya\xfnm[ A.]}, \bibinfo{author}{Saha\xfnm[ S.]},
  \bibinfo{author}{Sengupta\xfnm[ A.M.]}.
\newblock \bibinfo{title}{Informationally complete povm-based shadow
  tomography}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2105.05992}{\tt arXiv:2105.05992}.
%Type = Misc
\bibitem[{Hadfield(2021)}]{Hadfield2021}
\bibinfo{author}{Hadfield\xfnm[ C.]}.
\newblock \bibinfo{title}{Adaptive pauli shadows for energy estimation}.
\newblock \bibinfo{year}{2021}.
\newblock \URLprefix \url{https://arxiv.org/abs/2105.12207}.
  \DOIprefix\doi{10.48550/ARXIV.2105.12207}.
%Type = Article
\bibitem[{Hu and You(2022)}]{Hu2022}
\bibinfo{author}{Hu\xfnm[ H.Y.]}, \bibinfo{author}{You\xfnm[ Y.Z.]}.
\newblock \bibinfo{title}{Hamiltonian-driven shadow tomography of quantum
  states}.
\newblock \bibinfo{journal}{Physical Review Research}
  \bibinfo{year}{2022};\bibinfo{volume}{4}(\bibinfo{number}{1}).
\newblock \URLprefix \url{https://doi.org/10.1103/physrevresearch.4.013054}.
  \DOIprefix\doi{10.1103/physrevresearch.4.013054}.
%Type = Misc
\bibitem[{Hu et~al.(2021)Hu, Choi and You}]{Hu2021}
\bibinfo{author}{Hu\xfnm[ H.Y.]}, \bibinfo{author}{Choi\xfnm[ S.]},
  \bibinfo{author}{You\xfnm[ Y.Z.]}.
\newblock \bibinfo{title}{Classical shadow tomography with locally scrambled
  quantum dynamics}.
\newblock \bibinfo{year}{2021}.
\newblock \URLprefix \url{https://arxiv.org/abs/2107.04817}.
  \DOIprefix\doi{10.48550/ARXIV.2107.04817}.
%Type = Article
\bibitem[{Zhao et~al.(2021)Zhao, Rubin and Miyake}]{Zhao2021}
\bibinfo{author}{Zhao\xfnm[ A.]}, \bibinfo{author}{Rubin\xfnm[ N.C.]},
  \bibinfo{author}{Miyake\xfnm[ A.]}.
\newblock \bibinfo{title}{Fermionic partial tomography via classical shadows}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2021};\bibinfo{volume}{127}(\bibinfo{number}{11}).
\newblock \URLprefix \url{https://doi.org/10.1103/physrevlett.127.110504}.
  \DOIprefix\doi{10.1103/physrevlett.127.110504}.
%Type = Misc
\bibitem[{Bu et~al.(2022)Bu, Koh, Garcia and Jaffe}]{Bu2022}
\bibinfo{author}{Bu\xfnm[ K.]}, \bibinfo{author}{Koh\xfnm[ D.E.]},
  \bibinfo{author}{Garcia\xfnm[ R.J.]}, \bibinfo{author}{Jaffe\xfnm[ A.]}.
\newblock \bibinfo{title}{Classical shadows with pauli-invariant unitary
  ensembles}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2202.03272}.
  \DOIprefix\doi{10.48550/ARXIV.2202.03272}.
%Type = Article
\bibitem[{Lukens et~al.(2021)Lukens, Law and Bennink}]{Lukens2021}
\bibinfo{author}{Lukens\xfnm[ J.M.]}, \bibinfo{author}{Law\xfnm[ K.J.H.]},
  \bibinfo{author}{Bennink\xfnm[ R.S.]}.
\newblock \bibinfo{title}{A bayesian analysis of classical shadows}.
\newblock \bibinfo{journal}{npj Quantum Information}
  \bibinfo{year}{2021};\bibinfo{volume}{7}(\bibinfo{number}{1}).
\newblock \URLprefix \url{https://doi.org/10.1038/s41534-021-00447-6}.
  \DOIprefix\doi{10.1038/s41534-021-00447-6}.
%Type = Article
\bibitem[{Chen et~al.(2021{\natexlab{a}})Chen, Yu, Zeng and
  Flammia}]{Chen2021_shadow}
\bibinfo{author}{Chen\xfnm[ S.]}, \bibinfo{author}{Yu\xfnm[ W.]},
  \bibinfo{author}{Zeng\xfnm[ P.]}, \bibinfo{author}{Flammia\xfnm[ S.T.]}.
\newblock \bibinfo{title}{Robust shadow estimation}.
\newblock \bibinfo{journal}{{PRX} Quantum}
  \bibinfo{year}{2021}{\natexlab{a}};\bibinfo{volume}{2}(\bibinfo{number}{3}).
\newblock \URLprefix \url{https://doi.org/10.1103/prxquantum.2.030348}.
  \DOIprefix\doi{10.1103/prxquantum.2.030348}.
%Type = Misc
\bibitem[{Koh and Grewal(2020)}]{Koh2020}
\bibinfo{author}{Koh\xfnm[ D.E.]}, \bibinfo{author}{Grewal\xfnm[ S.]}.
\newblock \bibinfo{title}{Classical shadows with noise}.
\newblock \bibinfo{year}{2020}.
\newblock \URLprefix \url{https://arxiv.org/abs/2011.11580}.
  \DOIprefix\doi{10.48550/ARXIV.2011.11580}.
%Type = Misc
\bibitem[{Sack et~al.(2022)Sack, Medina, Michailidis, Kueng and
  Serbyn}]{Sack2022}
\bibinfo{author}{Sack\xfnm[ S.H.]}, \bibinfo{author}{Medina\xfnm[ R.A.]},
  \bibinfo{author}{Michailidis\xfnm[ A.A.]}, \bibinfo{author}{Kueng\xfnm[ R.]},
  \bibinfo{author}{Serbyn\xfnm[ M.]}.
\newblock \bibinfo{title}{Avoiding barren plateaus using classical shadows}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2201.08194}.
  \DOIprefix\doi{10.48550/ARXIV.2201.08194}.
%Type = Article
\bibitem[{Ackley et~al.(1985)Ackley, Hinton and Sejnowski}]{Ackley1985}
\bibinfo{author}{Ackley\xfnm[ D.H.]}, \bibinfo{author}{Hinton\xfnm[ G.E.]},
  \bibinfo{author}{Sejnowski\xfnm[ T.J.]}.
\newblock \bibinfo{title}{A learning algorithm for boltzmann machines}.
\newblock \bibinfo{journal}{Cognitive Science}
  \bibinfo{year}{1985};\bibinfo{volume}{9}(\bibinfo{number}{1}):\bibinfo{pages}{147--169}.
\newblock \DOIprefix\doi{10.1207/s15516709cog0901_7}.
%Type = Article
\bibitem[{Melko et~al.(2019)Melko, Carleo, Carrasquilla and Cirac}]{Melko2019}
\bibinfo{author}{Melko\xfnm[ R.G.]}, \bibinfo{author}{Carleo\xfnm[ G.]},
  \bibinfo{author}{Carrasquilla\xfnm[ J.]}, \bibinfo{author}{Cirac\xfnm[
  J.I.]}.
\newblock \bibinfo{title}{Restricted boltzmann machines in quantum physics}.
\newblock \bibinfo{journal}{Nature Physics}
  \bibinfo{year}{2019};\bibinfo{volume}{15}(\bibinfo{number}{9}):\bibinfo{pages}{887--892}.
\newblock \DOIprefix\doi{10.1038/s41567-019-0545-1}.
%Type = Article
\bibitem[{Torlai and Melko(2020)}]{Torlai2020_MLQS}
\bibinfo{author}{Torlai\xfnm[ G.]}, \bibinfo{author}{Melko\xfnm[ R.G.]}.
\newblock \bibinfo{title}{Machine-learning quantum states in the {NISQ} era}.
\newblock \bibinfo{journal}{Annual Review of Condensed Matter Physics}
  \bibinfo{year}{2020};\bibinfo{volume}{11}(\bibinfo{number}{1}):\bibinfo{pages}{325--344}.
\newblock \DOIprefix\doi{10.1146/annurev-conmatphys-031119-050651}.
%Type = Misc
\bibitem[{Gottesman(1997)}]{Gottesman1997}
\bibinfo{author}{Gottesman\xfnm[ D.]}.
\newblock \bibinfo{title}{Stabilizer codes and quantum error correction}.
\newblock \bibinfo{year}{1997}.
\newblock \href{http://arxiv.org/abs/quant-ph/9705052v1}{\tt
  arXiv:quant-ph/9705052v1}.
%Type = Misc
\bibitem[{Jena et~al.(2019)Jena, Genin and Mosca}]{Jena2019}
\bibinfo{author}{Jena\xfnm[ A.]}, \bibinfo{author}{Genin\xfnm[ S.]},
  \bibinfo{author}{Mosca\xfnm[ M.]}.
\newblock \bibinfo{title}{Pauli partitioning with respect to gate sets}.
\newblock \bibinfo{year}{2019}.
\newblock \href{http://arxiv.org/abs/1907.07859v1}{\tt arXiv:1907.07859v1}.
%Type = Article
\bibitem[{den Nest et~al.(2004)den Nest, Dehaene and Moor}]{VandenNest2004}
\bibinfo{author}{den Nest\xfnm[ M.V.]}, \bibinfo{author}{Dehaene\xfnm[ J.]},
  \bibinfo{author}{Moor\xfnm[ B.D.]}.
\newblock \bibinfo{title}{Graphical description of the action of local clifford
  transformations on graph states}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2004};\bibinfo{volume}{69}(\bibinfo{number}{2}).
\newblock \DOIprefix\doi{10.1103/physreva.69.022316}.
%Type = Article
\bibitem[{Aaronson and Gottesman(2004)}]{Aaronson2004}
\bibinfo{author}{Aaronson\xfnm[ S.]}, \bibinfo{author}{Gottesman\xfnm[ D.]}.
\newblock \bibinfo{title}{Improved simulation of stabilizer circuits}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2004};\bibinfo{volume}{70}(\bibinfo{number}{5}).
\newblock \DOIprefix\doi{10.1103/physreva.70.052328}.
%Type = Article
\bibitem[{Patel et~al.(2008)Patel, Markov and Hayes}]{Patel2008}
\bibinfo{author}{Patel\xfnm[ K.N.]}, \bibinfo{author}{Markov\xfnm[ I.L.]},
  \bibinfo{author}{Hayes\xfnm[ J.P.]}.
\newblock \bibinfo{title}{Optimal synthesis of linear reversible circuits}.
\newblock \bibinfo{journal}{Quantum Information {\&} Computation}
  \bibinfo{year}{2008};\bibinfo{volume}{8}(\bibinfo{number}{3}):\bibinfo{pages}{282–294}.
\newblock \DOIprefix\doi{10.5555/2011763.2011767}.
%Type = Article
\bibitem[{Zhao et~al.(2020)Zhao, Tranter, Kirby, Ung, Miyake and
  Love}]{Zhao2020}
\bibinfo{author}{Zhao\xfnm[ A.]}, \bibinfo{author}{Tranter\xfnm[ A.]},
  \bibinfo{author}{Kirby\xfnm[ W.M.]}, \bibinfo{author}{Ung\xfnm[ S.F.]},
  \bibinfo{author}{Miyake\xfnm[ A.]}, \bibinfo{author}{Love\xfnm[ P.J.]}.
\newblock \bibinfo{title}{Measurement reduction in variational quantum
  algorithms}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2020};\bibinfo{volume}{101}(\bibinfo{number}{6}):\bibinfo{pages}{062322}.
\newblock \DOIprefix\doi{10.1103/physreva.101.062322}.
%Type = Article
\bibitem[{Ralli et~al.(2021)Ralli, Love, Tranter and Coveney}]{Ralli2021}
\bibinfo{author}{Ralli\xfnm[ A.]}, \bibinfo{author}{Love\xfnm[ P.J.]},
  \bibinfo{author}{Tranter\xfnm[ A.]}, \bibinfo{author}{Coveney\xfnm[ P.V.]}.
\newblock \bibinfo{title}{Implementation of measurement reduction for the
  variational quantum eigensolver}.
\newblock \bibinfo{journal}{Phys Rev Research}
  \bibinfo{year}{2021};\bibinfo{volume}{3}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physrevresearch.3.033195}.
%Type = Article
\bibitem[{Motta et~al.(2021)Motta, Ye, McClean, Li, Minnich, Babbush
  et~al.}]{Motta2021}
\bibinfo{author}{Motta\xfnm[ M.]}, \bibinfo{author}{Ye\xfnm[ E.]},
  \bibinfo{author}{McClean\xfnm[ J.R.]}, \bibinfo{author}{Li\xfnm[ Z.]},
  \bibinfo{author}{Minnich\xfnm[ A.J.]}, \bibinfo{author}{Babbush\xfnm[ R.]},
  et~al.
\newblock \bibinfo{title}{Low rank representations for quantum simulation of
  electronic structure}.
\newblock \bibinfo{journal}{npj Quantum Information}
  \bibinfo{year}{2021};\bibinfo{volume}{7}(\bibinfo{number}{1}):\bibinfo{pages}{83}.
\newblock \DOIprefix\doi{10.1038/s41534-021-00416-z}.
%Type = Article
\bibitem[{Peng and Kowalski(2017)}]{Peng2017}
\bibinfo{author}{Peng\xfnm[ B.]}, \bibinfo{author}{Kowalski\xfnm[ K.]}.
\newblock \bibinfo{title}{Highly efficient and scalable compound decomposition
  of two-electron integral tensor and its application in coupled cluster
  calculations}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2017};\bibinfo{volume}{13}(\bibinfo{number}{9}):\bibinfo{pages}{4179--4192}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.7b00605}.
%Type = Article
\bibitem[{Berry et~al.(2019)Berry, Gidney, Motta, McClean and
  Babbush}]{Berry2019}
\bibinfo{author}{Berry\xfnm[ D.W.]}, \bibinfo{author}{Gidney\xfnm[ C.]},
  \bibinfo{author}{Motta\xfnm[ M.]}, \bibinfo{author}{McClean\xfnm[ J.R.]},
  \bibinfo{author}{Babbush\xfnm[ R.]}.
\newblock \bibinfo{title}{Qubitization of arbitrary basis quantum chemistry
  leveraging sparsity and low rank factorization}.
\newblock \bibinfo{journal}{Quantum}
  \bibinfo{year}{2019};\bibinfo{volume}{3}:\bibinfo{pages}{208}.
\newblock \DOIprefix\doi{10.22331/q-2019-12-02-208}.
%Type = Article
\bibitem[{Pedersen et~al.(2009)Pedersen, Aquilante and Lindh}]{Pedersen2009}
\bibinfo{author}{Pedersen\xfnm[ T.B.]}, \bibinfo{author}{Aquilante\xfnm[ F.]},
  \bibinfo{author}{Lindh\xfnm[ R.]}.
\newblock \bibinfo{title}{Density fitting with auxiliary basis sets from
  cholesky decompositions}.
\newblock \bibinfo{journal}{Theoretical Chemistry Accounts}
  \bibinfo{year}{2009};\bibinfo{volume}{124}(\bibinfo{number}{1}):\bibinfo{pages}{1--10}.
\newblock \DOIprefix\doi{10.1007/s00214-009-0608-y}.
%Type = Article
\bibitem[{Beebe and Linderberg(1977)}]{Beebe1977}
\bibinfo{author}{Beebe\xfnm[ N.H.F.]}, \bibinfo{author}{Linderberg\xfnm[ J.]}.
\newblock \bibinfo{title}{Simplifications in the generation and transformation
  of two-electron integrals in molecular calculations}.
\newblock \bibinfo{journal}{International Journal of Quantum Chemistry}
  \bibinfo{year}{1977};\bibinfo{volume}{12}(\bibinfo{number}{4}):\bibinfo{pages}{683--705}.
\newblock \DOIprefix\doi{10.1002/qua.560120408}.
%Type = Article
\bibitem[{Koch et~al.(2003)Koch, de~Mer{\'{a}}s and Pedersen}]{Koch2003}
\bibinfo{author}{Koch\xfnm[ H.]}, \bibinfo{author}{de~Mer{\'{a}}s\xfnm[ A.S.]},
  \bibinfo{author}{Pedersen\xfnm[ T.B.]}.
\newblock \bibinfo{title}{Reduced scaling in electronic structure calculations
  using cholesky decompositions}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2003};\bibinfo{volume}{118}(\bibinfo{number}{21}):\bibinfo{pages}{9481--9484}.
\newblock \DOIprefix\doi{10.1063/1.1578621}.
%Type = Article
\bibitem[{Purwanto et~al.(2011)Purwanto, Krakauer, Virgus and
  Zhang}]{Purwanto2011}
\bibinfo{author}{Purwanto\xfnm[ W.]}, \bibinfo{author}{Krakauer\xfnm[ H.]},
  \bibinfo{author}{Virgus\xfnm[ Y.]}, \bibinfo{author}{Zhang\xfnm[ S.]}.
\newblock \bibinfo{title}{Assessing weak hydrogen binding on ca+ centers: An
  accurate many-body study with large basis sets}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2011};\bibinfo{volume}{135}(\bibinfo{number}{16}):\bibinfo{pages}{164105}.
\newblock \DOIprefix\doi{10.1063/1.3654002}.
%Type = Article
\bibitem[{Mardirossian et~al.(2018)Mardirossian, McClain and
  Chan}]{Mardirossian2018}
\bibinfo{author}{Mardirossian\xfnm[ N.]}, \bibinfo{author}{McClain\xfnm[
  J.D.]}, \bibinfo{author}{Chan\xfnm[ G.K.L.]}.
\newblock \bibinfo{title}{Lowering of the complexity of quantum chemistry
  methods by choice of representation}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2018};\bibinfo{volume}{148}(\bibinfo{number}{4}):\bibinfo{pages}{044106}.
\newblock \DOIprefix\doi{10.1063/1.5007779}.
%Type = Article
\bibitem[{BROYDEN(1970)}]{broyden_convergence_1970}
\bibinfo{author}{BROYDEN\xfnm[ C.G.]}.
\newblock \bibinfo{title}{The convergence of a class of double-rank
  minimization algorithms 1. general considerations}.
\newblock \bibinfo{journal}{IMA Journal of Applied Mathematics}
  \bibinfo{year}{1970};\bibinfo{volume}{6}(\bibinfo{number}{1}):\bibinfo{pages}{76--90}.
\newblock \DOIprefix\doi{10.1093/imamat/6.1.76}.
%Type = Article
\bibitem[{Fletcher(1970)}]{fletcher_new_1970}
\bibinfo{author}{Fletcher\xfnm[ R.]}.
\newblock \bibinfo{title}{A new approach to variable metric algorithms}.
\newblock \bibinfo{journal}{The Computer Journal}
  \bibinfo{year}{1970};\bibinfo{volume}{13}(\bibinfo{number}{3}):\bibinfo{pages}{317--322}.
\newblock \DOIprefix\doi{10.1093/comjnl/13.3.317}.
%Type = Article
\bibitem[{Goldfarb(1970)}]{goldfarb_family_1970}
\bibinfo{author}{Goldfarb\xfnm[ D.]}.
\newblock \bibinfo{title}{A family of variable-metric methods derived by
  variational means}.
\newblock \bibinfo{journal}{Mathematics of Computation}
  \bibinfo{year}{1970};\bibinfo{volume}{24}(\bibinfo{number}{109}):\bibinfo{pages}{23--23}.
\newblock \DOIprefix\doi{10.1090/s0025-5718-1970-0258249-6}.
%Type = Article
\bibitem[{Shanno(1970)}]{shanno_conditioning_1970}
\bibinfo{author}{Shanno\xfnm[ D.F.]}.
\newblock \bibinfo{title}{Conditioning of quasi-newton methods for function
  minimization}.
\newblock \bibinfo{journal}{Mathematics of Computation}
  \bibinfo{year}{1970};\bibinfo{volume}{24}(\bibinfo{number}{111}):\bibinfo{pages}{647--647}.
\newblock \DOIprefix\doi{10.1090/s0025-5718-1970-0274029-x}.
%Type = Book
\bibitem[{Garey(1979)}]{Garey1979}
\bibinfo{author}{Garey\xfnm[ M.]}.
\newblock \bibinfo{title}{Computers and intractability : a guide to the theory
  of NP-completeness}.
\newblock \bibinfo{address}{San Francisco}: \bibinfo{publisher}{W.H. Freeman};
  \bibinfo{year}{1979}.
\newblock ISBN \bibinfo{isbn}{978-0-7167-1045-5}.
%Type = Incollection
\bibitem[{Karp(1972)}]{Karp1972}
\bibinfo{author}{Karp\xfnm[ R.M.]}.
\newblock \bibinfo{title}{Reducibility among combinatorial problems}.
\newblock In: \bibinfo{editor}{Miller~R.E. Thatcher~J.W.\xfnm[ B.J.]}, editor.
  \bibinfo{booktitle}{Complexity of Computer Computations. The IBM Research
  Symposia Series.} \bibinfo{address}{Boston, MA}: \bibinfo{publisher}{Springer
  US}.
\newblock ISBN \bibinfo{isbn}{978-1-4684-2001-2}; \bibinfo{year}{1972}, p.
  \bibinfo{pages}{85--103}.
\newblock \DOIprefix\doi{10.1007/978-1-4684-2001-2_9}.
%Type = Article
\bibitem[{Welsh(1967)}]{Welsh1967}
\bibinfo{author}{Welsh\xfnm[ D.J.A.]}.
\newblock \bibinfo{title}{An upper bound for the chromatic number of a graph
  and its application to timetabling problems}.
\newblock \bibinfo{journal}{The Computer Journal}
  \bibinfo{year}{1967};\bibinfo{volume}{10}(\bibinfo{number}{1}):\bibinfo{pages}{85--86}.
\newblock \DOIprefix\doi{10.1093/comjnl/10.1.85}.
%Type = Article
\bibitem[{Matula et~al.(1972)Matula, Marble and Isaacson}]{Matula1972}
\bibinfo{author}{Matula\xfnm[ D.W.]}, \bibinfo{author}{Marble\xfnm[ G.]},
  \bibinfo{author}{Isaacson\xfnm[ J.D.]}.
\newblock \bibinfo{title}{{GRAPH} {COLORING}
  {ALGORITHMS}{\textdagger}{\textdagger}this research was supported in part by
  the advanced research projects agency of the department of defense under
  contract {SD}-302 and by the national science foundation under contract
  {GJ}-446.}
\newblock \bibinfo{journal}{Graph Theory and Computing}
  \bibinfo{year}{1972};:\bibinfo{pages}{109--122}\DOIprefix\doi{10.1016/b978-1-4832-3187-7.50015-5}.
%Type = Article
\bibitem[{Br{\'{e}}laz(1979)}]{Brelaz1979}
\bibinfo{author}{Br{\'{e}}laz\xfnm[ D.]}.
\newblock \bibinfo{title}{New methods to color the vertices of a graph}.
\newblock \bibinfo{journal}{Communications of the ACM}
  \bibinfo{year}{1979};\bibinfo{volume}{22}(\bibinfo{number}{4}):\bibinfo{pages}{251--256}.
\newblock \DOIprefix\doi{10.1145/359094.359101}.
%Type = Article
\bibitem[{Vallury et~al.(2020)Vallury, Jones, Hill and
  Hollenberg}]{Vallury2020}
\bibinfo{author}{Vallury\xfnm[ H.J.]}, \bibinfo{author}{Jones\xfnm[ M.A.]},
  \bibinfo{author}{Hill\xfnm[ C.D.]}, \bibinfo{author}{Hollenberg\xfnm[
  L.C.L.]}.
\newblock \bibinfo{title}{Quantum computed moments correction to variational
  estimates}.
\newblock \bibinfo{journal}{Quantum}
  \bibinfo{year}{2020};\bibinfo{volume}{4}:\bibinfo{pages}{373}.
\newblock \DOIprefix\doi{10.22331/q-2020-12-15-373}.
%Type = Article
\bibitem[{Dutton(1981)}]{Dutton1981}
\bibinfo{author}{Dutton\xfnm[ R.D.]}.
\newblock \bibinfo{title}{A new graph colouring algorithm}.
\newblock \bibinfo{journal}{The Computer Journal}
  \bibinfo{year}{1981};\bibinfo{volume}{24}(\bibinfo{number}{1}):\bibinfo{pages}{85--86}.
\newblock \DOIprefix\doi{10.1093/comjnl/24.1.85}.
%Type = Article
\bibitem[{Hertz(1990)}]{Hertz1990}
\bibinfo{author}{Hertz\xfnm[ A.]}.
\newblock \bibinfo{title}{A fast algorithm for coloring meyniel graphs}.
\newblock \bibinfo{journal}{Journal of Combinatorial Theory, Series B}
  \bibinfo{year}{1990};\bibinfo{volume}{50}(\bibinfo{number}{2}):\bibinfo{pages}{231--240}.
\newblock \DOIprefix\doi{10.1016/0095-8956(90)90078-e}.
%Type = Article
\bibitem[{Boppana and Halld{\'{o}}rsson(1992)}]{Boppana1992}
\bibinfo{author}{Boppana\xfnm[ R.]}, \bibinfo{author}{Halld{\'{o}}rsson\xfnm[
  M.M.]}.
\newblock \bibinfo{title}{Approximating maximum independent sets by excluding
  subgraphs}.
\newblock \bibinfo{journal}{BIT}
  \bibinfo{year}{1992};\bibinfo{volume}{32}(\bibinfo{number}{2}):\bibinfo{pages}{180--196}.
\newblock \DOIprefix\doi{10.1007/bf01994876}.
%Type = Article
\bibitem[{Tomita et~al.(2006)Tomita, Tanaka and Takahashi}]{Tomita2006}
\bibinfo{author}{Tomita\xfnm[ E.]}, \bibinfo{author}{Tanaka\xfnm[ A.]},
  \bibinfo{author}{Takahashi\xfnm[ H.]}.
\newblock \bibinfo{title}{The worst-case time complexity for generating all
  maximal cliques and computational experiments}.
\newblock \bibinfo{journal}{Theoretical Computer Science}
  \bibinfo{year}{2006};\bibinfo{volume}{363}(\bibinfo{number}{1}):\bibinfo{pages}{28--42}.
\newblock \DOIprefix\doi{10.1016/j.tcs.2006.06.015}.
%Type = Book
\bibitem[{Kubale(2004)}]{Kubale2004}
\bibinfo{editor}{Kubale\xfnm[ M.]}, editor.
\newblock \bibinfo{title}{Graph Colorings}.
\newblock \bibinfo{publisher}{American Mathematical Society};
  \bibinfo{year}{2004}.
\newblock ISBN \bibinfo{isbn}{9780821879429}.
\newblock \DOIprefix\doi{10.1090/conm/352}.
%Type = Article
\bibitem[{Leighton(1979)}]{Leighton1979}
\bibinfo{author}{Leighton\xfnm[ F.T.]}.
\newblock \bibinfo{title}{A graph coloring algorithm for large scheduling
  problems}.
\newblock \bibinfo{journal}{Journal of Research of the National Institute of
  Standards and Technology}
  \bibinfo{year}{1979};\bibinfo{volume}{84}:\bibinfo{pages}{489--506}.
\newblock \URLprefix
  \url{https://nvlpubs.nist.gov/nistpubs/jres/84/jresv84n6p489_a1b.pdf}.
%Type = Article
\bibitem[{Sim et~al.(2019)Sim, Johnson and Aspuru-Guzik}]{Sim2019}
\bibinfo{author}{Sim\xfnm[ S.]}, \bibinfo{author}{Johnson\xfnm[ P.D.]},
  \bibinfo{author}{Aspuru-Guzik\xfnm[ A.]}.
\newblock \bibinfo{title}{Expressibility and entangling capability of
  parameterized quantum circuits for hybrid quantum-classical algorithms}.
\newblock \bibinfo{journal}{Advanced Quantum Technologies}
  \bibinfo{year}{2019};\bibinfo{volume}{2}(\bibinfo{number}{12}):\bibinfo{pages}{1900070}.
\newblock \DOIprefix\doi{10.1002/qute.201900070}.
%Type = Article
\bibitem[{Hubregtsen et~al.(2021)Hubregtsen, Pichlmeier, Stecher and
  Bertels}]{Hubregtsen2021}
\bibinfo{author}{Hubregtsen\xfnm[ T.]}, \bibinfo{author}{Pichlmeier\xfnm[ J.]},
  \bibinfo{author}{Stecher\xfnm[ P.]}, \bibinfo{author}{Bertels\xfnm[ K.]}.
\newblock \bibinfo{title}{Evaluation of parameterized quantum circuits: on the
  relation between classification accuracy, expressibility, and entangling
  capability}.
\newblock \bibinfo{journal}{Quantum Machine Intelligence}
  \bibinfo{year}{2021};\bibinfo{volume}{3}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1007/s42484-021-00038-w}.
%Type = Article
\bibitem[{Rasmussen et~al.(2020)Rasmussen, Loft, B{\ae}kkegaard, Kues and
  Zinner}]{Rasmussen2020}
\bibinfo{author}{Rasmussen\xfnm[ S.E.]}, \bibinfo{author}{Loft\xfnm[ N.J.S.]},
  \bibinfo{author}{B{\ae}kkegaard\xfnm[ T.]}, \bibinfo{author}{Kues\xfnm[ M.]},
  \bibinfo{author}{Zinner\xfnm[ N.T.]}.
\newblock \bibinfo{title}{Reducing the amount of single-qubit rotations in
  {VQE} and~related algorithms}.
\newblock \bibinfo{journal}{Advanced Quantum Technologies}
  \bibinfo{year}{2020};\bibinfo{volume}{3}(\bibinfo{number}{12}):\bibinfo{pages}{2000063}.
\newblock \URLprefix \url{https://doi.org/10.1002/qute.202000063}.
  \DOIprefix\doi{10.1002/qute.202000063}.
%Type = Article
\bibitem[{Funcke et~al.(2021)Funcke, Hartung, Jansen, K\"{u}hn and
  Stornati}]{Funcke2021}
\bibinfo{author}{Funcke\xfnm[ L.]}, \bibinfo{author}{Hartung\xfnm[ T.]},
  \bibinfo{author}{Jansen\xfnm[ K.]}, \bibinfo{author}{K\"{u}hn\xfnm[ S.]},
  \bibinfo{author}{Stornati\xfnm[ P.]}.
\newblock \bibinfo{title}{Dimensional expressivity analysis of parametric
  quantum circuits}.
\newblock \bibinfo{journal}{Quantum}
  \bibinfo{year}{2021};\bibinfo{volume}{5}:\bibinfo{pages}{422}.
\newblock \URLprefix \url{https://doi.org/10.22331/q-2021-03-29-422}.
  \DOIprefix\doi{10.22331/q-2021-03-29-422}.
%Type = Misc
\bibitem[{Wang et~al.(2020{\natexlab{b}})Wang, Fontana, Cerezo, Sharma, Sone,
  Cincio et~al.}]{Wang2020}
\bibinfo{author}{Wang\xfnm[ S.]}, \bibinfo{author}{Fontana\xfnm[ E.]},
  \bibinfo{author}{Cerezo\xfnm[ M.]}, \bibinfo{author}{Sharma\xfnm[ K.]},
  \bibinfo{author}{Sone\xfnm[ A.]}, \bibinfo{author}{Cincio\xfnm[ L.]}, et~al.
\newblock \bibinfo{title}{Noise-induced barren plateaus in variational quantum
  algorithms}.
\newblock \bibinfo{year}{2020}{\natexlab{b}}.
\newblock \href{http://arxiv.org/abs/2007.14384v3}{\tt arXiv:2007.14384v3}.
%Type = Misc
\bibitem[{Arrasmith et~al.(2021)Arrasmith, Holmes, Cerezo and
  Coles}]{Arrasmith2021}
\bibinfo{author}{Arrasmith\xfnm[ A.]}, \bibinfo{author}{Holmes\xfnm[ Z.]},
  \bibinfo{author}{Cerezo\xfnm[ M.]}, \bibinfo{author}{Coles\xfnm[ P.J.]}.
\newblock \bibinfo{title}{Equivalence of quantum barren plateaus to cost
  concentration and narrow gorges}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2104.05868v1}{\tt arXiv:2104.05868v1}.
%Type = Misc
\bibitem[{Arrasmith et~al.(2020{\natexlab{b}})Arrasmith, Cerezo, Czarnik,
  Cincio and Coles}]{Arrasmith2020_BP_GF}
\bibinfo{author}{Arrasmith\xfnm[ A.]}, \bibinfo{author}{Cerezo\xfnm[ M.]},
  \bibinfo{author}{Czarnik\xfnm[ P.]}, \bibinfo{author}{Cincio\xfnm[ L.]},
  \bibinfo{author}{Coles\xfnm[ P.J.]}.
\newblock \bibinfo{title}{Effect of barren plateaus on gradient-free
  optimization}.
\newblock \bibinfo{year}{2020}{\natexlab{b}}.
\newblock \href{http://arxiv.org/abs/2011.12245v1}{\tt arXiv:2011.12245v1}.
%Type = Misc
\bibitem[{Napp(2022)}]{Napp2022}
\bibinfo{author}{Napp\xfnm[ J.]}.
\newblock \bibinfo{title}{Quantifying the barren plateau phenomenon for a model
  of unstructured variational ansätze}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2203.06174}.
  \DOIprefix\doi{10.48550/ARXIV.2203.06174}.
%Type = Article
\bibitem[{Cerezo and Coles(2021)}]{Cerezo2021_BP_higher_order}
\bibinfo{author}{Cerezo\xfnm[ M.]}, \bibinfo{author}{Coles\xfnm[ P.J.]}.
\newblock \bibinfo{title}{Higher order derivatives of quantum neural networks
  with barren plateaus}.
\newblock \bibinfo{journal}{Quantum Science and Technology}
  \bibinfo{year}{2021};\bibinfo{volume}{6}(\bibinfo{number}{3}):\bibinfo{pages}{035006}.
\newblock \DOIprefix\doi{10.1088/2058-9565/abf51a}.
%Type = Misc
\bibitem[{Sauvage et~al.(2021)Sauvage, Sim, Kunitsa, Simon, Mauri and
  Perdomo-Ortiz}]{Sauvage2021}
\bibinfo{author}{Sauvage\xfnm[ F.]}, \bibinfo{author}{Sim\xfnm[ S.]},
  \bibinfo{author}{Kunitsa\xfnm[ A.A.]}, \bibinfo{author}{Simon\xfnm[ W.A.]},
  \bibinfo{author}{Mauri\xfnm[ M.]}, \bibinfo{author}{Perdomo-Ortiz\xfnm[ A.]}.
\newblock \bibinfo{title}{Flip: A flexible initializer for arbitrarily-sized
  parametrized quantum circuits}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2103.08572v2}{\tt arXiv:2103.08572v2}.
%Type = Misc
\bibitem[{Kulshrestha and Safro(2022)}]{Kulshrestha2022}
\bibinfo{author}{Kulshrestha\xfnm[ A.]}, \bibinfo{author}{Safro\xfnm[ I.]}.
\newblock \bibinfo{title}{Beinit: Avoiding barren plateaus in variational
  quantum algorithms}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2204.13751}.
  \DOIprefix\doi{10.48550/ARXIV.2204.13751}.
%Type = Article
\bibitem[{Volkoff and Coles(2021)}]{Volkoff2021}
\bibinfo{author}{Volkoff\xfnm[ T.]}, \bibinfo{author}{Coles\xfnm[ P.J.]}.
\newblock \bibinfo{title}{Large gradients via correlation in random
  parameterized quantum circuits}.
\newblock \bibinfo{journal}{Quantum Science and Technology}
  \bibinfo{year}{2021};\bibinfo{volume}{6}(\bibinfo{number}{2}):\bibinfo{pages}{025008}.
\newblock \DOIprefix\doi{10.1088/2058-9565/abd891}.
%Type = Article
\bibitem[{Skolik et~al.(2021)Skolik, McClean, Mohseni, van~der Smagt and
  Leib}]{Skolik2021}
\bibinfo{author}{Skolik\xfnm[ A.]}, \bibinfo{author}{McClean\xfnm[ J.R.]},
  \bibinfo{author}{Mohseni\xfnm[ M.]}, \bibinfo{author}{van~der Smagt\xfnm[
  P.]}, \bibinfo{author}{Leib\xfnm[ M.]}.
\newblock \bibinfo{title}{Layerwise learning for quantum neural networks}.
\newblock \bibinfo{journal}{Quantum Machine Intelligence}
  \bibinfo{year}{2021};\bibinfo{volume}{3}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1007/s42484-020-00036-4}.
%Type = Article
\bibitem[{Campos et~al.(2021)Campos, Nasrallah and Biamonte}]{Campos2021}
\bibinfo{author}{Campos\xfnm[ E.]}, \bibinfo{author}{Nasrallah\xfnm[ A.]},
  \bibinfo{author}{Biamonte\xfnm[ J.]}.
\newblock \bibinfo{title}{Abrupt transitions in variational quantum circuit
  training}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2021};\bibinfo{volume}{103}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physreva.103.032607}.
%Type = Misc
\bibitem[{Wu et~al.(2021{\natexlab{b}})Wu, Li, Ding and Xie}]{Wu2021_mit}
\bibinfo{author}{Wu\xfnm[ A.]}, \bibinfo{author}{Li\xfnm[ G.]},
  \bibinfo{author}{Ding\xfnm[ Y.]}, \bibinfo{author}{Xie\xfnm[ Y.]}.
\newblock \bibinfo{title}{Mitigating noise-induced gradient vanishing in
  variational quantum algorithm training}.
\newblock \bibinfo{year}{2021}{\natexlab{b}}.
\newblock \URLprefix \url{https://arxiv.org/abs/2111.13209}.
  \DOIprefix\doi{10.48550/ARXIV.2111.13209}.
%Type = Misc
\bibitem[{Pesah et~al.(2020)Pesah, Cerezo, Wang, Volkoff, Sornborger and
  Coles}]{Pesah2020}
\bibinfo{author}{Pesah\xfnm[ A.]}, \bibinfo{author}{Cerezo\xfnm[ M.]},
  \bibinfo{author}{Wang\xfnm[ S.]}, \bibinfo{author}{Volkoff\xfnm[ T.]},
  \bibinfo{author}{Sornborger\xfnm[ A.T.]}, \bibinfo{author}{Coles\xfnm[
  P.J.]}.
\newblock \bibinfo{title}{Absence of barren plateaus in quantum convolutional
  neural networks}.
\newblock \bibinfo{year}{2020}.
\newblock \href{http://arxiv.org/abs/2011.02966v1}{\tt arXiv:2011.02966v1}.
%Type = Article
\bibitem[{Ryabinkin et~al.(2018{\natexlab{a}})Ryabinkin, Yen, Genin and
  Izmaylov}]{Ryabinkin2018}
\bibinfo{author}{Ryabinkin\xfnm[ I.G.]}, \bibinfo{author}{Yen\xfnm[ T.C.]},
  \bibinfo{author}{Genin\xfnm[ S.N.]}, \bibinfo{author}{Izmaylov\xfnm[ A.F.]}.
\newblock \bibinfo{title}{Qubit coupled cluster method: A systematic approach
  to quantum chemistry on a quantum computer}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2018}{\natexlab{a}};\bibinfo{volume}{14}(\bibinfo{number}{12}):\bibinfo{pages}{6317--6326}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.8b00932}.
%Type = Article
\bibitem[{Xia and Kais(2020)}]{Xia2020}
\bibinfo{author}{Xia\xfnm[ R.]}, \bibinfo{author}{Kais\xfnm[ S.]}.
\newblock \bibinfo{title}{Qubit coupled cluster singles and doubles variational
  quantum eigensolver ansatz for electronic structure calculations}.
\newblock \bibinfo{journal}{Quantum Science and Technology}
  \bibinfo{year}{2020};\bibinfo{volume}{6}(\bibinfo{number}{1}):\bibinfo{pages}{015001}.
\newblock \DOIprefix\doi{10.1088/2058-9565/abbc74}.
%Type = Article
\bibitem[{Romero et~al.(2018)Romero, Babbush, McClean, Hempel, Love and
  Aspuru-Guzik}]{Romero2019}
\bibinfo{author}{Romero\xfnm[ J.]}, \bibinfo{author}{Babbush\xfnm[ R.]},
  \bibinfo{author}{McClean\xfnm[ J.R.]}, \bibinfo{author}{Hempel\xfnm[ C.]},
  \bibinfo{author}{Love\xfnm[ P.J.]}, \bibinfo{author}{Aspuru-Guzik\xfnm[ A.]}.
\newblock \bibinfo{title}{Strategies for quantum computing molecular energies
  using the unitary coupled cluster ansatz}.
\newblock \bibinfo{journal}{Quantum Science and Technology}
  \bibinfo{year}{2018};\bibinfo{volume}{4}(\bibinfo{number}{1}):\bibinfo{pages}{014008}.
\newblock \DOIprefix\doi{10.1088/2058-9565/aad3e4}.
%Type = Article
\bibitem[{Mizukami et~al.(2020)Mizukami, Mitarai, Nakagawa, Yamamoto, Yan and
  Ohnishi}]{Mizukami2020}
\bibinfo{author}{Mizukami\xfnm[ W.]}, \bibinfo{author}{Mitarai\xfnm[ K.]},
  \bibinfo{author}{Nakagawa\xfnm[ Y.O.]}, \bibinfo{author}{Yamamoto\xfnm[ T.]},
  \bibinfo{author}{Yan\xfnm[ T.]}, \bibinfo{author}{Ohnishi\xfnm[ Y.y.]}.
\newblock \bibinfo{title}{Orbital optimized unitary coupled cluster theory for
  quantum computer}.
\newblock \bibinfo{journal}{Physical Review Research}
  \bibinfo{year}{2020};\bibinfo{volume}{2}(\bibinfo{number}{3}):\bibinfo{pages}{033421}.
\newblock \DOIprefix\doi{10.1103/physrevresearch.2.033421}.
%Type = Article
\bibitem[{Mitarai et~al.(2019)Mitarai, Yan and Fujii}]{Mitarai2019}
\bibinfo{author}{Mitarai\xfnm[ K.]}, \bibinfo{author}{Yan\xfnm[ T.]},
  \bibinfo{author}{Fujii\xfnm[ K.]}.
\newblock \bibinfo{title}{Generalization of the output of a variational quantum
  eigensolver by parameter interpolation with a low-depth ansatz}.
\newblock \bibinfo{journal}{Physical Review Applied}
  \bibinfo{year}{2019};\bibinfo{volume}{11}(\bibinfo{number}{4}).
\newblock \DOIprefix\doi{10.1103/physrevapplied.11.044087}.
%Type = Article
\bibitem[{Higgott et~al.(2019)Higgott, Wang and
  Brierley}]{higgottVariationalQuantumComputation2019}
\bibinfo{author}{Higgott\xfnm[ O.]}, \bibinfo{author}{Wang\xfnm[ D.]},
  \bibinfo{author}{Brierley\xfnm[ S.]}.
\newblock \bibinfo{title}{Variational quantum computation of excited states}.
\newblock \bibinfo{journal}{Quantum}
  \bibinfo{year}{2019};\bibinfo{volume}{3}:\bibinfo{pages}{156}.
\newblock \DOIprefix\doi{10.22331/q-2019-07-01-156}.
%Type = Article
\bibitem[{Tilly et~al.(2020)Tilly, Jones, Chen, Wossnig and Grant}]{Tilly2020}
\bibinfo{author}{Tilly\xfnm[ J.]}, \bibinfo{author}{Jones\xfnm[ G.]},
  \bibinfo{author}{Chen\xfnm[ H.]}, \bibinfo{author}{Wossnig\xfnm[ L.]},
  \bibinfo{author}{Grant\xfnm[ E.]}.
\newblock \bibinfo{title}{Computation of molecular excited states on {IBM}
  quantum computers using a discriminative variational quantum eigensolver}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2020};\bibinfo{volume}{102}(\bibinfo{number}{6}).
\newblock \DOIprefix\doi{10.1103/physreva.102.062425}.
%Type = Article
\bibitem[{Chen et~al.(2021{\natexlab{b}})Chen, Nusspickel, Tilly and
  Booth}]{Chen2021}
\bibinfo{author}{Chen\xfnm[ H.]}, \bibinfo{author}{Nusspickel\xfnm[ M.]},
  \bibinfo{author}{Tilly\xfnm[ J.]}, \bibinfo{author}{Booth\xfnm[ G.H.]}.
\newblock \bibinfo{title}{Variational quantum eigensolver for dynamic
  correlation functions}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2021}{\natexlab{b}};\bibinfo{volume}{104}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physreva.104.032405}.
  \href{http://arxiv.org/abs/2105.01703v2}{\tt arXiv:2105.01703v2};
  \bibinfo{note}{phys. Rev. A 104, 032405 (2021)}.
%Type = Misc
\bibitem[{Wu et~al.(2021{\natexlab{c}})Wu, Li, Wang, Feng, Ding and
  Xie}]{Wu2021_hea}
\bibinfo{author}{Wu\xfnm[ A.]}, \bibinfo{author}{Li\xfnm[ G.]},
  \bibinfo{author}{Wang\xfnm[ Y.]}, \bibinfo{author}{Feng\xfnm[ B.]},
  \bibinfo{author}{Ding\xfnm[ Y.]}, \bibinfo{author}{Xie\xfnm[ Y.]}.
\newblock \bibinfo{title}{Towards efficient ansatz architecture for variational
  quantum algorithms}.
\newblock \bibinfo{year}{2021}{\natexlab{c}}.
\newblock \URLprefix \url{https://arxiv.org/abs/2111.13730}.
  \DOIprefix\doi{10.48550/ARXIV.2111.13730}.
%Type = Article
\bibitem[{Bravo-Prieto et~al.(2020)Bravo-Prieto, Lumbreras-Zarapico,
  Tagliacozzo and Latorre}]{BravoPrieto2020}
\bibinfo{author}{Bravo-Prieto\xfnm[ C.]},
  \bibinfo{author}{Lumbreras-Zarapico\xfnm[ J.]},
  \bibinfo{author}{Tagliacozzo\xfnm[ L.]}, \bibinfo{author}{Latorre\xfnm[
  J.I.]}.
\newblock \bibinfo{title}{Scaling of variational quantum circuit depth for
  condensed matter systems}.
\newblock \bibinfo{journal}{Quantum}
  \bibinfo{year}{2020};\bibinfo{volume}{4}:\bibinfo{pages}{272}.
\newblock \URLprefix \url{https://doi.org/10.22331/q-2020-05-28-272}.
  \DOIprefix\doi{10.22331/q-2020-05-28-272}.
%Type = Article
\bibitem[{Bartlett et~al.(1989)Bartlett, Kucharski and Noga}]{Bartlett1989}
\bibinfo{author}{Bartlett\xfnm[ R.J.]}, \bibinfo{author}{Kucharski\xfnm[
  S.A.]}, \bibinfo{author}{Noga\xfnm[ J.]}.
\newblock \bibinfo{title}{Alternative coupled-cluster ansätze {II}. the
  unitary coupled-cluster method}.
\newblock \bibinfo{journal}{Chemical Physics Letters}
  \bibinfo{year}{1989};\bibinfo{volume}{155}(\bibinfo{number}{1}):\bibinfo{pages}{133--140}.
\newblock \DOIprefix\doi{10.1016/s0009-2614(89)87372-5}.
%Type = Article
\bibitem[{Taube and Bartlett(2006)}]{Taube2006}
\bibinfo{author}{Taube\xfnm[ A.G.]}, \bibinfo{author}{Bartlett\xfnm[ R.J.]}.
\newblock \bibinfo{title}{New perspectives on unitary coupled-cluster theory}.
\newblock \bibinfo{journal}{International Journal of Quantum Chemistry}
  \bibinfo{year}{2006};\bibinfo{volume}{106}(\bibinfo{number}{15}):\bibinfo{pages}{3393--3401}.
\newblock \DOIprefix\doi{10.1002/qua.21198}.
%Type = Article
\bibitem[{Filip and Thom(2020)}]{Filip2020}
\bibinfo{author}{Filip\xfnm[ M.A.]}, \bibinfo{author}{Thom\xfnm[ A.J.W.]}.
\newblock \bibinfo{title}{A stochastic approach to unitary coupled cluster}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2020};\bibinfo{volume}{153}(\bibinfo{number}{21}):\bibinfo{pages}{214106}.
\newblock \DOIprefix\doi{10.1063/5.0026141}.
%Type = Article
\bibitem[{Coester and Kümmel(1960)}]{Coester1960}
\bibinfo{author}{Coester\xfnm[ F.]}, \bibinfo{author}{Kümmel\xfnm[ H.]}.
\newblock \bibinfo{title}{Short-range correlations in nuclear wave functions}.
\newblock \bibinfo{journal}{Nuclear Physics}
  \bibinfo{year}{1960};\bibinfo{volume}{17}:\bibinfo{pages}{477--485}.
\newblock \DOIprefix\doi{10.1016/0029-5582(60)90140-1}.
%Type = Article
\bibitem[{{\v{C}}{\'{\i}}{\v{z}}ek(1966)}]{Cizek1966}
\bibinfo{author}{{\v{C}}{\'{\i}}{\v{z}}ek\xfnm[ J.]}.
\newblock \bibinfo{title}{On the correlation problem in atomic and molecular
  systems. calculation of wavefunction components in ursell-type expansion
  using quantum-field theoretical methods}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{1966};\bibinfo{volume}{45}(\bibinfo{number}{11}):\bibinfo{pages}{4256--4266}.
\newblock \DOIprefix\doi{10.1063/1.1727484}.
%Type = Article
\bibitem[{Paldus et~al.(1972)Paldus, {\v{C}}{\'{\i}}{\v{z}}ek and
  Shavitt}]{Paldus1972}
\bibinfo{author}{Paldus\xfnm[ J.]},
  \bibinfo{author}{{\v{C}}{\'{\i}}{\v{z}}ek\xfnm[ J.]},
  \bibinfo{author}{Shavitt\xfnm[ I.]}.
\newblock \bibinfo{title}{Correlation problems in atomic and molecular systems.
  {IV}. extended coupled-pair many-electron theory and its application to the
  {BH}3molecule}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{1972};\bibinfo{volume}{5}(\bibinfo{number}{1}):\bibinfo{pages}{50--67}.
\newblock \DOIprefix\doi{10.1103/physreva.5.50}.
%Type = Article
\bibitem[{Paldus(1977)}]{Paldus1977}
\bibinfo{author}{Paldus\xfnm[ J.]}.
\newblock \bibinfo{title}{Correlation problems in atomic and molecular systems.
  v. spin-adapted coupled cluster many-electron theory}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{1977};\bibinfo{volume}{67}(\bibinfo{number}{1}):\bibinfo{pages}{303--318}.
\newblock \DOIprefix\doi{10.1063/1.434526}.
%Type = Article
\bibitem[{Cizek and Paldus(1980)}]{Cizek1980}
\bibinfo{author}{Cizek\xfnm[ J.]}, \bibinfo{author}{Paldus\xfnm[ J.]}.
\newblock \bibinfo{title}{Coupled cluster approach}.
\newblock \bibinfo{journal}{Physica Scripta}
  \bibinfo{year}{1980};\bibinfo{volume}{21}(\bibinfo{number}{3-4}):\bibinfo{pages}{251--254}.
\newblock \DOIprefix\doi{10.1088/0031-8949/21/3-4/006}.
%Type = Article
\bibitem[{Paldus et~al.(1984)Paldus, {\v{C}}{\'{\i}}{\v{z}}ek and
  Takahashi}]{Paldus1984}
\bibinfo{author}{Paldus\xfnm[ J.]},
  \bibinfo{author}{{\v{C}}{\'{\i}}{\v{z}}ek\xfnm[ J.]},
  \bibinfo{author}{Takahashi\xfnm[ M.]}.
\newblock \bibinfo{title}{Approximate account of the connected quadruply
  excited clusters in the coupled-pair many-electron theory}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{1984};\bibinfo{volume}{30}(\bibinfo{number}{5}):\bibinfo{pages}{2193--2209}.
\newblock \DOIprefix\doi{10.1103/physreva.30.2193}.
%Type = Article
\bibitem[{Piecuch et~al.(1995)Piecuch, Tobo?a and Paldus}]{Piecuch1995}
\bibinfo{author}{Piecuch\xfnm[ P.]}, \bibinfo{author}{Tobo?a\xfnm[ R.]},
  \bibinfo{author}{Paldus\xfnm[ J.]}.
\newblock \bibinfo{title}{Coupled-cluster approaches with an approximate
  account of triply and quadruply excited clusters: Implementation of the
  orthogonally spin-adapted ccd + st(ccd), ccsd + t(ccsd), and acpq + st(acpq)
  formalisms}.
\newblock \bibinfo{journal}{International Journal of Quantum Chemistry}
  \bibinfo{year}{1995};\bibinfo{volume}{55}(\bibinfo{number}{2}):\bibinfo{pages}{133--146}.
\newblock \DOIprefix\doi{10.1002/qua.560550208}.
%Type = Article
\bibitem[{Small and Head-Gordon(2012)}]{Small2012}
\bibinfo{author}{Small\xfnm[ D.W.]}, \bibinfo{author}{Head-Gordon\xfnm[ M.]}.
\newblock \bibinfo{title}{A fusion of the closed-shell coupled cluster singles
  and doubles method and valence-bond theory for bond breaking}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2012};\bibinfo{volume}{137}(\bibinfo{number}{11}):\bibinfo{pages}{114103}.
\newblock \DOIprefix\doi{10.1063/1.4751485}.
%Type = Article
\bibitem[{Small et~al.(2014)Small, Lawler and Head-Gordon}]{Small2014}
\bibinfo{author}{Small\xfnm[ D.W.]}, \bibinfo{author}{Lawler\xfnm[ K.V.]},
  \bibinfo{author}{Head-Gordon\xfnm[ M.]}.
\newblock \bibinfo{title}{Coupled cluster valence bond method: Efficient
  computer implementation and application to multiple bond dissociations and
  strong correlations in the acenes}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2014};\bibinfo{volume}{10}(\bibinfo{number}{5}):\bibinfo{pages}{2027--2040}.
\newblock \DOIprefix\doi{10.1021/ct500112y}.
%Type = Article
\bibitem[{Lee et~al.(2017)Lee, Small, Epifanovsky and Head-Gordon}]{Lee2017}
\bibinfo{author}{Lee\xfnm[ J.]}, \bibinfo{author}{Small\xfnm[ D.W.]},
  \bibinfo{author}{Epifanovsky\xfnm[ E.]}, \bibinfo{author}{Head-Gordon\xfnm[
  M.]}.
\newblock \bibinfo{title}{Coupled-cluster valence-bond singles and doubles for
  strongly correlated systems: Block-tensor based implementation and
  application to oligoacenes}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2017};\bibinfo{volume}{13}(\bibinfo{number}{2}):\bibinfo{pages}{602--615}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.6b01092}.
%Type = Article
\bibitem[{Lee et~al.(2018{\natexlab{b}})Lee, Small and Head-Gordon}]{Lee2018}
\bibinfo{author}{Lee\xfnm[ J.]}, \bibinfo{author}{Small\xfnm[ D.W.]},
  \bibinfo{author}{Head-Gordon\xfnm[ M.]}.
\newblock \bibinfo{title}{Open-shell coupled-cluster valence-bond theory
  augmented with an independent amplitude approximation for three-pair
  correlations: Application to a model oxygen-evolving complex and single
  molecular magnet}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2018}{\natexlab{b}};\bibinfo{volume}{149}(\bibinfo{number}{24}):\bibinfo{pages}{244121}.
\newblock \DOIprefix\doi{10.1063/1.5052667}.
%Type = Article
\bibitem[{Roos et~al.(1980)Roos, Taylor and Sigbahn}]{Roos1980}
\bibinfo{author}{Roos\xfnm[ B.O.]}, \bibinfo{author}{Taylor\xfnm[ P.R.]},
  \bibinfo{author}{Sigbahn\xfnm[ P.E.]}.
\newblock \bibinfo{title}{A complete active space scf method (casscf) using a
  density matrix formulated super-ci approach}.
\newblock \bibinfo{journal}{Chemical Physics}
  \bibinfo{year}{1980};\bibinfo{volume}{48}(\bibinfo{number}{2}):\bibinfo{pages}{157--173}.
\newblock \DOIprefix\doi{https://doi.org/10.1016/0301-0104(80)80045-0}.
%Type = Article
\bibitem[{Nooijen(2000)}]{Nooijen2000}
\bibinfo{author}{Nooijen\xfnm[ M.]}.
\newblock \bibinfo{title}{Can the eigenstates of a many-body hamiltonian be
  represented exactly using a general two-body cluster expansion?}
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2000};\bibinfo{volume}{84}(\bibinfo{number}{10}):\bibinfo{pages}{2108--2111}.
\newblock \DOIprefix\doi{10.1103/physrevlett.84.2108}.
%Type = Article
\bibitem[{Stein et~al.(2014)Stein, Henderson and Scuseria}]{Stein2014}
\bibinfo{author}{Stein\xfnm[ T.]}, \bibinfo{author}{Henderson\xfnm[ T.M.]},
  \bibinfo{author}{Scuseria\xfnm[ G.E.]}.
\newblock \bibinfo{title}{Seniority zero pair coupled cluster doubles theory}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2014};\bibinfo{volume}{140}(\bibinfo{number}{21}):\bibinfo{pages}{214113}.
\newblock \DOIprefix\doi{10.1063/1.4880819}.
%Type = Article
\bibitem[{Limacher et~al.(2013)Limacher, Ayers, Johnson, Baerdemacker, Neck and
  Bultinck}]{Limacher2013}
\bibinfo{author}{Limacher\xfnm[ P.A.]}, \bibinfo{author}{Ayers\xfnm[ P.W.]},
  \bibinfo{author}{Johnson\xfnm[ P.A.]}, \bibinfo{author}{Baerdemacker\xfnm[
  S.D.]}, \bibinfo{author}{Neck\xfnm[ D.V.]}, \bibinfo{author}{Bultinck\xfnm[
  P.]}.
\newblock \bibinfo{title}{A new mean-field method suitable for strongly
  correlated electrons: Computationally facile antisymmetric products of
  nonorthogonal geminals}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2013};\bibinfo{volume}{9}(\bibinfo{number}{3}):\bibinfo{pages}{1394--1401}.
\newblock \DOIprefix\doi{10.1021/ct300902c}.
%Type = Article
\bibitem[{Huggins et~al.(2020{\natexlab{a}})Huggins, Lee, Baek, O'Gorman and
  Whaley}]{Huggins2020}
\bibinfo{author}{Huggins\xfnm[ W.J.]}, \bibinfo{author}{Lee\xfnm[ J.]},
  \bibinfo{author}{Baek\xfnm[ U.]}, \bibinfo{author}{O'Gorman\xfnm[ B.]},
  \bibinfo{author}{Whaley\xfnm[ K.B.]}.
\newblock \bibinfo{title}{A non-orthogonal variational quantum eigensolver}.
\newblock \bibinfo{journal}{New J Phys}
  \bibinfo{year}{2020}{\natexlab{a}};\bibinfo{volume}{22}(\bibinfo{number}{7}):\bibinfo{pages}{073009}.
\newblock \DOIprefix\doi{10.1088/1367-2630/ab867b}.
%Type = Article
\bibitem[{Greene-Diniz and Ramo(2020)}]{GreeneDiniz2020}
\bibinfo{author}{Greene-Diniz\xfnm[ G.]}, \bibinfo{author}{Ramo\xfnm[ D.M.]}.
\newblock \bibinfo{title}{Generalized unitary coupled cluster excitations for
  multireference molecular states optimized by the variational quantum
  eigensolver}.
\newblock \bibinfo{journal}{International Journal of Quantum Chemistry}
  \bibinfo{year}{2020};\bibinfo{volume}{121}(\bibinfo{number}{4}).
\newblock \DOIprefix\doi{10.1002/qua.26352}.
%Type = Misc
\bibitem[{Kottmann and Aspuru-Guzik(2021)}]{Kottmann2021_2}
\bibinfo{author}{Kottmann\xfnm[ J.S.]}, \bibinfo{author}{Aspuru-Guzik\xfnm[
  A.]}.
\newblock \bibinfo{title}{Optimized low-depth quantum circuits for molecular
  electronic structure using a separable pair approximation}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2105.03836v2}{\tt arXiv:2105.03836v2}.
%Type = Article
\bibitem[{Edmiston and Krauss(1968)}]{Edmiston1968}
\bibinfo{author}{Edmiston\xfnm[ C.]}, \bibinfo{author}{Krauss\xfnm[ M.]}.
\newblock \bibinfo{title}{Pseudonatural orbitals as a basis for the
  superposition of configurations. {II}. energy surface for linear h3}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{1968};\bibinfo{volume}{49}(\bibinfo{number}{1}):\bibinfo{pages}{192--205}.
\newblock \DOIprefix\doi{10.1063/1.1669809}.
%Type = Article
\bibitem[{Ahlrichs et~al.(1975)Ahlrichs, Lischka, Staemmler and
  Kutzelnigg}]{Ahlrichs1975}
\bibinfo{author}{Ahlrichs\xfnm[ R.]}, \bibinfo{author}{Lischka\xfnm[ H.]},
  \bibinfo{author}{Staemmler\xfnm[ V.]}, \bibinfo{author}{Kutzelnigg\xfnm[
  W.]}.
\newblock \bibinfo{title}{{PNO}{\textendash}{CI} (pair natural orbital
  configuration interaction) and {CEPA}{\textendash}{PNO} (coupled electron
  pair approximation with pair natural orbitals) calculations of molecular
  systems. i. outline of the method for closed-shell states}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{1975};\bibinfo{volume}{62}(\bibinfo{number}{4}):\bibinfo{pages}{1225--1234}.
\newblock \DOIprefix\doi{10.1063/1.430637}.
%Type = Article
\bibitem[{Meyer(1973)}]{Meyer1973}
\bibinfo{author}{Meyer\xfnm[ W.]}.
\newblock \bibinfo{title}{{PNO}{\textendash}{CI} studies of electron
  correlation effects. i. configuration expansion by means of nonorthogonal
  orbitals, and application to the ground state and ionized states of methane}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{1973};\bibinfo{volume}{58}(\bibinfo{number}{3}):\bibinfo{pages}{1017--1035}.
\newblock \DOIprefix\doi{10.1063/1.1679283}.
%Type = Article
\bibitem[{Meyer(2009)}]{Meyer2009}
\bibinfo{author}{Meyer\xfnm[ W.]}.
\newblock \bibinfo{title}{Ionization energies of water from {PNO}-{CI}
  calculations}.
\newblock \bibinfo{journal}{International Journal of Quantum Chemistry}
  \bibinfo{year}{2009};\bibinfo{volume}{5}(\bibinfo{number}{S5}):\bibinfo{pages}{341--348}.
\newblock \DOIprefix\doi{10.1002/qua.560050839}.
%Type = Article
\bibitem[{Neese et~al.(2009{\natexlab{a}})Neese, Wennmohs and
  Hansen}]{Neese2009_1}
\bibinfo{author}{Neese\xfnm[ F.]}, \bibinfo{author}{Wennmohs\xfnm[ F.]},
  \bibinfo{author}{Hansen\xfnm[ A.]}.
\newblock \bibinfo{title}{Efficient and accurate local approximations to
  coupled-electron pair approaches: An attempt to revive the pair natural
  orbital method}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2009}{\natexlab{a}};\bibinfo{volume}{130}(\bibinfo{number}{11}):\bibinfo{pages}{114108}.
\newblock \DOIprefix\doi{10.1063/1.3086717}.
%Type = Article
\bibitem[{Neese et~al.(2009{\natexlab{b}})Neese, Hansen and
  Liakos}]{Neese2009_2}
\bibinfo{author}{Neese\xfnm[ F.]}, \bibinfo{author}{Hansen\xfnm[ A.]},
  \bibinfo{author}{Liakos\xfnm[ D.G.]}.
\newblock \bibinfo{title}{Efficient and accurate approximations to the local
  coupled cluster singles doubles method using a truncated pair natural orbital
  basis}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2009}{\natexlab{b}};\bibinfo{volume}{131}(\bibinfo{number}{6}):\bibinfo{pages}{064103}.
\newblock \DOIprefix\doi{10.1063/1.3173827}.
%Type = Article
\bibitem[{Nagy and K{\'{a}}llay(2019)}]{Nagy2019}
\bibinfo{author}{Nagy\xfnm[ P.R.]}, \bibinfo{author}{K{\'{a}}llay\xfnm[ M.]}.
\newblock \bibinfo{title}{Approaching the basis set limit of {CCSD}(t) energies
  for large molecules with local natural orbital coupled-cluster methods}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2019};\bibinfo{volume}{15}(\bibinfo{number}{10}):\bibinfo{pages}{5275--5298}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.9b00511}.
%Type = Article
\bibitem[{Yalouz et~al.(2021)Yalouz, Senjean, Günther, Buda, O'Brien and
  Visscher}]{Yalouz2021}
\bibinfo{author}{Yalouz\xfnm[ S.]}, \bibinfo{author}{Senjean\xfnm[ B.]},
  \bibinfo{author}{Günther\xfnm[ J.]}, \bibinfo{author}{Buda\xfnm[ F.]},
  \bibinfo{author}{O'Brien\xfnm[ T.E.]}, \bibinfo{author}{Visscher\xfnm[ L.]}.
\newblock \bibinfo{title}{A state-averaged orbital-optimized hybrid
  quantum{\textendash}classical algorithm for a democratic description of
  ground and excited states}.
\newblock \bibinfo{journal}{Quantum Science and Technology}
  \bibinfo{year}{2021};\bibinfo{volume}{6}(\bibinfo{number}{2}):\bibinfo{pages}{024004}.
\newblock \DOIprefix\doi{10.1088/2058-9565/abd334}.
%Type = Article
\bibitem[{Bozkaya et~al.(2011)Bozkaya, Turney, Yamaguchi, Schaefer and
  Sherrill}]{Bozkaya2011}
\bibinfo{author}{Bozkaya\xfnm[ U.]}, \bibinfo{author}{Turney\xfnm[ J.M.]},
  \bibinfo{author}{Yamaguchi\xfnm[ Y.]}, \bibinfo{author}{Schaefer\xfnm[
  H.F.]}, \bibinfo{author}{Sherrill\xfnm[ C.D.]}.
\newblock \bibinfo{title}{Quadratically convergent algorithm for orbital
  optimization in the orbital-optimized coupled-cluster doubles method and in
  orbital-optimized second-order m{\o}ller-plesset perturbation theory}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2011};\bibinfo{volume}{135}(\bibinfo{number}{10}):\bibinfo{pages}{104103}.
\newblock \DOIprefix\doi{10.1063/1.3631129}.
%Type = Article
\bibitem[{Bozkaya and Sherrill(2013)}]{Bozkaya2013}
\bibinfo{author}{Bozkaya\xfnm[ U.]}, \bibinfo{author}{Sherrill\xfnm[ C.D.]}.
\newblock \bibinfo{title}{Orbital-optimized coupled-electron pair theory and
  its analytic gradients: Accurate equilibrium geometries, harmonic vibrational
  frequencies, and hydrogen transfer reactions}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2013};\bibinfo{volume}{139}(\bibinfo{number}{5}):\bibinfo{pages}{054104}.
\newblock \DOIprefix\doi{10.1063/1.4816628}.
%Type = Article
\bibitem[{Bulik et~al.(2015)Bulik, Henderson and Scuseria}]{Bulik2015}
\bibinfo{author}{Bulik\xfnm[ I.W.]}, \bibinfo{author}{Henderson\xfnm[ T.M.]},
  \bibinfo{author}{Scuseria\xfnm[ G.E.]}.
\newblock \bibinfo{title}{Can single-reference coupled cluster theory describe
  static correlation?}
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2015};\bibinfo{volume}{11}(\bibinfo{number}{7}):\bibinfo{pages}{3171--3179}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.5b00422}.
%Type = Article
\bibitem[{Kowalski(2018)}]{Kowalski2018}
\bibinfo{author}{Kowalski\xfnm[ K.]}.
\newblock \bibinfo{title}{Properties of coupled-cluster equations originating
  in excitation sub-algebras}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2018};\bibinfo{volume}{148}(\bibinfo{number}{9}):\bibinfo{pages}{094104}.
\newblock \DOIprefix\doi{10.1063/1.5010693}.
%Type = Article
\bibitem[{Bauman et~al.(2019{\natexlab{a}})Bauman, Bylaska, Krishnamoorthy,
  Low, Wiebe, Granade et~al.}]{Bauman2019}
\bibinfo{author}{Bauman\xfnm[ N.P.]}, \bibinfo{author}{Bylaska\xfnm[ E.J.]},
  \bibinfo{author}{Krishnamoorthy\xfnm[ S.]}, \bibinfo{author}{Low\xfnm[
  G.H.]}, \bibinfo{author}{Wiebe\xfnm[ N.]}, \bibinfo{author}{Granade\xfnm[
  C.E.]}, et~al.
\newblock \bibinfo{title}{Downfolding of many-body hamiltonians using
  active-space models: Extension of the sub-system embedding sub-algebras
  approach to unitary coupled cluster formalisms}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2019}{\natexlab{a}};\bibinfo{volume}{151}(\bibinfo{number}{1}):\bibinfo{pages}{014107}.
\newblock \DOIprefix\doi{10.1063/1.5094643}.
%Type = Article
\bibitem[{Bauman et~al.(2019{\natexlab{b}})Bauman, Low and
  Kowalski}]{Bauman2019_2}
\bibinfo{author}{Bauman\xfnm[ N.P.]}, \bibinfo{author}{Low\xfnm[ G.H.]},
  \bibinfo{author}{Kowalski\xfnm[ K.]}.
\newblock \bibinfo{title}{Quantum simulations of excited states with
  active-space downfolded hamiltonians}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2019}{\natexlab{b}};\bibinfo{volume}{151}(\bibinfo{number}{23}):\bibinfo{pages}{234114}.
\newblock \DOIprefix\doi{10.1063/1.5128103}.
%Type = Article
\bibitem[{Kowalski and Bauman(2020)}]{Kowalski2020}
\bibinfo{author}{Kowalski\xfnm[ K.]}, \bibinfo{author}{Bauman\xfnm[ N.P.]}.
\newblock \bibinfo{title}{Sub-system quantum dynamics using coupled cluster
  downfolding techniques}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2020};\bibinfo{volume}{152}(\bibinfo{number}{24}):\bibinfo{pages}{244127}.
\newblock \DOIprefix\doi{10.1063/5.0008436}.
%Type = Article
\bibitem[{Kowalski(2021)}]{Kowalski2021}
\bibinfo{author}{Kowalski\xfnm[ K.]}.
\newblock \bibinfo{title}{Dimensionality reduction of the many-body problem
  using coupled-cluster subsystem flow equations: Classical and quantum
  computing perspective}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2021};\bibinfo{volume}{104}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physreva.104.032804}.
%Type = Article
\bibitem[{P et~al.(2021)P, Chl{\'{a}}dek, Veis, Pittner and Karol}]{Bauman2021}
\bibinfo{author}{P\xfnm[ B.N.]}, \bibinfo{author}{Chl{\'{a}}dek\xfnm[ J.]},
  \bibinfo{author}{Veis\xfnm[ L.]}, \bibinfo{author}{Pittner\xfnm[ J.]},
  \bibinfo{author}{Karol\xfnm[ K.]}.
\newblock \bibinfo{title}{Variational quantum eigensolver for approximate
  diagonalization of downfolded hamiltonians using generalized unitary coupled
  cluster ansatz}.
\newblock \bibinfo{journal}{Quantum Science and Technology}
  \bibinfo{year}{2021};\bibinfo{volume}{6}(\bibinfo{number}{3}):\bibinfo{pages}{034008}.
\newblock \DOIprefix\doi{10.1088/2058-9565/abf602}.
%Type = Article
\bibitem[{Metcalf et~al.(2020)Metcalf, Bauman, Kowalski and
  de~Jong}]{Metcalf2020}
\bibinfo{author}{Metcalf\xfnm[ M.]}, \bibinfo{author}{Bauman\xfnm[ N.P.]},
  \bibinfo{author}{Kowalski\xfnm[ K.]}, \bibinfo{author}{de~Jong\xfnm[ W.A.]}.
\newblock \bibinfo{title}{Resource-efficient chemistry on quantum computers
  with the variational quantum eigensolver and the double unitary
  coupled-cluster approach}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2020};\bibinfo{volume}{16}(\bibinfo{number}{10}):\bibinfo{pages}{6165--6175}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.0c00421}.
%Type = Article
\bibitem[{Matsuzawa and Kurashige(2020)}]{Matsuzawa2020}
\bibinfo{author}{Matsuzawa\xfnm[ Y.]}, \bibinfo{author}{Kurashige\xfnm[ Y.]}.
\newblock \bibinfo{title}{Jastrow-type decomposition in quantum chemistry for
  low-depth quantum circuits}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2020};\bibinfo{volume}{16}(\bibinfo{number}{2}):\bibinfo{pages}{944--952}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.9b00963}.
%Type = Article
\bibitem[{Foulkes et~al.(2001)Foulkes, Mitas, Needs and
  Rajagopal}]{Foulkes2001}
\bibinfo{author}{Foulkes\xfnm[ W.M.C.]}, \bibinfo{author}{Mitas\xfnm[ L.]},
  \bibinfo{author}{Needs\xfnm[ R.J.]}, \bibinfo{author}{Rajagopal\xfnm[ G.]}.
\newblock \bibinfo{title}{Quantum monte carlo simulations of solids}.
\newblock \bibinfo{journal}{Reviews of Modern Physics}
  \bibinfo{year}{2001};\bibinfo{volume}{73}(\bibinfo{number}{1}):\bibinfo{pages}{33--83}.
\newblock \DOIprefix\doi{10.1103/revmodphys.73.33}.
%Type = Article
\bibitem[{Neuscamman(2013)}]{Neuscamman2013}
\bibinfo{author}{Neuscamman\xfnm[ E.]}.
\newblock \bibinfo{title}{Communication: A jastrow factor coupled cluster
  theory for weak and strong electron correlation}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2013};\bibinfo{volume}{139}(\bibinfo{number}{18}):\bibinfo{pages}{181101}.
\newblock \DOIprefix\doi{10.1063/1.4829536}.
%Type = Article
\bibitem[{Pavo{\v{s}}evi{\'{c}} et~al.(2018)Pavo{\v{s}}evi{\'{c}}, Culpitt and
  Hammes-Schiffer}]{Pavosevic2018}
\bibinfo{author}{Pavo{\v{s}}evi{\'{c}}\xfnm[ F.]},
  \bibinfo{author}{Culpitt\xfnm[ T.]}, \bibinfo{author}{Hammes-Schiffer\xfnm[
  S.]}.
\newblock \bibinfo{title}{Multicomponent coupled cluster singles and doubles
  theory within the nuclear-electronic orbital framework}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2018};\bibinfo{volume}{15}(\bibinfo{number}{1}):\bibinfo{pages}{338--347}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.8b01120}.
%Type = Misc
\bibitem[{Pavošević and Flick(2021)}]{Pavosevic2021}
\bibinfo{author}{Pavošević\xfnm[ F.]}, \bibinfo{author}{Flick\xfnm[ J.]}.
\newblock \bibinfo{title}{Polaritonic unitary coupled cluster for quantum
  computations}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2106.09842v1}{\tt arXiv:2106.09842v1}.
%Type = Article
\bibitem[{Dallaire-Demers et~al.(2019)Dallaire-Demers, Romero, Veis, Sim and
  Aspuru-Guzik}]{Dallaire2019}
\bibinfo{author}{Dallaire-Demers\xfnm[ P.L.]}, \bibinfo{author}{Romero\xfnm[
  J.]}, \bibinfo{author}{Veis\xfnm[ L.]}, \bibinfo{author}{Sim\xfnm[ S.]},
  \bibinfo{author}{Aspuru-Guzik\xfnm[ A.]}.
\newblock \bibinfo{title}{Low-depth circuit ansatz for preparing correlated
  fermionic states on a quantum computer}.
\newblock \bibinfo{journal}{Quantum Science and Technology}
  \bibinfo{year}{2019};\bibinfo{volume}{4}(\bibinfo{number}{4}):\bibinfo{pages}{045005}.
\newblock \DOIprefix\doi{10.1088/2058-9565/ab3951}.
%Type = Article
\bibitem[{Stolarczyk and Monkhorst(2010)}]{Stolarczyk2010}
\bibinfo{author}{Stolarczyk\xfnm[ L.Z.]}, \bibinfo{author}{Monkhorst\xfnm[
  H.J.]}.
\newblock \bibinfo{title}{Quasiparticle fock-space coupled-cluster theory}.
\newblock \bibinfo{journal}{Molecular Physics}
  \bibinfo{year}{2010};\bibinfo{volume}{108}(\bibinfo{number}{21-23}):\bibinfo{pages}{3067--3089}.
\newblock \DOIprefix\doi{10.1080/00268976.2010.518981}.
%Type = Article
\bibitem[{Rolik and K{\'{a}}llay(2014)}]{Rolik2014}
\bibinfo{author}{Rolik\xfnm[ Z.]}, \bibinfo{author}{K{\'{a}}llay\xfnm[ M.]}.
\newblock \bibinfo{title}{A quasiparticle-based multi-reference coupled-cluster
  method}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2014};\bibinfo{volume}{141}(\bibinfo{number}{13}):\bibinfo{pages}{134112}.
\newblock \DOIprefix\doi{10.1063/1.4896703}.
%Type = Article
\bibitem[{Signoracci et~al.(2015)Signoracci, Duguet, Hagen and
  Jansen}]{Signoracci2015}
\bibinfo{author}{Signoracci\xfnm[ A.]}, \bibinfo{author}{Duguet\xfnm[ T.]},
  \bibinfo{author}{Hagen\xfnm[ G.]}, \bibinfo{author}{Jansen\xfnm[ G.R.]}.
\newblock \bibinfo{title}{Ab {initioBogoliubov} coupled cluster theory for
  open-shell nuclei}.
\newblock \bibinfo{journal}{Physical Review C}
  \bibinfo{year}{2015};\bibinfo{volume}{91}(\bibinfo{number}{6}).
\newblock \DOIprefix\doi{10.1103/physrevc.91.064320}.
%Type = Article
\bibitem[{Sim et~al.(2021)Sim, Romero, Gonthier and Kunitsa}]{Sim2021}
\bibinfo{author}{Sim\xfnm[ S.]}, \bibinfo{author}{Romero\xfnm[ J.]},
  \bibinfo{author}{Gonthier\xfnm[ J.F.]}, \bibinfo{author}{Kunitsa\xfnm[
  A.A.]}.
\newblock \bibinfo{title}{Adaptive pruning-based optimization of parameterized
  quantum circuits}.
\newblock \bibinfo{journal}{Quantum Science and Technology}
  \bibinfo{year}{2021};\bibinfo{volume}{6}(\bibinfo{number}{2}):\bibinfo{pages}{025019}.
\newblock \DOIprefix\doi{10.1088/2058-9565/abe107}.
%Type = Article
\bibitem[{Fedorov et~al.(2022)Fedorov, Alexeev, Gray and Otten}]{Fedorov2022}
\bibinfo{author}{Fedorov\xfnm[ D.A.]}, \bibinfo{author}{Alexeev\xfnm[ Y.]},
  \bibinfo{author}{Gray\xfnm[ S.K.]}, \bibinfo{author}{Otten\xfnm[ M.]}.
\newblock \bibinfo{title}{Unitary selective coupled-cluster method}.
\newblock \bibinfo{journal}{Quantum}
  \bibinfo{year}{2022};\bibinfo{volume}{6}:\bibinfo{pages}{703}.
\newblock \URLprefix \url{https://doi.org/10.22331/q-2022-05-02-703}.
  \DOIprefix\doi{10.22331/q-2022-05-02-703}.
%Type = Misc
\bibitem[{O'Gorman et~al.(2019)O'Gorman, Huggins, Rieffel and
  Whaley}]{OGorman2019}
\bibinfo{author}{O'Gorman\xfnm[ B.]}, \bibinfo{author}{Huggins\xfnm[ W.J.]},
  \bibinfo{author}{Rieffel\xfnm[ E.G.]}, \bibinfo{author}{Whaley\xfnm[ K.B.]}.
\newblock \bibinfo{title}{Generalized swap networks for near-term quantum
  computing}.
\newblock \bibinfo{year}{2019}.
\newblock \href{http://arxiv.org/abs/1905.05118v1}{\tt arXiv:1905.05118v1}.
%Type = Misc
\bibitem[{Anselmetti et~al.(2021)Anselmetti, Wierichs, Gogolin and
  Parrish}]{Anselmetti2021}
\bibinfo{author}{Anselmetti\xfnm[ G.L.R.]}, \bibinfo{author}{Wierichs\xfnm[
  D.]}, \bibinfo{author}{Gogolin\xfnm[ C.]}, \bibinfo{author}{Parrish\xfnm[
  R.M.]}.
\newblock \bibinfo{title}{Local, expressive, quantum-number-preserving vqe
  ansatze for fermionic systems}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2104.05695v2}{\tt arXiv:2104.05695v2}.
%Type = Article
\bibitem[{Yordanov et~al.(2020{\natexlab{b}})Yordanov, Arvidsson-Shukur and
  Barnes}]{Yordanov2020_QE}
\bibinfo{author}{Yordanov\xfnm[ Y.S.]}, \bibinfo{author}{Arvidsson-Shukur\xfnm[
  D.R.M.]}, \bibinfo{author}{Barnes\xfnm[ C.H.W.]}.
\newblock \bibinfo{title}{Efficient quantum circuits for quantum computational
  chemistry}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2020}{\natexlab{b}};\bibinfo{volume}{102}(\bibinfo{number}{6}).
\newblock \DOIprefix\doi{10.1103/physreva.102.062612}.
%Type = Article
\bibitem[{Izmaylov et~al.(2020)Izmaylov, D{\'{\i}}az-Tinoco and
  Lang}]{Izmaylov2020b}
\bibinfo{author}{Izmaylov\xfnm[ A.F.]},
  \bibinfo{author}{D{\'{\i}}az-Tinoco\xfnm[ M.]}, \bibinfo{author}{Lang\xfnm[
  R.A.]}.
\newblock \bibinfo{title}{On the order problem in construction of unitary
  operators for the variational quantum eigensolver}.
\newblock \bibinfo{journal}{Physical Chemistry Chemical Physics}
  \bibinfo{year}{2020};\bibinfo{volume}{22}(\bibinfo{number}{23}):\bibinfo{pages}{12980--12986}.
\newblock \DOIprefix\doi{10.1039/d0cp01707h}.
%Type = Article
\bibitem[{Ryabinkin et~al.(2018{\natexlab{b}})Ryabinkin, Genin and
  Izmaylov}]{Ryabinkin2019}
\bibinfo{author}{Ryabinkin\xfnm[ I.G.]}, \bibinfo{author}{Genin\xfnm[ S.N.]},
  \bibinfo{author}{Izmaylov\xfnm[ A.F.]}.
\newblock \bibinfo{title}{Constrained variational quantum eigensolver: Quantum
  computer search engine in the fock space}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2018}{\natexlab{b}};\bibinfo{volume}{15}(\bibinfo{number}{1}):\bibinfo{pages}{249--255}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.8b00943}.
%Type = Article
\bibitem[{Roth et~al.(2017)Roth, Ganzhorn, Moll, Filipp, Salis and
  Schmidt}]{Roth2018}
\bibinfo{author}{Roth\xfnm[ M.]}, \bibinfo{author}{Ganzhorn\xfnm[ M.]},
  \bibinfo{author}{Moll\xfnm[ N.]}, \bibinfo{author}{Filipp\xfnm[ S.]},
  \bibinfo{author}{Salis\xfnm[ G.]}, \bibinfo{author}{Schmidt\xfnm[ S.]}.
\newblock \bibinfo{title}{Analysis of a parametrically driven exchange-type
  gate and a two-photon excitation gate between superconducting qubits}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2017};\bibinfo{volume}{96}(\bibinfo{number}{6}):\bibinfo{pages}{062323}.
\newblock \DOIprefix\doi{10.1103/physreva.96.062323}.
%Type = Article
\bibitem[{Egger et~al.(2019)Egger, Ganzhorn, Salis, Fuhrer, M\"uller,
  Barkoutsos et~al.}]{Egger2019}
\bibinfo{author}{Egger\xfnm[ D.]}, \bibinfo{author}{Ganzhorn\xfnm[ M.]},
  \bibinfo{author}{Salis\xfnm[ G.]}, \bibinfo{author}{Fuhrer\xfnm[ A.]},
  \bibinfo{author}{M\"uller\xfnm[ P.]}, \bibinfo{author}{Barkoutsos\xfnm[ P.]},
  et~al.
\newblock \bibinfo{title}{Entanglement generation in superconducting qubits
  using holonomic operations}.
\newblock \bibinfo{journal}{Phys Rev Applied}
  \bibinfo{year}{2019};\bibinfo{volume}{11}:\bibinfo{pages}{014017}.
\newblock \DOIprefix\doi{10.1103/PhysRevApplied.11.014017}.
%Type = Article
\bibitem[{McKay et~al.(2016)McKay, Filipp, Mezzacapo, Magesan, Chow and
  Gambetta}]{McKay2016}
\bibinfo{author}{McKay\xfnm[ D.C.]}, \bibinfo{author}{Filipp\xfnm[ S.]},
  \bibinfo{author}{Mezzacapo\xfnm[ A.]}, \bibinfo{author}{Magesan\xfnm[ E.]},
  \bibinfo{author}{Chow\xfnm[ J.M.]}, \bibinfo{author}{Gambetta\xfnm[ J.M.]}.
\newblock \bibinfo{title}{Universal gate for fixed-frequency qubits via a
  tunable bus}.
\newblock \bibinfo{journal}{Physical Review Applied}
  \bibinfo{year}{2016};\bibinfo{volume}{6}(\bibinfo{number}{6}):\bibinfo{pages}{064007}.
\newblock \DOIprefix\doi{10.1103/physrevapplied.6.064007}.
%Type = Article
\bibitem[{Ganzhorn et~al.(2019)Ganzhorn, Egger, Barkoutsos, Ollitrault, Salis,
  Moll et~al.}]{Ganzhorn2019}
\bibinfo{author}{Ganzhorn\xfnm[ M.]}, \bibinfo{author}{Egger\xfnm[ D.]},
  \bibinfo{author}{Barkoutsos\xfnm[ P.]}, \bibinfo{author}{Ollitrault\xfnm[
  P.]}, \bibinfo{author}{Salis\xfnm[ G.]}, \bibinfo{author}{Moll\xfnm[ N.]},
  et~al.
\newblock \bibinfo{title}{Gate-efficient simulation of molecular eigenstates on
  a quantum computer}.
\newblock \bibinfo{journal}{Physical Review Applied}
  \bibinfo{year}{2019};\bibinfo{volume}{11}(\bibinfo{number}{4}):\bibinfo{pages}{044092}.
\newblock \DOIprefix\doi{10.1103/physrevapplied.11.044092}.
%Type = Misc
\bibitem[{Farhi et~al.(2000)Farhi, Goldstone, Gutmann and Sipser}]{Farhi2000}
\bibinfo{author}{Farhi\xfnm[ E.]}, \bibinfo{author}{Goldstone\xfnm[ J.]},
  \bibinfo{author}{Gutmann\xfnm[ S.]}, \bibinfo{author}{Sipser\xfnm[ M.]}.
\newblock \bibinfo{title}{Quantum computation by adiabatic evolution}.
\newblock \bibinfo{year}{2000}.
\newblock \href{http://arxiv.org/abs/quant-ph/0001106v1}{\tt
  arXiv:quant-ph/0001106v1}.
%Type = Misc
\bibitem[{Jattana et~al.(2022)Jattana, Jin, De~Raedt and
  Michielsen}]{Jattana2022}
\bibinfo{author}{Jattana\xfnm[ M.S.]}, \bibinfo{author}{Jin\xfnm[ F.]},
  \bibinfo{author}{De~Raedt\xfnm[ H.]}, \bibinfo{author}{Michielsen\xfnm[ K.]}.
\newblock \bibinfo{title}{Assessment of the variational quantum eigensolver:
  application to the heisenberg model}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2201.05065}.
  \DOIprefix\doi{10.48550/ARXIV.2201.05065}.
%Type = Misc
\bibitem[{Stanisic et~al.(2021)Stanisic, Bosse, Gambetta, Santos, Mruczkiewicz,
  O'Brien et~al.}]{Stanisic2021}
\bibinfo{author}{Stanisic\xfnm[ S.]}, \bibinfo{author}{Bosse\xfnm[ J.L.]},
  \bibinfo{author}{Gambetta\xfnm[ F.M.]}, \bibinfo{author}{Santos\xfnm[ R.A.]},
  \bibinfo{author}{Mruczkiewicz\xfnm[ W.]}, \bibinfo{author}{O'Brien\xfnm[
  T.E.]}, et~al.
\newblock \bibinfo{title}{Observing ground-state properties of the
  fermi-hubbard model using a scalable algorithm on a quantum computer}.
\newblock \bibinfo{year}{2021}.
\newblock \URLprefix \url{https://arxiv.org/abs/2112.02025}.
  \DOIprefix\doi{10.48550/ARXIV.2112.02025}.
%Type = Article
\bibitem[{Jiang et~al.(2018)Jiang, Sung, Kechedzhi, Smelyanskiy and
  Boixo}]{Jiang2018}
\bibinfo{author}{Jiang\xfnm[ Z.]}, \bibinfo{author}{Sung\xfnm[ K.J.]},
  \bibinfo{author}{Kechedzhi\xfnm[ K.]}, \bibinfo{author}{Smelyanskiy\xfnm[
  V.N.]}, \bibinfo{author}{Boixo\xfnm[ S.]}.
\newblock \bibinfo{title}{Quantum algorithms to simulate many-body physics of
  correlated fermions}.
\newblock \bibinfo{journal}{Physical Review Applied}
  \bibinfo{year}{2018};\bibinfo{volume}{9}(\bibinfo{number}{4}).
\newblock \DOIprefix\doi{10.1103/physrevapplied.9.044036}.
%Type = Article
\bibitem[{Verstraete et~al.(2009)Verstraete, Cirac and
  Latorre}]{Verstraete2009}
\bibinfo{author}{Verstraete\xfnm[ F.]}, \bibinfo{author}{Cirac\xfnm[ J.I.]},
  \bibinfo{author}{Latorre\xfnm[ J.I.]}.
\newblock \bibinfo{title}{Quantum circuits for strongly correlated quantum
  systems}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2009};\bibinfo{volume}{79}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physreva.79.032316}.
%Type = Article
\bibitem[{Ferris(2014)}]{Ferris2014}
\bibinfo{author}{Ferris\xfnm[ A.J.]}.
\newblock \bibinfo{title}{Fourier transform for fermionic systems and the
  spectral tensor network}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2014};\bibinfo{volume}{113}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1103/physrevlett.113.010401}.
%Type = Article
\bibitem[{Werschnik and Gross(2007)}]{Werschnik2007}
\bibinfo{author}{Werschnik\xfnm[ J.]}, \bibinfo{author}{Gross\xfnm[ E.K.U.]}.
\newblock \bibinfo{title}{Quantum optimal control theory}.
\newblock \bibinfo{journal}{Journal of Physics B: Atomic, Molecular and Optical
  Physics}
  \bibinfo{year}{2007};\bibinfo{volume}{40}(\bibinfo{number}{18}):\bibinfo{pages}{R175--R211}.
\newblock \DOIprefix\doi{10.1088/0953-4075/40/18/r01}.
%Type = Book
\bibitem[{D{\textquotesingle}Alessandro(2007)}]{Alessandro2007}
\bibinfo{author}{D{\textquotesingle}Alessandro\xfnm[ D.]}.
\newblock \bibinfo{title}{Introduction to Quantum Control and Dynamics}.
\newblock \bibinfo{publisher}{Chapman and Hall/{CRC}}; \bibinfo{year}{2007}.
\newblock ISBN \bibinfo{isbn}{9780429150425}.
\newblock \DOIprefix\doi{10.1201/9781584888833}.
%Type = Misc
\bibitem[{M{\"{u}}ller et~al.(2021)M{\"{u}}ller, Said, Jelezko, Calarco and
  Montangero}]{Muller2021}
\bibinfo{author}{M{\"{u}}ller\xfnm[ M.M.]}, \bibinfo{author}{Said\xfnm[ R.S.]},
  \bibinfo{author}{Jelezko\xfnm[ F.]}, \bibinfo{author}{Calarco\xfnm[ T.]},
  \bibinfo{author}{Montangero\xfnm[ S.]}.
\newblock \bibinfo{title}{One decade of quantum optimal control in the chopped
  random basis}.
\newblock \bibinfo{year}{2021}.
\newblock \URLprefix \url{https://arxiv.org/abs/2104.07687}.
  \DOIprefix\doi{10.48550/ARXIV.2104.07687}.
%Type = Article
\bibitem[{Liu et~al.(2021{\natexlab{b}})Liu, Li and Yang}]{Liu2021_adapt}
\bibinfo{author}{Liu\xfnm[ J.]}, \bibinfo{author}{Li\xfnm[ Z.]},
  \bibinfo{author}{Yang\xfnm[ J.]}.
\newblock \bibinfo{title}{An efficient adaptive variational quantum solver of
  the schr\"{o}dinger equation based on reduced density matrices}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2021}{\natexlab{b}};\bibinfo{volume}{154}(\bibinfo{number}{24}):\bibinfo{pages}{244112}.
\newblock \URLprefix \url{https://doi.org/10.1063/5.0054822}.
  \DOIprefix\doi{10.1063/5.0054822}.
%Type = Misc
\bibitem[{Grimsley et~al.(2022)Grimsley, Barron, Barnes, Economou and
  Mayhall}]{Grimsley2022}
\bibinfo{author}{Grimsley\xfnm[ H.R.]}, \bibinfo{author}{Barron\xfnm[ G.S.]},
  \bibinfo{author}{Barnes\xfnm[ E.]}, \bibinfo{author}{Economou\xfnm[ S.E.]},
  \bibinfo{author}{Mayhall\xfnm[ N.J.]}.
\newblock \bibinfo{title}{Adapt-vqe is insensitive to rough parameter
  landscapes and barren plateaus}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2204.07179}.
  \DOIprefix\doi{10.48550/ARXIV.2204.07179}.
%Type = Misc
\bibitem[{Bilkis et~al.(2021)Bilkis, Cerezo, Verdon, Coles and
  Cincio}]{Bilkis2021}
\bibinfo{author}{Bilkis\xfnm[ M.]}, \bibinfo{author}{Cerezo\xfnm[ M.]},
  \bibinfo{author}{Verdon\xfnm[ G.]}, \bibinfo{author}{Coles\xfnm[ P.J.]},
  \bibinfo{author}{Cincio\xfnm[ L.]}.
\newblock \bibinfo{title}{A semi-agnostic ansatz with variable structure for
  quantum machine learning}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2103.06712v1}{\tt arXiv:2103.06712v1}.
%Type = Misc
\bibitem[{Fan et~al.(2021)Fan, Cao, Xu, Li, Lv and Yung}]{Fan2021}
\bibinfo{author}{Fan\xfnm[ Y.]}, \bibinfo{author}{Cao\xfnm[ C.]},
  \bibinfo{author}{Xu\xfnm[ X.]}, \bibinfo{author}{Li\xfnm[ Z.]},
  \bibinfo{author}{Lv\xfnm[ D.]}, \bibinfo{author}{Yung\xfnm[ M.H.]}.
\newblock \bibinfo{title}{Circuit-depth reduction of unitary-coupled-cluster
  ansatz by energy sorting}.
\newblock \bibinfo{year}{2021}.
\newblock \URLprefix \url{https://arxiv.org/abs/2106.15210}.
  \DOIprefix\doi{10.48550/ARXIV.2106.15210}.
%Type = Article
\bibitem[{Lipkin et~al.(1965)Lipkin, Meshkov and Glick}]{Lipkin1965}
\bibinfo{author}{Lipkin\xfnm[ H.]}, \bibinfo{author}{Meshkov\xfnm[ N.]},
  \bibinfo{author}{Glick\xfnm[ A.]}.
\newblock \bibinfo{title}{Validity of many-body approximation methods for a
  solvable model}.
\newblock \bibinfo{journal}{Nuclear Physics}
  \bibinfo{year}{1965};\bibinfo{volume}{62}(\bibinfo{number}{2}):\bibinfo{pages}{188--198}.
\newblock \URLprefix \url{https://doi.org/10.1016/0029-5582(65)90862-x}.
  \DOIprefix\doi{10.1016/0029-5582(65)90862-x}.
%Type = Article
\bibitem[{Caurier et~al.(2005)Caurier, Mart{\'{\i}}nez-Pinedo, Nowacki, Poves
  and Zuker}]{Caurier2005}
\bibinfo{author}{Caurier\xfnm[ E.]},
  \bibinfo{author}{Mart{\'{\i}}nez-Pinedo\xfnm[ G.]},
  \bibinfo{author}{Nowacki\xfnm[ F.]}, \bibinfo{author}{Poves\xfnm[ A.]},
  \bibinfo{author}{Zuker\xfnm[ A.P.]}.
\newblock \bibinfo{title}{The shell model as a unified view of nuclear
  structure}.
\newblock \bibinfo{journal}{Reviews of Modern Physics}
  \bibinfo{year}{2005};\bibinfo{volume}{77}(\bibinfo{number}{2}):\bibinfo{pages}{427--488}.
\newblock \URLprefix \url{https://doi.org/10.1103/revmodphys.77.427}.
  \DOIprefix\doi{10.1103/revmodphys.77.427}.
%Type = Incollection
\bibitem[{Heyde(1994)}]{Heyde1994}
\bibinfo{author}{Heyde\xfnm[ K.L.G.]}.
\newblock \bibinfo{title}{The nuclear shell model}.
\newblock In: \bibinfo{booktitle}{The Nuclear Shell Model}.
  \bibinfo{publisher}{Springer Berlin Heidelberg}; \bibinfo{year}{1994}, p.
  \bibinfo{pages}{58--154}.
\newblock \URLprefix \url{https://doi.org/10.1007/978-3-642-79052-2_4}.
  \DOIprefix\doi{10.1007/978-3-642-79052-2_4}.
%Type = Misc
\bibitem[{Shkolnikov et~al.(2021)Shkolnikov, Mayhall, Economou and
  Barnes}]{Shkolnikov2021}
\bibinfo{author}{Shkolnikov\xfnm[ V.O.]}, \bibinfo{author}{Mayhall\xfnm[
  N.J.]}, \bibinfo{author}{Economou\xfnm[ S.E.]}, \bibinfo{author}{Barnes\xfnm[
  E.]}.
\newblock \bibinfo{title}{Avoiding symmetry roadblocks and minimizing the
  measurement overhead of adaptive variational quantum eigensolvers}.
\newblock \bibinfo{year}{2021}.
\newblock \URLprefix \url{https://arxiv.org/abs/2109.05340}.
  \DOIprefix\doi{10.48550/ARXIV.2109.05340}.
%Type = Misc
\bibitem[{Mukherjee et~al.(2022)Mukherjee, Berthusen, Getelina, Orth and
  Yao}]{Mukherjee2022}
\bibinfo{author}{Mukherjee\xfnm[ A.]}, \bibinfo{author}{Berthusen\xfnm[ N.F.]},
  \bibinfo{author}{Getelina\xfnm[ J.C.]}, \bibinfo{author}{Orth\xfnm[ P.P.]},
  \bibinfo{author}{Yao\xfnm[ Y.X.]}.
\newblock \bibinfo{title}{Comparative study of adaptive variational quantum
  eigensolvers for multi-orbital impurity models}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2203.06745}.
  \DOIprefix\doi{10.48550/ARXIV.2203.06745}.
%Type = Article
\bibitem[{Zhang et~al.(2021{\natexlab{c}})Zhang, Kyaw, Kottmann, Degroote and
  Aspuru-Guzik}]{Zhang2021_CEP}
\bibinfo{author}{Zhang\xfnm[ Z.J.]}, \bibinfo{author}{Kyaw\xfnm[ T.H.]},
  \bibinfo{author}{Kottmann\xfnm[ J.S.]}, \bibinfo{author}{Degroote\xfnm[ M.]},
  \bibinfo{author}{Aspuru-Guzik\xfnm[ A.]}.
\newblock \bibinfo{title}{Mutual information-assisted adaptive variational
  quantum eigensolver}.
\newblock \bibinfo{journal}{Quantum Science and Technology}
  \bibinfo{year}{2021}{\natexlab{c}};\bibinfo{volume}{6}(\bibinfo{number}{3}):\bibinfo{pages}{035001}.
\newblock \DOIprefix\doi{10.1088/2058-9565/abdca4}.
%Type = Article
\bibitem[{Amico et~al.(2008)Amico, Fazio, Osterloh and Vedral}]{Amico2008}
\bibinfo{author}{Amico\xfnm[ L.]}, \bibinfo{author}{Fazio\xfnm[ R.]},
  \bibinfo{author}{Osterloh\xfnm[ A.]}, \bibinfo{author}{Vedral\xfnm[ V.]}.
\newblock \bibinfo{title}{Entanglement in many-body systems}.
\newblock \bibinfo{journal}{Reviews of Modern Physics}
  \bibinfo{year}{2008};\bibinfo{volume}{80}(\bibinfo{number}{2}):\bibinfo{pages}{517--576}.
\newblock \DOIprefix\doi{10.1103/revmodphys.80.517}.
%Type = Article
\bibitem[{Huang and Kais(2005)}]{Huang2005}
\bibinfo{author}{Huang\xfnm[ Z.]}, \bibinfo{author}{Kais\xfnm[ S.]}.
\newblock \bibinfo{title}{Entanglement as measure of
  electron{\textendash}electron correlation in quantum chemistry calculations}.
\newblock \bibinfo{journal}{Chemical Physics Letters}
  \bibinfo{year}{2005};\bibinfo{volume}{413}(\bibinfo{number}{1-3}):\bibinfo{pages}{1--5}.
\newblock \DOIprefix\doi{10.1016/j.cplett.2005.07.045}.
%Type = Article
\bibitem[{Rissler et~al.(2006)Rissler, Noack and White}]{Rissler2006}
\bibinfo{author}{Rissler\xfnm[ J.]}, \bibinfo{author}{Noack\xfnm[ R.M.]},
  \bibinfo{author}{White\xfnm[ S.R.]}.
\newblock \bibinfo{title}{Measuring orbital interaction using quantum
  information theory}.
\newblock \bibinfo{journal}{Chemical Physics}
  \bibinfo{year}{2006};\bibinfo{volume}{323}(\bibinfo{number}{2-3}):\bibinfo{pages}{519--531}.
\newblock \DOIprefix\doi{10.1016/j.chemphys.2005.10.018}.
%Type = Article
\bibitem[{Lang et~al.(2020)Lang, Ryabinkin and Izmaylov}]{Lang2020}
\bibinfo{author}{Lang\xfnm[ R.A.]}, \bibinfo{author}{Ryabinkin\xfnm[ I.G.]},
  \bibinfo{author}{Izmaylov\xfnm[ A.F.]}.
\newblock \bibinfo{title}{Unitary transformation of the electronic hamiltonian
  with an exact quadratic truncation of the baker-campbell-hausdorff
  expansion}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2020};\bibinfo{volume}{17}(\bibinfo{number}{1}):\bibinfo{pages}{66--78}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.0c00170}.
%Type = Article
\bibitem[{Genin et~al.(2022)Genin, Ryabinkin, Paisley, Whelan, Helander and
  Hudson}]{Genin2022}
\bibinfo{author}{Genin\xfnm[ S.N.]}, \bibinfo{author}{Ryabinkin\xfnm[ I.G.]},
  \bibinfo{author}{Paisley\xfnm[ N.R.]}, \bibinfo{author}{Whelan\xfnm[ S.O.]},
  \bibinfo{author}{Helander\xfnm[ M.G.]}, \bibinfo{author}{Hudson\xfnm[ Z.M.]}.
\newblock \bibinfo{title}{Estimating phosphorescent emission energies in
  ir$^{III}$ complexes using large-scale quantum computing simulations}.
\newblock \bibinfo{journal}{Angewandte Chemie}
  \bibinfo{year}{2022};\bibinfo{volume}{134}(\bibinfo{number}{19}).
\newblock \URLprefix \url{https://doi.org/10.1002/ange.202116175}.
  \DOIprefix\doi{10.1002/ange.202116175}.
%Type = Article
\bibitem[{Ryabinkin et~al.(2021)Ryabinkin, Izmaylov and Genin}]{Ryabinkin2021}
\bibinfo{author}{Ryabinkin\xfnm[ I.G.]}, \bibinfo{author}{Izmaylov\xfnm[
  A.F.]}, \bibinfo{author}{Genin\xfnm[ S.N.]}.
\newblock \bibinfo{title}{A posteriori corrections to the iterative qubit
  coupled cluster method to minimize the use of quantum resources in
  large-scale calculations}.
\newblock \bibinfo{journal}{Quantum Science and Technology}
  \bibinfo{year}{2021};\bibinfo{volume}{6}(\bibinfo{number}{2}):\bibinfo{pages}{024012}.
\newblock \DOIprefix\doi{10.1088/2058-9565/abda8e}.
%Type = Misc
\bibitem[{Rattew et~al.(2019)Rattew, Hu, Pistoia, Chen and Wood}]{Rattew2019}
\bibinfo{author}{Rattew\xfnm[ A.G.]}, \bibinfo{author}{Hu\xfnm[ S.]},
  \bibinfo{author}{Pistoia\xfnm[ M.]}, \bibinfo{author}{Chen\xfnm[ R.]},
  \bibinfo{author}{Wood\xfnm[ S.]}.
\newblock \bibinfo{title}{A domain-agnostic, noise-resistant,
  hardware-efficient evolutionary variational quantum eigensolver}.
\newblock \bibinfo{year}{2019}.
\newblock \href{http://arxiv.org/abs/1910.09694v4}{\tt arXiv:1910.09694v4}.
%Type = Misc
\bibitem[{Chivilikhin et~al.(2020)Chivilikhin, Samarin, Ulyantsev, Iorsh,
  Oganov and Kyriienko}]{Chivilikhin2020}
\bibinfo{author}{Chivilikhin\xfnm[ D.]}, \bibinfo{author}{Samarin\xfnm[ A.]},
  \bibinfo{author}{Ulyantsev\xfnm[ V.]}, \bibinfo{author}{Iorsh\xfnm[ I.]},
  \bibinfo{author}{Oganov\xfnm[ A.R.]}, \bibinfo{author}{Kyriienko\xfnm[ O.]}.
\newblock \bibinfo{title}{Mog-vqe: Multiobjective genetic variational quantum
  eigensolver}.
\newblock \bibinfo{year}{2020}.
\newblock \href{http://arxiv.org/abs/2007.04424v1}{\tt arXiv:2007.04424v1}.
%Type = Misc
\bibitem[{Du et~al.(2020)Du, Huang, You, Hsieh and Tao}]{Du2020}
\bibinfo{author}{Du\xfnm[ Y.]}, \bibinfo{author}{Huang\xfnm[ T.]},
  \bibinfo{author}{You\xfnm[ S.]}, \bibinfo{author}{Hsieh\xfnm[ M.H.]},
  \bibinfo{author}{Tao\xfnm[ D.]}.
\newblock \bibinfo{title}{Quantum circuit architecture search: error mitigation
  and trainability enhancement for variational quantum solvers}.
\newblock \bibinfo{year}{2020}.
\newblock \href{http://arxiv.org/abs/2010.10217v2}{\tt arXiv:2010.10217v2}.
%Type = Misc
\bibitem[{Zhang et~al.(2020{\natexlab{b}})Zhang, Hsieh, Zhang and
  Yao}]{Zhang2020_QAS}
\bibinfo{author}{Zhang\xfnm[ S.X.]}, \bibinfo{author}{Hsieh\xfnm[ C.Y.]},
  \bibinfo{author}{Zhang\xfnm[ S.]}, \bibinfo{author}{Yao\xfnm[ H.]}.
\newblock \bibinfo{title}{Differentiable quantum architecture search}.
\newblock \bibinfo{year}{2020}{\natexlab{b}}.
\newblock \href{http://arxiv.org/abs/2010.08561v2}{\tt arXiv:2010.08561v2}.
%Type = Misc
\bibitem[{Liu et~al.(2018)Liu, Simonyan and Yang}]{Liu2018}
\bibinfo{author}{Liu\xfnm[ H.]}, \bibinfo{author}{Simonyan\xfnm[ K.]},
  \bibinfo{author}{Yang\xfnm[ Y.]}.
\newblock \bibinfo{title}{Darts: Differentiable architecture search}.
\newblock \bibinfo{year}{2018}.
\newblock \href{http://arxiv.org/abs/1806.09055v2}{\tt arXiv:1806.09055v2}.
%Type = Misc
\bibitem[{Zhang et~al.(2021{\natexlab{d}})Zhang, Hsieh, Zhang and
  Yao}]{Zhang2021_QAS}
\bibinfo{author}{Zhang\xfnm[ S.X.]}, \bibinfo{author}{Hsieh\xfnm[ C.Y.]},
  \bibinfo{author}{Zhang\xfnm[ S.]}, \bibinfo{author}{Yao\xfnm[ H.]}.
\newblock \bibinfo{title}{Neural predictor based quantum architecture search}.
\newblock \bibinfo{year}{2021}{\natexlab{d}}.
\newblock \href{http://arxiv.org/abs/2103.06524v1}{\tt arXiv:2103.06524v1}.
%Type = Misc
\bibitem[{Kuo et~al.(2021)Kuo, Fang and Chen}]{Kuo2021}
\bibinfo{author}{Kuo\xfnm[ E.J.]}, \bibinfo{author}{Fang\xfnm[ Y.L.L.]},
  \bibinfo{author}{Chen\xfnm[ S.Y.C.]}.
\newblock \bibinfo{title}{Quantum architecture search via deep reinforcement
  learning}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2104.07715v1}{\tt arXiv:2104.07715v1}.
%Type = Misc
\bibitem[{Chen et~al.(2021{\natexlab{c}})Chen, He, Li, Zheng and
  Situ}]{Chen2021_QAS}
\bibinfo{author}{Chen\xfnm[ C.]}, \bibinfo{author}{He\xfnm[ Z.]},
  \bibinfo{author}{Li\xfnm[ L.]}, \bibinfo{author}{Zheng\xfnm[ S.]},
  \bibinfo{author}{Situ\xfnm[ H.]}.
\newblock \bibinfo{title}{Quantum architecture search with meta-learning}.
\newblock \bibinfo{year}{2021}{\natexlab{c}}.
\newblock \href{http://arxiv.org/abs/2106.06248v1}{\tt arXiv:2106.06248v1}.
%Type = Misc
\bibitem[{Wang et~al.(2021{\natexlab{a}})Wang, Ding, Gu, Lin, Pan, Chong
  et~al.}]{Wang2021_QAS}
\bibinfo{author}{Wang\xfnm[ H.]}, \bibinfo{author}{Ding\xfnm[ Y.]},
  \bibinfo{author}{Gu\xfnm[ J.]}, \bibinfo{author}{Lin\xfnm[ Y.]},
  \bibinfo{author}{Pan\xfnm[ D.Z.]}, \bibinfo{author}{Chong\xfnm[ F.T.]},
  et~al.
\newblock \bibinfo{title}{Quantumnas: Noise-adaptive search for robust quantum
  circuits}.
\newblock \bibinfo{year}{2021}{\natexlab{a}}.
\newblock \href{http://arxiv.org/abs/2107.10845v2}{\tt arXiv:2107.10845v2}.
%Type = Article
\bibitem[{Gutzwiller(1963)}]{Gutzwiller1963}
\bibinfo{author}{Gutzwiller\xfnm[ M.C.]}.
\newblock \bibinfo{title}{Effect of correlation on the ferromagnetism of
  transition metals}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{1963};\bibinfo{volume}{10}(\bibinfo{number}{5}):\bibinfo{pages}{159--162}.
\newblock \DOIprefix\doi{10.1103/physrevlett.10.159}.
%Type = Article
\bibitem[{Hubbard(1963)}]{Hubbard1963}
\bibinfo{author}{Hubbard\xfnm[ J.]}.
\newblock \bibinfo{title}{Electron correlations in narrow energy bands}.
\newblock \bibinfo{journal}{Proceedings of the Royal Society of London Series A
  Mathematical and Physical Sciences}
  \bibinfo{year}{1963};\bibinfo{volume}{276}(\bibinfo{number}{1365}):\bibinfo{pages}{238--257}.
\newblock \DOIprefix\doi{10.1098/rspa.1963.0204}.
%Type = Article
\bibitem[{Seki et~al.(2022)Seki, Otsuka and Yunoki}]{Seki2022}
\bibinfo{author}{Seki\xfnm[ K.]}, \bibinfo{author}{Otsuka\xfnm[ Y.]},
  \bibinfo{author}{Yunoki\xfnm[ S.]}.
\newblock \bibinfo{title}{Gutzwiller wave function on a quantum computer using
  a discrete hubbard-stratonovich transformation}.
\newblock \bibinfo{journal}{Physical Review B}
  \bibinfo{year}{2022};\bibinfo{volume}{105}(\bibinfo{number}{15}).
\newblock \URLprefix \url{https://doi.org/10.1103/physrevb.105.155119}.
  \DOIprefix\doi{10.1103/physrevb.105.155119}.
%Type = Article
\bibitem[{Gentini et~al.(2020)Gentini, Cuccoli, Pirandola, Verrucchi and
  Banchi}]{gentini_noise-resilient_2020}
\bibinfo{author}{Gentini\xfnm[ L.]}, \bibinfo{author}{Cuccoli\xfnm[ A.]},
  \bibinfo{author}{Pirandola\xfnm[ S.]}, \bibinfo{author}{Verrucchi\xfnm[ P.]},
  \bibinfo{author}{Banchi\xfnm[ L.]}.
\newblock \bibinfo{title}{Noise-resilient variational hybrid quantum-classical
  optimization}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2020};\bibinfo{volume}{102}(\bibinfo{number}{5}):\bibinfo{pages}{052414}.
\newblock \DOIprefix\doi{10.1103/physreva.102.052414}.
%Type = Article
\bibitem[{Fran{\c{c}}a and Garc{\'{\i}}a-Patr{\'{o}}n(2021)}]{Franca2021}
\bibinfo{author}{Fran{\c{c}}a\xfnm[ D.S.]},
  \bibinfo{author}{Garc{\'{\i}}a-Patr{\'{o}}n\xfnm[ R.]}.
\newblock \bibinfo{title}{Limitations of optimization algorithms on noisy
  quantum devices}.
\newblock \bibinfo{journal}{Nature Physics}
  \bibinfo{year}{2021};\DOIprefix\doi{10.1038/s41567-021-01356-3}.
%Type = Article
\bibitem[{Schuld et~al.(2019)Schuld, Bergholm, Gogolin, Izaac and
  Killoran}]{schuld_evaluating_2019}
\bibinfo{author}{Schuld\xfnm[ M.]}, \bibinfo{author}{Bergholm\xfnm[ V.]},
  \bibinfo{author}{Gogolin\xfnm[ C.]}, \bibinfo{author}{Izaac\xfnm[ J.]},
  \bibinfo{author}{Killoran\xfnm[ N.]}.
\newblock \bibinfo{title}{Evaluating analytic gradients on quantum hardware}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2019};\bibinfo{volume}{99}(\bibinfo{number}{3}):\bibinfo{pages}{032331}.
\newblock \DOIprefix\doi{10.1103/physreva.99.032331}; \bibinfo{note}{arXiv:
  1811.11184}.
%Type = Misc
\bibitem[{Parrish et~al.(2019{\natexlab{a}})Parrish, Iosue, Ozaeta and
  McMahon}]{parrish_jacobi_2019}
\bibinfo{author}{Parrish\xfnm[ R.M.]}, \bibinfo{author}{Iosue\xfnm[ J.T.]},
  \bibinfo{author}{Ozaeta\xfnm[ A.]}, \bibinfo{author}{McMahon\xfnm[ P.L.]}.
\newblock \bibinfo{title}{A jacobi diagonalization and anderson acceleration
  algorithm for variational quantum algorithm parameter optimization}.
\newblock \bibinfo{year}{2019}{\natexlab{a}}.
\newblock \href{http://arxiv.org/abs/1904.03206v1}{\tt arXiv:1904.03206v1}.
%Type = Article
\bibitem[{Cao et~al.(2020)Cao, Wossnig, Vlastakis, Leek and
  Grant}]{CostFunction2020Cao}
\bibinfo{author}{Cao\xfnm[ S.]}, \bibinfo{author}{Wossnig\xfnm[ L.]},
  \bibinfo{author}{Vlastakis\xfnm[ B.]}, \bibinfo{author}{Leek\xfnm[ P.]},
  \bibinfo{author}{Grant\xfnm[ E.]}.
\newblock \bibinfo{title}{Cost-function embedding and dataset encoding for
  machine learning with parametrized quantum circuits}.
\newblock \bibinfo{journal}{Phys Rev A}
  \bibinfo{year}{2020};\bibinfo{volume}{101}:\bibinfo{pages}{052309}.
\newblock \DOIprefix\doi{10.1103/PhysRevA.101.052309}.
%Type = Article
\bibitem[{Ebel et~al.(2021)Ebel, Joas, Schalk, Weinbrenner, Angerer, Majer
  et~al.}]{ebel_dispersive_2021}
\bibinfo{author}{Ebel\xfnm[ J.]}, \bibinfo{author}{Joas\xfnm[ T.]},
  \bibinfo{author}{Schalk\xfnm[ M.]}, \bibinfo{author}{Weinbrenner\xfnm[ P.]},
  \bibinfo{author}{Angerer\xfnm[ A.]}, \bibinfo{author}{Majer\xfnm[ J.]},
  et~al.
\newblock \bibinfo{title}{Dispersive readout of room-temperature ensemble spin
  sensors}.
\newblock \bibinfo{journal}{Quantum Science and Technology}
  \bibinfo{year}{2021};\bibinfo{volume}{6}(\bibinfo{number}{3}):\bibinfo{pages}{03LT01}.
\newblock \DOIprefix\doi{10.1088/2058-9565/abfaaf}.
%Type = Misc
\bibitem[{Lu et~al.(2015)Lu, Brodutch, Park, Katiyar, Jochym-O'Connor and
  Laflamme}]{lu_nmr_2015}
\bibinfo{author}{Lu\xfnm[ D.]}, \bibinfo{author}{Brodutch\xfnm[ A.]},
  \bibinfo{author}{Park\xfnm[ J.]}, \bibinfo{author}{Katiyar\xfnm[ H.]},
  \bibinfo{author}{Jochym-O'Connor\xfnm[ T.]}, \bibinfo{author}{Laflamme\xfnm[
  R.]}.
\newblock \bibinfo{title}{Nmr quantum information processing}.
\newblock \bibinfo{year}{2015}.
\newblock \href{http://arxiv.org/abs/1501.01353v1}{\tt arXiv:1501.01353v1}.
%Type = Article
\bibitem[{Kiefer and Wolfowitz(1952)}]{kiefer_stochastic_1952}
\bibinfo{author}{Kiefer\xfnm[ J.]}, \bibinfo{author}{Wolfowitz\xfnm[ J.]}.
\newblock \bibinfo{title}{Stochastic estimation of the maximum of a regression
  function}.
\newblock \bibinfo{journal}{The Annals of Mathematical Statistics}
  \bibinfo{year}{1952};\bibinfo{volume}{23}(\bibinfo{number}{3}):\bibinfo{pages}{462--466}.
\newblock \DOIprefix\doi{10.1214/aoms/1177729392}; \bibinfo{note}{publisher:
  Institute of Mathematical Statistics}.
%Type = Article
\bibitem[{Finck and Beyer(2012)}]{s_performance_2012}
\bibinfo{author}{Finck\xfnm[ S.]}, \bibinfo{author}{Beyer\xfnm[ H.G.]}.
\newblock \bibinfo{title}{Performance analysis of the simultaneous perturbation
  stochastic approximation algorithm on the noisy sphere model}.
\newblock \bibinfo{journal}{Theoretical Computer Science}
  \bibinfo{year}{2012};\bibinfo{volume}{419}(\bibinfo{number}{C}):\bibinfo{pages}{50--72}.
\newblock \DOIprefix\doi{10.1016/j.tcs.2011.11.015}; \bibinfo{note}{publisher:
  Theor Comput Sci}.
%Type = Inproceedings
\bibitem[{Durrani and Morison(2003)}]{morison_spsa_2003}
\bibinfo{author}{Durrani\xfnm[ T.]}, \bibinfo{author}{Morison\xfnm[ G.]}.
\newblock \bibinfo{title}{Spsa for noisy non-stationary blind source
  separation}.
\newblock In: \bibinfo{booktitle}{2003 IEEE International Conference on
  Acoustics, Speech, and Signal Processing, 2003. Proceedings. (ICASSP '03).};
  vol.~\bibinfo{volume}{5}. \bibinfo{year}{2003}, p. \bibinfo{pages}{V--285}.
\newblock \DOIprefix\doi{10.1109/ICASSP.2003.1199925}.
%Type = Inproceedings
\bibitem[{Wang et~al.(2018)Wang, Zhu and Spall}]{wang_mixed_2018}
\bibinfo{author}{Wang\xfnm[ L.]}, \bibinfo{author}{Zhu\xfnm[ J.]},
  \bibinfo{author}{Spall\xfnm[ J.C.]}.
\newblock \bibinfo{title}{Mixed simultaneous perturbation stochastic
  approximation for gradient-free optimization with noisy measurements}.
\newblock In: \bibinfo{booktitle}{2018 {Annual} {American} {Control}
  {Conference} ({ACC})}. \bibinfo{publisher}{{IEEE}}; \bibinfo{year}{2018}, p.
  \bibinfo{pages}{3774--3779}.
\newblock \DOIprefix\doi{10.23919/acc.2018.8430974}; \bibinfo{note}{iSSN:
  2378-5861}.
%Type = Inproceedings
\bibitem[{Spall(1997)}]{Spall1997AcceleratedMeasurements}
\bibinfo{author}{Spall\xfnm[ J.]}.
\newblock \bibinfo{title}{Accelerated second-order stochastic optimization
  using only function measurements}.
\newblock In: \bibinfo{booktitle}{Proceedings of the 36th IEEE Conference on
  Decision and Control}; vol.~\bibinfo{volume}{2}. \bibinfo{year}{1997}, p.
  \bibinfo{pages}{1417--1424 vol.2}.
\newblock \DOIprefix\doi{10.1109/CDC.1997.657661}.
%Type = Article
\bibitem[{Mitarai and Fujii(2019)}]{mitarai_methodology_2019}
\bibinfo{author}{Mitarai\xfnm[ K.]}, \bibinfo{author}{Fujii\xfnm[ K.]}.
\newblock \bibinfo{title}{Methodology for replacing indirect measurements with
  direct measurements}.
\newblock \bibinfo{journal}{Physical Review Research}
  \bibinfo{year}{2019};\bibinfo{volume}{1}(\bibinfo{number}{1}):\bibinfo{pages}{013006}.
\newblock \DOIprefix\doi{10.1103/physrevresearch.1.013006}.
%Type = Article
\bibitem[{Hubregtsen et~al.(2022)Hubregtsen, Wilde, Qasim and
  Eisert}]{Hubregtsen2022}
\bibinfo{author}{Hubregtsen\xfnm[ T.]}, \bibinfo{author}{Wilde\xfnm[ F.]},
  \bibinfo{author}{Qasim\xfnm[ S.]}, \bibinfo{author}{Eisert\xfnm[ J.]}.
\newblock \bibinfo{title}{Single-component gradient rules for variational
  quantum algorithms}.
\newblock \bibinfo{journal}{Quantum Science and Technology}
  \bibinfo{year}{2022};\bibinfo{volume}{7}(\bibinfo{number}{3}):\bibinfo{pages}{035008}.
\newblock \URLprefix \url{https://doi.org/10.1088/2058-9565/ac6824}.
  \DOIprefix\doi{10.1088/2058-9565/ac6824}.
%Type = Article
\bibitem[{Wierichs et~al.(2022{\natexlab{a}})Wierichs, Izaac, Wang and
  Lin}]{GeneralGradientsWierichs2022}
\bibinfo{author}{Wierichs\xfnm[ D.]}, \bibinfo{author}{Izaac\xfnm[ J.]},
  \bibinfo{author}{Wang\xfnm[ C.]}, \bibinfo{author}{Lin\xfnm[ C.Y.Y.]}.
\newblock \bibinfo{title}{General parameter-shift rules for quantum gradients}.
\newblock \bibinfo{journal}{Quantum}
  \bibinfo{year}{2022}{\natexlab{a}};\bibinfo{volume}{6}:\bibinfo{pages}{677}.
\newblock \URLprefix \url{https://doi.org/10.22331/q-2022-03-30-677}.
  \DOIprefix\doi{10.22331/q-2022-03-30-677}.
%Type = Misc
\bibitem[{Theis(2021)}]{OptimalityCircuits2021Theis}
\bibinfo{author}{Theis\xfnm[ D.O.]}.
\newblock \bibinfo{title}{Optimality of finite-support parameter shift rules
  for derivatives of variational quantum circuits}.
\newblock \bibinfo{year}{2021}.
\newblock \URLprefix \url{https://arxiv.org/abs/2112.14669}.
  \DOIprefix\doi{10.48550/ARXIV.2112.14669}.
%Type = Article
\bibitem[{Kottmann et~al.(2021{\natexlab{b}})Kottmann, Anand and
  Aspuru-Guzik}]{Kottmann2021_3}
\bibinfo{author}{Kottmann\xfnm[ J.S.]}, \bibinfo{author}{Anand\xfnm[ A.]},
  \bibinfo{author}{Aspuru-Guzik\xfnm[ A.]}.
\newblock \bibinfo{title}{A feasible approach for automatically differentiable
  unitary coupled-cluster on quantum computers}.
\newblock \bibinfo{journal}{Chemical Science}
  \bibinfo{year}{2021}{\natexlab{b}};\bibinfo{volume}{12}(\bibinfo{number}{10}):\bibinfo{pages}{3497--3508}.
\newblock \URLprefix \url{https://doi.org/10.1039/d0sc06627c}.
  \DOIprefix\doi{10.1039/d0sc06627c}.
%Type = Misc
\bibitem[{Lemaréchal(2012)}]{Lemarechal12cauchyand}
\bibinfo{author}{Lemaréchal\xfnm[ C.]}.
\newblock \bibinfo{title}{Cauchy and the gradient method}.
\newblock \bibinfo{year}{2012}.
\newblock \URLprefix
  \url{https://www.math.uni-bielefeld.de/documenta/vol-ismp/40_lemarechal-claude.html}.
%Type = Article
\bibitem[{Courant(1943)}]{Courant1943Variational}
\bibinfo{author}{Courant\xfnm[ R.]}.
\newblock \bibinfo{title}{{Variational methods for the solution of problems of
  equilibrium and vibrations}}.
\newblock \bibinfo{journal}{Bulletin of the American Mathematical Society}
  \bibinfo{year}{1943};\bibinfo{volume}{49}(\bibinfo{number}{1}):\bibinfo{pages}{1
  -- 23}.
\newblock \DOIprefix\doi{bams/1183504922}.
%Type = Misc
\bibitem[{Kingma and Ba(2014)}]{kingma_adam_2017}
\bibinfo{author}{Kingma\xfnm[ D.P.]}, \bibinfo{author}{Ba\xfnm[ J.]}.
\newblock \bibinfo{title}{Adam: A method for stochastic optimization}.
\newblock \bibinfo{year}{2014}.
\newblock \href{http://arxiv.org/abs/1412.6980v9}{\tt arXiv:1412.6980v9}.
%Type = Article
\bibitem[{Byrd et~al.(1995)Byrd, Lu, Nocedal and Zhu}]{byrdt_limited_nodate}
\bibinfo{author}{Byrd\xfnm[ R.H.]}, \bibinfo{author}{Lu\xfnm[ P.]},
  \bibinfo{author}{Nocedal\xfnm[ J.]}, \bibinfo{author}{Zhu\xfnm[ C.]}.
\newblock \bibinfo{title}{A limited memory algorithm for bound constrained
  optimization}.
\newblock \bibinfo{journal}{SIAM Journal on Scientific Computing}
  \bibinfo{year}{1995};\bibinfo{volume}{16}(\bibinfo{number}{5}):\bibinfo{pages}{1190--1208}.
\newblock \DOIprefix\doi{10.1137/0916069}.
%Type = Article
\bibitem[{Huembeli and Dauphin(2021)}]{huembeli_characterizing_2021}
\bibinfo{author}{Huembeli\xfnm[ P.]}, \bibinfo{author}{Dauphin\xfnm[ A.]}.
\newblock \bibinfo{title}{Characterizing the loss landscape of variational
  quantum circuits}.
\newblock \bibinfo{journal}{Quantum Science and Technology}
  \bibinfo{year}{2021};\bibinfo{volume}{6}(\bibinfo{number}{2}):\bibinfo{pages}{025011}.
\newblock \DOIprefix\doi{10.1088/2058-9565/abdbc9}.
%Type = Article
\bibitem[{Amari(1998)}]{amari_natural_1998}
\bibinfo{author}{Amari\xfnm[ S.i.]}.
\newblock \bibinfo{title}{Natural gradient works efficiently in learning}.
\newblock \bibinfo{journal}{Neural Computation}
  \bibinfo{year}{1998};\bibinfo{volume}{10}(\bibinfo{number}{2}):\bibinfo{pages}{251--276}.
\newblock \DOIprefix\doi{10.1162/089976698300017746}; \bibinfo{note}{conference
  Name: Neural Computation}.
%Type = Misc
\bibitem[{Martens(2014)}]{martens_new_2020}
\bibinfo{author}{Martens\xfnm[ J.]}.
\newblock \bibinfo{title}{New insights and perspectives on the natural gradient
  method}.
\newblock \bibinfo{year}{2014}.
\newblock \href{http://arxiv.org/abs/1412.1193v11}{\tt arXiv:1412.1193v11}.
%Type = Article
\bibitem[{Wierichs et~al.(2020)Wierichs, Gogolin and
  Kastoryano}]{wierichs_avoiding_2020}
\bibinfo{author}{Wierichs\xfnm[ D.]}, \bibinfo{author}{Gogolin\xfnm[ C.]},
  \bibinfo{author}{Kastoryano\xfnm[ M.]}.
\newblock \bibinfo{title}{Avoiding local minima in variational quantum
  eigensolvers with the natural gradient optimizer}.
\newblock \bibinfo{journal}{Physical Review Research}
  \bibinfo{year}{2020};\bibinfo{volume}{2}(\bibinfo{number}{4}):\bibinfo{pages}{043246}.
\newblock \DOIprefix\doi{10.1103/physrevresearch.2.043246}.
%Type = Misc
\bibitem[{Wiersema and Killoran(2022)}]{Wiersema2022OptimizingGradientFlow}
\bibinfo{author}{Wiersema\xfnm[ R.]}, \bibinfo{author}{Killoran\xfnm[ N.]}.
\newblock \bibinfo{title}{Optimizing quantum circuits with riemannian gradient
  flow}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2202.06976}.
  \DOIprefix\doi{10.48550/ARXIV.2202.06976}.
%Type = Article
\bibitem[{Kullback and Leibler(1951)}]{Kullback1951}
\bibinfo{author}{Kullback\xfnm[ S.]}, \bibinfo{author}{Leibler\xfnm[ R.A.]}.
\newblock \bibinfo{title}{On information and sufficiency}.
\newblock \bibinfo{journal}{The Annals of Mathematical Statistics}
  \bibinfo{year}{1951};\bibinfo{volume}{22}(\bibinfo{number}{1}):\bibinfo{pages}{79--86}.
\newblock \DOIprefix\doi{10.1214/aoms/1177729694}.
%Type = Article
\bibitem[{{\v{S}}afr{\'{a}}nek(2018)}]{safranek_simple_2018}
\bibinfo{author}{{\v{S}}afr{\'{a}}nek\xfnm[ D.]}.
\newblock \bibinfo{title}{Simple expression for the quantum fisher information
  matrix}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2018};\bibinfo{volume}{97}(\bibinfo{number}{4}):\bibinfo{pages}{042322}.
\newblock \DOIprefix\doi{10.1103/physreva.97.042322}; \bibinfo{note}{arXiv:
  1801.00945}.
%Type = Article
\bibitem[{Liu et~al.(2019)Liu, Yuan, Lu and Wang}]{liu_quantum_2020}
\bibinfo{author}{Liu\xfnm[ J.]}, \bibinfo{author}{Yuan\xfnm[ H.]},
  \bibinfo{author}{Lu\xfnm[ X.M.]}, \bibinfo{author}{Wang\xfnm[ X.]}.
\newblock \bibinfo{title}{Quantum fisher information matrix and multiparameter
  estimation}.
\newblock \bibinfo{journal}{Journal of Physics A: Mathematical and Theoretical}
  \bibinfo{year}{2019};\bibinfo{volume}{53}(\bibinfo{number}{2}):\bibinfo{pages}{023001}.
\newblock \DOIprefix\doi{10.1088/1751-8121/ab5d4d}; \bibinfo{note}{arXiv:
  1907.08037}.
%Type = Misc
\bibitem[{Yamamoto(2019)}]{yamamoto_natural_2019}
\bibinfo{author}{Yamamoto\xfnm[ N.]}.
\newblock \bibinfo{title}{On the natural gradient for variational quantum
  eigensolver}.
\newblock \bibinfo{year}{2019}.
\newblock \href{http://arxiv.org/abs/1909.05074v1}{\tt arXiv:1909.05074v1}.
%Type = Article
\bibitem[{van Straaten and Koczor(2021)}]{Straaten2020}
\bibinfo{author}{van Straaten\xfnm[ B.]}, \bibinfo{author}{Koczor\xfnm[ B.]}.
\newblock \bibinfo{title}{Measurement cost of metric-aware variational quantum
  algorithms}.
\newblock \bibinfo{journal}{PRX Quantum}
  \bibinfo{year}{2021};\bibinfo{volume}{2}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/prxquantum.2.030324}.
  \href{http://arxiv.org/abs/2005.05172v2}{\tt arXiv:2005.05172v2};
  \bibinfo{note}{pRX Quantum 2, 030324 (2021)}.
%Type = Article
\bibitem[{Gacon et~al.(2021)Gacon, Zoufal, Carleo and
  Woerner}]{Gacon2021simultaneous}
\bibinfo{author}{Gacon\xfnm[ J.]}, \bibinfo{author}{Zoufal\xfnm[ C.]},
  \bibinfo{author}{Carleo\xfnm[ G.]}, \bibinfo{author}{Woerner\xfnm[ S.]}.
\newblock \bibinfo{title}{Simultaneous {P}erturbation {S}tochastic
  {A}pproximation of the {Q}uantum {F}isher {I}nformation}.
\newblock \bibinfo{journal}{{Quantum}}
  \bibinfo{year}{2021};\bibinfo{volume}{5}:\bibinfo{pages}{567}.
\newblock \DOIprefix\doi{10.22331/q-2021-10-20-567}.
%Type = Article
\bibitem[{Nelder and Mead(1965)}]{nelder_simplex_1965}
\bibinfo{author}{Nelder\xfnm[ J.A.]}, \bibinfo{author}{Mead\xfnm[ R.]}.
\newblock \bibinfo{title}{A simplex method for function minimization}.
\newblock \bibinfo{journal}{The Computer Journal}
  \bibinfo{year}{1965};\bibinfo{volume}{7}(\bibinfo{number}{4}):\bibinfo{pages}{308--313}.
\newblock \DOIprefix\doi{10.1093/comjnl/7.4.308}.
%Type = Inproceedings
\bibitem[{Lavrijsen et~al.(2020)Lavrijsen, Tudor, Müller, Iancu and
  de~Jong}]{Lavrijsen2020ClassicalDevices}
\bibinfo{author}{Lavrijsen\xfnm[ W.]}, \bibinfo{author}{Tudor\xfnm[ A.]},
  \bibinfo{author}{Müller\xfnm[ J.]}, \bibinfo{author}{Iancu\xfnm[ C.]},
  \bibinfo{author}{de~Jong\xfnm[ W.]}.
\newblock \bibinfo{title}{Classical optimizers for noisy intermediate-scale
  quantum devices}.
\newblock In: \bibinfo{booktitle}{2020 IEEE International Conference on Quantum
  Computing and Engineering (QCE)}. \bibinfo{year}{2020}, p.
  \bibinfo{pages}{267--277}.
\newblock \DOIprefix\doi{10.1109/QCE49297.2020.00041}.
%Type = Article
\bibitem[{Powell(1964)}]{Powell1964}
\bibinfo{author}{Powell\xfnm[ M.J.D.]}.
\newblock \bibinfo{title}{{An efficient method for finding the minimum of a
  function of several variables without calculating derivatives}}.
\newblock \bibinfo{journal}{The Computer Journal}
  \bibinfo{year}{1964};\bibinfo{volume}{7}(\bibinfo{number}{2}):\bibinfo{pages}{155--162}.
\newblock \DOIprefix\doi{10.1093/comjnl/7.2.155}.
%Type = Misc
\bibitem[{Vidal and
  Theis(2018{\natexlab{b}})}]{Vidal2018CalculusQuantumCircuit}
\bibinfo{author}{Vidal\xfnm[ J.G.]}, \bibinfo{author}{Theis\xfnm[ D.O.]}.
\newblock \bibinfo{title}{Calculus on parameterized quantum circuits}.
\newblock \bibinfo{year}{2018}{\natexlab{b}}.
\newblock \URLprefix \url{https://arxiv.org/abs/1812.06323}.
  \DOIprefix\doi{10.48550/ARXIV.1812.06323}.
%Type = Article
\bibitem[{Wierichs et~al.(2022{\natexlab{b}})Wierichs, Izaac, Wang and
  Lin}]{Wierichs2022}
\bibinfo{author}{Wierichs\xfnm[ D.]}, \bibinfo{author}{Izaac\xfnm[ J.]},
  \bibinfo{author}{Wang\xfnm[ C.]}, \bibinfo{author}{Lin\xfnm[ C.Y.Y.]}.
\newblock \bibinfo{title}{General parameter-shift rules for quantum gradients}.
\newblock \bibinfo{journal}{Quantum}
  \bibinfo{year}{2022}{\natexlab{b}};\bibinfo{volume}{6}:\bibinfo{pages}{677}.
\newblock \URLprefix \url{https://doi.org/10.22331/q-2022-03-30-677}.
  \DOIprefix\doi{10.22331/q-2022-03-30-677}.
%Type = Article
\bibitem[{Sung et~al.(2020)Sung, Yao, Harrigan, Rubin, Jiang, Lin
  et~al.}]{sung_using_2020}
\bibinfo{author}{Sung\xfnm[ K.J.]}, \bibinfo{author}{Yao\xfnm[ J.]},
  \bibinfo{author}{Harrigan\xfnm[ M.P.]}, \bibinfo{author}{Rubin\xfnm[ N.C.]},
  \bibinfo{author}{Jiang\xfnm[ Z.]}, \bibinfo{author}{Lin\xfnm[ L.]}, et~al.
\newblock \bibinfo{title}{Using models to improve optimizers for variational
  quantum algorithms}.
\newblock \bibinfo{journal}{Quantum Science and Technology}
  \bibinfo{year}{2020};\bibinfo{volume}{5}(\bibinfo{number}{4}):\bibinfo{pages}{044008}.
\newblock \DOIprefix\doi{10.1088/2058-9565/abb6d9}.
%Type = Article
\bibitem[{Golub and van~der Vorst(2000)}]{golub_eigenvalue_2000}
\bibinfo{author}{Golub\xfnm[ G.H.]}, \bibinfo{author}{van~der Vorst\xfnm[
  H.A.]}.
\newblock \bibinfo{title}{Eigenvalue computation in the 20th century}.
\newblock \bibinfo{journal}{Journal of Computational and Applied Mathematics}
  \bibinfo{year}{2000};\bibinfo{volume}{123}(\bibinfo{number}{1-2}):\bibinfo{pages}{35--65}.
\newblock \DOIprefix\doi{10.1016/s0377-0427(00)00413-1}.
%Type = Article
\bibitem[{Zhang and Yin(2020)}]{zhang_collective_2020}
\bibinfo{author}{Zhang\xfnm[ D.B.]}, \bibinfo{author}{Yin\xfnm[ T.]}.
\newblock \bibinfo{title}{Collective optimization for variational quantum
  eigensolvers}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2020};\bibinfo{volume}{101}(\bibinfo{number}{3}):\bibinfo{pages}{032311}.
\newblock \DOIprefix\doi{10.1103/physreva.101.032311}.
%Type = Article
\bibitem[{Barkoutsos et~al.(2020)Barkoutsos, Nannicini, Robert, Tavernelli and
  Woerner}]{barkoutsos_improving_2020}
\bibinfo{author}{Barkoutsos\xfnm[ P.K.]}, \bibinfo{author}{Nannicini\xfnm[
  G.]}, \bibinfo{author}{Robert\xfnm[ A.]}, \bibinfo{author}{Tavernelli\xfnm[
  I.]}, \bibinfo{author}{Woerner\xfnm[ S.]}.
\newblock \bibinfo{title}{Improving variational quantum optimization using
  {CVaR}}.
\newblock \bibinfo{journal}{Quantum}
  \bibinfo{year}{2020};\bibinfo{volume}{4}:\bibinfo{pages}{256}.
\newblock \DOIprefix\doi{10.22331/q-2020-04-20-256}; \bibinfo{note}{arXiv:
  1907.04769}.
%Type = Article
\bibitem[{Kuroiwa and Nakagawa(2021)}]{KuroiwaPenaltyEigensolver2021}
\bibinfo{author}{Kuroiwa\xfnm[ K.]}, \bibinfo{author}{Nakagawa\xfnm[ Y.O.]}.
\newblock \bibinfo{title}{Penalty methods for a variational quantum
  eigensolver}.
\newblock \bibinfo{journal}{Phys Rev Research}
  \bibinfo{year}{2021};\bibinfo{volume}{3}:\bibinfo{pages}{013197}.
\newblock \URLprefix
  \url{https://link.aps.org/doi/10.1103/PhysRevResearch.3.013197}.
  \DOIprefix\doi{10.1103/PhysRevResearch.3.013197}.
%Type = Misc
\bibitem[{Xuchen~You(2021)}]{ExponentiallyNetworks2021}
\bibinfo{author}{Xuchen~You\xfnm[ X.W.]}.
\newblock \bibinfo{title}{Exponentially many local minima in quantum neural
  networks}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2110.02479v1}{\tt arXiv:2110.02479v1}.
%Type = Article
\bibitem[{Mih{\'{a}}likov{\'{a}} et~al.(2022)Mih{\'{a}}likov{\'{a}},
  Fri{\'{a}}k, Pivoluska, Plesch, Saip and {\v{S}}ob}]{Mihlikov2022}
\bibinfo{author}{Mih{\'{a}}likov{\'{a}}\xfnm[ I.]},
  \bibinfo{author}{Fri{\'{a}}k\xfnm[ M.]}, \bibinfo{author}{Pivoluska\xfnm[
  M.]}, \bibinfo{author}{Plesch\xfnm[ M.]}, \bibinfo{author}{Saip\xfnm[ M.]},
  \bibinfo{author}{{\v{S}}ob\xfnm[ M.]}.
\newblock \bibinfo{title}{Best-practice aspects of quantum-computer
  calculations: A case study of the hydrogen molecule}.
\newblock \bibinfo{journal}{Molecules}
  \bibinfo{year}{2022};\bibinfo{volume}{27}(\bibinfo{number}{3}):\bibinfo{pages}{597}.
\newblock \URLprefix \url{https://doi.org/10.3390/molecules27030597}.
  \DOIprefix\doi{10.3390/molecules27030597}.
%Type = Misc
\bibitem[{Bonet-Monroig et~al.(2021)Bonet-Monroig, Wang, Vermetten, Senjean,
  Moussa, Bäck et~al.}]{BonetMonroig2021}
\bibinfo{author}{Bonet-Monroig\xfnm[ X.]}, \bibinfo{author}{Wang\xfnm[ H.]},
  \bibinfo{author}{Vermetten\xfnm[ D.]}, \bibinfo{author}{Senjean\xfnm[ B.]},
  \bibinfo{author}{Moussa\xfnm[ C.]}, \bibinfo{author}{Bäck\xfnm[ T.]}, et~al.
\newblock \bibinfo{title}{Performance comparison of optimization methods on
  variational quantum algorithms}.
\newblock \bibinfo{year}{2021}.
\newblock \URLprefix \url{https://arxiv.org/abs/2111.13454}.
  \DOIprefix\doi{10.48550/ARXIV.2111.13454}.
%Type = Misc
\bibitem[{Boyd and Koczor(2022)}]{BoydCoVar2022}
\bibinfo{author}{Boyd\xfnm[ G.]}, \bibinfo{author}{Koczor\xfnm[ B.]}.
\newblock \bibinfo{title}{Training variational quantum circuits with covar:
  covariance root finding with classical shadows}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2204.08494}.
  \DOIprefix\doi{10.48550/ARXIV.2204.08494}.
%Type = Misc
\bibitem[{Mueller et~al.(2022)Mueller, Lavrijsen, Iancu and
  de~jong}]{AcceleratingProcessesMueller2021}
\bibinfo{author}{Mueller\xfnm[ J.]}, \bibinfo{author}{Lavrijsen\xfnm[ W.]},
  \bibinfo{author}{Iancu\xfnm[ C.]}, \bibinfo{author}{de~jong\xfnm[ W.]}.
\newblock \bibinfo{title}{Accelerating noisy vqe optimization with gaussian
  processes}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2204.07331}.
  \DOIprefix\doi{10.48550/ARXIV.2204.07331}.
%Type = Misc
\bibitem[{Gidi et~al.(2022)Gidi, Candia, Muñoz-Moller, Rojas, Pereira, Muñoz
  et~al.}]{StochasticApplications2022Gidi}
\bibinfo{author}{Gidi\xfnm[ J.A.]}, \bibinfo{author}{Candia\xfnm[ B.]},
  \bibinfo{author}{Muñoz-Moller\xfnm[ A.D.]}, \bibinfo{author}{Rojas\xfnm[
  A.]}, \bibinfo{author}{Pereira\xfnm[ L.]}, \bibinfo{author}{Muñoz\xfnm[
  M.]}, et~al.
\newblock \bibinfo{title}{Stochastic optimization algorithms for quantum
  applications}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2203.06044}.
  \DOIprefix\doi{10.48550/ARXIV.2203.06044}.
%Type = Misc
\bibitem[{Patti et~al.(2021{\natexlab{b}})Patti, Shehab, Najafi and
  Yelin}]{PattiMarkovChain2021}
\bibinfo{author}{Patti\xfnm[ T.L.]}, \bibinfo{author}{Shehab\xfnm[ O.]},
  \bibinfo{author}{Najafi\xfnm[ K.]}, \bibinfo{author}{Yelin\xfnm[ S.F.]}.
\newblock \bibinfo{title}{Markov chain monte-carlo enhanced variational quantum
  algorithms}.
\newblock \bibinfo{year}{2021}{\natexlab{b}}.
\newblock \URLprefix \url{https://arxiv.org/abs/2112.02190}.
  \DOIprefix\doi{10.48550/ARXIV.2112.02190}.
%Type = Article
\bibitem[{Andersen et~al.(2020)Andersen, Remm, Lazar, Krinner, Lacroix, Norris
  et~al.}]{andersenRepeatedQuantumError2020a}
\bibinfo{author}{Andersen\xfnm[ C.K.]}, \bibinfo{author}{Remm\xfnm[ A.]},
  \bibinfo{author}{Lazar\xfnm[ S.]}, \bibinfo{author}{Krinner\xfnm[ S.]},
  \bibinfo{author}{Lacroix\xfnm[ N.]}, \bibinfo{author}{Norris\xfnm[ G.J.]},
  et~al.
\newblock \bibinfo{title}{Repeated quantum error detection in a surface code}.
\newblock \bibinfo{journal}{Nature Physics}
  \bibinfo{year}{2020};\bibinfo{volume}{16}(\bibinfo{number}{8}):\bibinfo{pages}{875--880}.
\newblock \DOIprefix\doi{10.1038/s41567-020-0920-y}.
%Type = Article
\bibitem[{Barends et~al.(2014)Barends, Kelly, Megrant, Veitia, Sank, Jeffrey
  et~al.}]{barendsSuperconductingQuantumCircuits2014}
\bibinfo{author}{Barends\xfnm[ R.]}, \bibinfo{author}{Kelly\xfnm[ J.]},
  \bibinfo{author}{Megrant\xfnm[ A.]}, \bibinfo{author}{Veitia\xfnm[ A.]},
  \bibinfo{author}{Sank\xfnm[ D.]}, \bibinfo{author}{Jeffrey\xfnm[ E.]}, et~al.
\newblock \bibinfo{title}{Superconducting quantum circuits at the surface code
  threshold for fault tolerance}.
\newblock \bibinfo{journal}{Nature}
  \bibinfo{year}{2014};\bibinfo{volume}{508}(\bibinfo{number}{7497}):\bibinfo{pages}{500--503}.
\newblock \DOIprefix\doi{10.1038/nature13171}.
%Type = Article
\bibitem[{Campagne-Ibarcq et~al.(2020)Campagne-Ibarcq, Eickbusch, Touzard,
  Zalys-Geller, Frattini, Sivak
  et~al.}]{campagne-ibarcqQuantumErrorCorrection2020}
\bibinfo{author}{Campagne-Ibarcq\xfnm[ P.]}, \bibinfo{author}{Eickbusch\xfnm[
  A.]}, \bibinfo{author}{Touzard\xfnm[ S.]},
  \bibinfo{author}{Zalys-Geller\xfnm[ E.]}, \bibinfo{author}{Frattini\xfnm[
  N.E.]}, \bibinfo{author}{Sivak\xfnm[ V.V.]}, et~al.
\newblock \bibinfo{title}{Quantum error correction of a qubit encoded in grid
  states of an oscillator}.
\newblock \bibinfo{journal}{Nature}
  \bibinfo{year}{2020};\bibinfo{volume}{584}(\bibinfo{number}{7821}):\bibinfo{pages}{368--372}.
\newblock \DOIprefix\doi{10.1038/s41586-020-2603-3}.
%Type = Article
\bibitem[{Nigg et~al.(2014)Nigg, Müller, Martinez, Schindler, Hennrich, Monz
  et~al.}]{niggQuantumComputationsTopologically2014}
\bibinfo{author}{Nigg\xfnm[ D.]}, \bibinfo{author}{Müller\xfnm[ M.]},
  \bibinfo{author}{Martinez\xfnm[ E.A.]}, \bibinfo{author}{Schindler\xfnm[
  P.]}, \bibinfo{author}{Hennrich\xfnm[ M.]}, \bibinfo{author}{Monz\xfnm[ T.]},
  et~al.
\newblock \bibinfo{title}{Quantum computations on a topologically encoded
  qubit}.
\newblock \bibinfo{journal}{Science}
  \bibinfo{year}{2014};\bibinfo{volume}{345}(\bibinfo{number}{6194}):\bibinfo{pages}{302--305}.
\newblock \DOIprefix\doi{10.1126/science.1253742}.
%Type = Article
\bibitem[{Ofek et~al.(2016)Ofek, Petrenko, Heeres, Reinhold, Leghtas, Vlastakis
  et~al.}]{ofekExtendingLifetimeQuantum2016}
\bibinfo{author}{Ofek\xfnm[ N.]}, \bibinfo{author}{Petrenko\xfnm[ A.]},
  \bibinfo{author}{Heeres\xfnm[ R.]}, \bibinfo{author}{Reinhold\xfnm[ P.]},
  \bibinfo{author}{Leghtas\xfnm[ Z.]}, \bibinfo{author}{Vlastakis\xfnm[ B.]},
  et~al.
\newblock \bibinfo{title}{Extending the lifetime of a quantum bit with error
  correction in superconducting circuits}.
\newblock \bibinfo{journal}{Nature}
  \bibinfo{year}{2016};\bibinfo{volume}{536}(\bibinfo{number}{7617}):\bibinfo{pages}{441--445}.
\newblock \DOIprefix\doi{10.1038/nature18949}.
%Type = Article
\bibitem[{Waldherr et~al.(2014)Waldherr, Wang, Zaiser, Jamali,
  Schulte-Herbr{\"u}ggen, Abe et~al.}]{waldherrQuantumErrorCorrection2014}
\bibinfo{author}{Waldherr\xfnm[ G.]}, \bibinfo{author}{Wang\xfnm[ Y.]},
  \bibinfo{author}{Zaiser\xfnm[ S.]}, \bibinfo{author}{Jamali\xfnm[ M.]},
  \bibinfo{author}{Schulte-Herbr{\"u}ggen\xfnm[ T.]},
  \bibinfo{author}{Abe\xfnm[ H.]}, et~al.
\newblock \bibinfo{title}{Quantum error correction in a solid-state hybrid spin
  register}.
\newblock \bibinfo{journal}{Nature}
  \bibinfo{year}{2014};\bibinfo{volume}{506}(\bibinfo{number}{7487}):\bibinfo{pages}{204--207}.
\newblock \DOIprefix\doi{10.1038/nature12919}.
%Type = Article
\bibitem[{Krinner et~al.(2022{\natexlab{a}})Krinner, Lacroix, Remm, Di~Paolo,
  Genois, Leroux et~al.}]{Postler_2022}
\bibinfo{author}{Krinner\xfnm[ S.]}, \bibinfo{author}{Lacroix\xfnm[ N.]},
  \bibinfo{author}{Remm\xfnm[ A.]}, \bibinfo{author}{Di~Paolo\xfnm[ A.]},
  \bibinfo{author}{Genois\xfnm[ E.]}, \bibinfo{author}{Leroux\xfnm[ C.]},
  et~al.
\newblock \bibinfo{title}{Demonstration of fault-tolerant universal quantum
  gate operations}.
\newblock \bibinfo{journal}{Nature}
  \bibinfo{year}{2022}{\natexlab{a}};\bibinfo{volume}{605}(\bibinfo{number}{7911}):\bibinfo{pages}{675--680}.
\newblock \URLprefix \url{https://doi.org/10.1038/s41586-022-04721-1}.
  \DOIprefix\doi{10.1038/s41586-022-04721-1}.
%Type = Article
\bibitem[{Krinner et~al.(2022{\natexlab{b}})Krinner, Lacroix, Remm, Paolo,
  Genois, Leroux et~al.}]{Krinner_2022}
\bibinfo{author}{Krinner\xfnm[ S.]}, \bibinfo{author}{Lacroix\xfnm[ N.]},
  \bibinfo{author}{Remm\xfnm[ A.]}, \bibinfo{author}{Paolo\xfnm[ A.D.]},
  \bibinfo{author}{Genois\xfnm[ E.]}, \bibinfo{author}{Leroux\xfnm[ C.]},
  et~al.
\newblock \bibinfo{title}{Realizing repeated quantum error correction in a
  distance-three surface code}.
\newblock \bibinfo{journal}{Nature}
  \bibinfo{year}{2022}{\natexlab{b}};\bibinfo{volume}{605}(\bibinfo{number}{7911}):\bibinfo{pages}{669--674}.
\newblock \URLprefix \url{https://www.nature.com/articles/s41586-022-04566-8}.
  \DOIprefix\doi{10.1038/s41586-022-04566-8}.
%Type = Article
\bibitem[{Endo et~al.(2021)Endo, Cai, Benjamin and
  Yuan}]{endoHybridQuantumClassicalAlgorithms2021}
\bibinfo{author}{Endo\xfnm[ S.]}, \bibinfo{author}{Cai\xfnm[ Z.]},
  \bibinfo{author}{Benjamin\xfnm[ S.C.]}, \bibinfo{author}{Yuan\xfnm[ X.]}.
\newblock \bibinfo{title}{Hybrid quantum-classical algorithms and quantum error
  mitigation}.
\newblock \bibinfo{journal}{Journal of the Physical Society of Japan}
  \bibinfo{year}{2021};\bibinfo{volume}{90}(\bibinfo{number}{3}):\bibinfo{pages}{032001}.
\newblock \DOIprefix\doi{10.7566/jpsj.90.032001}.
%Type = Article
\bibitem[{Cai(2021{\natexlab{a}})}]{caiMultiexponentialErrorExtrapolation2021}
\bibinfo{author}{Cai\xfnm[ Z.]}.
\newblock \bibinfo{title}{Multi-exponential error extrapolation and combining
  error mitigation techniques for {NISQ} applications}.
\newblock \bibinfo{journal}{npj Quantum Information}
  \bibinfo{year}{2021}{\natexlab{a}};\bibinfo{volume}{7}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1038/s41534-021-00404-3}.
  \href{http://arxiv.org/abs/2007.01265v2}{\tt arXiv:2007.01265v2};
  \bibinfo{note}{npj Quantum Inf 7, 80 (2021)}.
%Type = Article
\bibitem[{Kandala et~al.(2019)Kandala, Temme, C{\'{o}}rcoles, Mezzacapo, Chow
  and Gambetta}]{kandalaErrorMitigationExtends2019}
\bibinfo{author}{Kandala\xfnm[ A.]}, \bibinfo{author}{Temme\xfnm[ K.]},
  \bibinfo{author}{C{\'{o}}rcoles\xfnm[ A.D.]},
  \bibinfo{author}{Mezzacapo\xfnm[ A.]}, \bibinfo{author}{Chow\xfnm[ J.M.]},
  \bibinfo{author}{Gambetta\xfnm[ J.M.]}.
\newblock \bibinfo{title}{Error mitigation extends the computational reach of a
  noisy quantum processor}.
\newblock \bibinfo{journal}{Nature}
  \bibinfo{year}{2019};\bibinfo{volume}{567}(\bibinfo{number}{7749}):\bibinfo{pages}{491--495}.
\newblock \DOIprefix\doi{10.1038/s41586-019-1040-7}.
%Type = Misc
\bibitem[{McKay et~al.(2018)McKay, Alexander, Bello, Biercuk, Bishop, Chen
  et~al.}]{mckayQiskitBackendSpecifications2018}
\bibinfo{author}{McKay\xfnm[ D.C.]}, \bibinfo{author}{Alexander\xfnm[ T.]},
  \bibinfo{author}{Bello\xfnm[ L.]}, \bibinfo{author}{Biercuk\xfnm[ M.J.]},
  \bibinfo{author}{Bishop\xfnm[ L.]}, \bibinfo{author}{Chen\xfnm[ J.]}, et~al.
\newblock \bibinfo{title}{Qiskit backend specifications for openqasm and
  openpulse experiments}.
\newblock \bibinfo{year}{2018}.
\newblock \href{http://arxiv.org/abs/1809.03452v1}{\tt arXiv:1809.03452v1}.
%Type = Article
\bibitem[{Garmon et~al.(2020)Garmon, Pooser and
  Dumitrescu}]{garmonBenchmarkingNoiseExtrapolation2020}
\bibinfo{author}{Garmon\xfnm[ J.W.O.]}, \bibinfo{author}{Pooser\xfnm[ R.C.]},
  \bibinfo{author}{Dumitrescu\xfnm[ E.F.]}.
\newblock \bibinfo{title}{Benchmarking noise extrapolation with the {OpenPulse}
  control framework}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2020};\bibinfo{volume}{101}(\bibinfo{number}{4}):\bibinfo{pages}{042308}.
\newblock \DOIprefix\doi{10.1103/physreva.101.042308}.
%Type = Article
\bibitem[{Dumitrescu et~al.(2018)Dumitrescu, McCaskey, Hagen, Jansen, Morris,
  Papenbrock et~al.}]{dumitrescuCloudQuantumComputing2018}
\bibinfo{author}{Dumitrescu\xfnm[ E.]}, \bibinfo{author}{McCaskey\xfnm[ A.]},
  \bibinfo{author}{Hagen\xfnm[ G.]}, \bibinfo{author}{Jansen\xfnm[ G.]},
  \bibinfo{author}{Morris\xfnm[ T.]}, \bibinfo{author}{Papenbrock\xfnm[ T.]},
  et~al.
\newblock \bibinfo{title}{Cloud quantum computing of an atomic nucleus}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2018};\bibinfo{volume}{120}(\bibinfo{number}{21}):\bibinfo{pages}{210501}.
\newblock \DOIprefix\doi{10.1103/physrevlett.120.210501}.
%Type = Article
\bibitem[{He et~al.(2020)He, Nachman, de~Jong and
  Bauer}]{heResourceEfficientZero2020}
\bibinfo{author}{He\xfnm[ A.]}, \bibinfo{author}{Nachman\xfnm[ B.]},
  \bibinfo{author}{de~Jong\xfnm[ W.A.]}, \bibinfo{author}{Bauer\xfnm[ C.W.]}.
\newblock \bibinfo{title}{Zero-noise extrapolation for quantum-gate error
  mitigation with identity insertions}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2020};\bibinfo{volume}{102}(\bibinfo{number}{1}):\bibinfo{pages}{012426}.
\newblock \DOIprefix\doi{10.1103/physreva.102.012426}.
  \href{http://arxiv.org/abs/2003.04941}{\tt arXiv:2003.04941}.
%Type = Inproceedings
\bibitem[{Giurgica-Tiron et~al.(2020)Giurgica-Tiron, Hindy, LaRose, Mari and
  Zeng}]{giurgica-tironDigitalZeroNoise2020}
\bibinfo{author}{Giurgica-Tiron\xfnm[ T.]}, \bibinfo{author}{Hindy\xfnm[ Y.]},
  \bibinfo{author}{LaRose\xfnm[ R.]}, \bibinfo{author}{Mari\xfnm[ A.]},
  \bibinfo{author}{Zeng\xfnm[ W.J.]}.
\newblock \bibinfo{title}{Digital zero noise extrapolation for quantum error
  mitigation}.
\newblock In: \bibinfo{booktitle}{2020 {{IEEE International Conference}} on
  {{Quantum Computing}} and {{Engineering}} ({{QCE}})}.
  \bibinfo{address}{{Denver, CO, USA}}: \bibinfo{publisher}{{IEEE}}.
\newblock ISBN \bibinfo{isbn}{978-1-72818-969-7}; \bibinfo{year}{2020}, p.
  \bibinfo{pages}{306--316}.
\newblock \DOIprefix\doi{10.1109/qce49297.2020.00045}.
%Type = Article
\bibitem[{Otten and Gray(2019)}]{ottenRecoveringNoisefreeQuantum2019}
\bibinfo{author}{Otten\xfnm[ M.]}, \bibinfo{author}{Gray\xfnm[ S.K.]}.
\newblock \bibinfo{title}{Recovering noise-free quantum observables}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2019};\bibinfo{volume}{99}(\bibinfo{number}{1}):\bibinfo{pages}{012338}.
\newblock \DOIprefix\doi{10.1103/physreva.99.012338}.
%Type = Book
\bibitem[{Goodfellow(2016)}]{goodfellowDeepLearning2016}
\bibinfo{author}{Goodfellow\xfnm[ I.]}.
\newblock \bibinfo{title}{Deep learning}.
\newblock \bibinfo{address}{Cambridge, Massachusetts}: \bibinfo{publisher}{The
  MIT Press}; \bibinfo{year}{2016}.
\newblock ISBN \bibinfo{isbn}{0262035618}.
%Type = Book
\bibitem[{Hastie et~al.(2015)Hastie, Tibshirani and
  Wainwright}]{hastie2015statistical}
\bibinfo{author}{Hastie\xfnm[ T.]}, \bibinfo{author}{Tibshirani\xfnm[ R.]},
  \bibinfo{author}{Wainwright\xfnm[ M.]}.
\newblock \bibinfo{title}{Statistical Learning with Sparsity: The Lasso and
  Generalizations}.
\newblock Chapman \& Hall/CRC Monographs on Statistics \& Applied Probability;
  \bibinfo{publisher}{Taylor \& Francis}; \bibinfo{year}{2015}.
\newblock ISBN \bibinfo{isbn}{9781498712163}.
\newblock \URLprefix \url{https://books.google.co.uk/books?id=LnUIrgEACAAJ}.
%Type = Phdthesis
\bibitem[{Endo(2019)}]{suguru2019a}
\bibinfo{author}{Endo\xfnm[ S.]}.
\newblock \bibinfo{title}{Hybrid quantum-classical algorithms and error
  mitigation}.
\newblock Ph.D. thesis; University of Oxford; \bibinfo{year}{2019}.
\newblock \URLprefix
  \url{https://ora.ox.ac.uk/objects/uuid:6733c0f6-1b19-4d12-a899-18946aa5df85}.
%Type = Article
\bibitem[{Endo et~al.(2018)Endo, Benjamin and
  Li}]{endoPracticalQuantumError2018}
\bibinfo{author}{Endo\xfnm[ S.]}, \bibinfo{author}{Benjamin\xfnm[ S.C.]},
  \bibinfo{author}{Li\xfnm[ Y.]}.
\newblock \bibinfo{title}{Practical quantum error mitigation for near-future
  applications}.
\newblock \bibinfo{journal}{Physical Review X}
  \bibinfo{year}{2018};\bibinfo{volume}{8}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physrevx.8.031027}.
%Type = Misc
\bibitem[{Strikis et~al.(2020)Strikis, Qin, Chen, Benjamin and
  Li}]{strikisLearningbasedQuantumError2020}
\bibinfo{author}{Strikis\xfnm[ A.]}, \bibinfo{author}{Qin\xfnm[ D.]},
  \bibinfo{author}{Chen\xfnm[ Y.]}, \bibinfo{author}{Benjamin\xfnm[ S.C.]},
  \bibinfo{author}{Li\xfnm[ Y.]}.
\newblock \bibinfo{title}{Learning-based quantum error mitigation}.
\newblock \bibinfo{year}{2020}.
\newblock \href{http://arxiv.org/abs/2005.07601v2}{\tt arXiv:2005.07601v2}.
%Type = Article
\bibitem[{Takagi(2021)}]{Takagi2021OptimalResource}
\bibinfo{author}{Takagi\xfnm[ R.]}.
\newblock \bibinfo{title}{Optimal resource cost for error mitigation}.
\newblock \bibinfo{journal}{Phys Rev Research}
  \bibinfo{year}{2021};\bibinfo{volume}{3}:\bibinfo{pages}{033178}.
\newblock \DOIprefix\doi{10.1103/PhysRevResearch.3.033178}.
%Type = Article
\bibitem[{Koczor(2021{\natexlab{a}})}]{koczorExponentialErrorSuppression2021}
\bibinfo{author}{Koczor\xfnm[ B.]}.
\newblock \bibinfo{title}{Exponential error suppression for near-term quantum
  devices}.
\newblock \bibinfo{journal}{Physical Review X}
  \bibinfo{year}{2021}{\natexlab{a}};\bibinfo{volume}{11}(\bibinfo{number}{3}):\bibinfo{pages}{031057}.
\newblock \DOIprefix\doi{10.1103/physrevx.11.031057}.
%Type = Misc
\bibitem[{Huggins et~al.(2020{\natexlab{b}})Huggins, McArdle, O'Brien, Lee,
  Rubin, Boixo et~al.}]{hugginsVirtualDistillationQuantum2021}
\bibinfo{author}{Huggins\xfnm[ W.J.]}, \bibinfo{author}{McArdle\xfnm[ S.]},
  \bibinfo{author}{O'Brien\xfnm[ T.E.]}, \bibinfo{author}{Lee\xfnm[ J.]},
  \bibinfo{author}{Rubin\xfnm[ N.C.]}, \bibinfo{author}{Boixo\xfnm[ S.]},
  et~al.
\newblock \bibinfo{title}{Virtual distillation for quantum error mitigation}.
\newblock \bibinfo{year}{2020}{\natexlab{b}}.
\newblock \href{http://arxiv.org/abs/2011.07064v3}{\tt arXiv:2011.07064v3}.
%Type = Article
\bibitem[{O'Brien et~al.(2021{\natexlab{b}})O'Brien, Polla, Rubin, Huggins,
  McArdle, Boixo et~al.}]{obrienErrorMitigationVerified2021}
\bibinfo{author}{O'Brien\xfnm[ T.E.]}, \bibinfo{author}{Polla\xfnm[ S.]},
  \bibinfo{author}{Rubin\xfnm[ N.C.]}, \bibinfo{author}{Huggins\xfnm[ W.J.]},
  \bibinfo{author}{McArdle\xfnm[ S.]}, \bibinfo{author}{Boixo\xfnm[ S.]},
  et~al.
\newblock \bibinfo{title}{Error mitigation via verified phase estimation}.
\newblock \bibinfo{journal}{PRX Quantum}
  \bibinfo{year}{2021}{\natexlab{b}};\bibinfo{volume}{2}(\bibinfo{number}{2}):\bibinfo{pages}{020317}.
\newblock \DOIprefix\doi{10.1103/prxquantum.2.020317}.
%Type = Misc
\bibitem[{Huo and Li(2021)}]{huoDualstatePurificationPractical2021}
\bibinfo{author}{Huo\xfnm[ M.]}, \bibinfo{author}{Li\xfnm[ Y.]}.
\newblock \bibinfo{title}{Dual-state purification for practical quantum error
  mitigation}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2105.01239v1}{\tt arXiv:2105.01239v1}.
%Type = Misc
\bibitem[{Cai(2021{\natexlab{b}})}]{cai2021resourceefficient}
\bibinfo{author}{Cai\xfnm[ Z.]}.
\newblock \bibinfo{title}{Resource-efficient purification-based quantum error
  mitigation}.
\newblock \bibinfo{year}{2021}{\natexlab{b}}.
\newblock \href{http://arxiv.org/abs/2107.07279v1}{\tt arXiv:2107.07279v1}.
%Type = Misc
\bibitem[{Koczor(2021{\natexlab{b}})}]{koczorDominantEigenvectorNoisy2021}
\bibinfo{author}{Koczor\xfnm[ B.]}.
\newblock \bibinfo{title}{The dominant eigenvector of a noisy quantum state}.
\newblock \bibinfo{year}{2021}{\natexlab{b}}.
\newblock \href{http://arxiv.org/abs/2104.00608v2}{\tt arXiv:2104.00608v2}.
%Type = Article
\bibitem[{Geller(2020)}]{gellerRigorousMeasurementError2020}
\bibinfo{author}{Geller\xfnm[ M.R.]}.
\newblock \bibinfo{title}{Rigorous measurement error correction}.
\newblock \bibinfo{journal}{Quantum Science and Technology}
  \bibinfo{year}{2020};\bibinfo{volume}{5}(\bibinfo{number}{3}):\bibinfo{pages}{03LT01}.
\newblock \DOIprefix\doi{10.1088/2058-9565/ab9591}.
%Type = Misc
\bibitem[{IBM(2021)}]{IBMQ}
\bibinfo{title}{Ibm quantum}.
\newblock \bibinfo{howpublished}{\url{https://quantum-computing.ibm.com/}};
  \bibinfo{year}{2021}.
\newblock \bibinfo{note}{Accessed: 2021-10-20}.
%Type = Article
\bibitem[{Geller and Sun(2021)}]{gellerEfficientCorrectionMultiqubit2020}
\bibinfo{author}{Geller\xfnm[ M.R.]}, \bibinfo{author}{Sun\xfnm[ M.]}.
\newblock \bibinfo{title}{Toward efficient correction of multiqubit measurement
  errors: pair correlation method}.
\newblock \bibinfo{journal}{Quantum Science and Technology}
  \bibinfo{year}{2021};\bibinfo{volume}{6}(\bibinfo{number}{2}):\bibinfo{pages}{025009}.
\newblock \DOIprefix\doi{10.1088/2058-9565/abd5c9}.
  \href{http://arxiv.org/abs/2001.09980v2}{\tt arXiv:2001.09980v2};
  \bibinfo{note}{quantum Sci. Technol. 6 (2021) 025009}.
%Type = Misc
\bibitem[{Gambetta et~al.(2021)Gambetta, Treinish, Nation, Kassebaum,
  Rodríguez, {Qiskit-Bot} et~al.}]{Qiskit}
\bibinfo{author}{Gambetta\xfnm[ J.]}, \bibinfo{author}{Treinish\xfnm[ M.]},
  \bibinfo{author}{Nation\xfnm[ P.]}, \bibinfo{author}{Kassebaum\xfnm[ P.]},
  \bibinfo{author}{Rodríguez\xfnm[ D.M.]},
  \bibinfo{author}{{Qiskit-Bot}\xfnm[]}, et~al.
\newblock \bibinfo{title}{Qiskit/qiskit: Qiskit 0.25.0}.
\newblock \bibinfo{year}{2021}.
\newblock \DOIprefix\doi{10.5281/ZENODO.4660156}.
%Type = Article
\bibitem[{Yeter-Aydeniz et~al.(2020)Yeter-Aydeniz, Pooser and
  Siopsis}]{yeter-aydenizPracticalQuantumComputation2020}
\bibinfo{author}{Yeter-Aydeniz\xfnm[ K.]}, \bibinfo{author}{Pooser\xfnm[
  R.C.]}, \bibinfo{author}{Siopsis\xfnm[ G.]}.
\newblock \bibinfo{title}{Practical quantum computation of chemical and nuclear
  energy levels using quantum imaginary time evolution and lanczos algorithms}.
\newblock \bibinfo{journal}{npj Quantum Information}
  \bibinfo{year}{2020};\bibinfo{volume}{6}(\bibinfo{number}{1}):\bibinfo{pages}{63}.
\newblock \DOIprefix\doi{10.1038/s41534-020-00290-1}.
%Type = Article
\bibitem[{Yeter-Aydeniz et~al.(2019)Yeter-Aydeniz, Dumitrescu, McCaskey,
  Bennink, Pooser and Siopsis}]{yeter-aydenizScalarQuantumField2019}
\bibinfo{author}{Yeter-Aydeniz\xfnm[ K.]}, \bibinfo{author}{Dumitrescu\xfnm[
  E.F.]}, \bibinfo{author}{McCaskey\xfnm[ A.J.]},
  \bibinfo{author}{Bennink\xfnm[ R.S.]}, \bibinfo{author}{Pooser\xfnm[ R.C.]},
  \bibinfo{author}{Siopsis\xfnm[ G.]}.
\newblock \bibinfo{title}{Scalar quantum field theories as a benchmark for
  near-term quantum computers}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2019};\bibinfo{volume}{99}(\bibinfo{number}{3}):\bibinfo{pages}{032306}.
\newblock \DOIprefix\doi{10.1103/physreva.99.032306}.
%Type = Article
\bibitem[{Nachman et~al.(2020)Nachman, Urbanek, de~Jong and
  Bauer}]{nachmanUnfoldingQuantumComputer2020}
\bibinfo{author}{Nachman\xfnm[ B.]}, \bibinfo{author}{Urbanek\xfnm[ M.]},
  \bibinfo{author}{de~Jong\xfnm[ W.A.]}, \bibinfo{author}{Bauer\xfnm[ C.W.]}.
\newblock \bibinfo{title}{Unfolding quantum computer readout noise}.
\newblock \bibinfo{journal}{npj Quantum Information}
  \bibinfo{year}{2020};\bibinfo{volume}{6}(\bibinfo{number}{1}):\bibinfo{pages}{84}.
\newblock \DOIprefix\doi{10.1038/s41534-020-00309-7}.
%Type = Inproceedings
\bibitem[{Tannu and Qureshi(2019)}]{tannuMitigatingMeasurementErrors2019}
\bibinfo{author}{Tannu\xfnm[ S.S.]}, \bibinfo{author}{Qureshi\xfnm[ M.K.]}.
\newblock \bibinfo{title}{Mitigating measurement errors in quantum computers by
  exploiting state-dependent bias}.
\newblock In: \bibinfo{booktitle}{Proceedings of the 52nd {{Annual IEEE}}/{{ACM
  International Symposium}} on {{Microarchitecture}}}.
  \bibinfo{address}{{Columbus OH USA}}: \bibinfo{publisher}{{ACM}}.
\newblock ISBN \bibinfo{isbn}{978-1-4503-6938-1}; \bibinfo{year}{2019}, p.
  \bibinfo{pages}{279--290}.
\newblock \DOIprefix\doi{10.1145/3352460.3358265}.
%Type = Misc
\bibitem[{Mari et~al.(2021)Mari, Shammah and Zeng}]{mari2021extending}
\bibinfo{author}{Mari\xfnm[ A.]}, \bibinfo{author}{Shammah\xfnm[ N.]},
  \bibinfo{author}{Zeng\xfnm[ W.J.]}.
\newblock \bibinfo{title}{Extending quantum probabilistic error cancellation by
  noise scaling}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2108.02237v1}{\tt arXiv:2108.02237v1}.
%Type = Article
\bibitem[{Urbanek et~al.(2020)Urbanek, Nachman and
  de~Jong}]{urbanekQuantumErrorDetection2019}
\bibinfo{author}{Urbanek\xfnm[ M.]}, \bibinfo{author}{Nachman\xfnm[ B.]},
  \bibinfo{author}{de~Jong\xfnm[ W.A.]}.
\newblock \bibinfo{title}{Error detection on quantum computers improving the
  accuracy of chemical calculations}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2020};\bibinfo{volume}{102}(\bibinfo{number}{2}).
\newblock \DOIprefix\doi{10.1103/physreva.102.022427}.
%Type = Misc
\bibitem[{Mezher et~al.(2021)Mezher, Mills and Kashefi}]{mezher2021mitigating}
\bibinfo{author}{Mezher\xfnm[ R.]}, \bibinfo{author}{Mills\xfnm[ J.]},
  \bibinfo{author}{Kashefi\xfnm[ E.]}.
\newblock \bibinfo{title}{Mitigating errors by quantum verification and
  post-selection}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2109.14329v1}{\tt arXiv:2109.14329v1}.
%Type = Article
\bibitem[{Truflandier et~al.(2016)Truflandier, Dianzinga and
  Bowler}]{mcweenypurificationformula}
\bibinfo{author}{Truflandier\xfnm[ L.A.]}, \bibinfo{author}{Dianzinga\xfnm[
  R.M.]}, \bibinfo{author}{Bowler\xfnm[ D.R.]}.
\newblock \bibinfo{title}{Communication: Generalized canonical purification for
  density matrix minimization}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2016};\bibinfo{volume}{144}(\bibinfo{number}{9}):\bibinfo{pages}{091102}.
\newblock \DOIprefix\doi{10.1063/1.4943213}.
%Type = Article
\bibitem[{Vovrosh et~al.(2021)Vovrosh, Khosla, Greenaway, Self, Kim and
  Knolle}]{vovroshSimpleMitigationGlobal2021}
\bibinfo{author}{Vovrosh\xfnm[ J.]}, \bibinfo{author}{Khosla\xfnm[ K.E.]},
  \bibinfo{author}{Greenaway\xfnm[ S.]}, \bibinfo{author}{Self\xfnm[ C.]},
  \bibinfo{author}{Kim\xfnm[ M.S.]}, \bibinfo{author}{Knolle\xfnm[ J.]}.
\newblock \bibinfo{title}{Simple mitigation of global depolarizing errors in
  quantum simulations}.
\newblock \bibinfo{journal}{Physical Review E}
  \bibinfo{year}{2021};\bibinfo{volume}{104}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physreve.104.035309}.
%Type = Misc
\bibitem[{Czarnik et~al.(2020)Czarnik, Arrasmith, Coles and
  Cincio}]{czarnikErrorMitigationClifford2021}
\bibinfo{author}{Czarnik\xfnm[ P.]}, \bibinfo{author}{Arrasmith\xfnm[ A.]},
  \bibinfo{author}{Coles\xfnm[ P.J.]}, \bibinfo{author}{Cincio\xfnm[ L.]}.
\newblock \bibinfo{title}{Error mitigation with clifford quantum-circuit data}.
\newblock \bibinfo{year}{2020}.
\newblock \href{http://arxiv.org/abs/2005.10189v2}{\tt arXiv:2005.10189v2}.
%Type = Misc
\bibitem[{Montanaro and Stanisic(2021)}]{montanaroErrorMitigationTraining2021}
\bibinfo{author}{Montanaro\xfnm[ A.]}, \bibinfo{author}{Stanisic\xfnm[ S.]}.
\newblock \bibinfo{title}{Error mitigation by training with fermionic linear
  optics}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2102.02120v1}{\tt arXiv:2102.02120v1}.
%Type = Article
\bibitem[{Lowe et~al.(2021)Lowe, Gordon, Czarnik, Arrasmith, Coles and
  Cincio}]{loweUnifiedApproachDatadriven2020a}
\bibinfo{author}{Lowe\xfnm[ A.]}, \bibinfo{author}{Gordon\xfnm[ M.H.]},
  \bibinfo{author}{Czarnik\xfnm[ P.]}, \bibinfo{author}{Arrasmith\xfnm[ A.]},
  \bibinfo{author}{Coles\xfnm[ P.J.]}, \bibinfo{author}{Cincio\xfnm[ L.]}.
\newblock \bibinfo{title}{Unified approach to data-driven quantum error
  mitigation}.
\newblock \bibinfo{journal}{Physical Review Research}
  \bibinfo{year}{2021};\bibinfo{volume}{3}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physrevresearch.3.033098}.
  \href{http://arxiv.org/abs/2011.01157v2}{\tt arXiv:2011.01157v2};
  \bibinfo{note}{phys. Rev. Research 3, 033098 (2021)}.
%Type = Article
\bibitem[{Kim et~al.(2020)Kim, Park and Rhee}]{kimQuantumErrorMitigation2020}
\bibinfo{author}{Kim\xfnm[ C.]}, \bibinfo{author}{Park\xfnm[ K.D.]},
  \bibinfo{author}{Rhee\xfnm[ J.K.]}.
\newblock \bibinfo{title}{Quantum error mitigation with artificial neural
  network}.
\newblock \bibinfo{journal}{IEEE Access}
  \bibinfo{year}{2020};\bibinfo{volume}{8}:\bibinfo{pages}{188853--188860}.
\newblock \DOIprefix\doi{10.1109/access.2020.3031607}.
%Type = Misc
\bibitem[{Zlokapa and Gheorghiu(2020)}]{zlokapaDeepLearningModel2020}
\bibinfo{author}{Zlokapa\xfnm[ A.]}, \bibinfo{author}{Gheorghiu\xfnm[ A.]}.
\newblock \bibinfo{title}{A deep learning model for noise prediction on
  near-term quantum devices}.
\newblock \bibinfo{year}{2020}.
\newblock \href{http://arxiv.org/abs/2005.10811v1}{\tt arXiv:2005.10811v1}.
%Type = Misc
\bibitem[{Kim(2017)}]{kim2017noiseresilient}
\bibinfo{author}{Kim\xfnm[ I.H.]}.
\newblock \bibinfo{title}{Noise-resilient preparation of quantum many-body
  ground states}.
\newblock \bibinfo{year}{2017}.
\newblock \href{http://arxiv.org/abs/1703.00032}{\tt arXiv:1703.00032}.
%Type = Article
\bibitem[{Cincio et~al.(2021)Cincio, Rudinger, Sarovar and
  Coles}]{cincioMachineLearningNoiseResilient2021}
\bibinfo{author}{Cincio\xfnm[ L.]}, \bibinfo{author}{Rudinger\xfnm[ K.]},
  \bibinfo{author}{Sarovar\xfnm[ M.]}, \bibinfo{author}{Coles\xfnm[ P.J.]}.
\newblock \bibinfo{title}{Machine learning of noise-resilient quantum
  circuits}.
\newblock \bibinfo{journal}{PRX Quantum}
  \bibinfo{year}{2021};\bibinfo{volume}{2}(\bibinfo{number}{1}):\bibinfo{pages}{010324}.
\newblock \DOIprefix\doi{10.1103/prxquantum.2.010324}.
%Type = Article
\bibitem[{Wang et~al.(2021{\natexlab{b}})Wang, Koh, Johnson and
  Cao}]{Wang2021MinimizeEstimationRuntime}
\bibinfo{author}{Wang\xfnm[ G.]}, \bibinfo{author}{Koh\xfnm[ D.E.]},
  \bibinfo{author}{Johnson\xfnm[ P.D.]}, \bibinfo{author}{Cao\xfnm[ Y.]}.
\newblock \bibinfo{title}{Minimizing estimation runtime on noisy quantum
  computers}.
\newblock \bibinfo{journal}{PRX Quantum}
  \bibinfo{year}{2021}{\natexlab{b}};\bibinfo{volume}{2}:\bibinfo{pages}{010346}.
\newblock \DOIprefix\doi{10.1103/PRXQuantum.2.010346}.
%Type = Misc
\bibitem[{Katabarwa et~al.(2021)Katabarwa, Kunitsa, Peropadre and
  Johnson}]{katabarwa2021reducing}
\bibinfo{author}{Katabarwa\xfnm[ A.]}, \bibinfo{author}{Kunitsa\xfnm[ A.]},
  \bibinfo{author}{Peropadre\xfnm[ B.]}, \bibinfo{author}{Johnson\xfnm[ P.]}.
\newblock \bibinfo{title}{Reducing runtime and error in vqe using deeper and
  noisier quantum circuits}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2110.10664}{\tt arXiv:2110.10664}.
%Type = Misc
\bibitem[{Ito et~al.(2021)Ito, Mizukami and Fujii}]{ito2021universal}
\bibinfo{author}{Ito\xfnm[ K.]}, \bibinfo{author}{Mizukami\xfnm[ W.]},
  \bibinfo{author}{Fujii\xfnm[ K.]}.
\newblock \bibinfo{title}{Universal noise-precision relations in variational
  quantum algorithms}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2106.03390}{\tt arXiv:2106.03390}.
%Type = Misc
\bibitem[{Piveteau et~al.(2021)Piveteau, Sutter and
  Woerner}]{piveteau2021quasiprobability}
\bibinfo{author}{Piveteau\xfnm[ C.]}, \bibinfo{author}{Sutter\xfnm[ D.]},
  \bibinfo{author}{Woerner\xfnm[ S.]}.
\newblock \bibinfo{title}{Quasiprobability decompositions with reduced sampling
  overhead}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2101.09290v1}{\tt arXiv:2101.09290v1}.
%Type = Misc
\bibitem[{Cai(2021{\natexlab{c}})}]{cai2021practical}
\bibinfo{author}{Cai\xfnm[ Z.]}.
\newblock \bibinfo{title}{A practical framework for quantum error mitigation}.
\newblock \bibinfo{year}{2021}{\natexlab{c}}.
\newblock \href{http://arxiv.org/abs/2110.05389}{\tt arXiv:2110.05389}.
%Type = Article
\bibitem[{Yuan et~al.(2019{\natexlab{a}})Yuan, Endo, Zhao, Li and
  Benjamin}]{yuanTheoryVariationalQuantum2019}
\bibinfo{author}{Yuan\xfnm[ X.]}, \bibinfo{author}{Endo\xfnm[ S.]},
  \bibinfo{author}{Zhao\xfnm[ Q.]}, \bibinfo{author}{Li\xfnm[ Y.]},
  \bibinfo{author}{Benjamin\xfnm[ S.C.]}.
\newblock \bibinfo{title}{Theory of variational quantum simulation}.
\newblock \bibinfo{journal}{Quantum}
  \bibinfo{year}{2019}{\natexlab{a}};\bibinfo{volume}{3}:\bibinfo{pages}{191}.
\newblock \DOIprefix\doi{10.22331/q-2019-10-07-191}.
  \href{http://arxiv.org/abs/1812.08767}{\tt arXiv:1812.08767}.
%Type = Misc
\bibitem[{Karamlou et~al.(2020)Karamlou, Simon, Katabarwa, Scholten, Peropadre
  and Cao}]{karamlouAnalyzingPerformanceVariational2021}
\bibinfo{author}{Karamlou\xfnm[ A.H.]}, \bibinfo{author}{Simon\xfnm[ W.A.]},
  \bibinfo{author}{Katabarwa\xfnm[ A.]}, \bibinfo{author}{Scholten\xfnm[
  T.L.]}, \bibinfo{author}{Peropadre\xfnm[ B.]}, \bibinfo{author}{Cao\xfnm[
  Y.]}.
\newblock \bibinfo{title}{Analyzing the performance of variational quantum
  factoring on a superconducting quantum processor}.
\newblock \bibinfo{year}{2020}.
\newblock \href{http://arxiv.org/abs/2012.07825v2}{\tt arXiv:2012.07825v2}.
%Type = Article
\bibitem[{Karim et~al.(2018)Karim, Ong, Abdullah, Yousuf, Cheng and
  Khan}]{Karim2018}
\bibinfo{author}{Karim\xfnm[ K.M.R.]}, \bibinfo{author}{Ong\xfnm[ H.R.]},
  \bibinfo{author}{Abdullah\xfnm[ H.]}, \bibinfo{author}{Yousuf\xfnm[ A.]},
  \bibinfo{author}{Cheng\xfnm[ C.K.]}, \bibinfo{author}{Khan\xfnm[ M.M.R.]}.
\newblock \bibinfo{title}{Photoelectrochemical reduction of carbon dioxide to
  methanol on p-type {CuFe}2o4 under visible light irradiation}.
\newblock \bibinfo{journal}{International Journal of Hydrogen Energy}
  \bibinfo{year}{2018};\bibinfo{volume}{43}(\bibinfo{number}{39}):\bibinfo{pages}{18185--18193}.
\newblock \DOIprefix\doi{10.1016/j.ijhydene.2018.07.174}.
%Type = Article
\bibitem[{Zeinalipour-Yazdi et~al.(2018)Zeinalipour-Yazdi, Hargreaves and
  Catlow}]{ZeinalipourYazdi2018}
\bibinfo{author}{Zeinalipour-Yazdi\xfnm[ C.D.]},
  \bibinfo{author}{Hargreaves\xfnm[ J.S.J.]}, \bibinfo{author}{Catlow\xfnm[
  C.R.A.]}.
\newblock \bibinfo{title}{Low-t mechanisms of ammonia synthesis on co3mo3n}.
\newblock \bibinfo{journal}{The Journal of Physical Chemistry C}
  \bibinfo{year}{2018};\bibinfo{volume}{122}(\bibinfo{number}{11}):\bibinfo{pages}{6078--6082}.
\newblock \DOIprefix\doi{10.1021/acs.jpcc.7b12364}.
%Type = Article
\bibitem[{Matsika and Krylov(2018)}]{Matsika2018}
\bibinfo{author}{Matsika\xfnm[ S.]}, \bibinfo{author}{Krylov\xfnm[ A.I.]}.
\newblock \bibinfo{title}{Introduction: Theoretical modeling of excited state
  processes}.
\newblock \bibinfo{journal}{Chem Rev}
  \bibinfo{year}{2018};\bibinfo{volume}{118}(\bibinfo{number}{15}):\bibinfo{pages}{6925--6926}.
\newblock \DOIprefix\doi{10.1021/acs.chemrev.8b00436}.
%Type = Article
\bibitem[{Stanton and Bartlett(1993)}]{Stanton1993}
\bibinfo{author}{Stanton\xfnm[ J.F.]}, \bibinfo{author}{Bartlett\xfnm[ R.J.]}.
\newblock \bibinfo{title}{The equation of motion coupled-cluster method. a
  systematic biorthogonal approach to molecular excitation energies, transition
  probabilities, and excited state properties}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{1993};\bibinfo{volume}{98}(\bibinfo{number}{9}):\bibinfo{pages}{7029--7039}.
\newblock \DOIprefix\doi{10.1063/1.464746}.
%Type = Article
\bibitem[{Monkhorst(2009)}]{Monkhorst2009}
\bibinfo{author}{Monkhorst\xfnm[ H.J.]}.
\newblock \bibinfo{title}{Calculation of properties with the coupled-cluster
  method}.
\newblock \bibinfo{journal}{International Journal of Quantum Chemistry}
  \bibinfo{year}{2009};\bibinfo{volume}{12}(\bibinfo{number}{S11}):\bibinfo{pages}{421--432}.
\newblock \DOIprefix\doi{10.1002/qua.560120850}.
%Type = Article
\bibitem[{Jeziorski and Monkhorst(1981)}]{Jeziorski1981}
\bibinfo{author}{Jeziorski\xfnm[ B.]}, \bibinfo{author}{Monkhorst\xfnm[ H.J.]}.
\newblock \bibinfo{title}{Coupled-cluster method for multideterminantal
  reference states}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{1981};\bibinfo{volume}{24}(\bibinfo{number}{4}):\bibinfo{pages}{1668--1681}.
\newblock \DOIprefix\doi{10.1103/physreva.24.1668}.
%Type = Article
\bibitem[{Sun et~al.(2021)Sun, Motta, Tazhigulov, Tan, Chan and
  Minnich}]{sunQuantumComputationFiniteTemperature2021}
\bibinfo{author}{Sun\xfnm[ S.N.]}, \bibinfo{author}{Motta\xfnm[ M.]},
  \bibinfo{author}{Tazhigulov\xfnm[ R.N.]}, \bibinfo{author}{Tan\xfnm[ A.T.]},
  \bibinfo{author}{Chan\xfnm[ G.K.L.]}, \bibinfo{author}{Minnich\xfnm[ A.J.]}.
\newblock \bibinfo{title}{Quantum computation of finite-temperature static and
  dynamical properties of spin systems using quantum imaginary time evolution}.
\newblock \bibinfo{journal}{PRX Quantum}
  \bibinfo{year}{2021};\bibinfo{volume}{2}(\bibinfo{number}{1}):\bibinfo{pages}{010317}.
\newblock \DOIprefix\doi{10.1103/prxquantum.2.010317}.
%Type = Article
\bibitem[{McClean et~al.(2017)McClean, Kimchi-Schwartz, Carter and
  de~Jong}]{McClean2017}
\bibinfo{author}{McClean\xfnm[ J.R.]}, \bibinfo{author}{Kimchi-Schwartz\xfnm[
  M.E.]}, \bibinfo{author}{Carter\xfnm[ J.]}, \bibinfo{author}{de~Jong\xfnm[
  W.A.]}.
\newblock \bibinfo{title}{Hybrid quantum-classical hierarchy for mitigation of
  decoherence and determination of excited states}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2017};\bibinfo{volume}{95}(\bibinfo{number}{4}):\bibinfo{pages}{042308}.
\newblock \DOIprefix\doi{10.1103/physreva.95.042308}.
%Type = Article
\bibitem[{Ollitrault et~al.(2020{\natexlab{b}})Ollitrault, Kandala, Chen,
  Barkoutsos, Mezzacapo, Pistoia et~al.}]{Ollitrault2020}
\bibinfo{author}{Ollitrault\xfnm[ P.J.]}, \bibinfo{author}{Kandala\xfnm[ A.]},
  \bibinfo{author}{Chen\xfnm[ C.F.]}, \bibinfo{author}{Barkoutsos\xfnm[ P.K.]},
  \bibinfo{author}{Mezzacapo\xfnm[ A.]}, \bibinfo{author}{Pistoia\xfnm[ M.]},
  et~al.
\newblock \bibinfo{title}{Quantum equation of motion for computing molecular
  excitation energies on a noisy quantum processor}.
\newblock \bibinfo{journal}{Physical Review Research}
  \bibinfo{year}{2020}{\natexlab{b}};\bibinfo{volume}{2}(\bibinfo{number}{4}).
\newblock \DOIprefix\doi{10.1103/physrevresearch.2.043140}.
%Type = Article
\bibitem[{Parrish et~al.(2019{\natexlab{b}})Parrish, Hohenstein, McMahon and
  Mart{\'{\i}}nez}]{Parrish2019}
\bibinfo{author}{Parrish\xfnm[ R.M.]}, \bibinfo{author}{Hohenstein\xfnm[
  E.G.]}, \bibinfo{author}{McMahon\xfnm[ P.L.]},
  \bibinfo{author}{Mart{\'{\i}}nez\xfnm[ T.J.]}.
\newblock \bibinfo{title}{Quantum computation of electronic transitions using a
  variational quantum eigensolver}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2019}{\natexlab{b}};\bibinfo{volume}{122}(\bibinfo{number}{23}):\bibinfo{pages}{230401--230401}.
\newblock \DOIprefix\doi{10.1103/physrevlett.122.230401}.
%Type = Article
\bibitem[{Colless et~al.(2018)Colless, Ramasesh, Dahlen, Blok, Kimchi-Schwartz,
  McClean et~al.}]{collessComputationMolecularSpectra2018}
\bibinfo{author}{Colless\xfnm[ J.]}, \bibinfo{author}{Ramasesh\xfnm[ V.]},
  \bibinfo{author}{Dahlen\xfnm[ D.]}, \bibinfo{author}{Blok\xfnm[ M.]},
  \bibinfo{author}{Kimchi-Schwartz\xfnm[ M.]}, \bibinfo{author}{McClean\xfnm[
  J.]}, et~al.
\newblock \bibinfo{title}{Computation of molecular spectra on a quantum
  processor with an error-resilient algorithm}.
\newblock \bibinfo{journal}{Physical Review X}
  \bibinfo{year}{2018};\bibinfo{volume}{8}(\bibinfo{number}{1}):\bibinfo{pages}{011021--011021}.
\newblock \DOIprefix\doi{10.1103/physrevx.8.011021}.
%Type = Article
\bibitem[{Blunt et~al.(2018)Blunt, Alavi and Booth}]{Blunt2018}
\bibinfo{author}{Blunt\xfnm[ N.S.]}, \bibinfo{author}{Alavi\xfnm[ A.]},
  \bibinfo{author}{Booth\xfnm[ G.H.]}.
\newblock \bibinfo{title}{Nonlinear biases, stochastically sampled effective
  hamiltonians, and spectral functions in quantum monte carlo methods}.
\newblock \bibinfo{journal}{Physical Review B}
  \bibinfo{year}{2018};\bibinfo{volume}{98}(\bibinfo{number}{8}).
\newblock \DOIprefix\doi{10.1103/physrevb.98.085118}.
%Type = Misc
\bibitem[{Epperly et~al.(2021)Epperly, Lin and Nakatsukasa}]{Epperly2021}
\bibinfo{author}{Epperly\xfnm[ E.N.]}, \bibinfo{author}{Lin\xfnm[ L.]},
  \bibinfo{author}{Nakatsukasa\xfnm[ Y.]}.
\newblock \bibinfo{title}{A theory of quantum subspace diagonalization}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2110.07492}{\tt arXiv:2110.07492}.
%Type = Article
\bibitem[{Wang and Zunger(1994)}]{Wang1994}
\bibinfo{author}{Wang\xfnm[ L.W.]}, \bibinfo{author}{Zunger\xfnm[ A.]}.
\newblock \bibinfo{title}{Solving schr\"{o}dinger's equation around a desired
  energy: Application to silicon quantum dots}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{1994};\bibinfo{volume}{100}(\bibinfo{number}{3}):\bibinfo{pages}{2394--2397}.
\newblock \URLprefix \url{https://doi.org/10.1063/1.466486}.
  \DOIprefix\doi{10.1063/1.466486}.
%Type = Misc
\bibitem[{Liu et~al.(2021{\natexlab{c}})Liu, Zhang, Hsieh, Zhang and
  Yao}]{Liu2021_MBL}
\bibinfo{author}{Liu\xfnm[ S.]}, \bibinfo{author}{Zhang\xfnm[ S.X.]},
  \bibinfo{author}{Hsieh\xfnm[ C.Y.]}, \bibinfo{author}{Zhang\xfnm[ S.]},
  \bibinfo{author}{Yao\xfnm[ H.]}.
\newblock \bibinfo{title}{Probing many-body localization by excited-state vqe}.
\newblock \bibinfo{year}{2021}{\natexlab{c}}.
\newblock \URLprefix \url{https://arxiv.org/abs/2111.13719}.
  \DOIprefix\doi{10.48550/ARXIV.2111.13719}.
%Type = Article
\bibitem[{Nakanishi et~al.(2019)Nakanishi, Mitarai and
  Fujii}]{nakanishiSubspacesearchVariationalQuantum2019}
\bibinfo{author}{Nakanishi\xfnm[ K.M.]}, \bibinfo{author}{Mitarai\xfnm[ K.]},
  \bibinfo{author}{Fujii\xfnm[ K.]}.
\newblock \bibinfo{title}{Subspace-search variational quantum eigensolver for
  excited states}.
\newblock \bibinfo{journal}{Physical Review Research}
  \bibinfo{year}{2019};\bibinfo{volume}{1}(\bibinfo{number}{3}):\bibinfo{pages}{1--7}.
\newblock \DOIprefix\doi{10.1103/physrevresearch.1.033062}.
%Type = Article
\bibitem[{Jones et~al.(2019)Jones, Endo, McArdle, Yuan and
  Benjamin}]{Jones2019}
\bibinfo{author}{Jones\xfnm[ T.]}, \bibinfo{author}{Endo\xfnm[ S.]},
  \bibinfo{author}{McArdle\xfnm[ S.]}, \bibinfo{author}{Yuan\xfnm[ X.]},
  \bibinfo{author}{Benjamin\xfnm[ S.C.]}.
\newblock \bibinfo{title}{Variational quantum algorithms for discovering
  hamiltonian spectra}.
\newblock \bibinfo{journal}{Physical Review A}
  \bibinfo{year}{2019};\bibinfo{volume}{99}(\bibinfo{number}{6}).
\newblock \DOIprefix\doi{10.1103/physreva.99.062304}.
%Type = Misc
\bibitem[{Chan et~al.(2021)Chan, Fitzpatrick, Segarra-Marti, Bearpark and
  Tew}]{Chan2021}
\bibinfo{author}{Chan\xfnm[ H.H.S.]}, \bibinfo{author}{Fitzpatrick\xfnm[ N.]},
  \bibinfo{author}{Segarra-Marti\xfnm[ J.]}, \bibinfo{author}{Bearpark\xfnm[
  M.J.]}, \bibinfo{author}{Tew\xfnm[ D.P.]}.
\newblock \bibinfo{title}{Molecular excited state calculations with adaptive
  wavefunctions on a quantum eigensolver emulation: Reducing circuit depth and
  separating spin states}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2105.10275}{\tt arXiv:2105.10275}.
%Type = Misc
\bibitem[{Wakaura and Suksmono(2021)}]{Wakaura2021}
\bibinfo{author}{Wakaura\xfnm[ H.]}, \bibinfo{author}{Suksmono\xfnm[ A.B.]}.
\newblock \bibinfo{title}{Tangent vector variational quantum eigensolver: A
  robust variational quantum eigensolver against the inaccuracy of derivative}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2105.01141}{\tt arXiv:2105.01141}.
%Type = Article
\bibitem[{Lloyd and Weedbrook(2018)}]{Lloyd2018}
\bibinfo{author}{Lloyd\xfnm[ S.]}, \bibinfo{author}{Weedbrook\xfnm[ C.]}.
\newblock \bibinfo{title}{Quantum generative adversarial learning}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2018};\bibinfo{volume}{121}(\bibinfo{number}{4}).
\newblock \DOIprefix\doi{10.1103/physrevlett.121.040502}.
%Type = Article
\bibitem[{Benedetti et~al.(2019)Benedetti, Grant, Wossnig and
  Severini}]{Benedetti2019}
\bibinfo{author}{Benedetti\xfnm[ M.]}, \bibinfo{author}{Grant\xfnm[ E.]},
  \bibinfo{author}{Wossnig\xfnm[ L.]}, \bibinfo{author}{Severini\xfnm[ S.]}.
\newblock \bibinfo{title}{Adversarial quantum circuit learning for pure state
  approximation}.
\newblock \bibinfo{journal}{New Journal of Physics}
  \bibinfo{year}{2019};\bibinfo{volume}{21}(\bibinfo{number}{4}):\bibinfo{pages}{043023}.
\newblock \DOIprefix\doi{10.1088/1367-2630/ab14b5}.
%Type = Misc
\bibitem[{Zhang et~al.(2020{\natexlab{c}})Zhang, Yuan and
  Yin}]{zhang2020variance_minimization}
\bibinfo{author}{Zhang\xfnm[ D.B.]}, \bibinfo{author}{Yuan\xfnm[ Z.H.]},
  \bibinfo{author}{Yin\xfnm[ T.]}.
\newblock \bibinfo{title}{Variational quantum eigensolvers by variance
  minimization}.
\newblock \bibinfo{year}{2020}{\natexlab{c}}.
\newblock \href{http://arxiv.org/abs/2006.15781}{\tt arXiv:2006.15781}.
%Type = Article
\bibitem[{Bartlett et~al.(1935)Bartlett, Gibbons and Dunn}]{Bartlett1935}
\bibinfo{author}{Bartlett\xfnm[ J.H.]}, \bibinfo{author}{Gibbons\xfnm[ J.J.]},
  \bibinfo{author}{Dunn\xfnm[ C.G.]}.
\newblock \bibinfo{title}{The normal helium atom}.
\newblock \bibinfo{journal}{Physical Review}
  \bibinfo{year}{1935};\bibinfo{volume}{47}(\bibinfo{number}{9}):\bibinfo{pages}{679--680}.
\newblock \DOIprefix\doi{10.1103/physrev.47.679}.
%Type = Article
\bibitem[{Siringo and Marotta(2005)}]{Siringo2005}
\bibinfo{author}{Siringo\xfnm[ F.]}, \bibinfo{author}{Marotta\xfnm[ L.]}.
\newblock \bibinfo{title}{A variational method from the variance of energy}.
\newblock \bibinfo{journal}{The European Physical Journal C}
  \bibinfo{year}{2005};\bibinfo{volume}{44}(\bibinfo{number}{2}):\bibinfo{pages}{293--298}.
\newblock \DOIprefix\doi{10.1140/epjc/s2005-02358-x}.
%Type = Article
\bibitem[{Umrigar and Filippi(2005)}]{Umrigar2005}
\bibinfo{author}{Umrigar\xfnm[ C.J.]}, \bibinfo{author}{Filippi\xfnm[ C.]}.
\newblock \bibinfo{title}{Energy and variance optimization of many-body wave
  functions}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2005};\bibinfo{volume}{94}(\bibinfo{number}{15}).
\newblock \DOIprefix\doi{10.1103/physrevlett.94.150201}.
%Type = Article
\bibitem[{Khemani et~al.(2016)Khemani, Pollmann and Sondhi}]{Khemani2016}
\bibinfo{author}{Khemani\xfnm[ V.]}, \bibinfo{author}{Pollmann\xfnm[ F.]},
  \bibinfo{author}{Sondhi\xfnm[ S.]}.
\newblock \bibinfo{title}{Obtaining highly excited eigenstates of many-body
  localized hamiltonians by the density matrix renormalization group approach}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2016};\bibinfo{volume}{116}(\bibinfo{number}{24}).
\newblock \DOIprefix\doi{10.1103/physrevlett.116.247204}.
%Type = Article
\bibitem[{Pollmann et~al.(2016)Pollmann, Khemani, Cirac and
  Sondhi}]{Pollmann2016}
\bibinfo{author}{Pollmann\xfnm[ F.]}, \bibinfo{author}{Khemani\xfnm[ V.]},
  \bibinfo{author}{Cirac\xfnm[ J.I.]}, \bibinfo{author}{Sondhi\xfnm[ S.L.]}.
\newblock \bibinfo{title}{Efficient variational diagonalization of fully
  many-body localized hamiltonians}.
\newblock \bibinfo{journal}{Physical Review B}
  \bibinfo{year}{2016};\bibinfo{volume}{94}(\bibinfo{number}{4}).
\newblock \DOIprefix\doi{10.1103/physrevb.94.041116}.
%Type = Article
\bibitem[{Vicentini et~al.(2019)Vicentini, Biella, Regnault and
  Ciuti}]{Vicentini2019}
\bibinfo{author}{Vicentini\xfnm[ F.]}, \bibinfo{author}{Biella\xfnm[ A.]},
  \bibinfo{author}{Regnault\xfnm[ N.]}, \bibinfo{author}{Ciuti\xfnm[ C.]}.
\newblock \bibinfo{title}{Variational neural-network ansatz for steady states
  in open quantum systems}.
\newblock \bibinfo{journal}{Physical Review Letters}
  \bibinfo{year}{2019};\bibinfo{volume}{122}(\bibinfo{number}{25}).
\newblock \DOIprefix\doi{10.1103/physrevlett.122.250503}.
%Type = Article
\bibitem[{Zhang et~al.(2021{\natexlab{e}})Zhang, Gomes, Yao, Orth and
  Iadecola}]{zhangAdaptiveVariationalQuantum2021}
\bibinfo{author}{Zhang\xfnm[ F.]}, \bibinfo{author}{Gomes\xfnm[ N.]},
  \bibinfo{author}{Yao\xfnm[ Y.]}, \bibinfo{author}{Orth\xfnm[ P.P.]},
  \bibinfo{author}{Iadecola\xfnm[ T.]}.
\newblock \bibinfo{title}{Adaptive variational quantum eigensolvers for highly
  excited states}.
\newblock \bibinfo{journal}{Physical Review B}
  \bibinfo{year}{2021}{\natexlab{e}};\bibinfo{volume}{104}(\bibinfo{number}{7}).
\newblock \DOIprefix\doi{10.1103/physrevb.104.075159}.
  \href{http://arxiv.org/abs/2104.12636v1}{\tt arXiv:2104.12636v1};
  \bibinfo{note}{phys. Rev. B 104, 075159 (2021)}.
%Type = Article
\bibitem[{Endo et~al.(2020)Endo, Kurata and Nakagawa}]{Endo2019GF}
\bibinfo{author}{Endo\xfnm[ S.]}, \bibinfo{author}{Kurata\xfnm[ I.]},
  \bibinfo{author}{Nakagawa\xfnm[ Y.O.]}.
\newblock \bibinfo{title}{Calculation of the green{\textquotesingle}s function
  on near-term quantum computers}.
\newblock \bibinfo{journal}{Physical Review Research}
  \bibinfo{year}{2020};\bibinfo{volume}{2}(\bibinfo{number}{3}):\bibinfo{pages}{033281}.
\newblock \DOIprefix\doi{10.1103/physrevresearch.2.033281}.
%Type = Misc
\bibitem[{Rungger et~al.(2019)Rungger, Fitzpatrick, Chen, Alderete, Apel,
  Cowtan et~al.}]{runggerDynamicalMeanField2020}
\bibinfo{author}{Rungger\xfnm[ I.]}, \bibinfo{author}{Fitzpatrick\xfnm[ N.]},
  \bibinfo{author}{Chen\xfnm[ H.]}, \bibinfo{author}{Alderete\xfnm[ C.H.]},
  \bibinfo{author}{Apel\xfnm[ H.]}, \bibinfo{author}{Cowtan\xfnm[ A.]}, et~al.
\newblock \bibinfo{title}{Dynamical mean field theory algorithm and experiment
  on quantum computers}.
\newblock \bibinfo{year}{2019}.
\newblock \href{http://arxiv.org/abs/1910.04735v2}{\tt arXiv:1910.04735v2}.
%Type = Misc
\bibitem[{Zhu et~al.(2021)Zhu, Nakagawa, Li, Guo and
  Zhang}]{zhuCalculatingGreenFunction2021}
\bibinfo{author}{Zhu\xfnm[ J.]}, \bibinfo{author}{Nakagawa\xfnm[ Y.O.]},
  \bibinfo{author}{Li\xfnm[ C.F.]}, \bibinfo{author}{Guo\xfnm[ G.C.]},
  \bibinfo{author}{Zhang\xfnm[ Y.S.]}.
\newblock \bibinfo{title}{Calculating the green's function of two-site
  fermionic hubbard model in a photonic system}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2104.12361v1}{\tt arXiv:2104.12361v1}.
%Type = Misc
\bibitem[{Jamet et~al.(2021)Jamet, Agarwal, Lupo, Browne, Weber and
  Rungger}]{Jamet2021}
\bibinfo{author}{Jamet\xfnm[ F.]}, \bibinfo{author}{Agarwal\xfnm[ A.]},
  \bibinfo{author}{Lupo\xfnm[ C.]}, \bibinfo{author}{Browne\xfnm[ D.E.]},
  \bibinfo{author}{Weber\xfnm[ C.]}, \bibinfo{author}{Rungger\xfnm[ I.]}.
\newblock \bibinfo{title}{Krylov variational quantum algorithm for first
  principles materials simulations}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2105.13298v2}{\tt arXiv:2105.13298v2}.
%Type = Misc
\bibitem[{Jamet et~al.(2022)Jamet, Agarwal and Rungger}]{Jamet2022}
\bibinfo{author}{Jamet\xfnm[ F.]}, \bibinfo{author}{Agarwal\xfnm[ A.]},
  \bibinfo{author}{Rungger\xfnm[ I.]}.
\newblock \bibinfo{title}{Quantum subspace expansion algorithm for green's
  functions}.
\newblock \bibinfo{year}{2022}.
\newblock \href{http://arxiv.org/abs/2205.00094}{\tt arXiv:2205.00094}.
%Type = Article
\bibitem[{Wecker et~al.(2015{\natexlab{b}})Wecker, Hastings, Wiebe, Clark,
  Nayak and Troyer}]{Wecker2015_Solving}
\bibinfo{author}{Wecker\xfnm[ D.]}, \bibinfo{author}{Hastings\xfnm[ M.B.]},
  \bibinfo{author}{Wiebe\xfnm[ N.]}, \bibinfo{author}{Clark\xfnm[ B.K.]},
  \bibinfo{author}{Nayak\xfnm[ C.]}, \bibinfo{author}{Troyer\xfnm[ M.]}.
\newblock \bibinfo{title}{Solving strongly correlated electron models on a
  quantum computer}.
\newblock \bibinfo{journal}{Phys Rev A}
  \bibinfo{year}{2015}{\natexlab{b}};\bibinfo{volume}{92}(\bibinfo{number}{6}).
\newblock \DOIprefix\doi{10.1103/physreva.92.062318}.
%Type = Article
\bibitem[{Xu et~al.(2021)Xu, Sun, Endo, Li, Benjamin and
  Yuan}]{xuVariationalAlgorithmsLinear2021}
\bibinfo{author}{Xu\xfnm[ X.]}, \bibinfo{author}{Sun\xfnm[ J.]},
  \bibinfo{author}{Endo\xfnm[ S.]}, \bibinfo{author}{Li\xfnm[ Y.]},
  \bibinfo{author}{Benjamin\xfnm[ S.C.]}, \bibinfo{author}{Yuan\xfnm[ X.]}.
\newblock \bibinfo{title}{Variational algorithms for linear algebra}.
\newblock \bibinfo{journal}{Science Bulletin}
  \bibinfo{year}{2021};\bibinfo{volume}{66}(\bibinfo{number}{21}):\bibinfo{pages}{2181--2188}.
\newblock \DOIprefix\doi{10.1016/j.scib.2021.06.023}.
  \href{http://arxiv.org/abs/1909.03898}{\tt arXiv:1909.03898}.
%Type = Article
\bibitem[{Cai et~al.(2020)Cai, Fang, Fan and
  Li}]{caiQuantumComputationMolecular2020}
\bibinfo{author}{Cai\xfnm[ X.]}, \bibinfo{author}{Fang\xfnm[ W.H.]},
  \bibinfo{author}{Fan\xfnm[ H.]}, \bibinfo{author}{Li\xfnm[ Z.]}.
\newblock \bibinfo{title}{Quantum computation of molecular response
  properties}.
\newblock \bibinfo{journal}{Physical Review Research}
  \bibinfo{year}{2020};\bibinfo{volume}{2}(\bibinfo{number}{3}):\bibinfo{pages}{033324}.
\newblock \DOIprefix\doi{10.1103/physrevresearch.2.033324}.
%Type = Article
\bibitem[{Tong et~al.(2021)Tong, An, Wiebe and Lin}]{Tong2021}
\bibinfo{author}{Tong\xfnm[ Y.]}, \bibinfo{author}{An\xfnm[ D.]},
  \bibinfo{author}{Wiebe\xfnm[ N.]}, \bibinfo{author}{Lin\xfnm[ L.]}.
\newblock \bibinfo{title}{Fast inversion, preconditioned quantum linear system
  solvers, fast green{\textquotesingle}s-function computation, and fast
  evaluation of matrix functions}.
\newblock \bibinfo{journal}{Phys Rev A}
  \bibinfo{year}{2021};\bibinfo{volume}{104}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/physreva.104.032422}.
%Type = Article
\bibitem[{Levine et~al.(2021)Levine, Durden, Esch, Liang and Shu}]{Levine2021}
\bibinfo{author}{Levine\xfnm[ B.G.]}, \bibinfo{author}{Durden\xfnm[ A.S.]},
  \bibinfo{author}{Esch\xfnm[ M.P.]}, \bibinfo{author}{Liang\xfnm[ F.]},
  \bibinfo{author}{Shu\xfnm[ Y.]}.
\newblock \bibinfo{title}{{CAS} without {SCF}{\textemdash}why to use {CASCI}
  and where to get the orbitals}.
\newblock \bibinfo{journal}{Journal of Chemical Physics}
  \bibinfo{year}{2021};\bibinfo{volume}{154}(\bibinfo{number}{9}):\bibinfo{pages}{090902}.
\newblock \DOIprefix\doi{10.1063/5.0042147}.
%Type = Article
\bibitem[{Sun et~al.(2017)Sun, Yang and Chan}]{Sun2017}
\bibinfo{author}{Sun\xfnm[ Q.]}, \bibinfo{author}{Yang\xfnm[ J.]},
  \bibinfo{author}{Chan\xfnm[ G.K.L.]}.
\newblock \bibinfo{title}{A general second order complete active space
  self-consistent-field solver for large-scale systems}.
\newblock \bibinfo{journal}{Chemical Physics Letters}
  \bibinfo{year}{2017};\bibinfo{volume}{683}:\bibinfo{pages}{291--299}.
\newblock \DOIprefix\doi{10.1016/j.cplett.2017.03.004}.
%Type = Article
\bibitem[{Ma{\~{n}}eru et~al.(2013)Ma{\~{n}}eru, Pal, de~P.~R.~Moreira, Datta
  and Illas}]{RetaManeru2014}
\bibinfo{author}{Ma{\~{n}}eru\xfnm[ D.R.]}, \bibinfo{author}{Pal\xfnm[ A.K.]},
  \bibinfo{author}{de~P.~R.~Moreira\xfnm[ I.]}, \bibinfo{author}{Datta\xfnm[
  S.N.]}, \bibinfo{author}{Illas\xfnm[ F.]}.
\newblock \bibinfo{title}{The triplet{\textendash}singlet gap in the m-xylylene
  radical: A not so simple one}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2013};\bibinfo{volume}{10}(\bibinfo{number}{1}):\bibinfo{pages}{335--345}.
\newblock \DOIprefix\doi{10.1021/ct400883m}.
%Type = Article
\bibitem[{Li et~al.(2015)Li, Wang, Guo and Zhang}]{Li2015}
\bibinfo{author}{Li\xfnm[ Y.]}, \bibinfo{author}{Wang\xfnm[ L.]},
  \bibinfo{author}{Guo\xfnm[ X.]}, \bibinfo{author}{Zhang\xfnm[ J.]}.
\newblock \bibinfo{title}{A {CASSCF}/{CASPT}2 insight into excited-state
  intramolecular proton transfer of four imidazole derivatives}.
\newblock \bibinfo{journal}{Journal of Computational Chemistry}
  \bibinfo{year}{2015};\bibinfo{volume}{36}(\bibinfo{number}{32}):\bibinfo{pages}{2374--2380}.
\newblock \DOIprefix\doi{10.1002/jcc.24216}.
%Type = Article
\bibitem[{Olsen(2011)}]{olsen11}
\bibinfo{author}{Olsen\xfnm[ J.]}.
\newblock \bibinfo{title}{The {CASSCF} method: A perspective and commentary}.
\newblock \bibinfo{journal}{International Journal of Quantum Chemistry}
  \bibinfo{year}{2011};\bibinfo{volume}{111}(\bibinfo{number}{13}):\bibinfo{pages}{3267--3272}.
\newblock \DOIprefix\doi{10.1002/qua.23107}.
%Type = Article
\bibitem[{Takeshita et~al.(2020)Takeshita, Rubin, Jiang, Lee, Babbush and
  McClean}]{Takeshita2020}
\bibinfo{author}{Takeshita\xfnm[ T.]}, \bibinfo{author}{Rubin\xfnm[ N.C.]},
  \bibinfo{author}{Jiang\xfnm[ Z.]}, \bibinfo{author}{Lee\xfnm[ E.]},
  \bibinfo{author}{Babbush\xfnm[ R.]}, \bibinfo{author}{McClean\xfnm[ J.R.]}.
\newblock \bibinfo{title}{Increasing the representation accuracy of quantum
  simulations of chemistry without extra quantum resources}.
\newblock \bibinfo{journal}{Phys Rev X}
  \bibinfo{year}{2020};\bibinfo{volume}{10}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1103/physrevx.10.011004}.
%Type = Incollection
\bibitem[{Abe et~al.(2008)Abe, Gopakmar, Nakajima and Hirao}]{Abe2008}
\bibinfo{author}{Abe\xfnm[ M.]}, \bibinfo{author}{Gopakmar\xfnm[ G.]},
  \bibinfo{author}{Nakajima\xfnm[ T.]}, \bibinfo{author}{Hirao\xfnm[ K.]}.
\newblock \bibinfo{title}{Relativistic multireference perturbation theory:
  Complete active-space second-order perturbation theory ({CASPT}2) with the
  four-component dirac hamiltonian}.
\newblock In: \bibinfo{booktitle}{Radiation Induced Molecular Phenomena in
  Nucleic Acids}. \bibinfo{publisher}{Springer Netherlands};
  \bibinfo{year}{2008}, p. \bibinfo{pages}{157--177}.
\newblock \DOIprefix\doi{10.1007/978-1-4020-8184-2_6}.
%Type = Article
\bibitem[{Rossmannek et~al.(2021)Rossmannek, Barkoutsos, Ollitrault and
  Tavernelli}]{Rossmannek2021}
\bibinfo{author}{Rossmannek\xfnm[ M.]}, \bibinfo{author}{Barkoutsos\xfnm[
  P.K.]}, \bibinfo{author}{Ollitrault\xfnm[ P.J.]},
  \bibinfo{author}{Tavernelli\xfnm[ I.]}.
\newblock \bibinfo{title}{Quantum {HF}/{DFT}-embedding algorithms for
  electronic structure calculations: Scaling up to complex molecular systems}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2021};\bibinfo{volume}{154}(\bibinfo{number}{11}):\bibinfo{pages}{114105}.
\newblock \DOIprefix\doi{10.1063/5.0029536}.
%Type = Misc
\bibitem[{Schade et~al.(2022)Schade, Bauer, Tamoev, Mazur, Plessl and
  Kühne}]{Schade2022}
\bibinfo{author}{Schade\xfnm[ R.]}, \bibinfo{author}{Bauer\xfnm[ C.]},
  \bibinfo{author}{Tamoev\xfnm[ K.]}, \bibinfo{author}{Mazur\xfnm[ L.]},
  \bibinfo{author}{Plessl\xfnm[ C.]}, \bibinfo{author}{Kühne\xfnm[ T.D.]}.
\newblock \bibinfo{title}{Parallel quantum chemistry on noisy
  intermediate-scale quantum computers}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2202.02417}.
  \DOIprefix\doi{10.48550/ARXIV.2202.02417}.
%Type = Article
\bibitem[{Knizia and Chan(2013)}]{Knizia2013}
\bibinfo{author}{Knizia\xfnm[ G.]}, \bibinfo{author}{Chan\xfnm[ G.K.L.]}.
\newblock \bibinfo{title}{Density matrix embedding: A strong-coupling quantum
  embedding theory}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2013};\bibinfo{volume}{9}(\bibinfo{number}{3}):\bibinfo{pages}{1428--1432}.
\newblock \DOIprefix\doi{10.1021/ct301044e}.
%Type = Article
\bibitem[{Wouters et~al.(2016)Wouters, Jim{\'{e}}nez-Hoyos, Sun and
  Chan}]{Wouters2016}
\bibinfo{author}{Wouters\xfnm[ S.]}, \bibinfo{author}{Jim{\'{e}}nez-Hoyos\xfnm[
  C.A.]}, \bibinfo{author}{Sun\xfnm[ Q.]}, \bibinfo{author}{Chan\xfnm[
  G.K.L.]}.
\newblock \bibinfo{title}{A practical guide to density matrix embedding theory
  in quantum chemistry}.
\newblock \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \bibinfo{year}{2016};\bibinfo{volume}{12}(\bibinfo{number}{6}):\bibinfo{pages}{2706--2719}.
\newblock \DOIprefix\doi{10.1021/acs.jctc.6b00316}.
%Type = Article
\bibitem[{Georges et~al.(1996)Georges, Kotliar, Krauth and
  Rozenberg}]{Georges1996}
\bibinfo{author}{Georges\xfnm[ A.]}, \bibinfo{author}{Kotliar\xfnm[ G.]},
  \bibinfo{author}{Krauth\xfnm[ W.]}, \bibinfo{author}{Rozenberg\xfnm[ M.J.]}.
\newblock \bibinfo{title}{Dynamical mean-field theory of strongly correlated
  fermion systems and the limit of infinite dimensions}.
\newblock \bibinfo{journal}{Rev Mod Phys}
  \bibinfo{year}{1996};\bibinfo{volume}{68}(\bibinfo{number}{1}):\bibinfo{pages}{13--125}.
\newblock \DOIprefix\doi{10.1103/revmodphys.68.13}.
%Type = Misc
\bibitem[{Rubin(2016)}]{Rubin2016}
\bibinfo{author}{Rubin\xfnm[ N.C.]}.
\newblock \bibinfo{title}{A hybrid classical/quantum approach for large-scale
  studies of quantum systems with density matrix embedding theory}.
\newblock \bibinfo{year}{2016}.
\newblock \href{http://arxiv.org/abs/1610.06910v2}{\tt arXiv:1610.06910v2}.
%Type = Misc
\bibitem[{Yamazaki et~al.(2018)Yamazaki, Matsuura, Narimani, Saidmuradov and
  Zaribafiyan}]{Yamazaki2018}
\bibinfo{author}{Yamazaki\xfnm[ T.]}, \bibinfo{author}{Matsuura\xfnm[ S.]},
  \bibinfo{author}{Narimani\xfnm[ A.]}, \bibinfo{author}{Saidmuradov\xfnm[
  A.]}, \bibinfo{author}{Zaribafiyan\xfnm[ A.]}.
\newblock \bibinfo{title}{Towards the practical application of near-term
  quantum computers in quantum chemistry simulations: A problem decomposition
  approach}.
\newblock \bibinfo{year}{2018}.
\newblock \href{http://arxiv.org/abs/1806.01305v1}{\tt arXiv:1806.01305v1}.
%Type = Article
\bibitem[{Ma et~al.(2020)Ma, Govoni and Galli}]{Ma2020}
\bibinfo{author}{Ma\xfnm[ H.]}, \bibinfo{author}{Govoni\xfnm[ M.]},
  \bibinfo{author}{Galli\xfnm[ G.]}.
\newblock \bibinfo{title}{Quantum simulations of materials on near-term quantum
  computers}.
\newblock \bibinfo{journal}{npj Computational Materials}
  \bibinfo{year}{2020};\bibinfo{volume}{6}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1038/s41524-020-00353-z}.
%Type = Article
\bibitem[{Mineh and Montanaro(2022)}]{Mineh2021}
\bibinfo{author}{Mineh\xfnm[ L.]}, \bibinfo{author}{Montanaro\xfnm[ A.]}.
\newblock \bibinfo{title}{Solving the hubbard model using density matrix
  embedding theory and the variational quantum eigensolver}.
\newblock \bibinfo{journal}{Physical Review B}
  \bibinfo{year}{2022};\bibinfo{volume}{105}(\bibinfo{number}{12}).
\newblock \URLprefix \url{https://doi.org/10.1103/physrevb.105.125117}.
  \DOIprefix\doi{10.1103/physrevb.105.125117}.
%Type = Misc
\bibitem[{Li et~al.(2021)Li, Huang, Cao, Huang, Shuai, Sun et~al.}]{Li2021}
\bibinfo{author}{Li\xfnm[ W.]}, \bibinfo{author}{Huang\xfnm[ Z.]},
  \bibinfo{author}{Cao\xfnm[ C.]}, \bibinfo{author}{Huang\xfnm[ Y.]},
  \bibinfo{author}{Shuai\xfnm[ Z.]}, \bibinfo{author}{Sun\xfnm[ X.]}, et~al.
\newblock \bibinfo{title}{Toward practical quantum embedding simulation of
  realistic chemical systems on near-term quantum computers}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2109.08062v1}{\tt arXiv:2109.08062v1}.
%Type = Article
\bibitem[{Fertitta and Booth(2018)}]{Fertitta2018}
\bibinfo{author}{Fertitta\xfnm[ E.]}, \bibinfo{author}{Booth\xfnm[ G.H.]}.
\newblock \bibinfo{title}{Rigorous wave function embedding with dynamical
  fluctuations}.
\newblock \bibinfo{journal}{Physical Review B}
  \bibinfo{year}{2018};\bibinfo{volume}{98}(\bibinfo{number}{23}).
\newblock \DOIprefix\doi{10.1103/physrevb.98.235132}.
%Type = Article
\bibitem[{Fertitta and Booth(2019)}]{Fertitta2019}
\bibinfo{author}{Fertitta\xfnm[ E.]}, \bibinfo{author}{Booth\xfnm[ G.H.]}.
\newblock \bibinfo{title}{Energy-weighted density matrix embedding of open
  correlated chemical fragments}.
\newblock \bibinfo{journal}{The Journal of Chemical Physics}
  \bibinfo{year}{2019};\bibinfo{volume}{151}(\bibinfo{number}{1}):\bibinfo{pages}{014115}.
\newblock \DOIprefix\doi{10.1063/1.5100290}.
%Type = Article
\bibitem[{Sriluckshmy et~al.(2021)Sriluckshmy, Nusspickel, Fertitta and
  Booth}]{Sriluckshmy2021}
\bibinfo{author}{Sriluckshmy\xfnm[ P.V.]}, \bibinfo{author}{Nusspickel\xfnm[
  M.]}, \bibinfo{author}{Fertitta\xfnm[ E.]}, \bibinfo{author}{Booth\xfnm[
  G.H.]}.
\newblock \bibinfo{title}{Fully algebraic and self-consistent effective
  dynamics in a static quantum embedding}.
\newblock \bibinfo{journal}{Physical Review B}
  \bibinfo{year}{2021};\bibinfo{volume}{103}(\bibinfo{number}{8}).
\newblock \DOIprefix\doi{10.1103/physrevb.103.085131}.
%Type = Article
\bibitem[{Kreula et~al.(2016)Kreula, Garc{\'{\i}}a-{\'{A}}lvarez, Lamata,
  Clark, Solano and Jaksch}]{Kreula2016}
\bibinfo{author}{Kreula\xfnm[ J.M.]},
  \bibinfo{author}{Garc{\'{\i}}a-{\'{A}}lvarez\xfnm[ L.]},
  \bibinfo{author}{Lamata\xfnm[ L.]}, \bibinfo{author}{Clark\xfnm[ S.R.]},
  \bibinfo{author}{Solano\xfnm[ E.]}, \bibinfo{author}{Jaksch\xfnm[ D.]}.
\newblock \bibinfo{title}{Few-qubit quantum-classical simulation of strongly
  correlated lattice fermions}.
\newblock \bibinfo{journal}{EPJ Quantum Technol}
  \bibinfo{year}{2016};\bibinfo{volume}{3}(\bibinfo{number}{1}).
\newblock \DOIprefix\doi{10.1140/epjqt/s40507-016-0049-1}.
%Type = Article
\bibitem[{Wei et~al.(2020)Wei, Li and Long}]{Wei2020}
\bibinfo{author}{Wei\xfnm[ S.]}, \bibinfo{author}{Li\xfnm[ H.]},
  \bibinfo{author}{Long\xfnm[ G.]}.
\newblock \bibinfo{title}{A full quantum eigensolver for quantum chemistry
  simulations}.
\newblock \bibinfo{journal}{Research}
  \bibinfo{year}{2020};\bibinfo{volume}{2020}:\bibinfo{pages}{1--11}.
\newblock \DOIprefix\doi{10.34133/2020/1486935}.
%Type = Article
\bibitem[{Stair and Evangelista(2021)}]{Stair2021}
\bibinfo{author}{Stair\xfnm[ N.H.]}, \bibinfo{author}{Evangelista\xfnm[ F.A.]}.
\newblock \bibinfo{title}{Simulating many-body systems with a projective
  quantum eigensolver}.
\newblock \bibinfo{journal}{PRX Quantum}
  \bibinfo{year}{2021};\bibinfo{volume}{2}(\bibinfo{number}{3}).
\newblock \DOIprefix\doi{10.1103/prxquantum.2.030301}.
%Type = Misc
\bibitem[{Bharti and Haug(2020{\natexlab{a}})}]{Bharti2020}
\bibinfo{author}{Bharti\xfnm[ K.]}, \bibinfo{author}{Haug\xfnm[ T.]}.
\newblock \bibinfo{title}{Quantum assisted simulator}.
\newblock \bibinfo{year}{2020}{\natexlab{a}}.
\newblock \href{http://arxiv.org/abs/2011.06911v1}{\tt arXiv:2011.06911v1}.
%Type = Article
\bibitem[{Haug and Bharti(2022)}]{Haug2020}
\bibinfo{author}{Haug\xfnm[ T.]}, \bibinfo{author}{Bharti\xfnm[ K.]}.
\newblock \bibinfo{title}{Generalized quantum assisted simulator}.
\newblock \bibinfo{journal}{Quantum Science and Technology}
  \bibinfo{year}{2022};\bibinfo{volume}{7}(\bibinfo{number}{4}):\bibinfo{pages}{045019}.
\newblock \URLprefix \url{https://doi.org/10.1088/2058-9565/ac83e7}.
  \DOIprefix\doi{10.1088/2058-9565/ac83e7}.
%Type = Misc
\bibitem[{Bharti and Haug(2020{\natexlab{b}})}]{Bharti2020_IQAE}
\bibinfo{author}{Bharti\xfnm[ K.]}, \bibinfo{author}{Haug\xfnm[ T.]}.
\newblock \bibinfo{title}{Iterative quantum assisted eigensolver}.
\newblock \bibinfo{year}{2020}{\natexlab{b}}.
\newblock \href{http://arxiv.org/abs/2010.05638v1}{\tt arXiv:2010.05638v1}.
%Type = Misc
\bibitem[{Rivero et~al.(2020)Rivero, Cloët and Sullivan}]{Rivero2020}
\bibinfo{author}{Rivero\xfnm[ P.]}, \bibinfo{author}{Cloët\xfnm[ I.C.]},
  \bibinfo{author}{Sullivan\xfnm[ Z.]}.
\newblock \bibinfo{title}{An optimal quantum sampling regression algorithm for
  variational eigensolving in the low qubit number regime}.
\newblock \bibinfo{year}{2020}.
\newblock \href{http://arxiv.org/abs/2012.02338}{\tt arXiv:2012.02338}.
%Type = Misc
\bibitem[{Cerezo et~al.(2020)Cerezo, Sharma, Arrasmith and
  Coles}]{Cerezo2020_VQSE}
\bibinfo{author}{Cerezo\xfnm[ M.]}, \bibinfo{author}{Sharma\xfnm[ K.]},
  \bibinfo{author}{Arrasmith\xfnm[ A.]}, \bibinfo{author}{Coles\xfnm[ P.J.]}.
\newblock \bibinfo{title}{Variational quantum state eigensolver}.
\newblock \bibinfo{year}{2020}.
\newblock \href{http://arxiv.org/abs/2004.01372v1}{\tt arXiv:2004.01372v1}.
%Type = Article
\bibitem[{Tkachenko et~al.(2021)Tkachenko, Sud, Zhang, Tretiak, Anisimov,
  Arrasmith et~al.}]{Tkachenko2021}
\bibinfo{author}{Tkachenko\xfnm[ N.V.]}, \bibinfo{author}{Sud\xfnm[ J.]},
  \bibinfo{author}{Zhang\xfnm[ Y.]}, \bibinfo{author}{Tretiak\xfnm[ S.]},
  \bibinfo{author}{Anisimov\xfnm[ P.M.]}, \bibinfo{author}{Arrasmith\xfnm[
  A.T.]}, et~al.
\newblock \bibinfo{title}{Correlation-informed permutation of qubits for
  reducing ansatz depth in the variational quantum eigensolver}.
\newblock \bibinfo{journal}{PRX Quantum}
  \bibinfo{year}{2021};\bibinfo{volume}{2}(\bibinfo{number}{2}).
\newblock \DOIprefix\doi{10.1103/prxquantum.2.020337}.
%Type = Article
\bibitem[{Amaro et~al.(2022)Amaro, Modica, Rosenkranz, Fiorentini, Benedetti
  and Lubasch}]{Amaro2022}
\bibinfo{author}{Amaro\xfnm[ D.]}, \bibinfo{author}{Modica\xfnm[ C.]},
  \bibinfo{author}{Rosenkranz\xfnm[ M.]}, \bibinfo{author}{Fiorentini\xfnm[
  M.]}, \bibinfo{author}{Benedetti\xfnm[ M.]}, \bibinfo{author}{Lubasch\xfnm[
  M.]}.
\newblock \bibinfo{title}{Filtering variational quantum algorithms for
  combinatorial optimization}.
\newblock \bibinfo{journal}{Quantum Science and Technology}
  \bibinfo{year}{2022};\bibinfo{volume}{7}(\bibinfo{number}{1}):\bibinfo{pages}{015021}.
\newblock \URLprefix \url{https://doi.org/10.1088/2058-9565/ac3e54}.
  \DOIprefix\doi{10.1088/2058-9565/ac3e54}.
%Type = Article
\bibitem[{Kochenberger et~al.(2014)Kochenberger, Hao, Glover, Lewis, L\"{u},
  Wang et~al.}]{Kochenberger2014}
\bibinfo{author}{Kochenberger\xfnm[ G.]}, \bibinfo{author}{Hao\xfnm[ J.K.]},
  \bibinfo{author}{Glover\xfnm[ F.]}, \bibinfo{author}{Lewis\xfnm[ M.]},
  \bibinfo{author}{L\"{u}\xfnm[ Z.]}, \bibinfo{author}{Wang\xfnm[ H.]}, et~al.
\newblock \bibinfo{title}{The unconstrained binary quadratic programming
  problem: a survey}.
\newblock \bibinfo{journal}{Journal of Combinatorial Optimization}
  \bibinfo{year}{2014};\bibinfo{volume}{28}(\bibinfo{number}{1}):\bibinfo{pages}{58--81}.
\newblock \URLprefix \url{https://doi.org/10.1007/s10878-014-9734-0}.
  \DOIprefix\doi{10.1007/s10878-014-9734-0}.
%Type = Misc
\bibitem[{Fujii et~al.(2020)Fujii, Mizuta, Ueda, Mitarai, Mizukami and
  Nakagawa}]{Fujii2020}
\bibinfo{author}{Fujii\xfnm[ K.]}, \bibinfo{author}{Mizuta\xfnm[ K.]},
  \bibinfo{author}{Ueda\xfnm[ H.]}, \bibinfo{author}{Mitarai\xfnm[ K.]},
  \bibinfo{author}{Mizukami\xfnm[ W.]}, \bibinfo{author}{Nakagawa\xfnm[ Y.O.]}.
\newblock \bibinfo{title}{Deep variational quantum eigensolver: a
  divide-and-conquer method for solving a larger problem with smaller size
  quantum computers}.
\newblock \bibinfo{year}{2020}.
\newblock \URLprefix \url{https://arxiv.org/abs/2007.10917}.
  \DOIprefix\doi{10.48550/ARXIV.2007.10917}.
%Type = Article
\bibitem[{Mizuta et~al.(2021)Mizuta, Fujii, Fujii, Ichikawa, Imamura, Okuno
  et~al.}]{Mizuta2021}
\bibinfo{author}{Mizuta\xfnm[ K.]}, \bibinfo{author}{Fujii\xfnm[ M.]},
  \bibinfo{author}{Fujii\xfnm[ S.]}, \bibinfo{author}{Ichikawa\xfnm[ K.]},
  \bibinfo{author}{Imamura\xfnm[ Y.]}, \bibinfo{author}{Okuno\xfnm[ Y.]},
  et~al.
\newblock \bibinfo{title}{Deep variational quantum eigensolver for excited
  states and its application to quantum chemistry calculation of periodic
  materials}.
\newblock \bibinfo{journal}{Physical Review Research}
  \bibinfo{year}{2021};\bibinfo{volume}{3}(\bibinfo{number}{4}).
\newblock \URLprefix \url{https://doi.org/10.1103/physrevresearch.3.043121}.
  \DOIprefix\doi{10.1103/physrevresearch.3.043121}.
%Type = Article
\bibitem[{Meitei et~al.(2021)Meitei, Gard, Barron, Pappas, Economou, Barnes
  et~al.}]{Meitei2021}
\bibinfo{author}{Meitei\xfnm[ O.R.]}, \bibinfo{author}{Gard\xfnm[ B.T.]},
  \bibinfo{author}{Barron\xfnm[ G.S.]}, \bibinfo{author}{Pappas\xfnm[ D.P.]},
  \bibinfo{author}{Economou\xfnm[ S.E.]}, \bibinfo{author}{Barnes\xfnm[ E.]},
  et~al.
\newblock \bibinfo{title}{Gate-free state preparation for fast variational
  quantum eigensolver simulations}.
\newblock \bibinfo{journal}{npj Quantum Information}
  \bibinfo{year}{2021};\bibinfo{volume}{7}(\bibinfo{number}{1}).
\newblock \URLprefix \url{https://doi.org/10.1038/s41534-021-00493-0}.
  \DOIprefix\doi{10.1038/s41534-021-00493-0}.
%Type = Misc
\bibitem[{Asthana et~al.(2022)Asthana, Liu, Meitei, Economou, Barnes and
  Mayhall}]{Asthana2022}
\bibinfo{author}{Asthana\xfnm[ A.]}, \bibinfo{author}{Liu\xfnm[ C.]},
  \bibinfo{author}{Meitei\xfnm[ O.R.]}, \bibinfo{author}{Economou\xfnm[ S.E.]},
  \bibinfo{author}{Barnes\xfnm[ E.]}, \bibinfo{author}{Mayhall\xfnm[ N.J.]}.
\newblock \bibinfo{title}{Minimizing state preparation times in pulse-level
  variational molecular simulations}.
\newblock \bibinfo{year}{2022}.
\newblock \URLprefix \url{https://arxiv.org/abs/2203.06818}.
  \DOIprefix\doi{10.48550/ARXIV.2203.06818}.
%Type = Article
\bibitem[{Yuan et~al.(2019{\natexlab{b}})Yuan, Endo, Zhao, Li and
  Benjamin}]{Yuan2019}
\bibinfo{author}{Yuan\xfnm[ X.]}, \bibinfo{author}{Endo\xfnm[ S.]},
  \bibinfo{author}{Zhao\xfnm[ Q.]}, \bibinfo{author}{Li\xfnm[ Y.]},
  \bibinfo{author}{Benjamin\xfnm[ S.C.]}.
\newblock \bibinfo{title}{Theory of variational quantum simulation}.
\newblock \bibinfo{journal}{Quantum}
  \bibinfo{year}{2019}{\natexlab{b}};\bibinfo{volume}{3}:\bibinfo{pages}{191}.
\newblock \URLprefix \url{https://doi.org/10.22331/q-2019-10-07-191}.
  \DOIprefix\doi{10.22331/q-2019-10-07-191}.
%Type = Article
\bibitem[{Gustafson et~al.(2021)Gustafson, Dreher, Hang and
  Meurice}]{Gustafson2021}
\bibinfo{author}{Gustafson\xfnm[ E.]}, \bibinfo{author}{Dreher\xfnm[ P.]},
  \bibinfo{author}{Hang\xfnm[ Z.]}, \bibinfo{author}{Meurice\xfnm[ Y.]}.
\newblock \bibinfo{title}{Indexed improvements for real-time trotter evolution
  of a (1 + 1) field theory using {NISQ} quantum computers}.
\newblock \bibinfo{journal}{Quantum Science and Technology}
  \bibinfo{year}{2021};\bibinfo{volume}{6}(\bibinfo{number}{4}):\bibinfo{pages}{045020}.
\newblock \URLprefix \url{https://doi.org/10.1088/2058-9565/ac1dff}.
  \DOIprefix\doi{10.1088/2058-9565/ac1dff}.
%Type = Article
\bibitem[{Lin et~al.(2021)Lin, Dilip, Green, Smith and Pollmann}]{Lin2021}
\bibinfo{author}{Lin\xfnm[ S.H.]}, \bibinfo{author}{Dilip\xfnm[ R.]},
  \bibinfo{author}{Green\xfnm[ A.G.]}, \bibinfo{author}{Smith\xfnm[ A.]},
  \bibinfo{author}{Pollmann\xfnm[ F.]}.
\newblock \bibinfo{title}{Real- and imaginary-time evolution with compressed
  quantum circuits}.
\newblock \bibinfo{journal}{{PRX} Quantum}
  \bibinfo{year}{2021};\bibinfo{volume}{2}(\bibinfo{number}{1}).
\newblock \URLprefix \url{https://doi.org/10.1103/prxquantum.2.010342}.
  \DOIprefix\doi{10.1103/prxquantum.2.010342}.
%Type = Misc
\bibitem[{Mansuroglu et~al.(2021)Mansuroglu, Eckstein, Nützel, Wilkinson and
  Hartmann}]{Mansuroglu2021}
\bibinfo{author}{Mansuroglu\xfnm[ R.]}, \bibinfo{author}{Eckstein\xfnm[ T.]},
  \bibinfo{author}{Nützel\xfnm[ L.]}, \bibinfo{author}{Wilkinson\xfnm[ S.A.]},
  \bibinfo{author}{Hartmann\xfnm[ M.J.]}.
\newblock \bibinfo{title}{Variational hamiltonian simulation for translational
  invariant systems via classical pre-processing}.
\newblock \bibinfo{year}{2021}.
\newblock \URLprefix \url{https://arxiv.org/abs/2106.03680}.
  \DOIprefix\doi{10.48550/ARXIV.2106.03680}.
%Type = Article
\bibitem[{Nishi et~al.(2021)Nishi, Kosugi and ichiro Matsushita}]{Nishi2021}
\bibinfo{author}{Nishi\xfnm[ H.]}, \bibinfo{author}{Kosugi\xfnm[ T.]},
  \bibinfo{author}{ichiro Matsushita\xfnm[ Y.]}.
\newblock \bibinfo{title}{Implementation of quantum imaginary-time evolution
  method on {NISQ} devices by introducing nonlocal approximation}.
\newblock \bibinfo{journal}{npj Quantum Information}
  \bibinfo{year}{2021};\bibinfo{volume}{7}(\bibinfo{number}{1}).
\newblock \URLprefix \url{https://doi.org/10.1038/s41534-021-00409-y}.
  \DOIprefix\doi{10.1038/s41534-021-00409-y}.
%Type = Article
\bibitem[{Benedetti et~al.(2021)Benedetti, Fiorentini and
  Lubasch}]{Benedetti2021}
\bibinfo{author}{Benedetti\xfnm[ M.]}, \bibinfo{author}{Fiorentini\xfnm[ M.]},
  \bibinfo{author}{Lubasch\xfnm[ M.]}.
\newblock \bibinfo{title}{Hardware-efficient variational quantum algorithms for
  time evolution}.
\newblock \bibinfo{journal}{Physical Review Research}
  \bibinfo{year}{2021};\bibinfo{volume}{3}(\bibinfo{number}{3}).
\newblock \URLprefix \url{https://doi.org/10.1103/physrevresearch.3.033083}.
  \DOIprefix\doi{10.1103/physrevresearch.3.033083}.
%Type = Article
\bibitem[{Gomes et~al.(2021)Gomes, Mukherjee, Zhang, Iadecola, Wang, Ho
  et~al.}]{Gomes2021}
\bibinfo{author}{Gomes\xfnm[ N.]}, \bibinfo{author}{Mukherjee\xfnm[ A.]},
  \bibinfo{author}{Zhang\xfnm[ F.]}, \bibinfo{author}{Iadecola\xfnm[ T.]},
  \bibinfo{author}{Wang\xfnm[ C.Z.]}, \bibinfo{author}{Ho\xfnm[ K.M.]}, et~al.
\newblock \bibinfo{title}{Adaptive variational quantum imaginary time evolution
  approach for ground state preparation}.
\newblock \bibinfo{journal}{Advanced Quantum Technologies}
  \bibinfo{year}{2021};\bibinfo{volume}{4}(\bibinfo{number}{12}):\bibinfo{pages}{2100114}.
\newblock \URLprefix \url{https://doi.org/10.1002/qute.202100114}.
  \DOIprefix\doi{10.1002/qute.202100114}.
%Type = Misc
\bibitem[{Merrill and Brown(2012)}]{merrillProgressCompensatingPulse2012}
\bibinfo{author}{Merrill\xfnm[ J.T.]}, \bibinfo{author}{Brown\xfnm[ K.R.]}.
\newblock \bibinfo{title}{Progress in compensating pulse sequences for quantum
  computation}.
\newblock \bibinfo{year}{2012}.
\newblock \href{http://arxiv.org/abs/1203.6392v1}{\tt arXiv:1203.6392v1}.
%Type = Misc
\bibitem[{Bultrini et~al.(2020)Bultrini, Gordon, López and
  Sierra}]{bultriniSimpleMitigationStrategy2020}
\bibinfo{author}{Bultrini\xfnm[ D.]}, \bibinfo{author}{Gordon\xfnm[ M.H.]},
  \bibinfo{author}{López\xfnm[ E.]}, \bibinfo{author}{Sierra\xfnm[ G.]}.
\newblock \bibinfo{title}{Simple mitigation strategy for a systematic gate
  error in ibmq}.
\newblock \bibinfo{year}{2020}.
\newblock \href{http://arxiv.org/abs/2012.00831v3}{\tt arXiv:2012.00831v3}.
%Type = Misc
\bibitem[{Czarnik et~al.(2021)Czarnik, Arrasmith, Cincio and
  Coles}]{czarnikQubitefficientExponentialSuppression2021}
\bibinfo{author}{Czarnik\xfnm[ P.]}, \bibinfo{author}{Arrasmith\xfnm[ A.]},
  \bibinfo{author}{Cincio\xfnm[ L.]}, \bibinfo{author}{Coles\xfnm[ P.J.]}.
\newblock \bibinfo{title}{Qubit-efficient exponential suppression of errors}.
\newblock \bibinfo{year}{2021}.
\newblock \href{http://arxiv.org/abs/2102.06056v2}{\tt arXiv:2102.06056v2}.
%Type = Misc
\bibitem[{Seif et~al.(2022)Seif, Cian, Zhou, Chen and
  Jiang}]{Seif2022ShadowDistillation}
\bibinfo{author}{Seif\xfnm[ A.]}, \bibinfo{author}{Cian\xfnm[ Z.P.]},
  \bibinfo{author}{Zhou\xfnm[ S.]}, \bibinfo{author}{Chen\xfnm[ S.]},
  \bibinfo{author}{Jiang\xfnm[ L.]}.
\newblock \bibinfo{title}{Shadow distillation: Quantum error mitigation with
  classical shadows for near-term quantum processors}.
\newblock \bibinfo{year}{2022}.
\newblock \href{http://arxiv.org/abs/2203.07309}{\tt arXiv:2203.07309}.
%Type = Misc
\bibitem[{Hu et~al.(2022)Hu, LaRose, You, Rieffel and
  Wang}]{Hu2022LogicalShadowTomography}
\bibinfo{author}{Hu\xfnm[ H.Y.]}, \bibinfo{author}{LaRose\xfnm[ R.]},
  \bibinfo{author}{You\xfnm[ Y.Z.]}, \bibinfo{author}{Rieffel\xfnm[ E.]},
  \bibinfo{author}{Wang\xfnm[ Z.]}.
\newblock \bibinfo{title}{Logical shadow tomography: Efficient estimation of
  error-mitigated observables}.
\newblock \bibinfo{year}{2022}.
\newblock \href{http://arxiv.org/abs/2203.07263}{\tt arXiv:2203.07263}.

\end{thebibliography}


\end{document}